### 2024-10-20 paper/paper.qmd
update with appendix

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

# Appendix
## Emerson College Polling Methodology
For this deep dive, I'll focus on Emerson College Polling based on the link: Emerson College Polling - October 2024 National Poll.
Survey Overview:
The Emerson College Polling conducted a national survey in October 2024 to assess voter preferences for the upcoming U.S. presidential election. This appendix provides an in-depth analysis of their polling methodology, including the population, sample frame, recruitment process, and key strengths and weaknesses of their approach.

Methodology
1. Population, Frame, and Sample:\
Target Population: The target population for this poll includes U.S. citizens who are eligible to vote in the 2024 presidential election.
Sample Frame: The sample consists of likely voters across the United States. Emerson College Polling uses voter registration databases to develop a sampling frame of registered voters, ensuring they capture individuals who are most likely to vote in the upcoming election.
Sample Size: For this particular poll, 1,000 likely voters were surveyed. This sample size provides a margin of error of approximately ±3 percentage points, allowing for reasonable confidence in the poll's accuracy.

2. Sample Recruitment:\
Recruitment Method: Emerson College employs a multi-mode recruitment approach, including online, phone (landline and mobile), and SMS text outreach.
Phone Interviews: Live interviewers call both landlines and mobile phones using random digit dialing (RDD) to ensure they capture respondents without internet access.
Online Panels: Emerson also recruits respondents through online panels, using email invitations to individuals who match their demographic quotas.
SMS Text Polling: In recent years, Emerson has increasingly used SMS text polling, allowing respondents to complete the survey via mobile devices.

Trade-offs of Recruitment Method:\
Strengths: The multi-mode approach ensures better coverage of different demographic groups, including older adults and those less likely to engage with online surveys.
Weaknesses: The RDD approach can lead to lower response rates, especially with the increasing number of people avoiding unsolicited calls. The online component also introduces self-selection bias, where more politically engaged individuals may be overrepresented.

3. Sampling Approach and Trade-offs:\
Quota-based Sampling: Emerson uses quota sampling to ensure that the sample is representative of key demographics, including age, gender, race, and region. The quotas are based on U.S. Census data to maintain demographic diversity.
Weighting: After data collection, Emerson applies post-stratification weighting to adjust for any imbalances in the sample, aligning it with population benchmarks.
Trade-offs: While quota sampling ensures demographic diversity, it can introduce bias if certain groups are harder to reach or more likely to refuse participation (non-response bias). Weighting helps mitigate this issue but relies on accurate population benchmarks, which may not always reflect the electorate’s behavior accurately.

4. Non-response Handling:\
Non-response Bias: To minimize non-response bias, Emerson College Polling uses a combination of call-backs and reminder emails for online respondents. Additionally, post-survey weighting accounts for non-response patterns across key demographic groups.
Adjustments for Non-response: Emerson uses statistical weighting to adjust the final results based on the response rate within each demographic group (e.g., age, gender, and race). This helps to reduce the skew in the data caused by differential response rates.

5. Questionnaire Design:\
Strengths:
The survey is concise, focusing on core topics like voter intention, candidate preference, and key issues such as the economy and healthcare. This increases the likelihood that respondents complete the survey accurately and without fatigue.
Emerson regularly tests its questionnaire to ensure clarity and avoid ambiguous questions, improving the reliability of the responses.
Weaknesses:
Binary Choice Bias: Some sections of the questionnaire force a binary choice between two candidates, which may oversimplify the respondents' true preferences, especially in a race with multiple candidates or undecided voters.
Social Desirability Bias: Like most political polls, respondents may answer questions in a way they believe is socially acceptable, especially in terms of voter turnout or support for controversial candidates. This could lead to over-reporting of voter intention.
Summary of Strengths and Weaknesses
Strengths:

Multi-mode Surveying: Emerson’s use of phone, online, and SMS recruitment allows them to reach a broader cross-section of the population, minimizing the biases introduced by any one method.
Post-stratification Weighting: The weighting process ensures the sample reflects the U.S. population, improving the reliability of the poll results.
Timely Polling: The frequent release of polling data makes it possible to track shifts in voter sentiment over time.
Weaknesses:

Potential for Non-response Bias: Despite efforts to mitigate it, non-response remains a concern, particularly among certain voter demographics who may be harder to reach through phone or online surveys.
Self-selection Bias in Online Surveys: The online component may disproportionately attract respondents who are more politically engaged, which could skew results.
By employing a multi-mode approach and adjusting for demographic imbalances through weighting, Emerson College Polling provides robust and timely data. However, like all polls, it is subject to limitations, particularly around non-response and self-selection biases​
\newpage

# References

### 2024-10-21 paper/paper.qmd
Update paper.qmd

@@
 
-Overview paragraph
+Forecasting election outcomes has become a critical endeavor in political science and public policy, as it not only informs campaigns and media coverage but also shapes voter perceptions.
+The ability to accurately predict the winner of a presidential election holds significant implications for political strategy, governance, and public trust in polling methodologies.
+In this context, leveraging aggregated polling data, or “poll-of-polls,” offers a more comprehensive and reliable prediction model, as it aims to reduce the biases and errors associated with individual polls (Blumenthal 2014; Pasek 2015).
 
-Estimand paragraph
+This paper aims to explore the predictive power of a linear or generalized linear model using a poll-of-polls approach to forecast the winner of the upcoming US presidential election.
+The motivation behind this research stems from the persistent challenge of balancing sample biases, framing, and non-response rates, which can all impact the reliability of a single poll.
+By aggregating data from multiple polls, the goal is to create a robust and reproducible model that accounts for these discrepancies and better reflects voter sentiment.
 
-Results paragraph
+To achieve this, the study focuses on a deep-dive analysis of a specific pollster, examining their methodology in detail.
+This analysis includes understanding the population, sampling frame, and recruitment process, as well as evaluating the strengths and limitations of their questionnaire design.
+Additionally, the paper proposes an idealized survey and methodology, imagining a scenario with a $100K budget to forecast the election outcome.
+This hypothetical scenario explores alternative approaches to survey design, data collection, and aggregation techniques.
 
-Why it matters paragraph
+This study is significant because it not only aims to build an effective model for election forecasting but also provides critical insights into the methodologies of polling organizations.
+The findings of this research can contribute to a more nuanced understanding of how polling data is collected and interpreted, ultimately improving the accuracy of election predictions.
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+The structure of the paper is as follows: first, the methodology for the forecasting model is presented; second, a detailed analysis of the chosen pollster is included in an appendix, followed by the idealized survey design and methodology.
+Together, these elements provide a comprehensive understanding of the challenges and opportunities in election forecasting using aggregated polling data.
 

### 2024-10-22 paper/paper.qmd
Update paper.qmd

--- 2024-10-20 paper/paper.qmd
@@
 
-Overview paragraph
+Election forecasting has long played a crucial role in understanding public opinion and predicting the outcome of political contests.
+The use of data-driven methods, particularly polling data, has become an important pre-election analytical tool for political analysts.
+The purpose of this paper is to predict the winner of the upcoming 2024 U.S.
+presidential election by constructing a statistical model based on aggregated polling data.
+The “polling” approach combines results from different pollsters to provide a more comprehensive picture of voter preferences (Blumenthal 2014; Pasek 2015), and our goal is to predict the outcome of the popular vote and the Electoral College.
+Our analysis, based on data collected from multiple polling sources, captures voter intentions for the two major candidates, Kamala Harris (Democrat) and Donald Trump (Republican).
 
-Estimand paragraph
+In addition to constructing and interpreting predictive models, this paper dive into the methods used by xx pollsters, analyzing the strengths as well as the weaknesses of the methods used against them.
+At the end of the paper, we also propose an idealized survey methodology for election forecasting with a budget of $100,000 USD.
 
-Results paragraph
-
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+This paper begins with an introduction to data in Section 2.
+In this section, we focus on measurement techniques and the visualization and analysis of key variables.
+Next, in Section 3, we provide an overview of the linear model used to analyze the relationships within the dataset.
+The results of the analysis are detailed in Section 4 (Results).
+Finally, in Section 5, we summarize our main conclusions as well as suggest some possible future research directions.
 
@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
-
-Overview text
+The data for this paper was sourced from ABC News (xxxxx).
+The statistical software R (R Core Team, 2023) was employed to retrieve, clean, and process the dataset.
+Specifically, the tidyverse package (Wickham et al., 2019) was used for data acquisition, cleaning, and processing.
+The ggplot2 (Wickham, 2016) package was utilized to generate the visualizations.
 
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+The data used to predict the outcome of the 2024 U.S.
+presidential election in this study came from a variety of polling sources.
+The results of these polls represent key measures of electoral support and voter sentiment, and are therefore the main variables in our analysis.
+
+To ensure that polling data accurately reflect real-world voter preferences, we rely on several key measurement constructs.
+First, voter preferences are measured by the percentage of respondents who indicated support for each candidate.
+Each poll is conducted using different sample sizes, sampling methods (e.g., online surveys, IVR calls, etc.), which can inject more variability into the data.
+To mitigate these differences, we aggregate poll results using a “”poll of polls“” methodology that eliminates anomalies and provides a more comprehensive picture of voter preferences (Blumenthal 2014; Pasek 2015).
+
+In this study, we recognize the measurement problems inherent in polling data.
+Polls rely on sample data to represent the entire voting population, and therefore, there may be potential biases in the data.
+For example, there may be no-response bias due to the potential under representation of certain populations, or because of the wording of the questions and thus the influence of respondents to report their preferences.
+Therefore, in this study, we chose to analyze aggregated data from multiple pollsters and adjust for sampling variability and response rates in an effort to be able to provide a more robust measure of electoral support.
+We believe that our aggregated dataset can serve as a reliable basis for our predictive model to help us translate the data into quantitative metrics that can be used to predict election outcomes.
 

### 2024-10-22 paper/paper.qmd
Update paper.qmd

@@
 
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+We performed multi-level regression with post-stratification (MRP) to predict support for Kamala Harris in the upcoming election.
+To perform MRP, we fit a logistic regression model to predict support for Harris using sex, age, race, race_hispanic, highest level of education, state, and urban as predictors on our survey data set [@americaspoliticalpulse], and post-stratified it using ACS census data [@citeIPUMS].
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+We built our Bayesian logistic regression model using the `stan_glm()` function of the `rstanarm` package [@rstanarm]. The model that we use is:
 
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+vote\_harris_i|\pi_i &\sim \text{Bernoulli}(\pi_i) \\
+\text{logit}(\pi_i) &= \beta_0 + \beta_1 \text{sex}_i + \beta_2  \text{age\_bracket}_i + \beta_3 \text{race}_i + \beta_4 \text{race\_hispanic}_i + \beta_5 \text{education\_level}_i + \beta_6 \text{urban}_i \\
+\beta_0 &\sim \text{Normal}(0, 2.5) \\
+\beta_1 &\sim \text{Normal}(0, 2.5) \\
+\beta_2 &\sim \text{Normal}(0, 2.5) \\
+\beta_3 &\sim \text{Normal}(0, 2.5) \\
+\beta_4 &\sim \text{Normal}(0, 2.5) \\
+\beta_5 &\sim \text{Normal}(0, 2.5) \\
+\beta_6 &\sim \text{Normal}(0, 2.5)
 \end{align}
+
+where binary variable $vote\_harris_i$ is equal to 1 if the respondent's preferred 2024 presidential candidate is Kamala Harris, or 0 if the respondent's preferred 2024 presidential candidate is Donald Trump.
+We run our model in R [@citeR] using `stan_glm`, with the default priors from `rstanarm` [@citerstanarm].
+We then apply our model to our post-stratification data [@citeIPUMS] to predict the popular vote and electoral college results of the 2024 U.S.
+Presidential election.
+
+Our model uses logistic regression, therefore one of its weaknesses is the fact that it predicts a binary outcome and does not consider the possibility that some American adults might vote for a third-party candidate or abstain from voting.
+Tradeoffs and concerns about our model are discussed in more detail in @sec-weaknesses-limitations.
 
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+We expect a positive relationship between certain demographic characteristics and support for Kamala Harris. Specifically:
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+- **Sex**: We might expect differences in support between male and female respondents, with women potentially being more likely to support Kamala Harris due to certain policy stances that may appeal to this demographic.
+- **Age Bracket**: Age can be a significant factor, as younger voters might lean more progressive, potentially increasing support for Kamala Harris compared to Donald Trump.
+- **Race and Hispanic Ethnicity**: Historical voting patterns suggest that non-white racial groups, including Hispanic voters, may show stronger support for Democratic candidates, such as Harris.
+This is reflected in the coefficients $\beta_3$ for race and $\beta_4$ for Hispanic ethnicity.
+- **Education Level**: Higher education levels are often correlated with progressive political views, so we might expect a positive relationship between education level and support for Harris.
+- **Urban**: Respondents living in urban areas may be more likely to support Kamala Harris due to the urban-rural political divide observed in recent elections, where urban areas tend to lean more Democratic.
+
+The coefficients, such as $\beta_1$ for sex and $\beta_2$ for age bracket, represent the strength of these relationships.
+For example, a positive value of $\beta_1$ would suggest that being female increases the probability of supporting Harris, all else being equal.
+
+By using normal priors like $\beta_1 \sim \text{Normal}(0, 2.5)$, we assume that, before seeing the data, the effect of each predictor on the log-odds of supporting Kamala Harris is centered around zero, but with flexibility for the data to inform the posterior estimates.
+
+The Bayesian framework allows us to capture the uncertainty in our estimates and to refine our understanding of how different factors influence political support as new data becomes available.
+This is especially important in political forecasting, where the relationships between demographic factors and candidate support can be influenced by evolving social and political dynamics.
 

### 2024-10-22 paper/paper.qmd
update

--- 2024-10-21 paper/paper.qmd
@@
 
-Forecasting election outcomes has become a critical endeavor in political science and public policy, as it not only informs campaigns and media coverage but also shapes voter perceptions.
-The ability to accurately predict the winner of a presidential election holds significant implications for political strategy, governance, and public trust in polling methodologies.
-In this context, leveraging aggregated polling data, or “poll-of-polls,” offers a more comprehensive and reliable prediction model, as it aims to reduce the biases and errors associated with individual polls (Blumenthal 2014; Pasek 2015).
+Overview paragraph
 
-This paper aims to explore the predictive power of a linear or generalized linear model using a poll-of-polls approach to forecast the winner of the upcoming US presidential election.
-The motivation behind this research stems from the persistent challenge of balancing sample biases, framing, and non-response rates, which can all impact the reliability of a single poll.
-By aggregating data from multiple polls, the goal is to create a robust and reproducible model that accounts for these discrepancies and better reflects voter sentiment.
+Estimand paragraph
 
-To achieve this, the study focuses on a deep-dive analysis of a specific pollster, examining their methodology in detail.
-This analysis includes understanding the population, sampling frame, and recruitment process, as well as evaluating the strengths and limitations of their questionnaire design.
-Additionally, the paper proposes an idealized survey and methodology, imagining a scenario with a $100K budget to forecast the election outcome.
-This hypothetical scenario explores alternative approaches to survey design, data collection, and aggregation techniques.
+Results paragraph
 
-This study is significant because it not only aims to build an effective model for election forecasting but also provides critical insights into the methodologies of polling organizations.
-The findings of this research can contribute to a more nuanced understanding of how polling data is collected and interpreted, ultimately improving the accuracy of election predictions.
+Why it matters paragraph
 
-The structure of the paper is as follows: first, the methodology for the forecasting model is presented; second, a detailed analysis of the chosen pollster is included in an appendix, followed by the idealized survey design and methodology.
-Together, these elements provide a comprehensive understanding of the challenges and opportunities in election forecasting using aggregated polling data.
+Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
 
@@
 However, like all polls, it is subject to limitations, particularly around non-response and self-selection biases​
+
+## Idealized Methodology for US Presidential Election Forecast
+This appendix outlines the methodology and design for conducting a U.S.
+presidential election forecast survey with a budget of $100,000.
+The goal is to develop an accurate and reliable prediction of the election outcome, ensuring data quality through careful sampling, recruitment, validation, and aggregation of results.
+
+Methodology Overview
+1. Sampling Approach
+To ensure a representative sample of likely voters, I will use a stratified random sampling method based on demographic and voter turnout data from the U.S. Census and previous elections.
+
+Target Population: U.S. citizens eligible to vote in the 2024 U.S. presidential election.
+Sample Size: I plan to survey 3,500 respondents, providing a margin of error of approximately ±1.7 percentage points, ensuring a high level of confidence in the results.
+Stratification Variables: The sample will be stratified by age, gender, race/ethnicity, education level, geographic region, and income.
+This ensures that each demographic group is represented proportionally to the U.S.
+population.
+Oversampling: To ensure insights into underrepresented or low-response groups (e.g., younger voters, minorities), I will oversample these groups and apply appropriate post-stratification weighting.
+2. Recruitment of Respondents
+I will use a multi-modal approach to recruit a diverse and representative sample, employing both online and offline strategies to reach various segments of the population.
+
+Online Recruitment: Use targeted advertisements on social media platforms (e.g., Facebook, Instagram) and popular news websites.
+A portion of the budget will be allocated to recruiting via established online panel providers such as Qualtrics or YouGov.
+Phone and SMS Polling: To capture voters who may not engage online, I will employ live phone interviews using Random Digit Dialing (RDD) and SMS text polls, ensuring coverage of both landline and mobile users.
+In-Person Recruitment: In key battleground states, local fieldworkers will be deployed to recruit voters who may not be reached through digital or phone methods, ensuring a geographically diverse sample.
+3. Data Validation and Quality Control
+Data quality is crucial for accurate forecasting, and several measures will be implemented to ensure the validity of responses:\
+Voter Verification: Respondents will be asked to confirm their voter registration status, and a subset of the sample will be cross-checked with voter databases to validate their responses.
+Attention Checks: To minimize random or disengaged responses, I will include attention checks (e.g., questions asking respondents to select a specific answer) throughout the survey.
+Duplicate Prevention: Respondent IP addresses and email addresses will be tracked to prevent multiple submissions from the same individual.
+Weighting: Post-stratification weighting will be applied to adjust for any demographic imbalances in the final sample.
+Weighting factors will be based on age, gender, race, education, and voting history to match U.S.
+population benchmarks.
+
+4. Poll Aggregation and Forecasting Model
+In addition to my own survey, I will aggregate data from other reputable pollsters to improve the accuracy of the forecast.
+
+Poll Aggregation: I will collect data from publicly available polls (e.g., FiveThirtyEight, RealClearPolitics) and develop a weighted average based on the reliability of each poll, sample size, and recency.
+Weighting by Pollster Quality: Pollsters will be rated based on their historical accuracy, sample sizes, and transparency in methodology.
+More reliable polls will be weighted higher in the aggregation model.
+Predictive Modeling: I will use a Bayesian predictive model that incorporates current polling data, historical voting patterns, economic indicators, and other key variables to generate a probabilistic forecast of the election outcome.
+
+5. Questionnaire Design
+The survey will be structured to capture key insights into voting intention, candidate favorability, and the issues driving voter decisions.
+It will be short and simple, taking no more than 10 minutes to complete.
+Survey Link
+The survey has been implemented using Google Forms. Here is the link to access the survey:\
+https://docs.google.com/forms/d/e/1FAIpQLSetY5pPLMYHn4YXF2uIxVNnCGUB1PRvyHbSd3HF3E6DdN2EkA/viewform
+
+Budget Breakdown
+Here is a proposed allocation of the $100,000 budget:\
+Survey Platform and Software Costs: $5,000 for survey hosting on Google Forms and Qualtrics.
+Recruitment Costs: $40,000 for online panel recruitment, social media ads, and targeted outreach.
+Phone and SMS Polling: $20,000 to cover live phone interviews and SMS polling.
+Fieldwork in Key States: $15,000 for in-person recruitment in battleground states.
+Data Validation and Cleaning: $10,000 for voter verification, attention checks, and cleaning services.
+Poll Aggregation and Modeling Tools: $7,000 for the development of a poll aggregation tool and Bayesian forecasting model.
+Miscellaneous Costs: $3,000 for administrative costs, project management, and reporting.
+
 \newpage

### 2024-10-22 paper/paper.qmd

--- 2024-10-22 paper/paper.qmd
@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Forecasting 2024 US election using linear regression"
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
+  - Diana Shen
+  - Jinyan Wei
+  - Jerry Yu
+thanks: "Code and data are available at: [https://github.com/DianaShen1224/Forecast-2024-US-election](https://github.com/DianaShen1224/Forecast-2024-US-election)."
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "
+This paper predicts the outcome of the 2024 U.S.
+presidential election using a statistical model based on aggregated polling data for Kamala Harris and Donald Trump.
+We employ multi-level regression with post-stratification (MRP) using demographic predictors to estimate voter support.
+The analysis addresses polling biases and proposes an idealized survey methodology with a $100,000 budget.
+Our results offer insights into voter behavior and suggest improvements for future election forecasting models."
 format: pdf
@@
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
-
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
-
-Talk way more about it.
-
 ## Predictor variables
-
-Add graphs, tables and text.
-
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
 
@@
 
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
-
 # Discussion
@@
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
 ## Second discussion point
-
-Please don't use these as sub-heading labels - change them to be what your point actually is.
 
@@
 ## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
 

### 2024-10-24 paper/paper.qmd
Update with survey link
update acquire of data

@@
 date-format: long
-abstract: "
-This paper predicts the outcome of the 2024 U.S.
+abstract: "This paper predicts the outcome of the 2024 U.S.
 presidential election using a statistical model based on aggregated polling data for Kamala Harris and Donald Trump.
@@
 library(tidyverse)
-library(palmerpenguins)
 ```

### 2024-10-24 scripts/02-download_data.R

@@ -9,18 +9,23 @@
 
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
-
-
+#### Acquire ####
+raw_elections_data <-
+  read_csv(
+    file = 
+      "https://projects.fivethirtyeight.com/polls/data/president_polls.csv",
+    show_col_types = FALSE,
+    skip = 1
+  )
 
 #### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+write_csv(
+  x = raw_elections_data,
+  file = "~/2024 US Election Forecast/data/01-raw_data/raw_election_24.csv"
+)
 
-         
+head(toronto_shelters)
+

### 2024-10-25 paper/paper.qmd
update the appendix

@@
 In addition to constructing and interpreting predictive models, this paper dive into the methods used by xx pollsters, analyzing the strengths as well as the weaknesses of the methods used against them.
-At the end of the paper, we also propose an idealized survey methodology for election forecasting with a budget of $100,000 USD.
+At the end of the paper, we also propose an idealized survey methodology for election forecasting with a budget of \$100,000 USD.
 
@@
 
+```{=tex}
 \begin{align} 
@@
 \end{align}
-
+```
 where binary variable $vote\_harris_i$ is equal to 1 if the respondent's preferred 2024 presidential candidate is Kamala Harris, or 0 if the respondent's preferred 2024 presidential candidate is Donald Trump.
@@
 
-# Appendix {-}
+# Appendix {.unnumbered}
 
@@
 # Appendix
+
 ## Emerson College Polling Methodology
+
 For this deep dive, I'll focus on Emerson College Polling based on the link: Emerson College Polling - October 2024 National Poll.
-Survey Overview:
-The Emerson College Polling conducted a national survey in October 2024 to assess voter preferences for the upcoming U.S.
+Survey Overview: The Emerson College Polling conducted a national survey in October 2024 to assess voter preferences for the upcoming U.S.
 presidential election.
@@
 
-Methodology
-1. Population, Frame, and Sample:\
-Target Population: The target population for this poll includes U.S. citizens who are eligible to vote in the 2024 presidential election.
+Methodology 1. Population, Frame, and Sample:\
+Target Population: The target population for this poll includes U.S.
+citizens who are eligible to vote in the 2024 presidential election.
 Sample Frame: The sample consists of likely voters across the United States.
@@
 5.  Questionnaire Design:\
-Strengths:
-The survey is concise, focusing on core topics like voter intention, candidate preference, and key issues such as the economy and healthcare.
+    Strengths: The survey is concise, focusing on core topics like voter intention, candidate preference, and key issues such as the economy and healthcare.
 This increases the likelihood that respondents complete the survey accurately and without fatigue.
 Emerson regularly tests its questionnaire to ensure clarity and avoid ambiguous questions, improving the reliability of the responses.
-Weaknesses:
-Binary Choice Bias: Some sections of the questionnaire force a binary choice between two candidates, which may oversimplify the respondents' true preferences, especially in a race with multiple candidates or undecided voters.
+Weaknesses: Binary Choice Bias: Some sections of the questionnaire force a binary choice between two candidates, which may oversimplify the respondents' true preferences, especially in a race with multiple candidates or undecided voters.
 Social Desirability Bias: Like most political polls, respondents may answer questions in a way they believe is socially acceptable, especially in terms of voter turnout or support for controversial candidates.
 This could lead to over-reporting of voter intention.
-Summary of Strengths and Weaknesses
-Strengths:
+Summary of Strengths and Weaknesses Strengths:
 
 Multi-mode Surveying: Emerson’s use of phone, online, and SMS recruitment allows them to reach a broader cross-section of the population, minimizing the biases introduced by any one method.
-Post-stratification Weighting: The weighting process ensures the sample reflects the U.S. population, improving the reliability of the poll results.
+Post-stratification Weighting: The weighting process ensures the sample reflects the U.S.
+population, improving the reliability of the poll results.
 Timely Polling: The frequent release of polling data makes it possible to track shifts in voter sentiment over time.
@@
 ## Idealized Methodology for US Presidential Election Forecast
+
 This appendix outlines the methodology and design for conducting a U.S.
-presidential election forecast survey with a budget of $100,000.
-The goal is to develop an accurate and reliable prediction of the election outcome, ensuring data quality through careful sampling, recruitment, validation, and aggregation of results.
+presidential election forecast survey with a budget of \$100,000.
+The goal is to develop an accurate and reliable prediction of the election outcome, ensuring data quality through careful sampling, recruitment, validation, and aggregation of results.\
 
-Methodology Overview
-1. Sampling Approach
-To ensure a representative sample of likely voters, I will use a stratified random sampling method based on demographic and voter turnout data from the U.S. Census and previous elections.
+### Methodology
 
-Target Population: U.S. citizens eligible to vote in the 2024 U.S. presidential election.
-Sample Size: I plan to survey 3,500 respondents, providing a margin of error of approximately ±1.7 percentage points, ensuring a high level of confidence in the results.
+#### Sampling Approach
+
+To ensure a representative sample of likely voters, I will use a Composite Measure sampling method based on the past voter turnout data from the U.S.
+previous 2020 elections.After decising the sampling size in each state, I will use a stratified sampling bases on demographics,dividing population into subgroups, and a random sample is taken from each subgroup.
+We employ composite Measure sampling method refer from (), that increased our chances of selecting respondents from voters in states/ regions that have historically higher voter engagement as compared to the natural distribution we’d expect from the general population.
+While some states may have larger populations, we are interested in adjusting the sampling to reflect higher turnout rates.
+To better explain this composite measure of size, lets consider that we have two states that have similar population.
+For example, even though State A and State B may have similar populations, if State B consistently has a higher voter turnout in past elections, we want to increase the proportion of polls we conduct in State B.
+State A has a population of 1 million eligible voters, with a historical turnout rate of 50%.
+State B has a population of 1 million eligible voters, but its turnout rate is 70%.
+In a purely population-based sampling approach, each state would have an equal chance of being selected for polls: 50% for State A and 50% for State B.
+However, based on voter turnout, we modify these probabilities to increase the chance of selecting State B, since its voter turnout is historically higher.\
+In following steps, we will explore how to use **voter turnout** as a key factor to create a **composite measure of size** for sampling US election polls.
+Instead of using population size alone, we adjust the sample allocation based on historical voter turnout, ensuring regions with higher engagement are more heavily represented in our polling data.\
+
+##### Step 1: Define the Sampling Data
+
+We begin by collecting the **eligible voter population** and **historical voter turnout rates** for different states.
+In this simplified example, we will focus on two states: **State A** and **State B**.
+
+| State   | Eligible Voters | Turnout Rate |
+|---------|-----------------|--------------|
+| State A | 1,000,000       | 50%          |
+| State B | 1,000,000       | 70%          |
+
+##### Step 2: Calculate Actual Voters
+
+Next, we calculate the **number of actual voters** in each state by multiplying the eligible voters by the turnout rate: $$\text{Actual Voters} = \text{Eligible Voters} \times \text{Turnout Rate}$$\
+Actual voters in State A: $\text{Actual Voters}_A = 1,000,000 \times 0.50 = 500,000$\
+Actual voters in State B: $\text{Actual Voters}_B = 1,000,000 \times 0.70 = 700,000$\
+Total actual voters: $\text{Actual Voters}_A+\text{Actual Voters}_B= 500,000 + 700,000 = 1,200,000$\
+
+##### Step 3: Calculate Composite Measure of Size
+
+We now calculate the **total number of voters** across both states and determine the **proportion** of each state's turnout relative to the total.
+This forms the basis of the composite measure of size, which we will use to adjust the sampling weights.
+
+The total voters in two states are 1,200,000.
+Therefore, the sampling proportion for State A is: $\text{Sampling Proportion}_A = \frac{500,000}{1,200,000} \approx 0.417$, and for State B is: $\text{Sampling Proportion}_B = \frac{700,000}{1,200,000} \approx 0.583$
+
+##### Step 4: Allocate Sample Based on Turnout
+
+Finally, we allocate the sample size according to the calculated sampling proportions.
+For instance, if we are conducting 1,000 polls, we would allocate State A with $\text{Polls for State A} = 1,000 \times 0.417 \approx 417 \text{polls}$ and State B with $\text{Polls for State B} = 1,000 \times 0.583 \approx 583 \text{polls}$
+
+By using historical voter turnout to adjust our polling sample, we ensure that regions with higher voter engagement have a greater influence on the polling results.
+This composite measure of size ensures that our polling sample better reflects the actual voting patterns and preferences in different regions.
+Consequently, we can produce more accurate and representative poll outcomes that account for the varying levels of voter participation across the country.
+
+### Target Population
+
+Our target population is all U.S. citizens eligible to vote in the 2024 U.S. presidential election (age\>=18).
+
+### Sample frame
+
+### Sample
+
+#### Sample Size:
+
+We plan to survey 300 respondents, which will provide a margin of error of approximately ±1.7 percentage points, ensuring a high level of confidence in the results.
+Given the limited sample size and to enhance the effectiveness of stratified sampling, the states will be grouped into four regions: Midwest, Northeast, South, and West.
+The sample size for each region will be allocated based on the proportion of total ballots cast in each region during the 2020 election.
+The regional grouping of states is shown in @tbl-region.
+
+| **Region**    | **States**                                                                                                                                                 |
+|------------------------------------|------------------------------------|
+| **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
+| **Northeast** | Connecticut, Delaware, District of Columbia, Maine, Maryland, Massachusetts, New Hampshire, New Jersey, New York, Pennsylvania, Rhode Island, Vermont      |
+| **SOUTH**     | Alabama, Arkansas, Florida, Georgia, Kentucky, Louisiana, Mississippi, North Carolina, Oklahoma, South Carolina, Tennessee, Texas, Virginia, West Virginia |
+| **WEST**      | Alaska, Arizona, California, Colorado, Hawaii, Idaho, Montana, Nevada, New Mexico, Oregon, Utah, Washington, Wyoming                                       |
+
+: Regional Grouping of States in the USA {#tbl-region}
+
+| **Region**  | **Voter Turnout (%)** | **Total Ballots Cast** | **VEP**    | **Composite Measure Sampling Proportion** | **Sample Size** |
+|-----------|-----------|-----------|-----------|-----------------|-----------|
+| **MIDWEST** | 69%                   | 35,134,960             | 50,932,439 | 0.214805579                               | 64              |
+| **NW**      | 68%                   | 32,262,303             | 47,473,317 | 0.200216867                               | 60              |
+| **SOUTH**   | 65%                   | 54,746,770             | 84,563,831 | 0.356644666                               | 107             |
+| **WEST**    | 69%                   | 37,594,304             | 54,139,892 | 0.228332888                               | 68              |
+
+: Regional Voting Data and Sample Size Allocation Based on 2020 Election Turnout{#tbl-sample_size}
+
+@tbl-sample_size shows the regional breakdown of the 2020 election data, sourced from [@wiki], including voter turnout, total ballots cast, and Voting Eligible Population (VEP).
+The sample size for each region was determined based on the **Composite Measure Sampling Proportion**.
+
 Stratification Variables: The sample will be stratified by age, gender, race/ethnicity, education level, geographic region, and income.
@@
 population.
+
 Oversampling: To ensure insights into underrepresented or low-response groups (e.g., younger voters, minorities), I will oversample these groups and apply appropriate post-stratification weighting.
-2. Recruitment of Respondents
+
+#### Recruitment of Respondents
+
 I will use a multi-modal approach to recruit a diverse and representative sample, employing both online and offline strategies to reach various segments of the population.
@@
 In-Person Recruitment: In key battleground states, local fieldworkers will be deployed to recruit voters who may not be reached through digital or phone methods, ensuring a geographically diverse sample.
-3. Data Validation and Quality Control
-Data quality is crucial for accurate forecasting, and several measures will be implemented to ensure the validity of responses:\
+3.
+Data Validation and Quality Control Data quality is crucial for accurate forecasting, and several measures will be implemented to ensure the validity of responses:\
 Voter Verification: Respondents will be asked to confirm their voter registration status, and a subset of the sample will be cross-checked with voter databases to validate their responses.
@@
 
-4. Poll Aggregation and Forecasting Model
-In addition to my own survey, I will aggregate data from other reputable pollsters to improve the accuracy of the forecast.
+4.  Poll Aggregation and Forecasting Model In addition to my own survey, I will aggregate data from other reputable pollsters to improve the accuracy of the forecast.
 
@@
 
-5. Questionnaire Design
-The survey will be structured to capture key insights into voting intention, candidate favorability, and the issues driving voter decisions.
+5.
+Questionnaire Design The survey will be structured to capture key insights into voting intention, candidate favorability, and the issues driving voter decisions.
 It will be short and simple, taking no more than 10 minutes to complete.
-Survey Link
-The survey has been implemented using Google Forms. Here is the link to access the survey:\
-https://docs.google.com/forms/d/e/1FAIpQLSetY5pPLMYHn4YXF2uIxVNnCGUB1PRvyHbSd3HF3E6DdN2EkA/viewform
+Survey Link The survey has been implemented using Google Forms.
+Here is the link to access the survey:\
+    https://forms.gle/BAZhkWDyLxAibwvu5
 
-Budget Breakdown
-Here is a proposed allocation of the $100,000 budget:\
-Survey Platform and Software Costs: $5,000 for survey hosting on Google Forms and Qualtrics.
-Recruitment Costs: $40,000 for online panel recruitment, social media ads, and targeted outreach.
-Phone and SMS Polling: $20,000 to cover live phone interviews and SMS polling.
-Fieldwork in Key States: $15,000 for in-person recruitment in battleground states.
-Data Validation and Cleaning: $10,000 for voter verification, attention checks, and cleaning services.
-Poll Aggregation and Modeling Tools: $7,000 for the development of a poll aggregation tool and Bayesian forecasting model.
-Miscellaneous Costs: $3,000 for administrative costs, project management, and reporting.
+Budget Breakdown Here is a proposed allocation of the \$100,000 budget:\
+Survey Platform and Software Costs: \$5,000 for survey hosting on Google Forms and Qualtrics.
+Recruitment Costs: \$40,000 for online panel recruitment, social media ads, and targeted outreach.
+Phone and SMS Polling: \$20,000 to cover live phone interviews and SMS polling.
+Fieldwork in Key States: \$15,000 for in-person recruitment in battleground states.
+Data Validation and Cleaning: \$10,000 for voter verification, attention checks, and cleaning services.
+Poll Aggregation and Modeling Tools: \$7,000 for the development of a poll aggregation tool and Bayesian forecasting model.
+Miscellaneous Costs: \$3,000 for administrative costs, project management, and reporting.
 

### 2024-10-25 paper/paper.qmd
update the appendix B and C, with methodology and copy of survey

@@
 
-### Methodology
-
-#### Sampling Approach
+### Sampling Approach
 
@@
 
-##### Step 1: Define the Sampling Data
+#### Step 1: Define the Sampling Data
 
@@
 
-##### Step 2: Calculate Actual Voters
+#### Step 2: Calculate Actual Voters
 
@@
 
-##### Step 3: Calculate Composite Measure of Size
+#### Step 3: Calculate Composite Measure of Size
 
@@
 
-##### Step 4: Allocate Sample Based on Turnout
+#### Step 4: Allocate Sample Based on Turnout
 
@@
 
+Based on the recruitment method we discussed later, our sampling frame could be all registered voters in online panels like Qualtrics and YouGov and the millions of U.S.
+voters who are reachable via social media platforms like Facebook and Instagram.
+
 ### Sample
@@
 | **Region**    | **States**                                                                                                                                                 |
-|------------------------------------|------------------------------------|
+|---------------|------------------------------------------------------------------------------------------------------------------------------------------------------------|
 | **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
@@
 | **Region**  | **Voter Turnout (%)** | **Total Ballots Cast** | **VEP**    | **Composite Measure Sampling Proportion** | **Sample Size** |
-|-----------|-----------|-----------|-----------|-----------------|-----------|
-| **MIDWEST** | 69%                   | 35,134,960             | 50,932,439 | 0.214805579                               | 64              |
-| **NW**      | 68%                   | 32,262,303             | 47,473,317 | 0.200216867                               | 60              |
-| **SOUTH**   | 65%                   | 54,746,770             | 84,563,831 | 0.356644666                               | 107             |
-| **WEST**    | 69%                   | 37,594,304             | 54,139,892 | 0.228332888                               | 68              |
+|-------------|-----------------------|------------------------|------------|-------------------------------------------|-----------------|
+| **MIDWEST** | 69%                   | 35,134,960             | 50,932,439 | 0.214805579                               | 86              |
+| **NW**      | 68%                   | 32,262,303             | 47,473,317 | 0.200216867                               | 80              |
+| **SOUTH**   | 65%                   | 54,746,770             | 84,563,831 | 0.356644666                               | 143             |
+| **WEST**    | 69%                   | 37,594,304             | 54,139,892 | 0.228332888                               | 91              |
 
-: Regional Voting Data and Sample Size Allocation Based on 2020 Election Turnout{#tbl-sample_size}
+: Regional Voting Data and Sample Size Allocation Based on 2020 Election Turnout {#tbl-samplesize}
 
-@tbl-sample_size shows the regional breakdown of the 2020 election data, sourced from [@wiki], including voter turnout, total ballots cast, and Voting Eligible Population (VEP).
+@tbl-samplesize shows the regional breakdown of the 2020 election data, sourced from [@wiki], including voter turnout, total ballots cast, and Voting Eligible Population (VEP).
 The sample size for each region was determined based on the **Composite Measure Sampling Proportion**.
 
-Stratification Variables: The sample will be stratified by age, gender, race/ethnicity, education level, geographic region, and income.
-This ensures that each demographic group is represented proportionally to the U.S.
-population.
+**Stratification Variables**: After determining the number of respondents to be sampled from each region, stratified sampling will be applied across key demographic categories such as age, gender, race/ethnicity, and education level.
+This approach helps ensure that the final sample accurately reflects the diversity of the U.S.
+voting population by proportionally representing each subgroup within each region.
+To address potential non-response bias, post-stratification weighting[^1] will be applied, adjusting for any imbalances caused by differences in response rates across demographic groups.
+The sample will be stratified across several key demographic and geographic variables to ensure proportional representation of the U.S.
+voting population.
+These variables include age, with categories such as 18-24 (12%), 25-34 (17%), 35-44 (16%), 45-54 (16%), 55-64 (16%), and 65+ (23%); gender, split into male (48%), female (52%), and non-binary/other (less than 1%); and race/ethnicity, covering groups like White/Caucasian (67%), Black/African American (13%), Hispanic/Latino (13%), Asian/Pacific Islander (5%), Native American/Alaskan Native (1%), and Other/Mixed Race (1%).
+Additionally, education level will be stratified into high school diploma or less (36%), some college, no degree (17%), Associate’s degree (9%), Bachelor’s degree (23%), and graduate or professional degree (15%).
+Geographic region will also be a key factor, ensuring representation from the Midwest (21%), Northeast (17%), South (38%), and West (24%).
+For each variable, U.S.
+Census or voter turnout data will be used to proportionally allocate respondents, ensuring that the final sample closely mirrors the demographic and regional composition of the actual voting population.
+Post-stratification weighting will be applied to adjust for any imbalances that may occur during data collection.
 
-Oversampling: To ensure insights into underrepresented or low-response groups (e.g., younger voters, minorities), I will oversample these groups and apply appropriate post-stratification weighting.
+[^1]: Post-stratification weighting adjusts survey data by applying weights to under- or over-represented demographic groups in the sample, ensuring the final results align with the true population distribution and reducing biases such as non-response bias.
 
@@
 
-I will use a multi-modal approach to recruit a diverse and representative sample, employing both online and offline strategies to reach various segments of the population.
+Due to budget constraints, we will focus on online recruitment methods, which offer a cost-effective and efficient way to reach a diverse and representative sample of voters across the country.
 
-Online Recruitment: Use targeted advertisements on social media platforms (e.g., Facebook, Instagram) and popular news websites.
-A portion of the budget will be allocated to recruiting via established online panel providers such as Qualtrics or YouGov.
-Phone and SMS Polling: To capture voters who may not engage online, I will employ live phone interviews using Random Digit Dialing (RDD) and SMS text polls, ensuring coverage of both landline and mobile users.
-In-Person Recruitment: In key battleground states, local fieldworkers will be deployed to recruit voters who may not be reached through digital or phone methods, ensuring a geographically diverse sample.
-3.
-Data Validation and Quality Control Data quality is crucial for accurate forecasting, and several measures will be implemented to ensure the validity of responses:\
-Voter Verification: Respondents will be asked to confirm their voter registration status, and a subset of the sample will be cross-checked with voter databases to validate their responses.
-Attention Checks: To minimize random or disengaged responses, I will include attention checks (e.g., questions asking respondents to select a specific answer) throughout the survey.
-Duplicate Prevention: Respondent IP addresses and email addresses will be tracked to prevent multiple submissions from the same individual.
-Weighting: Post-stratification weighting will be applied to adjust for any demographic imbalances in the final sample.
-Weighting factors will be based on age, gender, race, education, and voting history to match U.S.
-population benchmarks.
+Online Recruitment: With the objective of surveying 400 respondents, we will focus our resources on implementing the survey and ensuring high-quality data collection.
+The survey will be developed in-house, and respondents will be recruited using online survey platforms.
+The recruitment approach is as follows:
 
-4.  Poll Aggregation and Forecasting Model In addition to my own survey, I will aggregate data from other reputable pollsters to improve the accuracy of the forecast.
+Sample Size Distribution Across Platforms
 
-Poll Aggregation: I will collect data from publicly available polls (e.g., FiveThirtyEight, RealClearPolitics) and develop a weighted average based on the reliability of each poll, sample size, and recency.
-Weighting by Pollster Quality: Pollsters will be rated based on their historical accuracy, sample sizes, and transparency in methodology.
-More reliable polls will be weighted higher in the aggregation model.
-Predictive Modeling: I will use a Bayesian predictive model that incorporates current polling data, historical voting patterns, economic indicators, and other key variables to generate a probabilistic forecast of the election outcome.
+Online Panel Providers (Qualtrics, YouGov): 200 respondents will be recruited through reputable online panel providers like Qualtrics and YouGov, known for high-quality samples with verified voter registration status.
+This recruitment source provides a strong base of quality data, given the stringent participant verification process in place.
 
-5.
-Questionnaire Design The survey will be structured to capture key insights into voting intention, candidate favorability, and the issues driving voter decisions.
-It will be short and simple, taking no more than 10 minutes to complete.
+Social Media Recruitment: We plan to recruit 400 respondents through targeted social media panels on platforms such as Facebook and Instagram.
+Given the typically lower data quality from social media recruitment, we anticipate that 50% of responses may be invalid.
+To compensate, we will oversample from this group, aiming to gather a sufficient number of valid and high-quality responses.
+To attract participants, each respondent will receive a small monetary reward (such as a gift card) for completing the survey.
+Targeted ads and eligibility screening will be used to reach respondents who meet key criteria, such as age and U.S.
+voter registration status.
+This approach helps ensure that those recruited are likely to be eligible voters.
+
+#### Respondent Validation
+
+To ensure high data quality and accuracy, respondent validation will be conducted through multiple checks and verification processes.
+This process ensures that only eligible and relevant participants are included in the survey, maintaining the integrity of the sample.
+
+Voter Registration Verification:
+
+Respondents will be required to confirm their voter registration status, with a portion of the sample cross-referenced against voter registration databases or verified through reputable online panel providers like Qualtrics or YouGov.
+This step ensures that the survey includes only registered and likely voters, crucial for representing the target population accurately.
+Screening and Eligibility Questions:
+
+Respondents will complete a set of screening questions to verify eligibility criteria, such as age (18 or older) and U.S.
+citizenship.
+Only those meeting these criteria will be allowed to proceed with the survey.
+Attention Checks:
+
+To detect and filter out inattentive or disengaged participants, attention-check questions will be embedded throughout the survey (e.g., asking respondents to select a specific answer to verify attentiveness).
+Respondents who fail these checks may be excluded from the final sample.
+Duplicate Prevention:
+
+Unique identifiers such as IP addresses and email addresses will be tracked to prevent multiple submissions from the same individual, ensuring that each response represents a unique participant.
+Post-Survey Data Cleaning:
+
+After data collection, responses will be reviewed for consistency and completeness.
+Inconsistent responses or incomplete surveys will be removed, maintaining the quality and reliability of the dataset.
+By implementing these respondent validation steps, the survey methodology ensures that data collected reflects only eligible, registered, and attentive respondents, thereby enhancing the validity and accuracy of the survey results.
+
+### Poll Aggregation
+
+After getting the survey response, we will aggregate polls from two recruitment sources: online panel providers and social media platforms.To weight the two panels effectively, we will first identify key demographic variables for stratification, such as age, gender, race/ethnicity, and education level, and establish population proportions using U.S.
+Census data or other reliable sources.
+For the online panel (200 respondents), we will compare the demographic distribution of respondents to these population benchmarks, calculating weights based on the degree of under- or over-representation.
+Similarly, we will perform this analysis for the social media panel (400 respondents) to determine its weights.
+Once we have calculated weights for each panel, we will combine them into a single weighting scheme that reflects the overall demographic composition of the target population.
+During data analysis, we will apply these weights to the responses, ensuring that underrepresented groups have a greater influence on the results while adjusting for those that are overrepresented.
+Finally, we will conduct post-stratification adjustments to confirm that the combined sample accurately mirrors the true characteristics of the U.S.
+voting population, providing reliable insights into voter preferences and behaviors.
+
+### Survey Design
+
+The survey will be structured to capture key insights into voting intention, candidate favorability, and the issues driving voter decisions.
+It will be short and simple, taking no more than 15 minutes to complete.
 Survey Link The survey has been implemented using Google Forms.
@@
 
-Budget Breakdown Here is a proposed allocation of the \$100,000 budget:\
-Survey Platform and Software Costs: \$5,000 for survey hosting on Google Forms and Qualtrics.
-Recruitment Costs: \$40,000 for online panel recruitment, social media ads, and targeted outreach.
-Phone and SMS Polling: \$20,000 to cover live phone interviews and SMS polling.
-Fieldwork in Key States: \$15,000 for in-person recruitment in battleground states.
-Data Validation and Cleaning: \$10,000 for voter verification, attention checks, and cleaning services.
-Poll Aggregation and Modeling Tools: \$7,000 for the development of a poll aggregation tool and Bayesian forecasting model.
-Miscellaneous Costs: \$3,000 for administrative costs, project management, and reporting.
+### Budget Breakdown
+
+Budget Breakdown With a total budget of \$100,000, the allocation for various components of the survey implementation and data collection is as follows:
+
+Survey Design and Development: \$2,000 This portion covers the design and development of the survey, including question formatting, testing, and integration with online platforms like Qualtrics and social media platforms.
+Ensuring the survey is user-friendly and addresses key research questions is essential for high-quality data collection.
+Online Panel Providers (Qualtrics, YouGov): \$80,000 (200 respondents at \$400 per respondent) We will recruit 100 respondents via reputable online panel providers like Qualtrics and YouGov.
+These platforms ensure high-quality responses through verified voter registration, but they come at a higher cost per respondent due to their validation processes.
+
+Social Media Recruitment (Facebook, Instagram): \$12,000 (400 respondents at \$30 per respondent) 400 respondents will be recruited using targeted social media ads.
+Since we expect 50% of responses to be invalid, oversampling will allow us to achieve a final valid sample of 200 respondents.
+The cost per respondent is lower than online panel providers, but rigorous validation and filtering are required to ensure data quality.
+
+Data Validation and Quality Control: \$6,000 This covers voter registration verification, attention checks within the survey, and extensive post-collection filtering, particularly for social media responses.
+Ensuring the integrity and accuracy of the data is crucial to minimize biases and errors.
+
+## U.S. Presidential Election Polls Survey
+
+---
+title: "U.S. Presidential Election Polls Survey"
+author: "Diana Shen, Jinyan Wei, Jerry Yu"
+date: "`r Sys.Date()`"
+output: pdf_document
+---
+
+Welcome
+
+Welcome to our 2024 U.S.
+Presidential Election Polls Survey.
+Your participation in this survey is vital in helping us understand voters' preferences and opinions on key issues.
+Rest assured that your responses are anonymous and will only be used for statistical analysis.
+
+This survey is for academic research in Statistics. It consists of 26 carefully designed questions and should take approximately 12-15 minutes to complete.
+
+For any questions or concerns regarding this survey, please contact:\
+**Email:** diana.shen\@mail.utoronto.ca
+
+------------------------------------------------------------------------
+
+Privacy Notice for Respondents
+
+Your privacy is our priority.
+In this survey, your responses are completely anonymous, ensuring that no one can link your answers back to you.
+We encourage you to share your true opinions, as this survey is conducted by a neutral, nonpartisan entity.
+Your data will only be used for research purposes, and you will not be identified individually.
+If you have concerns, we ask for your feedback at the end of the survey to ensure transparency and trust.
+
+------------------------------------------------------------------------
+
+Section 1: Survey Questions
+
+1.  **Do you approve or disapprove of the job Joe Biden is doing as President?**
+
+    -   Approve
+    -   Disapprove
+    -   Neutral or no opinion
+
+2.  **What is your party registration or affiliation?**
+
+    -   Democrat
+    -   Republican
+    -   Independent/ Other
+    -   Prefer not to say
+    -   Other: __________
+
+3.  **If the Presidential Election were held today, would you vote for Kamala Harris or Donald Trump?**
+
+    -   Kamala Harris
+    -   Donald Trump
+    -   Someone else
+    -   Undecided
+    -   Prefer not to say
+
+4.  **Although you are undecided, which candidate do you lean toward?**(Jump to this question only if responders choose undecided in Question 3)
+
+    -   Kamala Harris
+    -   Kamala Harris
+    -   Donald Trump
+
+5.  **How favorable are you towards the following candidates?**
+
+    |               | Very unfavorable | Unfavorable | Moderate | Favorable | Very favorable |
+    |---------------|------------------|-------------|----------|-----------|----------------|
+    | Kamala Harris |                  |             |          |           |                |
+    | Donald Trump  |                  |             |          |           |                |
+
+6.  **How certain are you about your candidate choice?**
+
+    -   Very certain
+    -   Somewhat certain
+    -   Not certain
+
+7.  **How do you plan to cast your vote?**
+
+    -   In-person on election day
+    -   Early voting in-person
+    -   By mail
+    -   Unsure
+
+8.  **Did you vote in the 2020 U.S. presidential election?**
+
+    -   Yes
+    -   No
+    -   Prefer not to say
+
+9.  **If you voted in 2020, who did you vote for?**
+
+    -   Joe Biden
+    -   Donald Trump
+    -   Other
+    -   Prefer not to say
+
+10.
+**Imagine the following candidates: Candidate A favors cutting taxes but has a weak stance on climate change, and Candidate B focuses on healthcare but supports increased military spending.
+Who would you vote for?**
+
+    -   Candidate A
+    -   Candidate B
+
+11. **Imagine two candidates: Candidate A supports education reform but plans to cut social security, and Candidate B focuses on green energy but raises taxes. Who would you vote for?**
+
+    -   Candidate A
+    -   Candidate B
+
+12. **What do you think is the most important issue facing the United States?**
+
+    -   Economy
+    -   Healthcare
+    -   Climate Change
+    -   Immigration
+    -   National Security
+    -   Education
+    -   Social Security
+    -   Other: __________
+
+13. **Select option 3 from the list below:**
+
+    -   Option 1
+    -   Option 2
+    -   Option 3
+    -   Option 4
+
+14. **How important is the economy in deciding your vote?**
+
+    -   Not important
+    -   1
+    -   2
+    -   3
+    -   4
+    -   5
+    -   Very important
+
+15. **How important is climate change in deciding your vote?**
+
+    -   Not important
+    -   1
+    -   2
+    -   3
+    -   4
+    -   5
+    -   Very important
+
+16. **How important is healthcare in deciding your vote?**
+
+    -   Not important
+    -   1
+    -   2
+    -   3
+    -   4
+    -   5
+    -   Very important
+
+17. **How closely are you following news about the 2024 U.S. presidential election?**
+
+    -   Very closely
+    -   Somewhat closely
+    -   Not closely
+
+18. **Which social media platforms do you use to get political news?** (Select all that apply)
+
+    -   Facebook
+    -   Twitter
+    -   Instagram
+    -   YouTube
+    -   None
+
+------------------------------------------------------------------------
+
+Section 2: Demographic Information
+
+**Privacy Notice for Demographic Information Collection**\
+Your demographic information is collected anonymously and will be used for statistical purposes only, helping us analyze trends across different groups.
+We ensure that your individual responses cannot be traced back to you, maintaining full confidentiality.
+Your privacy and honest participation are important to us.
+
+1.  **What is your age group?**
+    -   18-24
+    -   25-34
+    -   35-44
+    -   45-54
+    -   55-64
+    -   65+
+2.  **Region:**
+    -   Northeast
+    -   South
+    -   Midwest
+    -   West
+3.  **For statistical purposes only, can you please tell me your ethnicity?**
+    -   Hispanic or Latino of any race
+    -   White or Caucasian
+    -   Black or African American
+    -   Asian
+    -   Other or multiple races
+4.  **Can you please tell me your gender?**
+    -   Men
+    -   Women
+    -   Other
+    -   Prefer not to say
+5.  **What is the highest level of education you have attained?**
+    -   High school or less
+    -   Some college
+    -   Bachelor’s degree
+    -   Graduate degree
+6.  **What is your household annual income level?**
+    -   Less than \$50,000
+    -   \$50,000 - \$100,000
+    -   Over \$100,000
+    -   Prefer not to say
+
+------------------------------------------------------------------------
+
+Section 3: Feedback
+
+1.  **Do you have any concerns or feedback regarding the survey?**\
+    Your feedback is important to us and will help ensure transparency and trust in the research process.
+
+------------------------------------------------------------------------
+
+Thank You
+
+Thank you for taking the time to complete this survey. Your honest feedback is invaluable and will contribute greatly to our research. We appreciate your participation!
 

### 2024-10-25 paper/paper.qmd
update with Appendix B survey design

@@
 | **Region**    | **States**                                                                                                                                                 |
-|---------------|------------------------------------------------------------------------------------------------------------------------------------------------------------|
+|----------------------|--------------------------------------------------|
 | **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
@@
 | **Region**  | **Voter Turnout (%)** | **Total Ballots Cast** | **VEP**    | **Composite Measure Sampling Proportion** | **Sample Size** |
-|-------------|-----------------------|------------------------|------------|-------------------------------------------|-----------------|
+|------------|------------|------------|------------|------------|------------|
 | **MIDWEST** | 69%                   | 35,134,960             | 50,932,439 | 0.214805579                               | 86              |
@@
 
-The survey will be structured to capture key insights into voting intention, candidate favorability, and the issues driving voter decisions.
-It will be short and simple, taking no more than 15 minutes to complete.
-Survey Link The survey has been implemented using Google Forms.
-Here is the link to access the survey:\
-https://forms.gle/BAZhkWDyLxAibwvu5
+The survey is designed to capture essential insights into voting intentions, candidate favorability, and the issues influencing voter decisions.
+It will be concise and straightforward, taking no longer than 15 minutes to complete.
+
+**Survey Link**\
+The survey has been implemented using Google Forms. You can access it here: [Survey Link](https://forms.gle/BAZhkWDyLxAibwvu5).
+
+In our survey, several questions are adapted from the Emerson College Polling data [@emerson].
+We also apply insights from @survey to minimize response biases.
+Common biases identified in survey design include moderacy bias, extreme response bias, ordering bias, acquiescence bias, experimenter demand effect (EDE), and social desirability bias (SDB).
+Our survey primarily focuses on strategies to reduce moderacy bias, extreme response bias, ordering bias, SDB, and acquiescence bias.
+\#### Defination of the bias
+
+@survey define these bias as:
+
+-   Moderacy response bias is the tendency to respond to each question by choosing a category in the middle of the scale.
+
+-   Extreme response bias is the tendency to respond with extreme values on the rating scale.
+
+-   Response order bias occurs when the order of response options in a list or a rating scale influences the response chosen.
+The primacy effect occurs when respondents are more likely to select one of the first alternatives provided, and it is more common in written surveys.
+This tendency can be due to satisficing, whereby a respondent uses the first acceptable response alternative without paying particular attention to the other options.
+The recency effect occurs when respondents choose one of the last items presented to them (more common in face-to-face or orally presented surveys).
+
+-   Social desirability bias typically stems from the desire of respondents to avoid embarrassment and project a favorable image to others, resulting in respondents not revealing their actual attitudes.
+The prevalence of this bias will depend on the topic, questions, respondent, mode of the survey, and the social context.
+For instance, in some circles, anti-immigrant views are not tolerated, and those who hold them may try to hide them.
+In other settings, people express such views more freely.
+
+-   Acquiescence is the tendency to answer items in a positive way regardless of their content, for instance, systematically selecting categories such as “agree,” “true,” or “yes”.
+
+### Solution to the bias in our survey
+
+To mitigate bias, we enhance our survey in the following ways, drawing on recommendations from @survey:
+
+Addressing Extreme/Moderacy Bias: We customize the scale and response options with differentiated alternatives.
+Three-point answer scales can lead to extreme response bias or moderacy bias due to insufficient options.
+Therefore, for every scale question, we designed at least five response options, which reduces the likelihood of respondents choosing the middle answers because of a lack of alternatives.
+
+Mitigating Response Order Bias: We implement a solution involving seemingly open-ended questions and randomizing the order of response options for unordered (nominal) questions.
+For ordinal questions, we invert the order.
+For example, instead of asking, "Will you choose candidate A or candidate B?" we ask, "Who would you vote for?
+\[pause\] Candidate A or Candidate B?" Additionally, using Google Forms, we randomize the order of options for all unordered questions to further reduce response order bias.
+
+Minimizing Social Desirability Bias (SDB): Given that our survey is conducted online, we employ a minimized SDB format.
+A recommended strategy for recruiting respondents is to provide only basic information about the survey's purpose at the outset, which engages participants without overwhelming them.
+Therefore, in the introduction, we state that the survey aims for academic research in Statistics, omitting details about our affiliations or the specific use of the data.
+We simply inform participants that, "This survey is for nonpartisan researchers in academic research in Statistics." At the end of the survey, we include a feedback section to gauge attitudes toward the surveyor or entity.
+
+Ensuring Anonymity (Minimizing SDB): The complete anonymity of respondents is a crucial aspect of our survey.
+We guarantee this anonymity as stated on the survey landing and consent page.
+Before sensitive questions, we will reinforce that all answers are confidential and anonymous, reminding participants of their privacy.
+We will strategically place sensitive items within the survey to minimize the risk of social desirability bias (SDB).
+
+Reducing Acquiescence Bias: To tackle acquiescence bias, we avoid agree-disagree, true-false, and yes-no question formats.
+Instead of using agree-disagree questions, we formulate inquiries that utilize direct, item-specific scales tailored to the question.
+For instance, when asking for respondents' views on candidates, we use options like "very unfavorable, unfavorable, moderate, favorable, very favorable" instead of simple yes or no.
+Furthermore, we ensure that our questions offer answer options that encompass all possible views.
+For example, in the question "Do you approve or disapprove of the job Joe Biden is doing as President?", we provide the options "Approve, Disapprove, Neutral or no opinion" rather than just yes or no.
 
@@
 ## U.S. Presidential Election Polls Survey
-
----
-title: "U.S. Presidential Election Polls Survey"
-author: "Diana Shen, Jinyan Wei, Jerry Yu"
-date: "`r Sys.Date()`"
-output: pdf_document
----
-
-Welcome
 
@@
     -   Prefer not to say
-    -   Other: __________
+    -   Other: \_\_\_\_\_\_\_\_\_\_
 
@@
     -   Kamala Harris
-    -   Kamala Harris
     -   Donald Trump
@@
     |               | Very unfavorable | Unfavorable | Moderate | Favorable | Very favorable |
-    |---------------|------------------|-------------|----------|-----------|----------------|
+    |------------|------------|------------|------------|------------|------------|
     | Kamala Harris |                  |             |          |           |                |
@@
 10.
-**Imagine the following candidates: Candidate A favors cutting taxes but has a weak stance on climate change, and Candidate B focuses on healthcare but supports increased military spending.
-Who would you vote for?**
+**Imagine the following candidates: Candidate A favors cutting taxes but has a weak stance on climate change, and Candidate B focuses on healthcare but supports increased military spending.Who would you vote for?
+Candidate A or Candidate B?**
 
@@
 
-11. **Imagine two candidates: Candidate A supports education reform but plans to cut social security, and Candidate B focuses on green energy but raises taxes. Who would you vote for?**
+11.
+**Imagine two candidates: Candidate A supports education reform but plans to cut social security, and Candidate B focuses on green energy but raises taxes.
+Who would you vote for?
+Candidate A or Candidate B?**
 
@@
     -   Social Security
-    -   Other: __________
+    -   Other: \_\_\_\_\_\_\_\_\_\_
 
@@
 
-1.  **Do you have any concerns or feedback regarding the survey?**\
+1.  **Do you have any concerns or feedback regarding the survey, surveyor ,or entity?**\
     Your feedback is important to us and will help ensure transparency and trust in the research process.

### 2024-10-27 paper/paper.qmd
updated paper in appendix and reference

@@
 
+## Dataset and Graph Sketches
+
+Sketches depicting both the desired dataset and the graphs generated in this analysis are available in the GitHub Repository `other/sketches`.
+
+## Data Cleaning
+
+The data cleaning process involved filtering data to just high-quality pollsters (i.e numeric_grade >= 3.0) and filter to just Harris (i.e. candidate_name == "Kamala Harris")
+
+## Attribution Statement
+
+This work is licensed under a [Creative Commons Attribution 4.0 International License](https://creativecommons.org/licenses/by/4.0/).
+You are free to share, copy, redistribute, remix, transform, and build upon the material for any purpose, even commercially, as long as you credit the original creation.
+
+> "Title of the Work" by Author Name, licensed under CC BY 4.0.
+
 # Model details {#sec-model-details}
@@
 
-# Appendix
+# The New York Times/Siena College Polling Methodology
 
-## Emerson College Polling Methodology
+This appendix provides a comprehensive overview of the methodology employed by the Siena College Polling Institute in conducting its surveys.Siena College is renowned for its methodologically rigorous approach to political polling, focusing on accurately capturing voter sentiment during elections.
+Siena College has conducted polls in three key states: Michigan, Wisconsin, and Ohio.
 
-For this deep dive, I'll focus on Emerson College Polling based on the link: Emerson College Polling - October 2024 National Poll.
-Survey Overview: The Emerson College Polling conducted a national survey in October 2024 to assess voter preferences for the upcoming U.S.
-presidential election.
-This appendix provides an in-depth analysis of their polling methodology, including the population, sample frame, recruitment process, and key strengths and weaknesses of their approach.
+In this section, we will delve into the key components of Siena's polling methodology, including the target population, sampling frame, recruitment processes, and the sampling strategies used.
+We will also address how non-response is managed and evaluate the strengths and weaknesses of the questionnaire design.
+By exploring these elements, this appendix aims to clarify how Siena College ensures the reliability and validity of its polling results, contributing valuable insights to the understanding of voter behavior and election outcomes.
 
-Methodology 1. Population, Frame, and Sample:\
-Target Population: The target population for this poll includes U.S.
-citizens who are eligible to vote in the 2024 presidential election.
-Sample Frame: The sample consists of likely voters across the United States.
-Emerson College Polling uses voter registration databases to develop a sampling frame of registered voters, ensuring they capture individuals who are most likely to vote in the upcoming election.
-Sample Size: For this particular poll, 1,000 likely voters were surveyed.
-This sample size provides a margin of error of approximately ±3 percentage points, allowing for reasonable confidence in the poll's accuracy.
+## Pollster Overview
 
-2.  Sample Recruitment:\
-    Recruitment Method: Emerson College employs a multi-mode recruitment approach, including online, phone (landline and mobile), and SMS text outreach.
-Phone Interviews: Live interviewers call both landlines and mobile phones using random digit dialing (RDD) to ensure they capture respondents without internet access.
-Online Panels: Emerson also recruits respondents through online panels, using email invitations to individuals who match their demographic quotas.
-SMS Text Polling: In recent years, Emerson has increasingly used SMS text polling, allowing respondents to complete the survey via mobile devices.
+Siena College Polling Institute is a prominent pollster known for its comprehensive and methodologically rigorous surveys.
+It specializes in political polling and is particularly recognized for its work in understanding voter sentiment during elections.
 
-Trade-offs of Recruitment Method:\
-Strengths: The multi-mode approach ensures better coverage of different demographic groups, including older adults and those less likely to engage with online surveys.
-Weaknesses: The RDD approach can lead to lower response rates, especially with the increasing number of people avoiding unsolicited calls.
-The online component also introduces self-selection bias, where more politically engaged individuals may be overrepresented.
+Established in 1980 at Siena College in New York's Capital District, the Siena College Research Institute (SCRI) conducts surveys at regional, state, and national levels on various topics, including business, economics, politics, voter behavior, social issues, academics, and history.
+The institute carries out both expert and public opinion polls.
 
-3.  Sampling Approach and Trade-offs:\
-    Quota-based Sampling: Emerson uses quota sampling to ensure that the sample is representative of key demographics, including age, gender, race, and region.
-The quotas are based on U.S.
-Census data to maintain demographic diversity.
-Weighting: After data collection, Emerson applies post-stratification weighting to adjust for any imbalances in the sample, aligning it with population benchmarks.
-Trade-offs: While quota sampling ensures demographic diversity, it can introduce bias if certain groups are harder to reach or more likely to refuse participation (non-response bias).
-Weighting helps mitigate this issue but relies on accurate population benchmarks, which may not always reflect the electorate’s behavior accurately.
+Students from Siena and other colleges participate in every survey, gaining hands-on experience in fields such as political science, computing, communications, sociology, and psychology.
+SCRI also hires interns for special projects involving event planning, in-depth research, report writing, and analysis.
+The results of SCRI's surveys are featured in major regional and national publications, including The Wall Street Journal and The New York Times, as well as in academic journals, books, and encyclopedias, both in print and online.
+Their findings are regularly highlighted in local and national television and radio broadcasts.
+SCRI conducts the Siena New York Poll, a monthly survey that captures the opinions of registered voters across New York State on current political issues, along with the New York State Index of Consumer Sentiment, which offers a quarterly assessment of New Yorkers' spending intentions.
+SCRI adheres to the American Association of Public Opinion Research (AAPOR) Code of Professional Ethics and Practices.
+The institute is often commissioned to carry out surveys for various organizations, businesses, and local and state government agencies.
+[@aboutsiena]
 
-4.  Non-response Handling:\
-    Non-response Bias: To minimize non-response bias, Emerson College Polling uses a combination of call-backs and reminder emails for online respondents.
-Additionally, post-survey weighting accounts for non-response patterns across key demographic groups.
-Adjustments for Non-response: Emerson uses statistical weighting to adjust the final results based on the response rate within each demographic group (e.g., age, gender, and race).
-This helps to reduce the skew in the data caused by differential response rates.
+## Population, Frame and sample
 
-5.  Questionnaire Design:\
-    Strengths: The survey is concise, focusing on core topics like voter intention, candidate preference, and key issues such as the economy and healthcare.
-This increases the likelihood that respondents complete the survey accurately and without fatigue.
-Emerson regularly tests its questionnaire to ensure clarity and avoid ambiguous questions, improving the reliability of the responses.
-Weaknesses: Binary Choice Bias: Some sections of the questionnaire force a binary choice between two candidates, which may oversimplify the respondents' true preferences, especially in a race with multiple candidates or undecided voters.
-Social Desirability Bias: Like most political polls, respondents may answer questions in a way they believe is socially acceptable, especially in terms of voter turnout or support for controversial candidates.
-This could lead to over-reporting of voter intention.
-Summary of Strengths and Weaknesses Strengths:
+In essence, statistics is about collecting data and making informed conclusions, even though we can never access every piece of information.\
+From @tellingstories, we defined three key terms as:\
+Target population : The collection of all items about which we would like to speak. / The entire group about which we want to draw conclusions\
+Sampling frame : A list of all the items from the target population that we could get data about.\
+Sample : The items from the sampling frame that we get data about.\
 
-Multi-mode Surveying: Emerson’s use of phone, online, and SMS recruitment allows them to reach a broader cross-section of the population, minimizing the biases introduced by any one method.
-Post-stratification Weighting: The weighting process ensures the sample reflects the U.S.
-population, improving the reliability of the poll results.
-Timely Polling: The frequent release of polling data makes it possible to track shifts in voter sentiment over time.
-Weaknesses:
+The target population for Siena’s polls includes registered voters eligible to vote in Michigan, Wisconsin, and Ohio.
+The sampling frame consists of a comprehensive list of registered voters, which includes demographic information for each voter.
+This enables the pollsters to ensure an appropriate representation of voters across various parties, races, and regions [@poll].
+The sample of registered voters sourced from the voter file maintained by L2, a nonpartisan vendor, and supplemented with additional cellular phone numbers matched from Marketing Systems Group.
+The sample for the poll totals 2,055 likely voters, with 688 from Michigan, 687 from Ohio, and 680 from Wisconsin, surveyed from September 21 to 26, 2024.\
 
-Potential for Non-response Bias: Despite efforts to mitigate it, non-response remains a concern, particularly among certain voter demographics who may be harder to reach through phone or online surveys.
-Self-selection Bias in Online Surveys: The online component may disproportionately attract respondents who are more politically engaged, which could skew results.
-By employing a multi-mode approach and adjusting for demographic imbalances through weighting, Emerson College Polling provides robust and timely data.
-However, like all polls, it is subject to limitations, particularly around non-response and self-selection biases​
+## Sample Recruitment
 
-## Idealized Methodology for US Presidential Election Forecast
+Siena use phone poll to recruit sample.
+Telephone polling is a common method for gathering public opinion and assessing voter sentiment by contacting individuals via landlines and mobile phones.
+This approach uses live interviewers to enhance data quality, allowing for clarification and nuanced responses.
+By utilizing random digit dialing or national voter registration databases, researchers can ensure a representative sample across various demographics.
+Despite its effectiveness in reaching diverse audiences quickly, telephone polling must address potential biases, such as nonresponse and shifts in communication habits, to maintain the reliability of its findings.[^1]
 
-This appendix outlines the methodology and design for conducting a U.S.
+[^1]: Phone polls, once considered the gold standard in survey research, now compete with methods like online panels and text messaging.
+Their advantages have diminished due to declining response rates, which increase costs and may affect representativeness, raising concerns about their future viability.
+However, they still effectively reach a random selection of voters quickly, as there is no national email database and postal mail can be slow.
+Other methods, such as recruiting panelists by mail, risk attracting only the most politically engaged individuals.
+Recent elections have shown that telephone polls, including The Times/Siena Poll, continue to perform well due to the reliability of voter registration files in balancing party representation.
+
+According to @freqqa, the polls are conducted by live interviewers at call centers located in Florida, New York, South Carolina, Texas, and Virginia.
+The respondents are randomly selected from a national database of registered voters and are contacted via both landlines and cellphones.
+
+Siena polls are conducted over the phone in both English and Spanish.
+For these polls, interviewers made nearly 260,000 calls to just over 140,000 voters.
+Overall, about 97 percent of respondents were contacted on a cellphone for these polls.
+
+## Sampling Approach
+
+Siena employs a response-rate-adjusted stratified sampling of registered voters sourced from the voter file maintained by L2, a nonpartisan vendor, and supplemented with additional cellular phone numbers matched from Marketing Systems Group.
+The New York Times selected the sample in multiple stages to address differences in telephone coverage, nonresponses, and notable variations in telephone number productivity by state.
+
+Stratified sampling is typically utilized to ensure all strata of the population are represented.
+When considering our population, it typically consists of various groupings.
+These can range from a country being divided into states, provinces, counties, or statistical districts to a university comprising faculties and departments or even demographic characteristics groups among individuals.
+A stratified structure allows us to categorize the population into mutually exclusive and collectively exhaustive sub-populations known as "strata".
+
+Stratification is employed to enhance sampling efficiency and ensure balance within the survey.
+For example, the population of the United States is approximately 335 million, with around 40 million residents in California and roughly half a million in Wyoming.
+In a survey with 10,000 responses, we would expect to receive only about 15 responses from Wyoming, which could complicate any inferences about that state.
+By implementing stratification, we could ensure, for instance, that there are 200 responses from each state.
+Within each state, we could then use random sampling to select individuals for data collection [@tellingstories].
+
+In this scenario, we want to collect the polls from all strata of our target population to balance our poll result.
+The sample was stratified by political party, race, and region, and screened by M.S.G.
+to ensure that the cellular phone numbers were active.
+The Siena College Research Institute conducted the survey, with additional support from various institutions, including ReconMR, the Public Opinion Research Laboratory at the University of North Florida, the Institute for Policy and Opinion Research at Roanoke College, the Center for Public Opinion and Policy Research at Winthrop University in South Carolina, and the Survey Center at the University of New Hampshire.
+Interviewers sought to speak with the individuals listed on the voter file and would terminate the interview if those persons were unavailable.
+Overall, 97 percent of respondents across all four samples were reached via cellular phones.
+
+The survey instrument was translated into Spanish by ReconMR, and bilingual interviewers began in English, following the respondent's preference for either language.
+Among self-reported Hispanics, 11 percent of interviews were conducted in Spanish, with this percentage rising to 15 percent in the weighted sample of registered voters.
+An interview was considered complete for inclusion in the voting questions if the respondent did not drop out after answering the two self-reported variables used for weighting—age and education—and responded to at least one question related to age, education, or presidential candidate preference.
+
+Stratified sampling enhances the representativeness of the sample by ensuring that smaller subgroups, which might otherwise be underrepresented, are adequately included.
+A significant advantage of this method is that it allows for more efficient resource allocation, enabling researchers to target specific groups and gather more insightful data.
+However, this focus can lead to **higher overall costs**, particularly due to the comprehensive data collection and analysis required when sampling large states or countries.
+Additionally, while stratified sampling provides richer insights into the characteristics and opinions of different subgroups, it introduces **complexity in data analysis**, necessitating advanced statistical techniques to interpret the results accurately.
+Consequently, researchers must have sufficient evidence to determine how to weight each stratum appropriately.
+Lastly, if the strata are not well-defined or if there is an imbalance in sampling, it could still result in sampling bias.
+Overall, while stratified sampling offers substantial benefits in terms of representation and analytical depth, it also presents challenges related to complexity, cost, and potential bias if not executed carefully.
+
+## Non-response Bias
+
+An interview was deemed complete for inclusion in the voting preference questions if the respondent stayed engaged in the survey after answering the two self-reported variables used for weighting—age and education—and provided responses to at least one question concerning age, education, or the presidential election candidate reference.
+If these conditions were not met, the interview was recorded as a non-response.
+
+To handle the non-response bias, Siena choose to use weighting adjustments.
+Weighting is like balancing a scale to make sure each group in the survey counts the right amount.
+It changes the importance of each answer depending on how likely people are to skip the survey [@surveylab].
+
+Siena use several steps to address nonresponse bias and ensure the reliability of the results.
+The weighting process was conducted by The Times using the R survey package and involved multiple adjustments.
+Initially, the samples were adjusted for the unequal probability of selection by stratum.
+Subsequently, the first-stage weight was modified to account for the likelihood that a registrant would vote in the 2024 election, based on a model derived from turnout data in the 2020 election.
+
+To create a composition that reflects the likely electorate, the sample was further weighted to match specific targets.
+These targets were developed by aggregating individual-level turnout estimates from the L2 voter file, with categories aligning with those used for registered voters.
+Additionally, the initial likely electorate weight was adjusted to incorporate self-reported voting intentions.
+In this final adjustment, four-fifths of the probability that a registrant would vote in the 2024 election was based on their ex ante modeled turnout score, while one-fifth relied on their self-reported intentions, adjusted for the tendency of survey respondents to have higher turnout rates than nonrespondents.
+
+The final likely electorate weight was calculated by multiplying the modeled electorate rake weight by the final turnout probability and then dividing by the ex ante modeled turnout probability.
+This comprehensive approach to weighting helps mitigate nonresponse bias by ensuring that the sample reflects both the characteristics of the general population and the expected behavior of likely voters.
+As a result, the sample of respondents who completed all questions in the survey was adjusted to accurately represent the likely electorate, enhancing the overall validity of the findings.
+
+## Questionnaire Design
+
+**Strengths**:
+
+The questionnaire is crafted to be concise and straightforward, effectively minimizing respondent fatigue and maximizing clarity in question phrasing.
+This design is essential for maintaining participant engagement, especially in surveys that may include a wide array of questions.
+Additionally, the use of a mix of closed and open-ended formats allows for a comprehensive analysis of voter sentiment.
+Closed-ended questions yield quantifiable data, enabling researchers to identify trends and patterns, while open-ended questions provide rich qualitative insights that contextualize these trends.
+
+The careful structuring of questions also plays a crucial role in reducing moderacy bias, where respondents might lean towards neutral options when unsure.
+By providing clear response categories, the questionnaire encourages participants to express their opinions more decisively.
+Furthermore, the inclusion of diverse question types can mitigate acquiescence bias, which occurs when respondents habitually agree with statements instead of reflecting their true feelings.
+By framing questions in a balanced manner and avoiding leading language, the design helps ensure that participants feel comfortable expressing varied opinions.
+
+**Weaknesses**:
+
+However, the questionnaire is not without its weaknesses.
+Critics highlight that the reliance on agree-disagree formats can lead to acquiescence bias, where respondents might select favorable options rather than accurately expressing their true opinions.
+This tendency skews the results, potentially misrepresenting genuine voter sentiment and leading to misleading conclusions.
+
+Moreover, the questionnaire may not adequately address the nuances that are important to specific demographic groups, resulting in potential gaps in understanding voter motivations.
+For instance, certain groups may have distinct issues or concerns that are not adequately captured by the survey's questions.
+This limitation can contribute to nonresponse bias, where individuals from underrepresented groups choose not to participate or drop out of the survey, further skewing the results.
+
+Additionally, the structure of the questions could inadvertently create extreme response bias, where participants feel pressured to choose the most extreme options rather than selecting a moderate stance.
+This bias can be exacerbated by the order in which questions are presented.
+If respondents encounter highly charged or leading questions early in the survey, they may be influenced to respond similarly in subsequent questions, a phenomenon known as ordering bias.
+
+Furthermore, while the questionnaire aims to be inclusive, if it fails to adequately represent the voices of certain demographic groups, it could lead to a lack of adequacy in the data collected.
+This inadequacy undermines the ability to draw comprehensive conclusions about the electorate, particularly in a diverse political landscape.
+
+In summary, while the questionnaire design has strengths in clarity and mixed-format questions that encourage engagement and nuanced responses, it also faces challenges related to biases such as acquiescence, nonresponse, extreme response tendencies, and ordering effects.
+To enhance its effectiveness, future iterations of the questionnaire should strive to incorporate more varied question types, ensure demographic representation, and remain mindful of question order and phrasing to minimize the potential for bias and improve the overall validity of the findings.
+
+# Idealized Methodology for US Presidential Election Forecast
+
+This appendix details the methodology and design for conducting a U.S.
 presidential election forecast survey with a budget of \$100,000.
-The goal is to develop an accurate and reliable prediction of the election outcome, ensuring data quality through careful sampling, recruitment, validation, and aggregation of results.\
+The objective is to generate an accurate and reliable prediction of the election outcome while ensuring data quality through meticulous sampling, recruitment, validation, and aggregation of results.\
 
-### Sampling Approach
+## Sampling Approach
 
-To ensure a representative sample of likely voters, I will use a Composite Measure sampling method based on the past voter turnout data from the U.S.
-previous 2020 elections.After decising the sampling size in each state, I will use a stratified sampling bases on demographics,dividing population into subgroups, and a random sample is taken from each subgroup.
-We employ composite Measure sampling method refer from (), that increased our chances of selecting respondents from voters in states/ regions that have historically higher voter engagement as compared to the natural distribution we’d expect from the general population.
-While some states may have larger populations, we are interested in adjusting the sampling to reflect higher turnout rates.
-To better explain this composite measure of size, lets consider that we have two states that have similar population.
-For example, even though State A and State B may have similar populations, if State B consistently has a higher voter turnout in past elections, we want to increase the proportion of polls we conduct in State B.
-State A has a population of 1 million eligible voters, with a historical turnout rate of 50%.
-State B has a population of 1 million eligible voters, but its turnout rate is 70%.
-In a purely population-based sampling approach, each state would have an equal chance of being selected for polls: 50% for State A and 50% for State B.
-However, based on voter turnout, we modify these probabilities to increase the chance of selecting State B, since its voter turnout is historically higher.\
-In following steps, we will explore how to use **voter turnout** as a key factor to create a **composite measure of size** for sampling US election polls.
-Instead of using population size alone, we adjust the sample allocation based on historical voter turnout, ensuring regions with higher engagement are more heavily represented in our polling data.\
+To ensure a representative sample of likely voters, I will employ a Composite Measure sampling method based on past voter turnout data from the 2020 U.S.
+elections.
+After determining the sample size for each state, I will use stratified sampling based on demographics, dividing the population into subgroups and taking random samples from each subgroup.
+This Composite Measure sampling approach, as referenced in @india, enhances our chances of selecting respondents from states or regions that have historically exhibited higher voter engagement compared to the general population distribution.
+While some states may have larger populations, we aim to adjust the sampling to reflect higher turnout rates.
 
-#### Step 1: Define the Sampling Data
+To illustrate this Composite Measure of size, consider two states with similar populations.
+For instance, although State A and State B both have 1 million eligible voters, State B consistently shows a higher voter turnout in past elections.
+Therefore, we will increase the proportion of polls conducted in State B.
+In this scenario, State A has a historical turnout rate of 50%, while State B has a turnout rate of 70%.
+In a purely population-based sampling approach, both states would have an equal chance of being selected for polls: 50% for State A and 50% for State B.
+However, by incorporating voter turnout, we modify these probabilities to increase the likelihood of selecting State B due to its higher historical turnout.
+
+In the subsequent steps, we will detail how to utilize **voter turnout** as a crucial factor in creating a **composite measure of size** for sampling U.S.
+election polls.
+Rather than relying solely on population size, we will adjust the sample allocation based on historical voter turnout, ensuring that regions with higher engagement are more prominently represented in our polling data.
+
+### Step 1: Define the Sampling Data
 
@@
 
-#### Step 2: Calculate Actual Voters
+### Step 2: Calculate Actual Voters
 
@@
 
-#### Step 3: Calculate Composite Measure of Size
+### Step 3: Calculate Composite Measure of Size
 
@@
 
-#### Step 4: Allocate Sample Based on Turnout
+### Step 4: Allocate Sample Based on Turnout
 
@@
 
-### Target Population
+### Stratification Variables
+
+After determining the number of respondents to be sampled from each region, stratified sampling will be employed across key demographic categories, including age, gender, race/ethnicity, and education level.
+This approach ensures that the final sample accurately reflects the diversity of the U.S.
+voting population by proportionally representing each subgroup within every region.
+To mitigate potential non-response bias, post-stratification weighting[^2] will be applied, correcting for any imbalances caused by variations in response rates among different demographic groups.
+The sample will be stratified based on several critical demographic and geographic variables to guarantee proportional representation of the U.S.
+voting population.
+Strata information will be sourced from U.S.
+census data obtained through IPUMS USA [@ruggles2024ipums].
+
+These variables include age, with categories such as 18-24 (12%), 25-34 (17%), 35-44 (16%), 45-54 (16%), 55-64 (16%), and 65+ (23%); gender, split into male (48%), female (52%), and non-binary/other (less than 1%); and race/ethnicity, covering groups like White/Caucasian (67%), Black/African American (13%), Hispanic/Latino (13%), Asian/Pacific Islander (5%), Native American/Alaskan Native (1%), and Other/Mixed Race (1%).
+Additionally, education level will be stratified into high school diploma or less (36%), some college, no degree (17%), Associate’s degree (9%), Bachelor’s degree (23%), and graduate or professional degree (15%).
+Geographic region will also be a key factor, ensuring representation from the Midwest (21%), Northeast (17%), South (38%), and West (24%).
+For each variable, U.S.
+Census or voter turnout data will be used to proportionally allocate respondents, ensuring that the final sample closely mirrors the demographic and regional composition of the actual voting population.
+Post-stratification weighting will be applied to adjust for any imbalances that may occur during data collection.
+
+[^2]: Post-stratification weighting adjusts survey data by applying weights to under- or over-represented demographic groups in the sample, ensuring the final results align with the true population distribution and reducing biases such as non-response bias.
+
+## Target Population
 
@@
 
-### Sample frame
+## Sample frame
 
@@
 
-### Sample
-
-#### Sample Size:
+## Sample
 
@@
 | **Region**    | **States**                                                                                                                                                 |
-|----------------------|--------------------------------------------------|
+|------------------------|------------------------------------------------|
 | **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
@@
 
-@tbl-samplesize shows the regional breakdown of the 2020 election data, sourced from [@wiki], including voter turnout, total ballots cast, and Voting Eligible Population (VEP).
-The sample size for each region was determined based on the **Composite Measure Sampling Proportion**.
+@tbl-samplesize shows the regional breakdown of the 2020 election data, sourced from [@wikivote], including voter turnout, total ballots cast, and Voting Eligible Population (VEP).
+The sample size for each region shown in @tbl-samplesize was determined based on the **Composite Measure Sampling Proportion**.
 
-**Stratification Variables**: After determining the number of respondents to be sampled from each region, stratified sampling will be applied across key demographic categories such as age, gender, race/ethnicity, and education level.
-This approach helps ensure that the final sample accurately reflects the diversity of the U.S.
-voting population by proportionally representing each subgroup within each region.
-To address potential non-response bias, post-stratification weighting[^1] will be applied, adjusting for any imbalances caused by differences in response rates across demographic groups.
-The sample will be stratified across several key demographic and geographic variables to ensure proportional representation of the U.S.
-voting population.
-These variables include age, with categories such as 18-24 (12%), 25-34 (17%), 35-44 (16%), 45-54 (16%), 55-64 (16%), and 65+ (23%); gender, split into male (48%), female (52%), and non-binary/other (less than 1%); and race/ethnicity, covering groups like White/Caucasian (67%), Black/African American (13%), Hispanic/Latino (13%), Asian/Pacific Islander (5%), Native American/Alaskan Native (1%), and Other/Mixed Race (1%).
-Additionally, education level will be stratified into high school diploma or less (36%), some college, no degree (17%), Associate’s degree (9%), Bachelor’s degree (23%), and graduate or professional degree (15%).
-Geographic region will also be a key factor, ensuring representation from the Midwest (21%), Northeast (17%), South (38%), and West (24%).
-For each variable, U.S.
-Census or voter turnout data will be used to proportionally allocate respondents, ensuring that the final sample closely mirrors the demographic and regional composition of the actual voting population.
-Post-stratification weighting will be applied to adjust for any imbalances that may occur during data collection.
-
-[^1]: Post-stratification weighting adjusts survey data by applying weights to under- or over-represented demographic groups in the sample, ensuring the final results align with the true population distribution and reducing biases such as non-response bias.
-
-#### Recruitment of Respondents
+## Recruitment of Respondents
 
@@
 
-#### Respondent Validation
+## Handling Non-response bias
+
+Nonresponse bias occurs when participants are unwilling or unable to respond to specific questions or complete the entire survey.
+For example, since our survey takes about 15 minutes to finish, there is a potential for nonresponse bias to arise.
+To address this concern, as highlighted by @surveymonkey, we strive to establish clear expectations regarding the survey's objectives and the estimated time required for completion.
+Furthermore, we utilize post-stratification, which changes the survey weights to make sure the group that answered fits well with the actual population characteristics [@surveylab].
+
+## Respondent Validation
 
@@
 
-### Poll Aggregation
+## Poll Aggregation
 
@@
 
-### Survey Design
+## Survey Design
 
@@
 In our survey, several questions are adapted from the Emerson College Polling data [@emerson].
-We also apply insights from @survey to minimize response biases.
-Common biases identified in survey design include moderacy bias, extreme response bias, ordering bias, acquiescence bias, experimenter demand effect (EDE), and social desirability bias (SDB).
+We apply insights from @survey to minimize response biases.
+Common response biases identified in survey design include moderacy bias, extreme response bias, ordering bias, acquiescence bias, experimenter demand effect (EDE), and social desirability bias (SDB).
 Our survey primarily focuses on strategies to reduce moderacy bias, extreme response bias, ordering bias, SDB, and acquiescence bias.
-\#### Defination of the bias
+
+### Defination of the response bias
 
@@
 
-### Solution to the bias in our survey
+### Solution to the response bias in our survey
 
@@
 
-### Budget Breakdown
+## Budget Breakdown
 
@@
 
-## U.S. Presidential Election Polls Survey
+## Copy of U.S. Presidential Election Polls Survey
 
@@
 For any questions or concerns regarding this survey, please contact:\
-**Email:** diana.shen\@mail.utoronto.ca
+**Email:**  diana.shen\@mail.utoronto.ca; jinyan.wei\@mail.utoronto.ca; huayan.yu\@mail.utoronto.ca
 

### 2024-10-27 scripts/03-clean_data.R
Updated Scripts

@@ -1,44 +1,54 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw polling data for the 2024 U.S. presidential election and prepares it for multi-level regression with post-stratification (MRP) analysis
+# Author: [Your Name]
+# Date: [Today's Date]
+# Contact: [Your Email]
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Ensure the raw data file `president_polls_1027.csv` is located in the `data/01-raw_data/` directory, and that necessary packages are installed.
 
 #### Workspace setup ####
 library(tidyverse)
+library(janitor)
+library(lubridate)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+# Load the raw polling data
+raw_data <- read_csv("data/01-raw_data/president_polls.csv")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
+#### Clean data ####
+cleaned_data <- 
+  raw_data %>%
+  clean_names() %>%
+  # Select relevant columns for analysis
+  select(
+    pollster, numeric_grade, state, candidate_name, pct, sample_size, 
+    population, methodology, start_date, end_date
+  ) %>%
+  # Filter for Kamala Harris only, as we're interested in her percentage support
+  filter(candidate_name == "Kamala Harris") %>%
+  # Drop rows with missing values in essential columns
+  drop_na(numeric_grade, pct, sample_size, end_date) %>%
+  # Standardize state names and handle national vs. state-specific polls
   mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
[…]

### 2024-10-27 scripts/05-model_data.R

@@ -1,0 +1,95 @@
+#### Preamble ####
+# Purpose: Model Harris's support in the 2024 U.S. presidential election using weighted and unweighted linear models.
+# Author: [Your Name]
+# Date: [Today's Date]
+# Contact: [Your Email]
+# License: MIT
+# Pre-requisites: Cleaned data file `cleaned_harris_support.csv` should be available in the `data/02-analysis_data/` directory.
+
+#### Workspace setup ####
+library(dplyr)
+library(ggplot2)
+library(lubridate)
+
+#### Step 1: Load cleaned data ####
+data <- read.csv("data/02-analysis_data/cleaned_harris_support.csv")
+
+# Ensure `end_date` exists and is in Date format or set it to today's date if missing
+if (!"end_date" %in% names(data)) {
+  data$end_date <- Sys.Date()
+} else {
+  data$end_date <- as.Date(data$end_date)
+}
+data <- data %>% filter(!is.na(end_date))
+
+#### Step 2: Calculate weights ####
+# 2.1 Recency Weight
+data <- data %>%
+  mutate(
+    days_since_poll = as.numeric(difftime(Sys.Date(), end_date, units = "days")),
+    recency_weight = ifelse(days_since_poll < 30, exp(-days_since_poll / 15), exp(-days_since_poll / 30))
+  )
+
+# 2.2 Sample Size Weight (cap at 2,300 responses)
+data <- data %>%
+  mutate(sample_size_weight = pmin(sample_size / 2300, 1))
+
+# 2.3 Poll Frequency by Pollster
+data <- data %>%
+  group_by(pollster) %>%
+  mutate(
+    recent_poll_count = sum(days_since_poll < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
+  ) %>%
+  ungroup()
+
+# 2.4 Pollster Quality Weight
+data <- data %>%
+  mutate(pollster_quality_weight = numeric_grade / 4)
+
+
+# 2.5 Combined Weight
+data <- data %>%
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+
+# Verify combined weight creation
+if (!"combined_weight" %in% names(data)) {
+  stop("Error: `combined_weight` was not created successfully.")
+}
+
+#### Step 3: Model preparation ####
+# Filter to ensure no missing values in key columns
[…]

### 2024-10-27 scripts/02-download_data.R
update with scripts

@@ -27,5 +27,5 @@ write_csv(
   file = "~/2024 US Election Forecast/data/01-raw_data/raw_election_24.csv"
 )
 
-head(toronto_shelters)
-
+head(raw_elections_data)
+raw_elections_data<-read.csv("~/2024 US Election Forecast/data/01-raw_data/raw_election_24.csv")

### 2024-10-27 scripts/03-clean_data.R

@@ -1,44 +1,76 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw poll data recorded
+# Author: Diana Shen, Jinyan Wei, Huayan Yu
+# Date: 27 Octobor 2024 
+# Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: not needed
+# Any other information needed? not needed
 
 #### Workspace setup ####
 library(tidyverse)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+raw_data <- read_csv("data/01-raw_data/raw_election_24.csv")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
+cleaned_data <- raw_data |>
+  clean_names()
+summary(cleaned_data)##check summary statistics of raw cleaned data
+# Filter data to Harris estimates based on high-quality polls after she declared
+just_harris_high_quality <- cleaned_data |>
+  # Select relevant columns for analysis
+  select(
+    pollster, numeric_grade, state, candidate_name, pct, sample_size, 
+    population, methodology, start_date, end_date
+  )|>
+  # Drop rows with missing values in essential columns
+  drop_na(numeric_grade, pct, sample_size, end_date)|>
+  filter(
+    candidate_name == "Kamala Harris",
+    numeric_grade >= 2 # mean of numeric_gradeis 2.175, median is 1.9 
   ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
[…]

### 2024-10-27 scripts/03-clean_data.R
change clean scripts

@@ -30,21 +30,24 @@ just_harris_high_quality <- cleaned_data |>
     numeric_grade >= 2 # mean of numeric_gradeis 2.175, median is 1.9 
   ) |>
   mutate(
-    state = if_else(is.na(state), "National", state), # Hacky fix for national polls - come back and check
+    state = if_else(state == "--", NA_character_, state),
+    national_poll = if_else(is.na(state), 1, 0)  # 1 for national, 0 for state-specific
   ) |> mutate(
     start_date = mdy(start_date),
     end_date = mdy(end_date)
   )|>
-  filter(end_date >= as.Date("2024-07-21")) |> # When Harris declared
+  # Calculate recency weight using exponential decay (more recent polls get higher weight)
   mutate(
-    num_harris = round((pct / 100) * sample_size, 0) # Need number not percent for some models
-  )|>
-mutate(sample_size_weight = pmin(sample_size / 2300, 1)) |>
+    days_since_poll = as.numeric(difftime(Sys.Date(), end_date, units = "days")),
+    recency_weight = exp(-days_since_poll / 30)  # Adjust decay rate as needed
+  ) |>
+  # Apply sample size weight, capped at a maximum of 2,300 responses
+  mutate(sample_size_weight = pmin(sample_size / 2300, 1)) |>
   # Finalize relevant columns for modeling and remove unneeded columns
   select(pollster, numeric_grade, state, pct, sample_size, 
          population, methodology, recency_weight, sample_size_weight, national_poll)
 
-just_trump_high_quality <- cleaned_data cleaned_data |>
+just_trump_high_quality <- cleaned_data|>
   # Select relevant columns for analysis
   select(
     pollster, numeric_grade, state, candidate_name, pct, sample_size, 
@@ -53,24 +56,26 @@ just_trump_high_quality <- cleaned_data cleaned_data |>
   # Drop rows with missing values in essential columns
   drop_na(numeric_grade, pct, sample_size, end_date)|>
   filter(
-    candidate_name == "Donald Trump",
+    candidate_name == "Donal Trump",
     numeric_grade >= 2 # mean of numeric_gradeis 2.175, median is 1.9 
   ) |>
   mutate(
-    state = if_else(is.na(state), "National", state), # Hacky fix for national polls - come back and check
+    state = if_else(state == "--", NA_character_, state),
+    national_poll = if_else(is.na(state), 1, 0)  # 1 for national, 0 for state-specific
   ) |> mutate(
[…]

### 2024-10-27 scripts/03-clean_data.R
Update 03-clean_data.R

@@ -1,10 +1,11 @@
 #### Preamble ####
-# Purpose: Cleans the raw polling data for the 2024 U.S. presidential election and prepares it for multi-level regression with post-stratification (MRP) analysis
-# Author: [Your Name]
-# Date: [Today's Date]
-# Contact: [Your Email]
+# Purpose: Cleans the raw poll data recorded
+# Author: Diana Shen, Jinyan Wei, Huayan Yu
+# Date: 27 October 2024 
+# Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Ensure the raw data file `president_polls_1027.csv` is located in the `data/01-raw_data/` directory, and that necessary packages are installed.
+# Pre-requisites: not needed
+# Any other information needed? not needed
 
 #### Workspace setup ####
 library(tidyverse)
@@ -12,43 +13,72 @@ library(janitor)
 library(lubridate)
 
 #### Clean data ####
-# Load the raw polling data
-raw_data <- read_csv("data/01-raw_data/president_polls.csv")
+raw_data <- read_csv("data/01-raw_data/raw_election_24.csv")
 
-#### Clean data ####
-cleaned_data <- 
-  raw_data %>%
-  clean_names() %>%
+cleaned_data <- raw_data |>
+  clean_names()
+summary(cleaned_data)##check summary statistics of raw cleaned data
+
+# Filter data to Harris estimates based on high-quality polls after she declared
+just_harris_high_quality <- cleaned_data |>
   # Select relevant columns for analysis
   select(
     pollster, numeric_grade, state, candidate_name, pct, sample_size, 
     population, methodology, start_date, end_date
-  ) %>%
-  # Filter for Kamala Harris only, as we're interested in her percentage support
-  filter(candidate_name == "Kamala Harris") %>%
+  )|>
   # Drop rows with missing values in essential columns
-  drop_na(numeric_grade, pct, sample_size, end_date) %>%
-  # Standardize state names and handle national vs. state-specific polls
+  drop_na(numeric_grade, pct, sample_size, end_date)|>
+  filter(
+    candidate_name == "Kamala Harris",
+    numeric_grade >= 2 # mean of numeric_gradeis 2.175, median is 1.9 
+  ) |>
   mutate(
     state = if_else(state == "--", NA_character_, state),
[…]

### 2024-10-27 paper/paper.qmd
update with scripts
update appendix B and C

@@
 
-The data cleaning process involved filtering data to just high-quality pollsters (i.e numeric_grade >= 3.0) and filter to just Harris (i.e. candidate_name == "Kamala Harris")
+In this data-cleaning process, we focus on refining raw polling data to enhance its quality and relevance for subsequent analysis.
+The dataset is first loaded and cleaned using the janitor package to standardize column names, ensuring consistency.
+We then filter the data to include only relevant columns and remove any rows with missing values in critical fields such as numeric_grade, pct, sample_size, and end_date.
+Specifically, we isolate the polling data for Kamala Harris and Donald Trump, applying a condition to keep only high-quality polls with a numeric grade of 2 or higher since we find out that the mean of the numeric grade is 2.175 while the median is 1.9.
+
+For state-level polls, we address any placeholder states marked as "--" by converting them to NA.
+A national poll indicator is created, assigning a value of 1 for national polls and 0 for state-specific ones.
+Dates are converted to a standard format using the lubridate package to ensure correct handling in analyses.
+We calculate recency weights based on how many days have passed since the poll ended, applying an exponential decay to give more weight to recent polls.
+A sample size weight is also implemented, capping the weights at a maximum of 2,300 responses to reflect the reliability of larger sample sizes[@nyt_polling_averages].
+Finally, the cleaned datasets for both candidates are saved in CSV format for further modeling and analysis.
+This systematic approach ensures that the data is accurate, complete, and ready for insightful analysis.
+
+## Analysis Data Summary Statistics
+
+@tbl-analysisdata presents the summary statistics for each recorded incident type for the years 2017 to 2022.
 

### 2024-10-28 paper/paper.qmd
update appendix B

@@
 
-# The New York Times/Siena College Polling Methodology
+# The New York Times/Siena College Polling Methodology {#third-poll}
 
@@
 
+### Response bias defination
+
+In the design of the questionnaire, there will be some common bias that may occur when running the questionnaire.
+
+@survey define these bias as:
+
+-   Moderacy response bias is the tendency to respond to each question by choosing a category in the middle of the scale.
+
+-   Extreme response bias is the tendency to respond with extreme values on the rating scale.
+
+-   Response order bias occurs when the order of response options in a list or a rating scale influences the response chosen.
+The primacy effect occurs when respondents are more likely to select one of the first alternatives provided, and it is more common in written surveys.
+This tendency can be due to satisficing, whereby a respondent uses the first acceptable response alternative without paying particular attention to the other options.
+The recency effect occurs when respondents choose one of the last items presented to them (more common in face-to-face or orally presented surveys).
+
+-   Social desirability bias typically stems from the desire of respondents to avoid embarrassment and project a favorable image to others, resulting in respondents not revealing their actual attitudes.
+The prevalence of this bias will depend on the topic, questions, respondent, mode of the survey, and the social context.
+For instance, in some circles, anti-immigrant views are not tolerated, and those who hold them may try to hide them.
+In other settings, people express such views more freely.
+
+-   Acquiescence is the tendency to answer items in a positive way regardless of their content, for instance, systematically selecting categories such as “agree,” “true,” or “yes”.
+
+### Strengths and Weakness
+
 **Strengths**:
@@
 By providing clear response categories, the questionnaire encourages participants to express their opinions more decisively.
+For each of the degree question, Siena designed at least 4 options to help the respondents not only choose extreme or moderate answer in the question.
+
 Furthermore, the inclusion of diverse question types can mitigate acquiescence bias, which occurs when respondents habitually agree with statements instead of reflecting their true feelings.
@@
 However, the questionnaire is not without its weaknesses.
-Critics highlight that the reliance on agree-disagree formats can lead to acquiescence bias, where respondents might select favorable options rather than accurately expressing their true opinions.
+Critics highlight that the reliance on agree-disagree, yes-no formats can lead to acquiescence bias, where respondents might select favorable options rather than accurately expressing their true opinions.
 This tendency skews the results, potentially misrepresenting genuine voter sentiment and leading to misleading conclusions.
@@
 
-Additionally, the structure of the questions could inadvertently create extreme response bias, where participants feel pressured to choose the most extreme options rather than selecting a moderate stance.
-This bias can be exacerbated by the order in which questions are presented.
-If respondents encounter highly charged or leading questions early in the survey, they may be influenced to respond similarly in subsequent questions, a phenomenon known as ordering bias.
+Additionally, since we don’t know whether they use randomization when interviewers ask the respondents, there might be response order bias with the occurrence of recency effect, in which respondents choose one of the last items presented to them ( as telephone survey is orally presented surveys).
+This bias can be exacerbated by the order of response options in a list or a rating scale influences the response chosen [@survey].
 
-Furthermore, while the questionnaire aims to be inclusive, if it fails to adequately represent the voices of certain demographic groups, it could lead to a lack of adequacy in the data collected.
-This inadequacy undermines the ability to draw comprehensive conclusions about the electorate, particularly in a diverse political landscape.
+Furthermore, as the questionnaire hasn't been provided, we haven't found an assured of complete anonymity in the survey landing and consent page (record of interviewers' words) in the posted questionnaire.
+This might cause social desirability bias, which typically stems from the desire of respondents to avoid embarrassment and project a favorable image to others, resulting in respondents not revealing their actual attitudes.
+Thus Siena cannot get the true polls from their sample.
 
-In summary, while the questionnaire design has strengths in clarity and mixed-format questions that encourage engagement and nuanced responses, it also faces challenges related to biases such as acquiescence, nonresponse, extreme response tendencies, and ordering effects.
-To enhance its effectiveness, future iterations of the questionnaire should strive to incorporate more varied question types, ensure demographic representation, and remain mindful of question order and phrasing to minimize the potential for bias and improve the overall validity of the findings.
+Finally, we noticed that the questionnaire is quite long, with more than 50 questions.
+It will significantly increase the attribution rate of the questionnaires, especially in a telephone survey which takes more time than the online panel.
+This will increase the possibility of the occurrence of non-response bias.
+
+In summary, the questionnaire exhibits strengths such as clarity and a mixed-format approach that promotes engagement and nuanced responses.
+However, it faces significant challenges related to biases including acquiescence, nonresponse, social desirability, and ordering effects.
+To enhance its effectiveness, future iterations should incorporate a broader range of question types, ensure demographic representation, and carefully consider question order and phrasing.
+Addressing these issues is crucial for minimizing bias and improving the overall validity of the findings.
 
@@
 
+[^2]: Post-stratification weighting adjusts survey data by applying weights to under- or over-represented demographic groups in the sample, ensuring the final results align with the true population distribution and reducing biases such as non-response bias.
+
 These variables include age, with categories such as 18-24 (12%), 25-34 (17%), 35-44 (16%), 45-54 (16%), 55-64 (16%), and 65+ (23%); gender, split into male (48%), female (52%), and non-binary/other (less than 1%); and race/ethnicity, covering groups like White/Caucasian (67%), Black/African American (13%), Hispanic/Latino (13%), Asian/Pacific Islander (5%), Native American/Alaskan Native (1%), and Other/Mixed Race (1%).
@@
 Post-stratification weighting will be applied to adjust for any imbalances that may occur during data collection.
-
-[^2]: Post-stratification weighting adjusts survey data by applying weights to under- or over-represented demographic groups in the sample, ensuring the final results align with the true population distribution and reducing biases such as non-response bias.
 
@@
 | **Region**    | **States**                                                                                                                                                 |
-|------------------------|------------------------------------------------|
+|------------------------|-----------------------------------------------|
 | **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
@@
 
-@survey define these bias as:
-
--   Moderacy response bias is the tendency to respond to each question by choosing a category in the middle of the scale.
-
--   Extreme response bias is the tendency to respond with extreme values on the rating scale.
-
--   Response order bias occurs when the order of response options in a list or a rating scale influences the response chosen.
-The primacy effect occurs when respondents are more likely to select one of the first alternatives provided, and it is more common in written surveys.
-This tendency can be due to satisficing, whereby a respondent uses the first acceptable response alternative without paying particular attention to the other options.
-The recency effect occurs when respondents choose one of the last items presented to them (more common in face-to-face or orally presented surveys).
-
--   Social desirability bias typically stems from the desire of respondents to avoid embarrassment and project a favorable image to others, resulting in respondents not revealing their actual attitudes.
-The prevalence of this bias will depend on the topic, questions, respondent, mode of the survey, and the social context.
-For instance, in some circles, anti-immigrant views are not tolerated, and those who hold them may try to hide them.
-In other settings, people express such views more freely.
-
--   Acquiescence is the tendency to answer items in a positive way regardless of their content, for instance, systematically selecting categories such as “agree,” “true,” or “yes”.
+We have defined the bias we want to solve in [Appendix C](#third-poll).
 

### 2024-10-28 paper/paper.qmd
edit on model justification

--- 2024-10-27 paper/paper.qmd
@@
 bibliography: references.bib
+editor: 
+  markdown: 
+    wrap: 72
 ---
@@
 
-Election forecasting has long played a crucial role in understanding public opinion and predicting the outcome of political contests.
-The use of data-driven methods, particularly polling data, has become an important pre-election analytical tool for political analysts.
-The purpose of this paper is to predict the winner of the upcoming 2024 U.S.
-presidential election by constructing a statistical model based on aggregated polling data.
-The “polling” approach combines results from different pollsters to provide a more comprehensive picture of voter preferences (Blumenthal 2014; Pasek 2015), and our goal is to predict the outcome of the popular vote and the Electoral College.
-Our analysis, based on data collected from multiple polling sources, captures voter intentions for the two major candidates, Kamala Harris (Democrat) and Donald Trump (Republican).
-
-In addition to constructing and interpreting predictive models, this paper dive into the methods used by xx pollsters, analyzing the strengths as well as the weaknesses of the methods used against them.
-At the end of the paper, we also propose an idealized survey methodology for election forecasting with a budget of \$100,000 USD.
-
-This paper begins with an introduction to data in Section 2.
-In this section, we focus on measurement techniques and the visualization and analysis of key variables.
-Next, in Section 3, we provide an overview of the linear model used to analyze the relationships within the dataset.
+Election forecasting has long played a crucial role in understanding
+public opinion and predicting the outcome of political contests. The use
+of data-driven methods, particularly polling data, has become an
+important pre-election analytical tool for political analysts. The
+purpose of this paper is to predict the winner of the upcoming 2024 U.S.
+presidential election by constructing a statistical model based on
+aggregated polling data. The “polling” approach combines results from
+different pollsters to provide a more comprehensive picture of voter
+preferences (Blumenthal 2014; Pasek 2015), and our goal is to predict
+the outcome of the popular vote and the Electoral College. Our analysis,
+based on data collected from multiple polling sources, captures voter
+intentions for the two major candidates, Kamala Harris (Democrat) and
+Donald Trump (Republican).
+
+In addition to constructing and interpreting predictive models, this
+paper dive into the methods used by xx pollsters, analyzing the
+strengths as well as the weaknesses of the methods used against them. At
+the end of the paper, we also propose an idealized survey methodology
+for election forecasting with a budget of \$100,000 USD.
+
+This paper begins with an introduction to data in Section 2. In this
+section, we focus on measurement techniques and the visualization and
+analysis of key variables. Next, in Section 3, we provide an overview of
+the linear model used to analyze the relationships within the dataset.
 The results of the analysis are detailed in Section 4 (Results).
-Finally, in Section 5, we summarize our main conclusions as well as suggest some possible future research directions.
+Finally, in Section 5, we summarize our main conclusions as well as
+suggest some possible future research directions.
 
@@
 
-The data for this paper was sourced from ABC News (xxxxx).
-The statistical software R (R Core Team, 2023) was employed to retrieve, clean, and process the dataset.
-Specifically, the tidyverse package (Wickham et al., 2019) was used for data acquisition, cleaning, and processing.
-The ggplot2 (Wickham, 2016) package was utilized to generate the visualizations.
+The data for this paper was sourced from ABC News (xxxxx). The
+statistical software R (R Core Team, 2023) was employed to retrieve,
+clean, and process the dataset. Specifically, the tidyverse package
+(Wickham et al., 2019) was used for data acquisition, cleaning, and
+processing. The ggplot2 (Wickham, 2016) package was utilized to generate
+the visualizations.
 
@@
 
-The data used to predict the outcome of the 2024 U.S.
-presidential election in this study came from a variety of polling sources.
-The results of these polls represent key measures of electoral support and voter sentiment, and are therefore the main variables in our analysis.
-
-To ensure that polling data accurately reflect real-world voter preferences, we rely on several key measurement constructs.
-First, voter preferences are measured by the percentage of respondents who indicated support for each candidate.
-Each poll is conducted using different sample sizes, sampling methods (e.g., online surveys, IVR calls, etc.), which can inject more variability into the data.
-To mitigate these differences, we aggregate poll results using a “”poll of polls“” methodology that eliminates anomalies and provides a more comprehensive picture of voter preferences (Blumenthal 2014; Pasek 2015).
-
-In this study, we recognize the measurement problems inherent in polling data.
-Polls rely on sample data to represent the entire voting population, and therefore, there may be potential biases in the data.
-For example, there may be no-response bias due to the potential under representation of certain populations, or because of the wording of the questions and thus the influence of respondents to report their preferences.
-Therefore, in this study, we chose to analyze aggregated data from multiple pollsters and adjust for sampling variability and response rates in an effort to be able to provide a more robust measure of electoral support.
-We believe that our aggregated dataset can serve as a reliable basis for our predictive model to help us translate the data into quantitative metrics that can be used to predict election outcomes.
+The data used to predict the outcome of the 2024 U.S. presidential
+election in this study came from a variety of polling sources. The
+results of these polls represent key measures of electoral support and
+voter sentiment, and are therefore the main variables in our analysis.
+
+To ensure that polling data accurately reflect real-world voter
+preferences, we rely on several key measurement constructs. First, voter
+preferences are measured by the percentage of respondents who indicated
+support for each candidate. Each poll is conducted using different
+sample sizes, sampling methods (e.g., online surveys, IVR calls, etc.),
+which can inject more variability into the data. To mitigate these
+differences, we aggregate poll results using a “”poll of polls“”
+methodology that eliminates anomalies and provides a more comprehensive
+picture of voter preferences (Blumenthal 2014; Pasek 2015).
+
+In this study, we recognize the measurement problems inherent in polling
+data. Polls rely on sample data to represent the entire voting
+population, and therefore, there may be potential biases in the data.
+For example, there may be no-response bias due to the potential under
+representation of certain populations, or because of the wording of the
+questions and thus the influence of respondents to report their
+preferences. Therefore, in this study, we chose to analyze aggregated
+data from multiple pollsters and adjust for sampling variability and
+response rates in an effort to be able to provide a more robust measure
+of electoral support. We believe that our aggregated dataset can serve
+as a reliable basis for our predictive model to help us translate the
+data into quantitative metrics that can be used to predict election
+outcomes.
 
@@
 
-We performed multi-level regression with post-stratification (MRP) to predict support for Kamala Harris in the upcoming election.
-To perform MRP, we fit a logistic regression model to predict support for Harris using sex, age, race, race_hispanic, highest level of education, state, and urban as predictors on our survey data set [@americaspoliticalpulse], and post-stratified it using ACS census data [@citeIPUMS].
-
-## Model set-up
-
-We built our Bayesian logistic regression model using the `stan_glm()` function of the `rstanarm` package [@rstanarm]. The model that we use is:
-
-```{=tex}
-\begin{align} 
-vote\_harris_i|\pi_i &\sim \text{Bernoulli}(\pi_i) \\
-\text{logit}(\pi_i) &= \beta_0 + \beta_1 \text{sex}_i + \beta_2  \text{age\_bracket}_i + \beta_3 \text{race}_i + \beta_4 \text{race\_hispanic}_i + \beta_5 \text{education\_level}_i + \beta_6 \text{urban}_i \\
-\beta_0 &\sim \text{Normal}(0, 2.5) \\
-\beta_1 &\sim \text{Normal}(0, 2.5) \\
-\beta_2 &\sim \text{Normal}(0, 2.5) \\
-\beta_3 &\sim \text{Normal}(0, 2.5) \\
-\beta_4 &\sim \text{Normal}(0, 2.5) \\
-\beta_5 &\sim \text{Normal}(0, 2.5) \\
-\beta_6 &\sim \text{Normal}(0, 2.5)
-\end{align}
-```
-where binary variable $vote\_harris_i$ is equal to 1 if the respondent's preferred 2024 presidential candidate is Kamala Harris, or 0 if the respondent's preferred 2024 presidential candidate is Donald Trump.
-We run our model in R [@citeR] using `stan_glm`, with the default priors from `rstanarm` [@citerstanarm].
-We then apply our model to our post-stratification data [@citeIPUMS] to predict the popular vote and electoral college results of the 2024 U.S.
-Presidential election.
-
-Our model uses logistic regression, therefore one of its weaknesses is the fact that it predicts a binary outcome and does not consider the possibility that some American adults might vote for a third-party candidate or abstain from voting.
-Tradeoffs and concerns about our model are discussed in more detail in @sec-weaknesses-limitations.
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between certain demographic characteristics and support for Kamala Harris. Specifically:
-
--   **Sex**: We might expect differences in support between male and female respondents, with women potentially being more likely to support Kamala Harris due to certain policy stances that may appeal to this demographic.
--   **Age Bracket**: Age can be a significant factor, as younger voters might lean more progressive, potentially increasing support for Kamala Harris compared to Donald Trump.
--   **Race and Hispanic Ethnicity**: Historical voting patterns suggest that non-white racial groups, including Hispanic voters, may show stronger support for Democratic candidates, such as Harris.
-This is reflected in the coefficients $\beta_3$ for race and $\beta_4$ for Hispanic ethnicity.
--   **Education Level**: Higher education levels are often correlated with progressive political views, so we might expect a positive relationship between education level and support for Harris.
--   **Urban**: Respondents living in urban areas may be more likely to support Kamala Harris due to the urban-rural political divide observed in recent elections, where urban areas tend to lean more Democratic.
-
-The coefficients, such as $\beta_1$ for sex and $\beta_2$ for age bracket, represent the strength of these relationships.
-For example, a positive value of $\beta_1$ would suggest that being female increases the probability of supporting Harris, all else being equal.
-
-By using normal priors like $\beta_1 \sim \text{Normal}(0, 2.5)$, we assume that, before seeing the data, the effect of each predictor on the log-odds of supporting Kamala Harris is centered around zero, but with flexibility for the data to inform the posterior estimates.
-
-The Bayesian framework allows us to capture the uncertainty in our estimates and to refine our understanding of how different factors influence political support as new data becomes available.
-This is especially important in political forecasting, where the relationships between demographic factors and candidate support can be influenced by evolving social and political dynamics.
+We conducted a regression analysis to predict support for Kamala Harris
+in the 2024 U.S. presidential election. Our analysis includes two
+models: an **unweighted linear model** and a **weighted linear model**.
+These models predict Harris’s support as a continuous outcome across
+different states, using aggregated polling data with a focus on
+adjusting for poll quality, sample size, recency, and potential
+partisanship biases. This setup aligns with the New York Times
+methodology for election polling, which assigns weights based on poll
+quality, sample size, and recency of the poll to reflect an accurate
+picture of voter sentiment [@nytimes].
+
+## Model Set-up
+
+We implemented our linear regression models using the `lm()` function in
+R. The unweighted model provides a baseline with equal treatment for all
+polls, while the weighted model adjusts each poll observation based on
+combined factors, including recency, sample size, and poll quality. The
+model specifications are as follows:
+
+#### Unweighted Linear Model
+
+The unweighted model serves as a baseline, treating all polls equally
+without incorporating adjustments for recency, sample size, or poll
+quality. The model is defined as:
+
+$$
+\text{Support_Harris}_i = \beta_0 + \beta_1 \cdot \text{National_Poll}_i + \epsilon_i
+$$
+
+This unweighted model provides a baseline estimate of Harris’s support
+across different polls without considering variations in poll recency,
+sample size, or quality. It allows us to understand Harris’s support
+level with a simplified assumption that all polls are of equal
+relevance.
+
+#### Weighted Linear Model
+
+To enhance the accuracy of our predictions, the weighted model
+incorporates adjustments for recency, sample size, and pollster quality.
+This model is defined as:
+
+$$
+\text{Support_Harris}_i = \beta_0 + \beta_1 \cdot \text{National_Poll}_i + \beta_2 \cdot \text{Recency_Weight}_i + \beta_3 \cdot \text{Sample_Size_Weight}_i + \beta_4 \cdot \text{Numeric_Grade}_i + \epsilon_i
+$$
+
+The weighted model applies these additional factors to account for
+variations in data quality and recency, offering a refined view of
+Harris’s support.
+
+## Model Justification
+
+In developing our model to predict support for Kamala Harris, we
+included adjustments based on national polling, recency, sample size,
+and pollster grade. These features were selected to mitigate common
+biases in polling data and to ensure our model reflects up-to-date and
+high-quality information. The decision to incorporate recency as a
+predictor is motivated by the observation that voter sentiment can shift
+rapidly in response to events, such as debates or political
+controversies, especially as the election date approaches (The New York
+Times, 2024). Sample size was also used as a weight, as larger polls
+tend to reduce sampling variability up to a reasonable threshold, set at
+2,300 responses.
+
+Pollster quality, represented through numeric grades, accounts for
+systematic differences in methodology, professionalism, and past
+accuracy. Pollsters with a strong historical performance are given more
+weight, as they are more likely to produce unbiased and reliable
+results. The model structure, however, is based on linear regression,
+meaning it assumes an additive relationship between these predictors and
+voter support. This simplification, while computationally efficient and
+interpretable, may not capture more complex interactions between
+factors, such as shifts in demographic or regional support.
+
+Our model was implemented in R using the `lm()` function for the
+unweighted model and a weighted version for the adjusted model.
+Validation was performed using out-of-sample testing and RMSE
+calculations to assess accuracy. Sensitivity analyses were also
+conducted, examining how the model performed across different subsets of
+data.
+
+The model has several limitations, including the linearity assumption,
+which may not fully capture the dynamic nature of voter support. Its
+effectiveness relies on the assumption that the weights (recency, sample
+size, pollster grade) adequately mitigate biases in polling data.
+Additionally, it does not account for third-party candidates or
+undecided voters, which could affect the election outcome. While
+Bayesian hierarchical models were considered for their capability to
+handle multi-level data, they were ultimately set aside for a simpler,
+more interpretable linear model due to the analysis's scope and
+computational constraints. Future research should explore these more
+complex methods if time and resources permit.
 
@@
 
-Sketches depicting both the desired dataset and the graphs generated in this analysis are available in the GitHub Repository `other/sketches`.
+Sketches depicting both the desired dataset and the graphs generated in
+this analysis are available in the GitHub Repository `other/sketches`.
 
@@
 
-The data cleaning process involved filtering data to just high-quality pollsters (i.e numeric_grade >= 3.0) and filter to just Harris (i.e. candidate_name == "Kamala Harris")
+The data cleaning process involved filtering data to just high-quality
+pollsters (i.e numeric_grade \>= 3.0) and filter to just Harris (i.e.
+candidate_name == "Kamala Harris")
 
@@
 
-This work is licensed under a [Creative Commons Attribution 4.0 International License](https://creativecommons.org/licenses/by/4.0/).
-You are free to share, copy, redistribute, remix, transform, and build upon the material for any purpose, even commercially, as long as you credit the original creation.
+This work is licensed under a [Creative Commons Attribution 4.0
+International License](https://creativecommons.org/licenses/by/4.0/).
+You are free to share, copy, redistribute, remix, transform, and build
+upon the material for any purpose, even commercially, as long as you
+credit the original creation.
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive
+check. This shows...
+
+In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the
+prior. This shows...
 
@@
 
-This appendix provides a comprehensive overview of the methodology employed by the Siena College Polling Institute in conducting its surveys.Siena College is renowned for its methodologically rigorous approach to political polling, focusing on accurately capturing voter sentiment during elections.
-Siena College has conducted polls in three key states: Michigan, Wisconsin, and Ohio.
-
-In this section, we will delve into the key components of Siena's polling methodology, including the target population, sampling frame, recruitment processes, and the sampling strategies used.
-We will also address how non-response is managed and evaluate the strengths and weaknesses of the questionnaire design.
-By exploring these elements, this appendix aims to clarify how Siena College ensures the reliability and validity of its polling results, contributing valuable insights to the understanding of voter behavior and election outcomes.
+This appendix provides a comprehensive overview of the methodology
+employed by the Siena College Polling Institute in conducting its
+surveys.Siena College is renowned for its methodologically rigorous
+approach to political polling, focusing on accurately capturing voter
+sentiment during elections. Siena College has conducted polls in three
+key states: Michigan, Wisconsin, and Ohio.
+
+In this section, we will delve into the key components of Siena's
+polling methodology, including the target population, sampling frame,
+recruitment processes, and the sampling strategies used. We will also
+address how non-response is managed and evaluate the strengths and
+weaknesses of the questionnaire design. By exploring these elements,
+this appendix aims to clarify how Siena College ensures the reliability
+and validity of its polling results, contributing valuable insights to
+the understanding of voter behavior and election outcomes.
 
@@
 
-Siena College Polling Institute is a prominent pollster known for its comprehensive and methodologically rigorous surveys.
-It specializes in political polling and is particularly recognized for its work in understanding voter sentiment during elections.
-
-Established in 1980 at Siena College in New York's Capital District, the Siena College Research Institute (SCRI) conducts surveys at regional, state, and national levels on various topics, including business, economics, politics, voter behavior, social issues, academics, and history.
-The institute carries out both expert and public opinion polls.
-
-Students from Siena and other colleges participate in every survey, gaining hands-on experience in fields such as political science, computing, communications, sociology, and psychology.
-SCRI also hires interns for special projects involving event planning, in-depth research, report writing, and analysis.
-The results of SCRI's surveys are featured in major regional and national publications, including The Wall Street Journal and The New York Times, as well as in academic journals, books, and encyclopedias, both in print and online.
-Their findings are regularly highlighted in local and national television and radio broadcasts.
-SCRI conducts the Siena New York Poll, a monthly survey that captures the opinions of registered voters across New York State on current political issues, along with the New York State Index of Consumer Sentiment, which offers a quarterly assessment of New Yorkers' spending intentions.
-SCRI adheres to the American Association of Public Opinion Research (AAPOR) Code of Professional Ethics and Practices.
-The institute is often commissioned to carry out surveys for various organizations, businesses, and local and state government agencies.
-[@aboutsiena]
+Siena College Polling Institute is a prominent pollster known for its
+comprehensive and methodologically rigorous surveys. It specializes in
+political polling and is particularly recognized for its work in
+understanding voter sentiment during elections.
+
+Established in 1980 at Siena College in New York's Capital District, the
+Siena College Research Institute (SCRI) conducts surveys at regional,
+state, and national levels on various topics, including business,
+economics, politics, voter behavior, social issues, academics, and
+history. The institute carries out both expert and public opinion polls.
+
+Students from Siena and other colleges participate in every survey,
+gaining hands-on experience in fields such as political science,
+computing, communications, sociology, and psychology. SCRI also hires
+interns for special projects involving event planning, in-depth
+research, report writing, and analysis. The results of SCRI's surveys
+are featured in major regional and national publications, including The
+Wall Street Journal and The New York Times, as well as in academic
+journals, books, and encyclopedias, both in print and online. Their
+findings are regularly highlighted in local and national television and
+radio broadcasts. SCRI conducts the Siena New York Poll, a monthly
+survey that captures the opinions of registered voters across New York
+State on current political issues, along with the New York State Index
+of Consumer Sentiment, which offers a quarterly assessment of New
+Yorkers' spending intentions. SCRI adheres to the American Association
+of Public Opinion Research (AAPOR) Code of Professional Ethics and
+Practices. The institute is often commissioned to carry out surveys for
+various organizations, businesses, and local and state government
+agencies. [@aboutsiena]
 
@@
 
-In essence, statistics is about collecting data and making informed conclusions, even though we can never access every piece of information.\
+In essence, statistics is about collecting data and making informed
+conclusions, even though we can never access every piece of
+information.\
 From @tellingstories, we defined three key terms as:\
-Target population : The collection of all items about which we would like to speak. / The entire group about which we want to draw conclusions\
-Sampling frame : A list of all the items from the target population that we could get data about.\
+Target population : The collection of all items about which we would
+like to speak. / The entire group about which we want to draw
+conclusions\
+Sampling frame : A list of all the items from the target population that
+we could get data about.\
 Sample : The items from the sampling frame that we get data about.\
 
-The target population for Siena’s polls includes registered voters eligible to vote in Michigan, Wisconsin, and Ohio.
-The sampling frame consists of a comprehensive list of registered voters, which includes demographic information for each voter.
-This enables the pollsters to ensure an appropriate representation of voters across various parties, races, and regions [@poll].
-The sample of registered voters sourced from the voter file maintained by L2, a nonpartisan vendor, and supplemented with additional cellular phone numbers matched from Marketing Systems Group.
-The sample for the poll totals 2,055 likely voters, with 688 from Michigan, 687 from Ohio, and 680 from Wisconsin, surveyed from September 21 to 26, 2024.\
+The target population for Siena’s polls includes registered voters
+eligible to vote in Michigan, Wisconsin, and Ohio. The sampling frame
+consists of a comprehensive list of registered voters, which includes
+demographic information for each voter. This enables the pollsters to
+ensure an appropriate representation of voters across various parties,
+races, and regions [@poll]. The sample of registered voters sourced from
+the voter file maintained by L2, a nonpartisan vendor, and supplemented
+with additional cellular phone numbers matched from Marketing Systems
+Group. The sample for the poll totals 2,055 likely voters, with 688 from
+Michigan, 687 from Ohio, and 680 from Wisconsin, surveyed from September
+21 to 26, 2024.\
 
@@
 
-Siena use phone poll to recruit sample.
-Telephone polling is a common method for gathering public opinion and assessing voter sentiment by contacting individuals via landlines and mobile phones.
-This approach uses live interviewers to enhance data quality, allowing for clarification and nuanced responses.
-By utilizing random digit dialing or national voter registration databases, researchers can ensure a representative sample across various demographics.
-Despite its effectiveness in reaching diverse audiences quickly, telephone polling must address potential biases, such as nonresponse and shifts in communication habits, to maintain the reliability of its findings.[^1]
-
-[^1]: Phone polls, once considered the gold standard in survey research, now compete with methods like online panels and text messaging.
-Their advantages have diminished due to declining response rates, which increase costs and may affect representativeness, raising concerns about their future viability.
-However, they still effectively reach a random selection of voters quickly, as there is no national email database and postal mail can be slow.
-Other methods, such as recruiting panelists by mail, risk attracting only the most politically engaged individuals.
-Recent elections have shown that telephone polls, including The Times/Siena Poll, continue to perform well due to the reliability of voter registration files in balancing party representation.
-
-According to @freqqa, the polls are conducted by live interviewers at call centers located in Florida, New York, South Carolina, Texas, and Virginia.
-The respondents are randomly selected from a national database of registered voters and are contacted via both landlines and cellphones.
+Siena use phone poll to recruit sample. Telephone polling is a common
+method for gathering public opinion and assessing voter sentiment by
+contacting individuals via landlines and mobile phones. This approach
+uses live interviewers to enhance data quality, allowing for
+clarification and nuanced responses. By utilizing random digit dialing
+or national voter registration databases, researchers can ensure a
+representative sample across various demographics. Despite its
+effectiveness in reaching diverse audiences quickly, telephone polling
+must address potential biases, such as nonresponse and shifts in
+communication habits, to maintain the reliability of its findings.[^1]
+
+[^1]: Phone polls, once considered the gold standard in survey research,
+    now compete with methods like online panels and text messaging.
+    Their advantages have diminished due to declining response rates,
+    which increase costs and may affect representativeness, raising
+    concerns about their future viability. However, they still
+    effectively reach a random selection of voters quickly, as there is
+    no national email database and postal mail can be slow. Other
+    methods, such as recruiting panelists by mail, risk attracting only
+    the most politically engaged individuals. Recent elections have
+    shown that telephone polls, including The Times/Siena Poll, continue
+    to perform well due to the reliability of voter registration files
+    in balancing party representation.
+
+According to @freqqa, the polls are conducted by live interviewers at
+call centers located in Florida, New York, South Carolina, Texas, and
+Virginia. The respondents are randomly selected from a national database
+of registered voters and are contacted via both landlines and
+cellphones.
 
 Siena polls are conducted over the phone in both English and Spanish.
-For these polls, interviewers made nearly 260,000 calls to just over 140,000 voters.
-Overall, about 97 percent of respondents were contacted on a cellphone for these polls.
+For these polls, interviewers made nearly 260,000 calls to just over
+140,000 voters. Overall, about 97 percent of respondents were contacted
+on a cellphone for these polls.
 
@@
 
-Siena employs a response-rate-adjusted stratified sampling of registered voters sourced from the voter file maintained by L2, a nonpartisan vendor, and supplemented with additional cellular phone numbers matched from Marketing Systems Group.
-The New York Times selected the sample in multiple stages to address differences in telephone coverage, nonresponses, and notable variations in telephone number productivity by state.
-
-Stratified sampling is typically utilized to ensure all strata of the population are represented.
-When considering our population, it typically consists of various groupings.
-These can range from a country being divided into states, provinces, counties, or statistical districts to a university comprising faculties and departments or even demographic characteristics groups among individuals.
-A stratified structure allows us to categorize the population into mutually exclusive and collectively exhaustive sub-populations known as "strata".
-
-Stratification is employed to enhance sampling efficiency and ensure balance within the survey.
-For example, the population of the United States is approximately 335 million, with around 40 million residents in California and roughly half a million in Wyoming.
-In a survey with 10,000 responses, we would expect to receive only about 15 responses from Wyoming, which could complicate any inferences about that state.
-By implementing stratification, we could ensure, for instance, that there are 200 responses from each state.
-Within each state, we could then use random sampling to select individuals for data collection [@tellingstories].
-
-In this scenario, we want to collect the polls from all strata of our target population to balance our poll result.
-The sample was stratified by political party, race, and region, and screened by M.S.G.
-to ensure that the cellular phone numbers were active.
-The Siena College Research Institute conducted the survey, with additional support from various institutions, including ReconMR, the Public Opinion Research Laboratory at the University of North Florida, the Institute for Policy and Opinion Research at Roanoke College, the Center for Public Opinion and Policy Research at Winthrop University in South Carolina, and the Survey Center at the University of New Hampshire.
-Interviewers sought to speak with the individuals listed on the voter file and would terminate the interview if those persons were unavailable.
-Overall, 97 percent of respondents across all four samples were reached via cellular phones.
-
-The survey instrument was translated into Spanish by ReconMR, and bilingual interviewers began in English, following the respondent's preference for either language.
-Among self-reported Hispanics, 11 percent of interviews were conducted in Spanish, with this percentage rising to 15 percent in the weighted sample of registered voters.
-An interview was considered complete for inclusion in the voting questions if the respondent did not drop out after answering the two self-reported variables used for weighting—age and education—and responded to at least one question related to age, education, or presidential candidate preference.
-
-Stratified sampling enhances the representativeness of the sample by ensuring that smaller subgroups, which might otherwise be underrepresented, are adequately included.
-A significant advantage of this method is that it allows for more efficient resource allocation, enabling researchers to target specific groups and gather more insightful data.
-However, this focus can lead to **higher overall costs**, particularly due to the comprehensive data collection and analysis required when sampling large states or countries.
-Additionally, while stratified sampling provides richer insights into the characteristics and opinions of different subgroups, it introduces **complexity in data analysis**, necessitating advanced statistical techniques to interpret the results accurately.
-Consequently, researchers must have sufficient evidence to determine how to weight each stratum appropriately.
-Lastly, if the strata are not well-defined or if there is an imbalance in sampling, it could still result in sampling bias.
-Overall, while stratified sampling offers substantial benefits in terms of representation and analytical depth, it also presents challenges related to complexity, cost, and potential bias if not executed carefully.
+Siena employs a response-rate-adjusted stratified sampling of registered
+voters sourced from the voter file maintained by L2, a nonpartisan
+vendor, and supplemented with additional cellular phone numbers matched
+from Marketing Systems Group. The New York Times selected the sample in
+multiple stages to address differences in telephone coverage,
+nonresponses, and notable variations in telephone number productivity by
+state.
+
+Stratified sampling is typically utilized to ensure all strata of the
+population are represented. When considering our population, it
+typically consists of various groupings. These can range from a country
+being divided into states, provinces, counties, or statistical districts
+to a university comprising faculties and departments or even demographic
+characteristics groups among individuals. A stratified structure allows
+us to categorize the population into mutually exclusive and collectively
+exhaustive sub-populations known as "strata".
+
+Stratification is employed to enhance sampling efficiency and ensure
+balance within the survey. For example, the population of the United
+States is approximately 335 million, with around 40 million residents in
+California and roughly half a million in Wyoming. In a survey with
+10,000 responses, we would expect to receive only about 15 responses
+from Wyoming, which could complicate any inferences about that state. By
+implementing stratification, we could ensure, for instance, that there
+are 200 responses from each state. Within each state, we could then use
+random sampling to select individuals for data collection
+[@tellingstories].
+
+In this scenario, we want to collect the polls from all strata of our
+target population to balance our poll result. The sample was stratified
+by political party, race, and region, and screened by M.S.G. to ensure
+that the cellular phone numbers were active. The Siena College Research
+Institute conducted the survey, with additional support from various
+institutions, including ReconMR, the Public Opinion Research Laboratory
+at the University of North Florida, the Institute for Policy and Opinion
+Research at Roanoke College, the Center for Public Opinion and Policy
+Research at Winthrop University in South Carolina, and the Survey Center
+at the University of New Hampshire. Interviewers sought to speak with
+the individuals listed on the voter file and would terminate the
+interview if those persons were unavailable. Overall, 97 percent of
+respondents across all four samples were reached via cellular phones.
+
+The survey instrument was translated into Spanish by ReconMR, and
+bilingual interviewers began in English, following the respondent's
+preference for either language. Among self-reported Hispanics, 11
+percent of interviews were conducted in Spanish, with this percentage
+rising to 15 percent in the weighted sample of registered voters. An
+interview was considered complete for inclusion in the voting questions
+if the respondent did not drop out after answering the two self-reported
+variables used for weighting—age and education—and responded to at least
+one question related to age, education, or presidential candidate
+preference.
+
+Stratified sampling enhances the representativeness of the sample by
+ensuring that smaller subgroups, which might otherwise be
+underrepresented, are adequately included. A significant advantage of
+this method is that it allows for more efficient resource allocation,
+enabling researchers to target specific groups and gather more
+insightful data. However, this focus can lead to **higher overall
+costs**, particularly due to the comprehensive data collection and
+analysis required when sampling large states or countries. Additionally,
+while stratified sampling provides richer insights into the
+characteristics and opinions of different subgroups, it introduces
+**complexity in data analysis**, necessitating advanced statistical
+techniques to interpret the results accurately. Consequently,
+researchers must have sufficient evidence to determine how to weight
+each stratum appropriately. Lastly, if the strata are not well-defined
+or if there is an imbalance in sampling, it could still result in
+sampling bias. Overall, while stratified sampling offers substantial
+benefits in terms of representation and analytical depth, it also
+presents challenges related to complexity, cost, and potential bias if
+not executed carefully.
 
@@
 
-An interview was deemed complete for inclusion in the voting preference questions if the respondent stayed engaged in the survey after answering the two self-reported variables used for weighting—age and education—and provided responses to at least one question concerning age, education, or the presidential election candidate reference.
-If these conditions were not met, the interview was recorded as a non-response.
-
-To handle the non-response bias, Siena choose to use weighting adjustments.
-Weighting is like balancing a scale to make sure each group in the survey counts the right amount.
-It changes the importance of each answer depending on how likely people are to skip the survey [@surveylab].
-
-Siena use several steps to address nonresponse bias and ensure the reliability of the results.
-The weighting process was conducted by The Times using the R survey package and involved multiple adjustments.
-Initially, the samples were adjusted for the unequal probability of selection by stratum.
-Subsequently, the first-stage weight was modified to account for the likelihood that a registrant would vote in the 2024 election, based on a model derived from turnout data in the 2020 election.
-
-To create a composition that reflects the likely electorate, the sample was further weighted to match specific targets.
-These targets were developed by aggregating individual-level turnout estimates from the L2 voter file, with categories aligning with those used for registered voters.
-Additionally, the initial likely electorate weight was adjusted to incorporate self-reported voting intentions.
-In this final adjustment, four-fifths of the probability that a registrant would vote in the 2024 election was based on their ex ante modeled turnout score, while one-fifth relied on their self-reported intentions, adjusted for the tendency of survey respondents to have higher turnout rates than nonrespondents.
-
-The final likely electorate weight was calculated by multiplying the modeled electorate rake weight by the final turnout probability and then dividing by the ex ante modeled turnout probability.
-This comprehensive approach to weighting helps mitigate nonresponse bias by ensuring that the sample reflects both the characteristics of the general population and the expected behavior of likely voters.
-As a result, the sample of respondents who completed all questions in the survey was adjusted to accurately represent the likely electorate, enhancing the overall validity of the findings.
+An interview was deemed complete for inclusion in the voting preference
+questions if the respondent stayed engaged in the survey after answering
+the two self-reported variables used for weighting—age and education—and
+provided responses to at least one question concerning age, education,
+or the presidential election candidate reference. If these conditions
+were not met, the interview was recorded as a non-response.
+
+To handle the non-response bias, Siena choose to use weighting
+adjustments. Weighting is like balancing a scale to make sure each group
+in the survey counts the right amount. It changes the importance of each
+answer depending on how likely people are to skip the survey
+[@surveylab].
+
+Siena use several steps to address nonresponse bias and ensure the
+reliability of the results. The weighting process was conducted by The
+Times using the R survey package and involved multiple adjustments.
+Initially, the samples were adjusted for the unequal probability of
+selection by stratum. Subsequently, the first-stage weight was modified
+to account for the likelihood that a registrant would vote in the 2024
+election, based on a model derived from turnout data in the 2020
+election.
+
+To create a composition that reflects the likely electorate, the sample
+was further weighted to match specific targets. These targets were
+developed by aggregating individual-level turnout estimates from the L2
+voter file, with categories aligning with those used for registered
+voters. Additionally, the initial likely electorate weight was adjusted
+to incorporate self-reported voting intentions. In this final
+adjustment, four-fifths of the probability that a registrant would vote
+in the 2024 election was based on their ex ante modeled turnout score,
+while one-fifth relied on their self-reported intentions, adjusted for
+the tendency of survey respondents to have higher turnout rates than
+nonrespondents.
+
+The final likely electorate weight was calculated by multiplying the
+modeled electorate rake weight by the final turnout probability and then
+dividing by the ex ante modeled turnout probability. This comprehensive
+approach to weighting helps mitigate nonresponse bias by ensuring that
+the sample reflects both the characteristics of the general population
+and the expected behavior of likely voters. As a result, the sample of
+respondents who completed all questions in the survey was adjusted to
+accurately represent the likely electorate, enhancing the overall
+validity of the findings.
 
@@
 
-The questionnaire is crafted to be concise and straightforward, effectively minimizing respondent fatigue and maximizing clarity in question phrasing.
-This design is essential for maintaining participant engagement, especially in surveys that may include a wide array of questions.
-Additionally, the use of a mix of closed and open-ended formats allows for a comprehensive analysis of voter sentiment.
-Closed-ended questions yield quantifiable data, enabling researchers to identify trends and patterns, while open-ended questions provide rich qualitative insights that contextualize these trends.
-
-The careful structuring of questions also plays a crucial role in reducing moderacy bias, where respondents might lean towards neutral options when unsure.
-By providing clear response categories, the questionnaire encourages participants to express their opinions more decisively.
-Furthermore, the inclusion of diverse question types can mitigate acquiescence bias, which occurs when respondents habitually agree with statements instead of reflecting their true feelings.
-By framing questions in a balanced manner and avoiding leading language, the design helps ensure that participants feel comfortable expressing varied opinions.
+The questionnaire is crafted to be concise and straightforward,
+effectively minimizing respondent fatigue and maximizing clarity in
+question phrasing. This design is essential for maintaining participant
+engagement, especially in surveys that may include a wide array of
+questions. Additionally, the use of a mix of closed and open-ended
+formats allows for a comprehensive analysis of voter sentiment.
+Closed-ended questions yield quantifiable data, enabling researchers to
+identify trends and patterns, while open-ended questions provide rich
+qualitative insights that contextualize these trends.
+
+The careful structuring of questions also plays a crucial role in
+reducing moderacy bias, where respondents might lean towards neutral
+options when unsure. By providing clear response categories, the
+questionnaire encourages participants to express their opinions more
+decisively. Furthermore, the inclusion of diverse question types can
+mitigate acquiescence bias, which occurs when respondents habitually
+agree with statements instead of reflecting their true feelings. By
+framing questions in a balanced manner and avoiding leading language,
+the design helps ensure that participants feel comfortable expressing
+varied opinions.
 
@@
 
-However, the questionnaire is not without its weaknesses.
-Critics highlight that the reliance on agree-disagree formats can lead to acquiescence bias, where respondents might select favorable options rather than accurately expressing their true opinions.
-This tendency skews the results, potentially misrepresenting genuine voter sentiment and leading to misleading conclusions.
-
-Moreover, the questionnaire may not adequately address the nuances that are important to specific demographic groups, resulting in potential gaps in understanding voter motivations.
-For instance, certain groups may have distinct issues or concerns that are not adequately captured by the survey's questions.
-This limitation can contribute to nonresponse bias, where individuals from underrepresented groups choose not to participate or drop out of the survey, further skewing the results.
-
-Additionally, the structure of the questions could inadvertently create extreme response bias, where participants feel pressured to choose the most extreme options rather than selecting a moderate stance.
-This bias can be exacerbated by the order in which questions are presented.
-If respondents encounter highly charged or leading questions early in the survey, they may be influenced to respond similarly in subsequent questions, a phenomenon known as ordering bias.
-
-Furthermore, while the questionnaire aims to be inclusive, if it fails to adequately represent the voices of certain demographic groups, it could lead to a lack of adequacy in the data collected.
-This inadequacy undermines the ability to draw comprehensive conclusions about the electorate, particularly in a diverse political landscape.
-
-In summary, while the questionnaire design has strengths in clarity and mixed-format questions that encourage engagement and nuanced responses, it also faces challenges related to biases such as acquiescence, nonresponse, extreme response tendencies, and ordering effects.
-To enhance its effectiveness, future iterations of the questionnaire should strive to incorporate more varied question types, ensure demographic representation, and remain mindful of question order and phrasing to minimize the potential for bias and improve the overall validity of the findings.
+However, the questionnaire is not without its weaknesses. Critics
+highlight that the reliance on agree-disagree formats can lead to
+acquiescence bias, where respondents might select favorable options
+rather than accurately expressing their true opinions. This tendency
+skews the results, potentially misrepresenting genuine voter sentiment
+and leading to misleading conclusions.
+
+Moreover, the questionnaire may not adequately address the nuances that
+are important to specific demographic groups, resulting in potential
+gaps in understanding voter motivations. For instance, certain groups
+may have distinct issues or concerns that are not adequately captured by
+the survey's questions. This limitation can contribute to nonresponse
+bias, where individuals from underrepresented groups choose not to
+participate or drop out of the survey, further skewing the results.
+
+Additionally, the structure of the questions could inadvertently create
+extreme response bias, where participants feel pressured to choose the
+most extreme options rather than selecting a moderate stance. This bias
+can be exacerbated by the order in which questions are presented. If
+respondents encounter highly charged or leading questions early in the
+survey, they may be influenced to respond similarly in subsequent
+questions, a phenomenon known as ordering bias.
+
+Furthermore, while the questionnaire aims to be inclusive, if it fails
+to adequately represent the voices of certain demographic groups, it
+could lead to a lack of adequacy in the data collected. This inadequacy
+undermines the ability to draw comprehensive conclusions about the
+electorate, particularly in a diverse political landscape.
+
+In summary, while the questionnaire design has strengths in clarity and
+mixed-format questions that encourage engagement and nuanced responses,
+it also faces challenges related to biases such as acquiescence,
+nonresponse, extreme response tendencies, and ordering effects. To
+enhance its effectiveness, future iterations of the questionnaire should
+strive to incorporate more varied question types, ensure demographic
+representation, and remain mindful of question order and phrasing to
+minimize the potential for bias and improve the overall validity of the
+findings.
 
@@
 This appendix details the methodology and design for conducting a U.S.
-presidential election forecast survey with a budget of \$100,000.
-The objective is to generate an accurate and reliable prediction of the election outcome while ensuring data quality through meticulous sampling, recruitment, validation, and aggregation of results.\
+presidential election forecast survey with a budget of \$100,000. The
+objective is to generate an accurate and reliable prediction of the
+election outcome while ensuring data quality through meticulous
+sampling, recruitment, validation, and aggregation of results.\
 
@@
 
-To ensure a representative sample of likely voters, I will employ a Composite Measure sampling method based on past voter turnout data from the 2020 U.S.
-elections.
-After determining the sample size for each state, I will use stratified sampling based on demographics, dividing the population into subgroups and taking random samples from each subgroup.
-This Composite Measure sampling approach, as referenced in @india, enhances our chances of selecting respondents from states or regions that have historically exhibited higher voter engagement compared to the general population distribution.
-While some states may have larger populations, we aim to adjust the sampling to reflect higher turnout rates.
-
-To illustrate this Composite Measure of size, consider two states with similar populations.
-For instance, although State A and State B both have 1 million eligible voters, State B consistently shows a higher voter turnout in past elections.
-Therefore, we will increase the proportion of polls conducted in State B.
-In this scenario, State A has a historical turnout rate of 50%, while State B has a turnout rate of 70%.
-In a purely population-based sampling approach, both states would have an equal chance of being selected for polls: 50% for State A and 50% for State B.
-However, by incorporating voter turnout, we modify these probabilities to increase the likelihood of selecting State B due to its higher historical turnout.
-
-In the subsequent steps, we will detail how to utilize **voter turnout** as a crucial factor in creating a **composite measure of size** for sampling U.S.
-election polls.
-Rather than relying solely on population size, we will adjust the sample allocation based on historical voter turnout, ensuring that regions with higher engagement are more prominently represented in our polling data.
+To ensure a representative sample of likely voters, I will employ a
+Composite Measure sampling method based on past voter turnout data from
+the 2020 U.S. elections. After determining the sample size for each
+state, I will use stratified sampling based on demographics, dividing
+the population into subgroups and taking random samples from each
+subgroup. This Composite Measure sampling approach, as referenced in
+@india, enhances our chances of selecting respondents from states or
+regions that have historically exhibited higher voter engagement
+compared to the general population distribution. While some states may
+have larger populations, we aim to adjust the sampling to reflect higher
+turnout rates.
+
+To illustrate this Composite Measure of size, consider two states with
+similar populations. For instance, although State A and State B both
+have 1 million eligible voters, State B consistently shows a higher
+voter turnout in past elections. Therefore, we will increase the
+proportion of polls conducted in State B. In this scenario, State A has
+a historical turnout rate of 50%, while State B has a turnout rate of
+70%. In a purely population-based sampling approach, both states would
+have an equal chance of being selected for polls: 50% for State A and
+50% for State B. However, by incorporating voter turnout, we modify
+these probabilities to increase the likelihood of selecting State B due
+to its higher historical turnout.
+
+In the subsequent steps, we will detail how to utilize **voter turnout**
+as a crucial factor in creating a **composite measure of size** for
+sampling U.S. election polls. Rather than relying solely on population
+size, we will adjust the sample allocation based on historical voter
+turnout, ensuring that regions with higher engagement are more
+prominently represented in our polling data.
 
@@
 
-We begin by collecting the **eligible voter population** and **historical voter turnout rates** for different states.
-In this simplified example, we will focus on two states: **State A** and **State B**.
+We begin by collecting the **eligible voter population** and
+**historical voter turnout rates** for different states. In this
+simplified example, we will focus on two states: **State A** and **State
+B**.
 
@@
 
-Next, we calculate the **number of actual voters** in each state by multiplying the eligible voters by the turnout rate: $$\text{Actual Voters} = \text{Eligible Voters} \times \text{Turnout Rate}$$\
-Actual voters in State A: $\text{Actual Voters}_A = 1,000,000 \times 0.50 = 500,000$\
-Actual voters in State B: $\text{Actual Voters}_B = 1,000,000 \times 0.70 = 700,000$\
-Total actual voters: $\text{Actual Voters}_A+\text{Actual Voters}_B= 500,000 + 700,000 = 1,200,000$\
+Next, we calculate the **number of actual voters** in each state by
+multiplying the eligible voters by the turnout rate:
+$$\text{Actual Voters} = \text{Eligible Voters} \times \text{Turnout Rate}$$\
+Actual voters in State A:
+$\text{Actual Voters}_A = 1,000,000 \times 0.50 = 500,000$\
+Actual voters in State B:
+$\text{Actual Voters}_B = 1,000,000 \times 0.70 = 700,000$\
+Total actual voters:
+$\text{Actual Voters}_A+\text{Actual Voters}_B= 500,000 + 700,000 = 1,200,000$\
 
@@
 
-We now calculate the **total number of voters** across both states and determine the **proportion** of each state's turnout relative to the total.
-This forms the basis of the composite measure of size, which we will use to adjust the sampling weights.
-
-The total voters in two states are 1,200,000.
-Therefore, the sampling proportion for State A is: $\text{Sampling Proportion}_A = \frac{500,000}{1,200,000} \approx 0.417$, and for State B is: $\text{Sampling Proportion}_B = \frac{700,000}{1,200,000} \approx 0.583$
+We now calculate the **total number of voters** across both states and
+determine the **proportion** of each state's turnout relative to the
+total. This forms the basis of the composite measure of size, which we
+will use to adjust the sampling weights.
+
+The total voters in two states are 1,200,000. Therefore, the sampling
+proportion for State A is:
+$\text{Sampling Proportion}_A = \frac{500,000}{1,200,000} \approx 0.417$,
+and for State B is:
+$\text{Sampling Proportion}_B = \frac{700,000}{1,200,000} \approx 0.583$
 
@@
 
-Finally, we allocate the sample size according to the calculated sampling proportions.
-For instance, if we are conducting 1,000 polls, we would allocate State A with $\text{Polls for State A} = 1,000 \times 0.417 \approx 417 \text{polls}$ and State B with $\text{Polls for State B} = 1,000 \times 0.583 \approx 583 \text{polls}$
-
-By using historical voter turnout to adjust our polling sample, we ensure that regions with higher voter engagement have a greater influence on the polling results.
-This composite measure of size ensures that our polling sample better reflects the actual voting patterns and preferences in different regions.
-Consequently, we can produce more accurate and representative poll outcomes that account for the varying levels of voter participation across the country.
+Finally, we allocate the sample size according to the calculated
+sampling proportions. For instance, if we are conducting 1,000 polls, we
+would allocate State A with
+$\text{Polls for State A} = 1,000 \times 0.417 \approx 417 \text{polls}$
+and State B with
+$\text{Polls for State B} = 1,000 \times 0.583 \approx 583 \text{polls}$
+
+By using historical voter turnout to adjust our polling sample, we
+ensure that regions with higher voter engagement have a greater
+influence on the polling results. This composite measure of size ensures
+that our polling sample better reflects the actual voting patterns and
+preferences in different regions. Consequently, we can produce more
+accurate and representative poll outcomes that account for the varying
+levels of voter participation across the country.
 
@@
 
-After determining the number of respondents to be sampled from each region, stratified sampling will be employed across key demographic categories, including age, gender, race/ethnicity, and education level.
-This approach ensures that the final sample accurately reflects the diversity of the U.S.
-voting population by proportionally representing each subgroup within every region.
-To mitigate potential non-response bias, post-stratification weighting[^2] will be applied, correcting for any imbalances caused by variations in response rates among different demographic groups.
-The sample will be stratified based on several critical demographic and geographic variables to guarantee proportional representation of the U.S.
-voting population.
-Strata information will be sourced from U.S.
-census data obtained through IPUMS USA [@ruggles2024ipums].
-
-These variables include age, with categories such as 18-24 (12%), 25-34 (17%), 35-44 (16%), 45-54 (16%), 55-64 (16%), and 65+ (23%); gender, split into male (48%), female (52%), and non-binary/other (less than 1%); and race/ethnicity, covering groups like White/Caucasian (67%), Black/African American (13%), Hispanic/Latino (13%), Asian/Pacific Islander (5%), Native American/Alaskan Native (1%), and Other/Mixed Race (1%).
-Additionally, education level will be stratified into high school diploma or less (36%), some college, no degree (17%), Associate’s degree (9%), Bachelor’s degree (23%), and graduate or professional degree (15%).
-Geographic region will also be a key factor, ensuring representation from the Midwest (21%), Northeast (17%), South (38%), and West (24%).
-For each variable, U.S.
-Census or voter turnout data will be used to proportionally allocate respondents, ensuring that the final sample closely mirrors the demographic and regional composition of the actual voting population.
-Post-stratification weighting will be applied to adjust for any imbalances that may occur during data collection.
-
-[^2]: Post-stratification weighting adjusts survey data by applying weights to under- or over-represented demographic groups in the sample, ensuring the final results align with the true population distribution and reducing biases such as non-response bias.
+After determining the number of respondents to be sampled from each
+region, stratified sampling will be employed across key demographic
+categories, including age, gender, race/ethnicity, and education level.
+This approach ensures that the final sample accurately reflects the
+diversity of the U.S. voting population by proportionally representing
+each subgroup within every region. To mitigate potential non-response
+bias, post-stratification weighting[^2] will be applied, correcting for
+any imbalances caused by variations in response rates among different
+demographic groups. The sample will be stratified based on several
+critical demographic and geographic variables to guarantee proportional
+representation of the U.S. voting population. Strata information will be
+sourced from U.S. census data obtained through IPUMS USA
+[@ruggles2024ipums].
+
+[^2]: Post-stratification weighting adjusts survey data by applying
+    weights to under- or over-represented demographic groups in the
+    sample, ensuring the final results align with the true population
+    distribution and reducing biases such as non-response bias.
+
+These variables include age, with categories such as 18-24 (12%), 25-34
+(17%), 35-44 (16%), 45-54 (16%), 55-64 (16%), and 65+ (23%); gender,
+split into male (48%), female (52%), and non-binary/other (less than
+1%); and race/ethnicity, covering groups like White/Caucasian (67%),
+Black/African American (13%), Hispanic/Latino (13%), Asian/Pacific
+Islander (5%), Native American/Alaskan Native (1%), and Other/Mixed Race
+(1%). Additionally, education level will be stratified into high school
+diploma or less (36%), some college, no degree (17%), Associate’s degree
+(9%), Bachelor’s degree (23%), and graduate or professional degree
+(15%). Geographic region will also be a key factor, ensuring
+representation from the Midwest (21%), Northeast (17%), South (38%), and
+West (24%). For each variable, U.S. Census or voter turnout data will be
+used to proportionally allocate respondents, ensuring that the final
+sample closely mirrors the demographic and regional composition of the
+actual voting population. Post-stratification weighting will be applied
+to adjust for any imbalances that may occur during data collection.
 
@@
 
-Our target population is all U.S. citizens eligible to vote in the 2024 U.S. presidential election (age\>=18).
+Our target population is all U.S. citizens eligible to vote in the 2024
+U.S. presidential election (age\>=18).
 
@@
 
-Based on the recruitment method we discussed later, our sampling frame could be all registered voters in online panels like Qualtrics and YouGov and the millions of U.S.
-voters who are reachable via social media platforms like Facebook and Instagram.
+Based on the recruitment method we discussed later, our sampling frame
+could be all registered voters in online panels like Qualtrics and
+YouGov and the millions of U.S. voters who are reachable via social
+media platforms like Facebook and Instagram.
 
@@
 
-We plan to survey 300 respondents, which will provide a margin of error of approximately ±1.7 percentage points, ensuring a high level of confidence in the results.
-Given the limited sample size and to enhance the effectiveness of stratified sampling, the states will be grouped into four regions: Midwest, Northeast, South, and West.
-The sample size for each region will be allocated based on the proportion of total ballots cast in each region during the 2020 election.
-The regional grouping of states is shown in @tbl-region.
+We plan to survey 300 respondents, which will provide a margin of error
+of approximately ±1.7 percentage points, ensuring a high level of
+confidence in the results. Given the limited sample size and to enhance
+the effectiveness of stratified sampling, the states will be grouped
+into four regions: Midwest, Northeast, South, and West. The sample size
+for each region will be allocated based on the proportion of total
+ballots cast in each region during the 2020 election. The regional
+grouping of states is shown in @tbl-region.
 
 | **Region**    | **States**                                                                                                                                                 |
-|------------------------|------------------------------------------------|
+|-------------------------|-----------------------------------------------|
 | **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
@@
 
-: Regional Voting Data and Sample Size Allocation Based on 2020 Election Turnout {#tbl-samplesize}
-
-@tbl-samplesize shows the regional breakdown of the 2020 election data, sourced from [@wikivote], including voter turnout, total ballots cast, and Voting Eligible Population (VEP).
-The sample size for each region shown in @tbl-samplesize was determined based on the **Composite Measure Sampling Proportion**.
+: Regional Voting Data and Sample Size Allocation Based on 2020 Election
+Turnout {#tbl-samplesize}
+
+@tbl-samplesize shows the regional breakdown of the 2020 election data,
+sourced from [@wikivote], including voter turnout, total ballots cast,
+and Voting Eligible Population (VEP). The sample size for each region
+shown in @tbl-samplesize was determined based on the **Composite Measure
+Sampling Proportion**.
 
@@
 
-Due to budget constraints, we will focus on online recruitment methods, which offer a cost-effective and efficient way to reach a diverse and representative sample of voters across the country.
-
-Online Recruitment: With the objective of surveying 400 respondents, we will focus our resources on implementing the survey and ensuring high-quality data collection.
-The survey will be developed in-house, and respondents will be recruited using online survey platforms.
-The recruitment approach is as follows:
+Due to budget constraints, we will focus on online recruitment methods,
+which offer a cost-effective and efficient way to reach a diverse and
+representative sample of voters across the country.
+
+Online Recruitment: With the objective of surveying 400 respondents, we
+will focus our resources on implementing the survey and ensuring
+high-quality data collection. The survey will be developed in-house, and
+respondents will be recruited using online survey platforms. The
+recruitment approach is as follows:
 
@@
 
-Online Panel Providers (Qualtrics, YouGov): 200 respondents will be recruited through reputable online panel providers like Qualtrics and YouGov, known for high-quality samples with verified voter registration status.
-This recruitment source provides a strong base of quality data, given the stringent participant verification process in place.
-
-Social Media Recruitment: We plan to recruit 400 respondents through targeted social media panels on platforms such as Facebook and Instagram.
-Given the typically lower data quality from social media recruitment, we anticipate that 50% of responses may be invalid.
-To compensate, we will oversample from this group, aiming to gather a sufficient number of valid and high-quality responses.
-To attract participants, each respondent will receive a small monetary reward (such as a gift card) for completing the survey.
-Targeted ads and eligibility screening will be used to reach respondents who meet key criteria, such as age and U.S.
-voter registration status.
-This approach helps ensure that those recruited are likely to be eligible voters.
+Online Panel Providers (Qualtrics, YouGov): 200 respondents will be
+recruited through reputable online panel providers like Qualtrics and
+YouGov, known for high-quality samples with verified voter registration
+status. This recruitment source provides a strong base of quality data,
+given the stringent participant verification process in place.
+
+Social Media Recruitment: We plan to recruit 400 respondents through
+targeted social media panels on platforms such as Facebook and
+Instagram. Given the typically lower data quality from social media
+recruitment, we anticipate that 50% of responses may be invalid. To
+compensate, we will oversample from this group, aiming to gather a
+sufficient number of valid and high-quality responses. To attract
+participants, each respondent will receive a small monetary reward (such
+as a gift card) for completing the survey. Targeted ads and eligibility
+screening will be used to reach respondents who meet key criteria, such
+as age and U.S. voter registration status. This approach helps ensure
+that those recruited are likely to be eligible voters.
 
@@
 
-Nonresponse bias occurs when participants are unwilling or unable to respond to specific questions or complete the entire survey.
-For example, since our survey takes about 15 minutes to finish, there is a potential for nonresponse bias to arise.
-To address this concern, as highlighted by @surveymonkey, we strive to establish clear expectations regarding the survey's objectives and the estimated time required for completion.
-Furthermore, we utilize post-stratification, which changes the survey weights to make sure the group that answered fits well with the actual population characteristics [@surveylab].
+Nonresponse bias occurs when participants are unwilling or unable to
+respond to specific questions or complete the entire survey. For
+example, since our survey takes about 15 minutes to finish, there is a
+potential for nonresponse bias to arise. To address this concern, as
+highlighted by @surveymonkey, we strive to establish clear expectations
+regarding the survey's objectives and the estimated time required for
+completion. Furthermore, we utilize post-stratification, which changes
+the survey weights to make sure the group that answered fits well with
+the actual population characteristics [@surveylab].
 
@@
 
-To ensure high data quality and accuracy, respondent validation will be conducted through multiple checks and verification processes.
-This process ensures that only eligible and relevant participants are included in the survey, maintaining the integrity of the sample.
+To ensure high data quality and accuracy, respondent validation will be
+conducted through multiple checks and verification processes. This
+process ensures that only eligible and relevant participants are
+included in the survey, maintaining the integrity of the sample.
 
@@
 
-Respondents will be required to confirm their voter registration status, with a portion of the sample cross-referenced against voter registration databases or verified through reputable online panel providers like Qualtrics or YouGov.
-This step ensures that the survey includes only registered and likely voters, crucial for representing the target population accurately.
-Screening and Eligibility Questions:
-
-Respondents will complete a set of screening questions to verify eligibility criteria, such as age (18 or older) and U.S.
-citizenship.
-Only those meeting these criteria will be allowed to proceed with the survey.
-Attention Checks:
-
-To detect and filter out inattentive or disengaged participants, attention-check questions will be embedded throughout the survey (e.g., asking respondents to select a specific answer to verify attentiveness).
+Respondents will be required to confirm their voter registration status,
+with a portion of the sample cross-referenced against voter registration
+databases or verified through reputable online panel providers like
+Qualtrics or YouGov. This step ensures that the survey includes only
+registered and likely voters, crucial for representing the target
+population accurately. Screening and Eligibility Questions:
+
+Respondents will complete a set of screening questions to verify
+eligibility criteria, such as age (18 or older) and U.S. citizenship.
+Only those meeting these criteria will be allowed to proceed with the
+survey. Attention Checks:
+
+To detect and filter out inattentive or disengaged participants,
+attention-check questions will be embedded throughout the survey (e.g.,
+asking respondents to select a specific answer to verify attentiveness).
 Respondents who fail these checks may be excluded from the final sample.
@@
 
-Unique identifiers such as IP addresses and email addresses will be tracked to prevent multiple submissions from the same individual, ensuring that each response represents a unique participant.
-Post-Survey Data Cleaning:
-
-After data collection, responses will be reviewed for consistency and completeness.
-Inconsistent responses or incomplete surveys will be removed, maintaining the quality and reliability of the dataset.
-By implementing these respondent validation steps, the survey methodology ensures that data collected reflects only eligible, registered, and attentive respondents, thereby enhancing the validity and accuracy of the survey results.
+Unique identifiers such as IP addresses and email addresses will be
+tracked to prevent multiple submissions from the same individual,
+ensuring that each response represents a unique participant. Post-Survey
+Data Cleaning:
+
+After data collection, responses will be reviewed for consistency and
+completeness. Inconsistent responses or incomplete surveys will be
+removed, maintaining the quality and reliability of the dataset. By
+implementing these respondent validation steps, the survey methodology
+ensures that data collected reflects only eligible, registered, and
+attentive respondents, thereby enhancing the validity and accuracy of
+the survey results.
 
@@
 
-After getting the survey response, we will aggregate polls from two recruitment sources: online panel providers and social media platforms.To weight the two panels effectively, we will first identify key demographic variables for stratification, such as age, gender, race/ethnicity, and education level, and establish population proportions using U.S.
-Census data or other reliable sources.
-For the online panel (200 respondents), we will compare the demographic distribution of respondents to these population benchmarks, calculating weights based on the degree of under- or over-representation.
-Similarly, we will perform this analysis for the social media panel (400 respondents) to determine its weights.
-Once we have calculated weights for each panel, we will combine them into a single weighting scheme that reflects the overall demographic composition of the target population.
-During data analysis, we will apply these weights to the responses, ensuring that underrepresented groups have a greater influence on the results while adjusting for those that are overrepresented.
-Finally, we will conduct post-stratification adjustments to confirm that the combined sample accurately mirrors the true characteristics of the U.S.
-voting population, providing reliable insights into voter preferences and behaviors.
+After getting the survey response, we will aggregate polls from two
+recruitment sources: online panel providers and social media
+platforms.To weight the two panels effectively, we will first identify
+key demographic variables for stratification, such as age, gender,
+race/ethnicity, and education level, and establish population
+proportions using U.S. Census data or other reliable sources. For the
+online panel (200 respondents), we will compare the demographic
+distribution of respondents to these population benchmarks, calculating
+weights based on the degree of under- or over-representation. Similarly,
+we will perform this analysis for the social media panel (400
+respondents) to determine its weights. Once we have calculated weights
+for each panel, we will combine them into a single weighting scheme that
+reflects the overall demographic composition of the target population.
+During data analysis, we will apply these weights to the responses,
+ensuring that underrepresented groups have a greater influence on the
+results while adjusting for those that are overrepresented. Finally, we
+will conduct post-stratification adjustments to confirm that the
+combined sample accurately mirrors the true characteristics of the U.S.
+voting population, providing reliable insights into voter preferences
+and behaviors.
 
@@
 
-The survey is designed to capture essential insights into voting intentions, candidate favorability, and the issues influencing voter decisions.
-It will be concise and straightforward, taking no longer than 15 minutes to complete.
+The survey is designed to capture essential insights into voting
+intentions, candidate favorability, and the issues influencing voter
+decisions. It will be concise and straightforward, taking no longer than
+15 minutes to complete.
 
 **Survey Link**\
-The survey has been implemented using Google Forms. You can access it here: [Survey Link](https://forms.gle/BAZhkWDyLxAibwvu5).
-
-In our survey, several questions are adapted from the Emerson College Polling data [@emerson].
-We apply insights from @survey to minimize response biases.
-Common response biases identified in survey design include moderacy bias, extreme response bias, ordering bias, acquiescence bias, experimenter demand effect (EDE), and social desirability bias (SDB).
-Our survey primarily focuses on strategies to reduce moderacy bias, extreme response bias, ordering bias, SDB, and acquiescence bias.
+The survey has been implemented using Google Forms. You can access it
+here: [Survey Link](https://forms.gle/BAZhkWDyLxAibwvu5).
+
+In our survey, several questions are adapted from the Emerson College
+Polling data [@emerson]. We apply insights from @survey to minimize
+response biases. Common response biases identified in survey design
+include moderacy bias, extreme response bias, ordering bias,
+acquiescence bias, experimenter demand effect (EDE), and social
+desirability bias (SDB). Our survey primarily focuses on strategies to
+reduce moderacy bias, extreme response bias, ordering bias, SDB, and
+acquiescence bias.
 
@@
 
--   Moderacy response bias is the tendency to respond to each question by choosing a category in the middle of the scale.
-
--   Extreme response bias is the tendency to respond with extreme values on the rating scale.
-
--   Response order bias occurs when the order of response options in a list or a rating scale influences the response chosen.
-The primacy effect occurs when respondents are more likely to select one of the first alternatives provided, and it is more common in written surveys.
-This tendency can be due to satisficing, whereby a respondent uses the first acceptable response alternative without paying particular attention to the other options.
-The recency effect occurs when respondents choose one of the last items presented to them (more common in face-to-face or orally presented surveys).
-
--   Social desirability bias typically stems from the desire of respondents to avoid embarrassment and project a favorable image to others, resulting in respondents not revealing their actual attitudes.
-The prevalence of this bias will depend on the topic, questions, respondent, mode of the survey, and the social context.
-For instance, in some circles, anti-immigrant views are not tolerated, and those who hold them may try to hide them.
-In other settings, people express such views more freely.
-
--   Acquiescence is the tendency to answer items in a positive way regardless of their content, for instance, systematically selecting categories such as “agree,” “true,” or “yes”.
+-   Moderacy response bias is the tendency to respond to each question
+    by choosing a category in the middle of the scale.
+
+-   Extreme response bias is the tendency to respond with extreme values
+    on the rating scale.
+
+-   Response order bias occurs when the order of response options in a
+    list or a rating scale influences the response chosen. The primacy
+    effect occurs when respondents are more likely to select one of the
+    first alternatives provided, and it is more common in written
+    surveys. This tendency can be due to satisficing, whereby a
+    respondent uses the first acceptable response alternative without
+    paying particular attention to the other options. The recency effect
+    occurs when respondents choose one of the last items presented to
+    them (more common in face-to-face or orally presented surveys).
+
+-   Social desirability bias typically stems from the desire of
+    respondents to avoid embarrassment and project a favorable image to
+    others, resulting in respondents not revealing their actual
+    attitudes. The prevalence of this bias will depend on the topic,
+    questions, respondent, mode of the survey, and the social context.
+    For instance, in some circles, anti-immigrant views are not
+    tolerated, and those who hold them may try to hide them. In other
+    settings, people express such views more freely.
+
+-   Acquiescence is the tendency to answer items in a positive way
+    regardless of their content, for instance, systematically selecting
+    categories such as “agree,” “true,” or “yes”.
 
@@
 
-To mitigate bias, we enhance our survey in the following ways, drawing on recommendations from @survey:
-
-Addressing Extreme/Moderacy Bias: We customize the scale and response options with differentiated alternatives.
-Three-point answer scales can lead to extreme response bias or moderacy bias due to insufficient options.
-Therefore, for every scale question, we designed at least five response options, which reduces the likelihood of respondents choosing the middle answers because of a lack of alternatives.
-
-Mitigating Response Order Bias: We implement a solution involving seemingly open-ended questions and randomizing the order of response options for unordered (nominal) questions.
-For ordinal questions, we invert the order.
-For example, instead of asking, "Will you choose candidate A or candidate B?" we ask, "Who would you vote for?
-\[pause\] Candidate A or Candidate B?" Additionally, using Google Forms, we randomize the order of options for all unordered questions to further reduce response order bias.
-
-Minimizing Social Desirability Bias (SDB): Given that our survey is conducted online, we employ a minimized SDB format.
-A recommended strategy for recruiting respondents is to provide only basic information about the survey's purpose at the outset, which engages participants without overwhelming them.
-Therefore, in the introduction, we state that the survey aims for academic research in Statistics, omitting details about our affiliations or the specific use of the data.
-We simply inform participants that, "This survey is for nonpartisan researchers in academic research in Statistics." At the end of the survey, we include a feedback section to gauge attitudes toward the surveyor or entity.
-
-Ensuring Anonymity (Minimizing SDB): The complete anonymity of respondents is a crucial aspect of our survey.
-We guarantee this anonymity as stated on the survey landing and consent page.
-Before sensitive questions, we will reinforce that all answers are confidential and anonymous, reminding participants of their privacy.
-We will strategically place sensitive items within the survey to minimize the risk of social desirability bias (SDB).
-
-Reducing Acquiescence Bias: To tackle acquiescence bias, we avoid agree-disagree, true-false, and yes-no question formats.
-Instead of using agree-disagree questions, we formulate inquiries that utilize direct, item-specific scales tailored to the question.
-For instance, when asking for respondents' views on candidates, we use options like "very unfavorable, unfavorable, moderate, favorable, very favorable" instead of simple yes or no.
-Furthermore, we ensure that our questions offer answer options that encompass all possible views.
-For example, in the question "Do you approve or disapprove of the job Joe Biden is doing as President?", we provide the options "Approve, Disapprove, Neutral or no opinion" rather than just yes or no.
+To mitigate bias, we enhance our survey in the following ways, drawing
+on recommendations from @survey:
+
+Addressing Extreme/Moderacy Bias: We customize the scale and response
+options with differentiated alternatives. Three-point answer scales can
+lead to extreme response bias or moderacy bias due to insufficient
+options. Therefore, for every scale question, we designed at least five
+response options, which reduces the likelihood of respondents choosing
+the middle answers because of a lack of alternatives.
+
+Mitigating Response Order Bias: We implement a solution involving
+seemingly open-ended questions and randomizing the order of response
+options for unordered (nominal) questions. For ordinal questions, we
+invert the order. For example, instead of asking, "Will you choose
+candidate A or candidate B?" we ask, "Who would you vote for? \[pause\]
+Candidate A or Candidate B?" Additionally, using Google Forms, we
+randomize the order of options for all unordered questions to further
+reduce response order bias.
+
+Minimizing Social Desirability Bias (SDB): Given that our survey is
+conducted online, we employ a minimized SDB format. A recommended
+strategy for recruiting respondents is to provide only basic information
+about the survey's purpose at the outset, which engages participants
+without overwhelming them. Therefore, in the introduction, we state that
+the survey aims for academic research in Statistics, omitting details
+about our affiliations or the specific use of the data. We simply inform
+participants that, "This survey is for nonpartisan researchers in
+academic research in Statistics." At the end of the survey, we include a
+feedback section to gauge attitudes toward the surveyor or entity.
+
+Ensuring Anonymity (Minimizing SDB): The complete anonymity of
+respondents is a crucial aspect of our survey. We guarantee this
+anonymity as stated on the survey landing and consent page. Before
+sensitive questions, we will reinforce that all answers are confidential
+and anonymous, reminding participants of their privacy. We will
+strategically place sensitive items within the survey to minimize the
+risk of social desirability bias (SDB).
+
+Reducing Acquiescence Bias: To tackle acquiescence bias, we avoid
+agree-disagree, true-false, and yes-no question formats. Instead of
+using agree-disagree questions, we formulate inquiries that utilize
+direct, item-specific scales tailored to the question. For instance,
+when asking for respondents' views on candidates, we use options like
+"very unfavorable, unfavorable, moderate, favorable, very favorable"
+instead of simple yes or no. Furthermore, we ensure that our questions
+offer answer options that encompass all possible views. For example, in
+the question "Do you approve or disapprove of the job Joe Biden is doing
+as President?", we provide the options "Approve, Disapprove, Neutral or
+no opinion" rather than just yes or no.
 
@@
 
-Budget Breakdown With a total budget of \$100,000, the allocation for various components of the survey implementation and data collection is as follows:
-
-Survey Design and Development: \$2,000 This portion covers the design and development of the survey, including question formatting, testing, and integration with online platforms like Qualtrics and social media platforms.
-Ensuring the survey is user-friendly and addresses key research questions is essential for high-quality data collection.
-Online Panel Providers (Qualtrics, YouGov): \$80,000 (200 respondents at \$400 per respondent) We will recruit 100 respondents via reputable online panel providers like Qualtrics and YouGov.
-These platforms ensure high-quality responses through verified voter registration, but they come at a higher cost per respondent due to their validation processes.
-
-Social Media Recruitment (Facebook, Instagram): \$12,000 (400 respondents at \$30 per respondent) 400 respondents will be recruited using targeted social media ads.
-Since we expect 50% of responses to be invalid, oversampling will allow us to achieve a final valid sample of 200 respondents.
-The cost per respondent is lower than online panel providers, but rigorous validation and filtering are required to ensure data quality.
-
-Data Validation and Quality Control: \$6,000 This covers voter registration verification, attention checks within the survey, and extensive post-collection filtering, particularly for social media responses.
-Ensuring the integrity and accuracy of the data is crucial to minimize biases and errors.
+Budget Breakdown With a total budget of \$100,000, the allocation for
+various components of the survey implementation and data collection is
+as follows:
+
+Survey Design and Development: \$2,000 This portion covers the design
+and development of the survey, including question formatting, testing,
+and integration with online platforms like Qualtrics and social media
+platforms. Ensuring the survey is user-friendly and addresses key
+research questions is essential for high-quality data collection. Online
+Panel Providers (Qualtrics, YouGov): \$80,000 (200 respondents at \$400
+per respondent) We will recruit 100 respondents via reputable online
+panel providers like Qualtrics and YouGov. These platforms ensure
+high-quality responses through verified voter registration, but they
+come at a higher cost per respondent due to their validation processes.
+
+Social Media Recruitment (Facebook, Instagram): \$12,000 (400
+respondents at \$30 per respondent) 400 respondents will be recruited
+using targeted social media ads. Since we expect 50% of responses to be
+invalid, oversampling will allow us to achieve a final valid sample of
+200 respondents. The cost per respondent is lower than online panel
+providers, but rigorous validation and filtering are required to ensure
+data quality.
+
+Data Validation and Quality Control: \$6,000 This covers voter
+registration verification, attention checks within the survey, and
+extensive post-collection filtering, particularly for social media
+responses. Ensuring the integrity and accuracy of the data is crucial to
+minimize biases and errors.
 
@@
 
-Welcome to our 2024 U.S.
-Presidential Election Polls Survey.
-Your participation in this survey is vital in helping us understand voters' preferences and opinions on key issues.
-Rest assured that your responses are anonymous and will only be used for statistical analysis.
-
-This survey is for academic research in Statistics. It consists of 26 carefully designed questions and should take approximately 12-15 minutes to complete.
+Welcome to our 2024 U.S. Presidential Election Polls Survey. Your
+participation in this survey is vital in helping us understand voters'
+preferences and opinions on key issues. Rest assured that your responses
+are anonymous and will only be used for statistical analysis.
+
+This survey is for academic research in Statistics. It consists of 26
+carefully designed questions and should take approximately 12-15 minutes
+to complete.
 
 For any questions or concerns regarding this survey, please contact:\
-**Email:**  diana.shen\@mail.utoronto.ca; jinyan.wei\@mail.utoronto.ca; huayan.yu\@mail.utoronto.ca
+**Email:** diana.shen\@mail.utoronto.ca; jinyan.wei\@mail.utoronto.ca;
+huayan.yu\@mail.utoronto.ca
 
@@
 
-Your privacy is our priority.
-In this survey, your responses are completely anonymous, ensuring that no one can link your answers back to you.
-We encourage you to share your true opinions, as this survey is conducted by a neutral, nonpartisan entity.
-Your data will only be used for research purposes, and you will not be identified individually.
-If you have concerns, we ask for your feedback at the end of the survey to ensure transparency and trust.
+Your privacy is our priority. In this survey, your responses are
+completely anonymous, ensuring that no one can link your answers back to
+you. We encourage you to share your true opinions, as this survey is
+conducted by a neutral, nonpartisan entity. Your data will only be used
+for research purposes, and you will not be identified individually. If
+you have concerns, we ask for your feedback at the end of the survey to
+ensure transparency and trust.
 
@@
 
-1.  **Do you approve or disapprove of the job Joe Biden is doing as President?**
+1.  **Do you approve or disapprove of the job Joe Biden is doing as
+    President?**
 
@@
 
-3.  **If the Presidential Election were held today, would you vote for Kamala Harris or Donald Trump?**
+3.  **If the Presidential Election were held today, would you vote for
+    Kamala Harris or Donald Trump?**
 
@@
 
-4.  **Although you are undecided, which candidate do you lean toward?**(Jump to this question only if responders choose undecided in Question 3)
+4.  **Although you are undecided, which candidate do you lean
+    toward?**(Jump to this question only if responders choose undecided
+    in Question 3)
 
@@
 
-10.
-**Imagine the following candidates: Candidate A favors cutting taxes but has a weak stance on climate change, and Candidate B focuses on healthcare but supports increased military spending.Who would you vote for?
-Candidate A or Candidate B?**
+10. **Imagine the following candidates: Candidate A favors cutting taxes
+    but has a weak stance on climate change, and Candidate B focuses on
+    healthcare but supports increased military spending.Who would you
+    vote for? Candidate A or Candidate B?**
 
@@
 
-11.
-**Imagine two candidates: Candidate A supports education reform but plans to cut social security, and Candidate B focuses on green energy but raises taxes.
-Who would you vote for?
-Candidate A or Candidate B?**
+11. **Imagine two candidates: Candidate A supports education reform but
+    plans to cut social security, and Candidate B focuses on green
+    energy but raises taxes. Who would you vote for? Candidate A or
+    Candidate B?**
 
@@
 
-12. **What do you think is the most important issue facing the United States?**
+12. **What do you think is the most important issue facing the United
+    States?**
 
@@
 
-17. **How closely are you following news about the 2024 U.S. presidential election?**
+17. **How closely are you following news about the 2024 U.S.
+    presidential election?**
 
@@
 
-18. **Which social media platforms do you use to get political news?** (Select all that apply)
+18. **Which social media platforms do you use to get political news?**
+    (Select all that apply)
 
@@
 **Privacy Notice for Demographic Information Collection**\
-Your demographic information is collected anonymously and will be used for statistical purposes only, helping us analyze trends across different groups.
-We ensure that your individual responses cannot be traced back to you, maintaining full confidentiality.
-Your privacy and honest participation are important to us.
+Your demographic information is collected anonymously and will be used
+for statistical purposes only, helping us analyze trends across
+different groups. We ensure that your individual responses cannot be
+traced back to you, maintaining full confidentiality. Your privacy and
+honest participation are important to us.
 
@@
     -   West
-3.  **For statistical purposes only, can you please tell me your ethnicity?**
+3.  **For statistical purposes only, can you please tell me your
+    ethnicity?**
     -   Hispanic or Latino of any race
@@
 
-1.  **Do you have any concerns or feedback regarding the survey, surveyor ,or entity?**\
-    Your feedback is important to us and will help ensure transparency and trust in the research process.
+1.  **Do you have any concerns or feedback regarding the survey,
+    surveyor ,or entity?**\
+    Your feedback is important to us and will help ensure transparency
+    and trust in the research process.
 
@@
 
-Thank you for taking the time to complete this survey. Your honest feedback is invaluable and will contribute greatly to our research. We appreciate your participation!
+Thank you for taking the time to complete this survey. Your honest
+feedback is invaluable and will contribute greatly to our research. We
+appreciate your participation!
 

### 2024-10-28 scripts/02-download_data.R
change the download of data include col_names

@@ -13,13 +13,11 @@ library(tidyverse)
 
 #### Download data ####
 #### Acquire ####
-raw_elections_data <-
-  read_csv(
-    file = 
-      "https://projects.fivethirtyeight.com/polls/data/president_polls.csv",
-    show_col_types = FALSE,
-    skip = 1
-  )
+raw_elections_data <- read_csv(
+  file = "https://projects.fivethirtyeight.com/polls/data/president_polls.csv",
+  show_col_types = FALSE,
+  col_names = TRUE  
+)
 
 #### Save data ####
 write_csv(

### 2024-10-28 paper/paper.qmd
update with merged version

@@
 
-The data cleaning process involved filtering data to just high-quality
-pollsters (i.e numeric_grade \>= 3.0) and filter to just Harris (i.e.
-candidate_name == "Kamala Harris")
+In this data-cleaning process, we focus on refining raw polling data to
+enhance its quality and relevance for subsequent analysis. The dataset
+is first loaded and cleaned using the janitor package to standardize
+column names, ensuring consistency. We then filter the data to include
+only relevant columns and remove any rows with missing values in
+critical fields such as numeric_grade, pct, sample_size, and end_date.
+Specifically, we isolate the polling data for Kamala Harris and Donald
+Trump, applying a condition to keep only high-quality polls with a
+numeric grade of 2 or higher since we find out that the mean of the
+numeric grade is 2.175 while the median is 1.9.
+
+For state-level polls, we address any placeholder states marked as "--"
+by converting them to NA. A national poll indicator is created,
+assigning a value of 1 for national polls and 0 for state-specific ones.
+Dates are converted to a standard format using the lubridate package to
+ensure correct handling in analyses. We calculate recency weights based
+on how many days have passed since the poll ended, applying an
+exponential decay to give more weight to recent polls. A sample size
+weight is also implemented, capping the weights at a maximum of 2,300
+responses to reflect the reliability of larger sample
+sizes[@nyt_polling_averages]. Finally, the cleaned datasets for both
+candidates are saved in CSV format for further modeling and analysis.
+This systematic approach ensures that the data is accurate, complete,
+and ready for insightful analysis.
+
+## Analysis Data Summary Statistics
+
+@tbl-analysisdata presents the summary statistics for each recorded
+incident type for the years 2017 to 2022.
 
@@
 credit the original creation.
-
-> "Title of the Work" by Author Name, licensed under CC BY 4.0.
 
@@
 
+### Response bias defination
+
+In the design of the questionnaire, there will be some common bias that
+may occur when running the questionnaire.
+
+@survey define these bias as:
+
+-   Moderacy response bias is the tendency to respond to each question
+    by choosing a category in the middle of the scale.
+
+-   Extreme response bias is the tendency to respond with extreme values
+    on the rating scale.
+
+-   Response order bias occurs when the order of response options in a
+    list or a rating scale influences the response chosen. The primacy
+    effect occurs when respondents are more likely to select one of the
+    first alternatives provided, and it is more common in written
+    surveys. This tendency can be due to satisficing, whereby a
+    respondent uses the first acceptable response alternative without
+    paying particular attention to the other options. The recency effect
+    occurs when respondents choose one of the last items presented to
+    them (more common in face-to-face or orally presented surveys).
+
+-   Social desirability bias typically stems from the desire of
+    respondents to avoid embarrassment and project a favorable image to
+    others, resulting in respondents not revealing their actual
+    attitudes. The prevalence of this bias will depend on the topic,
+    questions, respondent, mode of the survey, and the social context.
+    For instance, in some circles, anti-immigrant views are not
+    tolerated, and those who hold them may try to hide them. In other
+    settings, people express such views more freely.
+
+-   Acquiescence is the tendency to answer items in a positive way
+    regardless of their content, for instance, systematically selecting
+    categories such as “agree,” “true,” or “yes”.
+
+### Strengths and Weakness
+
 **Strengths**:
@@
 questionnaire encourages participants to express their opinions more
-decisively. Furthermore, the inclusion of diverse question types can
-mitigate acquiescence bias, which occurs when respondents habitually
-agree with statements instead of reflecting their true feelings. By
-framing questions in a balanced manner and avoiding leading language,
-the design helps ensure that participants feel comfortable expressing
-varied opinions.
+decisively. For each of the degree question, Siena designed at least 4
+options to help the respondents not only choose extreme or moderate
+answer in the question.
+
+Furthermore, the inclusion of diverse question types can mitigate
+acquiescence bias, which occurs when respondents habitually agree with
+statements instead of reflecting their true feelings. By framing
+questions in a balanced manner and avoiding leading language, the design
+helps ensure that participants feel comfortable expressing varied
+opinions.
 
@@
 However, the questionnaire is not without its weaknesses. Critics
-highlight that the reliance on agree-disagree formats can lead to
-acquiescence bias, where respondents might select favorable options
+highlight that the reliance on agree-disagree, yes-no formats can lead
+to acquiescence bias, where respondents might select favorable options
 rather than accurately expressing their true opinions. This tendency
@@
 
-Additionally, the structure of the questions could inadvertently create
-extreme response bias, where participants feel pressured to choose the
-most extreme options rather than selecting a moderate stance. This bias
-can be exacerbated by the order in which questions are presented. If
-respondents encounter highly charged or leading questions early in the
-survey, they may be influenced to respond similarly in subsequent
-questions, a phenomenon known as ordering bias.
-
-Furthermore, while the questionnaire aims to be inclusive, if it fails
-to adequately represent the voices of certain demographic groups, it
-could lead to a lack of adequacy in the data collected. This inadequacy
-undermines the ability to draw comprehensive conclusions about the
-electorate, particularly in a diverse political landscape.
-
-In summary, while the questionnaire design has strengths in clarity and
-mixed-format questions that encourage engagement and nuanced responses,
-it also faces challenges related to biases such as acquiescence,
-nonresponse, extreme response tendencies, and ordering effects. To
-enhance its effectiveness, future iterations of the questionnaire should
-strive to incorporate more varied question types, ensure demographic
-representation, and remain mindful of question order and phrasing to
-minimize the potential for bias and improve the overall validity of the
+Additionally, since we don’t know whether they use randomization when
+interviewers ask the respondents, there might be response order bias
+with the occurrence of recency effect, in which respondents choose one
+of the last items presented to them ( as telephone survey is orally
+presented surveys). This bias can be exacerbated by the order of
+response options in a list or a rating scale influences the response
+chosen [@survey].
+
+Furthermore, as the questionnaire hasn't been provided, we haven't found
+an assured of complete anonymity in the survey landing and consent page
+(record of interviewers' words) in the posted questionnaire. This might
+cause social desirability bias, which typically stems from the desire of
+respondents to avoid embarrassment and project a favorable image to
+others, resulting in respondents not revealing their actual attitudes.
+Thus Siena cannot get the true polls from their sample.
+
+Finally, we noticed that the questionnaire is quite long, with more than
+50 questions. It will significantly increase the attribution rate of the
+questionnaires, especially in a telephone survey which takes more time
+than the online panel. This will increase the possibility of the
+occurrence of non-response bias.
+
+In summary, the questionnaire exhibits strengths such as clarity and a
+mixed-format approach that promotes engagement and nuanced responses.
+However, it faces significant challenges related to biases including
+acquiescence, nonresponse, social desirability, and ordering effects. To
+enhance its effectiveness, future iterations should incorporate a
+broader range of question types, ensure demographic representation, and
+carefully consider question order and phrasing. Addressing these issues
+is crucial for minimizing bias and improving the overall validity of the
 findings.
@@
 each subgroup within every region. To mitigate potential non-response
-bias, post-stratification weighting[^2] will be applied, correcting for
-any imbalances caused by variations in response rates among different
-demographic groups. The sample will be stratified based on several
-critical demographic and geographic variables to guarantee proportional
-representation of the U.S. voting population. Strata information will be
-sourced from U.S. census data obtained through IPUMS USA
-[@ruggles2024ipums].
-
-[^2]: Post-stratification weighting adjusts survey data by applying
-    weights to under- or over-represented demographic groups in the
-    sample, ensuring the final results align with the true population
-    distribution and reducing biases such as non-response bias.
+bias, post-stratification weighting\[\^2\] will be applied, correcting
+for any imbalances caused by variations in response rates among
+different demographic groups. The sample will be stratified based on
+several critical demographic and geographic variables to guarantee
+proportional representation of the U.S. voting population. Strata
+information will be sourced from U.S. census data obtained through IPUMS
+USA [@ruggles2024ipums].
+
+\[\^2\]: Post-stratification weighting adjusts survey data by applying
+weights to under- or over-represented demographic groups in the sample,
+ensuring the final results align with the true population distribution
+and reducing biases such as non-response bias.
 
@@
 | **Region**    | **States**                                                                                                                                                 |
-|-------------------------|-----------------------------------------------|
+|--------------------------|----------------------------------------------|
 | **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
-| **Northeast** | Connecticut, Delaware, District of Columbia, Maine, Maryland, Massachusetts, New Hampshire, New Jersey, New York, Pennsylvania, Rhode Island, Vermont      |
+| **NORTHEAST** | Connecticut, Delaware, District of Columbia, Maine, Maryland, Massachusetts, New Hampshire, New Jersey, New York, Pennsylvania, Rhode Island, Vermont      |
 | **SOUTH**     | Alabama, Arkansas, Florida, Georgia, Kentucky, Louisiana, Mississippi, North Carolina, Oklahoma, South Carolina, Tennessee, Texas, Virginia, West Virginia |
@@
 | **MIDWEST**   | 69%                   | 35,134,960             | 50,932,439 | 0.214805579                               | 86              |
-| **NW**      | 68%                   | 32,262,303             | 47,473,317 | 0.200216867                               | 80              |
+| **NORTHEAST** | 68%                   | 32,262,303             | 47,473,317 | 0.200216867                               | 80              |
 | **SOUTH**     | 65%                   | 54,746,770             | 84,563,831 | 0.356644666                               | 143             |
@@
 
-: Regional Voting Data and Sample Size Allocation Based on 2020 Election
-Turnout {#tbl-samplesize}
+: Regional Voting Data and Sample Size Allocation calculated using
+Composite Measure Sampling Proportion based on 2020 US Election regional
+voter turnout (%) {#tbl-samplesize}
 
@@
 
-@survey define these bias as:
-
--   Moderacy response bias is the tendency to respond to each question
-    by choosing a category in the middle of the scale.
-
--   Extreme response bias is the tendency to respond with extreme values
-    on the rating scale.
-
--   Response order bias occurs when the order of response options in a
-    list or a rating scale influences the response chosen. The primacy
-    effect occurs when respondents are more likely to select one of the
-    first alternatives provided, and it is more common in written
-    surveys. This tendency can be due to satisficing, whereby a
-    respondent uses the first acceptable response alternative without
-    paying particular attention to the other options. The recency effect
-    occurs when respondents choose one of the last items presented to
-    them (more common in face-to-face or orally presented surveys).
-
--   Social desirability bias typically stems from the desire of
-    respondents to avoid embarrassment and project a favorable image to
-    others, resulting in respondents not revealing their actual
-    attitudes. The prevalence of this bias will depend on the topic,
-    questions, respondent, mode of the survey, and the social context.
-    For instance, in some circles, anti-immigrant views are not
-    tolerated, and those who hold them may try to hide them. In other
-    settings, people express such views more freely.
-
--   Acquiescence is the tendency to answer items in a positive way
-    regardless of their content, for instance, systematically selecting
-    categories such as “agree,” “true,” or “yes”.
+We have defined the bias we want to solve in [Appendix C](#third-poll).
 
@@
 
-    -   Not important
+    Not important
     -   1
@@
     -   5
-    -   Very important
+    Very important
 
@@
 1.  **Do you have any concerns or feedback regarding the survey,
-    surveyor ,or entity?**\
+    surveyor, or entity?**\
     Your feedback is important to us and will help ensure transparency

### 2024-10-28 paper/paper.qmd
update with merged version

@@
 International License](https://creativecommons.org/licenses/by/4.0/).
-You are free to share, copy, redistribute, remix, transform, and build
-upon the material for any purpose, even commercially, as long as you
+We are free to share, copy, redistribute, remix, transform, and build
+upon the material for any purpose, even commercially, as long as we
 credit the original creation.

### 2024-10-29 scripts/04-test_analysis_data.R
fix code in clean scripts

@@ -14,6 +14,16 @@ library(testthat)
 
 data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
+raw_igme_data <-
+  read_csv(
+    file = "data/01-raw_data/raw_election_24.csv",
+    col_select = c(`Geographic area`, TIME_PERIOD, OBS_VALUE),
+    col_types = cols(
+      `Geographic area` = col_character(),
+      TIME_PERIOD = col_character(),
+      OBS_VALUE = col_double(),
+    )
+  )
 
 #### Test data ####
 # Test that the dataset has 151 rows - there are 151 divisions in Australia
@@ -67,3 +77,16 @@ test_that("no empty strings in 'division', 'party', or 'state' columns", {
 test_that("'party' column contains at least 2 unique values", {
   expect_true(length(unique(analysis_data$party)) >= 2)
 })
+
+rules <- validator(
+  is.numeric(age),
+  is.character(gender),
+  is.numeric(income),
+  age < 120,
+  gender %in% c("female", "male", "other", "prefer not to disclose")
+)
+
+out <-
+  confront(dataset_with_issues, rules)
+
+summary(out)

### 2024-10-29 scripts/05-model_data.R
Edit on model_data

@@ -12,21 +12,25 @@ library(ggplot2)
 library(lubridate)
 
 #### Step 1: Load cleaned data ####
-data <- read.csv("data/02-analysis_data/cleaned_harris_support.csv")
+library(dplyr)  # Load dplyr package
 
-# Ensure `end_date` exists and is in Date format or set it to today's date if missing
-if (!"end_date" %in% names(data)) {
-  data$end_date <- Sys.Date()
+data <- read.csv("data/02-analysis_data/analysis_data_Harris.csv")
+
+# Set end date to October 27, 2024, if it doesn't exist or is NA
+if (!"end_date" %in% names(data) || is.na(data$end_date[1])) {
+  data$end_date <- as.Date("2024-10-27")  # Set the end date to October 27, 2024
 } else {
-  data$end_date <- as.Date(data$end_date)
+  data$end_date <- as.Date(data$end_date)  # Convert existing end_date to Date format
 }
-data <- data %>% filter(!is.na(end_date))
+data <- data %>% filter(!is.na(end_date))  # Filter out rows with NA in end_date
 
 #### Step 2: Calculate weights ####
 # 2.1 Recency Weight
 data <- data %>%
   mutate(
-    days_since_poll = as.numeric(difftime(Sys.Date(), end_date, units = "days")),
+    # Assuming 'poll_release_date' is a new column you will need to create or add.
+    poll_release_date = as.Date("2024-10-15"),  # Replace with actual poll release date if available
+    days_since_poll = as.numeric(difftime(end_date, poll_release_date, units = "days")),
     recency_weight = ifelse(days_since_poll < 30, exp(-days_since_poll / 15), exp(-days_since_poll / 30))
   )
 

### 2024-10-29 scripts/03-clean_data.R
update analysis data

@@ -59,7 +59,7 @@ just_trump_high_quality <- cleaned_data|>
   # Drop rows with missing values in essential columns
   drop_na(numeric_grade, pct, sample_size, end_date)|>
   filter(
-    candidate_name == "Donal Trump",
+    candidate_name == "Donald Trump",
     numeric_grade >= 2 # mean of numeric_gradeis 2.175, median is 1.9 
   ) |>
   mutate(
@@ -81,4 +81,4 @@ just_trump_high_quality <- cleaned_data|>
          population, methodology, recency_weight, sample_size_weight, national_poll)
 #### Save data ####
 write_csv(just_harris_high_quality, "data/02-analysis_data/analysis_data_Harris.csv")
-write_csv(just_harris_high_quality, "data/02-analysis_data/analysis_data_Trump.csv")
+write_csv(just_trump_high_quality, "data/02-analysis_data/analysis_data_Trump.csv")

### 2024-10-29 scripts/03-clean_data.R
change name date since poll as recency

@@ -41,14 +41,11 @@ just_harris_high_quality <- cleaned_data |>
   )|>
   # Calculate recency weight using exponential decay (more recent polls get higher weight)
   mutate(
-    days_since_poll = as.numeric(difftime(Sys.Date(), end_date, units = "days")),
-    recency_weight = exp(-days_since_poll / 30)  # Adjust decay rate as needed
+    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
+    recency_weight = exp(-recency*0.1)  # Adjust decay rate as needed
   ) |>
   # Apply sample size weight, capped at a maximum of 2,300 responses
-  mutate(sample_size_weight = pmin(sample_size / 2300, 1)) |>
-  # Finalize relevant columns for modeling and remove unneeded columns
-  select(pollster, numeric_grade, state, pct, sample_size, 
-         population, methodology, recency_weight, sample_size_weight, national_poll)
+  mutate(sample_size_weight = pmin(sample_size / 2300, 1))
 
 just_trump_high_quality <- cleaned_data|>
   # Select relevant columns for analysis
@@ -71,14 +68,11 @@ just_trump_high_quality <- cleaned_data|>
   )|>
   # Calculate recency weight using exponential decay (more recent polls get higher weight)
   mutate(
-    days_since_poll = as.numeric(difftime(Sys.Date(), end_date, units = "days")),
-    recency_weight = exp(-days_since_poll / 30)  # Adjust decay rate as needed
+    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
+    recency_weight = exp(-recency*0.1)  # Adjust decay rate as needed
   ) |>
   # Apply sample size weight, capped at a maximum of 2,300 responses
-  mutate(sample_size_weight = pmin(sample_size / 2300, 1)) |>
-  # Finalize relevant columns for modeling and remove unneeded columns
-  select(pollster, numeric_grade, state, pct, sample_size, 
-         population, methodology, recency_weight, sample_size_weight, national_poll)
+  mutate(sample_size_weight = pmin(sample_size / 2300, 1)) 
 #### Save data ####
 write_csv(just_harris_high_quality, "data/02-analysis_data/analysis_data_Harris.csv")
 write_csv(just_trump_high_quality, "data/02-analysis_data/analysis_data_Trump.csv")

### 2024-10-30 scripts/05-model_data.R
adjust model set up

@@ -6,95 +6,70 @@
 # License: MIT
 # Pre-requisites: Cleaned data file `cleaned_harris_support.csv` should be available in the `data/02-analysis_data/` directory.
 
-#### Workspace setup ####
+
+#### Load cleaned data ####
 library(dplyr)
-library(ggplot2)
-library(lubridate)
 
-#### Step 1: Load cleaned data ####
-library(dplyr)  # Load dplyr package
+# Load Harris and Trump data
+harris_data <- read.csv("data/02-analysis_data/analysis_data_Harris.csv")
+trump_data <- read.csv("data/02-analysis_data/analysis_data_Trump.csv")
 
-data <- read.csv("data/02-analysis_data/analysis_data_Harris.csv")
-
-# Set end date to October 27, 2024, if it doesn't exist or is NA
-if (!"end_date" %in% names(data) || is.na(data$end_date[1])) {
-  data$end_date <- as.Date("2024-10-27")  # Set the end date to October 27, 2024
-} else {
-  data$end_date <- as.Date(data$end_date)  # Convert existing end_date to Date format
-}
-data <- data %>% filter(!is.na(end_date))  # Filter out rows with NA in end_date
-
-#### Step 2: Calculate weights ####
-# 2.1 Recency Weight
-data <- data %>%
+#### Calculate Weights ####
+# Calculate weights for Harris data
+harris_data <- harris_data %>%
   mutate(
-    # Assuming 'poll_release_date' is a new column you will need to create or add.
-    poll_release_date = as.Date("2024-10-15"),  # Replace with actual poll release date if available
-    days_since_poll = as.numeric(difftime(end_date, poll_release_date, units = "days")),
-    recency_weight = ifelse(days_since_poll < 30, exp(-days_since_poll / 15), exp(-days_since_poll / 30))
-  )
-
-# 2.2 Sample Size Weight (cap at 2,300 responses)
-data <- data %>%
-  mutate(sample_size_weight = pmin(sample_size / 2300, 1))
-
-# 2.3 Poll Frequency by Pollster
-data <- data %>%
+    sample_size_weight = pmin(sample_size / 2300, 1),
+    pollster_quality_weight = numeric_grade / 4
+  ) %>%
   group_by(pollster) %>%
   mutate(
-    recent_poll_count = sum(days_since_poll < 30),
+    recent_poll_count = sum(recency < 30),
[…]

### 2024-10-30 paper/paper.qmd
update paper title

@@
 ---
-title: "Forecasting 2024 US election using linear regression"
+title: "Based on polling as of 27 October 2024, Harris expects to win on xxx%, leads Trump by xx% in 2024 US election"
+subtitle: "Weighted Linear Regression Analysis of Aggregated Poll Data: Utilizing National Polls indicator, Recency of Polls, Sample Size, Pollster Quality Rate, and Poll Frequency as Predictors."
 author: 
@@
 first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+  readRDS(file = here::here("models/model_unweighted.rds"))
 ```
@@
 
-## Analysis Data Summary Statistics
-
-@tbl-analysisdata presents the summary statistics for each recorded
-incident type for the years 2017 to 2022.
-
 ## Attribution Statement
@@
 This work is licensed under a [Creative Commons Attribution 4.0
-International License](https://creativecommons.org/licenses/by/4.0/).
-We are free to share, copy, redistribute, remix, transform, and build
-upon the material for any purpose, even commercially, as long as we
-credit the original creation.
+International License](https://creativecommons.org/licenses/by/4.0/). We
+are free to share, copy, redistribute, remix, transform, and build upon
+the material for any purpose, even commercially, as long as we credit
+the original creation.
 
@@
 
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive
-check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the
-prior. This shows...
+## Model validation
 
 ```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
+# Set seed for reproducibility
+set.seed(123)
+
+# Sample indices for training and testing sets
+train_index <- sample(seq_len(nrow(data)), size = 0.8 * nrow(data))
+
+# Split the data into training and testing sets
+train_data <- data[train_index, ]
+test_data <- data[-train_index, ]
+
+# Fit the weighted linear regression model
+first_model_test <- lm(pct ~ national_poll + pollster + population, 
+                     data = data, 
+                  data = train_data)
+
+# Predict on test data
+predictions <- predict(first_model_test, newdata = test_data)
+
+# Calculate RMSE using the correct outcome variable
+# Assuming 'pct' is the actual observed outcome variable in test_data
+rmse <- sqrt(mean((predictions - test_data$pct)^2, na.rm = TRUE))
+
+# Print RMSE
+print(paste("RMSE:", rmse))
+
 ```
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+@fig-stanareyouokay-1 is a residual plot of un-weighted model. It shows... This suggests...
+
+@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot. It shows... This suggests...
 
@@
 #| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
+#residual plot
+plot(first_model, which = 1,main ="Residual Plot of unweighted linear regression model residualsmodel" )
+# Q-Q plot for the residuals of the model
+qqnorm(residuals(first_model),main= "Q-Q Plot of unweighted linear regression model residuals
+")
+qqline(residuals(first_model), col = "red")
+
 ```
@@
 
-6.  **How certain are you about your candidate choice?**
-
-    -   Very certain
-    -   Somewhat certain
-    -   Not certain
+6.  **How likely are you going to vote in the 2024 election**
+
+    Definitely not to vote
+
+    -   1
+    -   2
+    -   3
+    -   4
+    -   5
+    -   6
+    -   7
+    -   8
+    -   9
+    -   10 Definitely will vote
 
@@
     Not important
+
     -   1
@@
     -   4
-    -   5
-    Very important
+    -   5 Very important
 

### 2024-10-30 paper/paper.qmd
update data cleaning part

@@
 title: "Based on polling as of 27 October 2024, Harris expects to win on xxx%, leads Trump by xx% in 2024 US election"
-subtitle: "Weighted Linear Regression Analysis of Aggregated Poll Data: Utilizing National Polls indicator, Recency of Polls, Sample Size, Pollster Quality Rate, and Poll Frequency as Predictors."
+subtitle: "Weighted Linear Regression Analysis of Aggregated Poll Data: Utilizing National Polls indicator, Population, and Pollster as Predictors."
 author: 
@@
 
-In this data-cleaning process, we focus on refining raw polling data to
-enhance its quality and relevance for subsequent analysis. The dataset
-is first loaded and cleaned using the janitor package to standardize
-column names, ensuring consistency. We then filter the data to include
-only relevant columns and remove any rows with missing values in
-critical fields such as numeric_grade, pct, sample_size, and end_date.
-Specifically, we isolate the polling data for Kamala Harris and Donald
-Trump, applying a condition to keep only high-quality polls with a
-numeric grade of 2 or higher since we find out that the mean of the
-numeric grade is 2.175 while the median is 1.9.
-
-For state-level polls, we address any placeholder states marked as "--"
-by converting them to NA. A national poll indicator is created,
-assigning a value of 1 for national polls and 0 for state-specific ones.
-Dates are converted to a standard format using the lubridate package to
-ensure correct handling in analyses. We calculate recency weights based
-on how many days have passed since the poll ended, applying an
-exponential decay to give more weight to recent polls. A sample size
-weight is also implemented, capping the weights at a maximum of 2,300
-responses to reflect the reliability of larger sample
-sizes[@nyt_polling_averages]. Finally, the cleaned datasets for both
-candidates are saved in CSV format for further modeling and analysis.
-This systematic approach ensures that the data is accurate, complete,
-and ready for insightful analysis.
+In this data-cleaning process, we focus on refining raw polling data to enhance its quality and relevance for subsequent analysis.
+The dataset is initially loaded and cleaned using the janitor package to standardize column names, ensuring consistency throughout.
+We then filter the data to retain only relevant columns and eliminate any rows with missing values in critical fields, including numeric_grade, pct, sample_size, and end_date.
+
+Specifically, we isolate the polling data for Kamala Harris and Donald Trump, applying a condition to include only high-quality polls with a numeric grade of 2 or higher, given that the mean of the numeric grade is 2.175 and the median is 1.9.
+
+For state-level polls, we handle any placeholder states marked as "--" by converting them to NA.
+A national poll indicator is generated, assigning a value of 1 for national polls and 0 for state-specific ones.
+Dates are standardized using the lubridate package to ensure accurate handling in subsequent analyses.
+
+Recency weights are calculated based on the number of days elapsed since the poll ended, utilizing an exponential decay function to give greater weight to more recent polls.
+Additionally, a sample size weight is implemented, capping the weights at a maximum of 2,300 responses to reflect the reliability of larger sample sizes.
+
+Finally, the cleaned datasets for both candidates are saved in CSV format for further modeling and analysis.
+This systematic approach guarantees that the data is accurate, complete, and ready for insightful analysis.
 

### 2024-10-30 scripts/03-clean_data.R
update analysis data as parquet form

@@ -11,7 +11,7 @@
 library(tidyverse)
 library(janitor)
 library(lubridate)
-
+library(arrow)
 #### Clean data ####
 raw_data <- read_csv("data/01-raw_data/raw_election_24.csv")
 
@@ -46,6 +46,14 @@ just_harris_high_quality <- cleaned_data |>
   ) |>
   # Apply sample size weight, capped at a maximum of 2,300 responses
   mutate(sample_size_weight = pmin(sample_size / 2300, 1))
+just_harris_high_quality <- just_harris_high_quality %>%
+  mutate(
+    pollster = factor(pollster),
+    state = factor(state),
+    candidate_name = factor(candidate_name),
+    population = factor(population),  # Only if appropriate
+    methodology = factor(methodology)
+  )
 
 just_trump_high_quality <- cleaned_data|>
   # Select relevant columns for analysis
@@ -73,6 +81,14 @@ just_trump_high_quality <- cleaned_data|>
   ) |>
   # Apply sample size weight, capped at a maximum of 2,300 responses
   mutate(sample_size_weight = pmin(sample_size / 2300, 1)) 
+just_trump_high_quality <- just_trump_high_quality %>%
+  mutate(
+    pollster = factor(pollster),
+    state = factor(state),
+    candidate_name = factor(candidate_name),
+    population = factor(population),  # Only if appropriate
+    methodology = factor(methodology)
+  )
 #### Save data ####
-write_csv(just_harris_high_quality, "data/02-analysis_data/analysis_data_Harris.csv")
-write_csv(just_trump_high_quality, "data/02-analysis_data/analysis_data_Trump.csv")
+write_parquet(just_harris_high_quality, "data/02-analysis_data/analysis_data_Harris.parquet")
+write_parquet(just_trump_high_quality, "data/02-analysis_data/analysis_data_Trump.parquet")

### 2024-10-30 scripts/02-download_data.R
update preamble

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from FiveThirtyeight.com
+# Author: Diana Shen, Jinyan Wei, Huayan Yu
+# Date: 27 October 2024 
+# Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: no
+# Any other information needed? no
 
 
 #### Workspace setup ####

### 2024-10-30 paper/paper.qmd
Change on data format

@@
 
-# Model
+## Model
 
 We conducted a regression analysis to predict support for Kamala Harris
-in the 2024 U.S. presidential election. Our analysis includes two
-models: an **unweighted linear model** and a **weighted linear model**.
-These models predict Harris’s support as a continuous outcome across
-different states, using aggregated polling data with a focus on
-adjusting for poll quality, sample size, recency, and potential
-partisanship biases. This setup aligns with the New York Times
-methodology for election polling, which assigns weights based on poll
-quality, sample size, and recency of the poll to reflect an accurate
-picture of voter sentiment [@nytimes].
+and Donald Trump in the 2024 U.S. presidential election, including
+models for Trump for comparison. Our analysis includes four models:
+**unweighted linear models** and **weighted linear models** for both
+candidates. These models predict each candidate’s support as a
+continuous outcome across different states, using **pollster**,
+**national poll**, and **population** as key predictors. The weighted
+models additionally incorporate adjustments for recency, sample size,
+and poll quality to account for potential biases. This setup aligns with
+the New York Times methodology for election polling, which assigns
+weights based on poll quality, sample size, and recency to better
+reflect voter sentiment [@nytimes].
 
@@
 We implemented our linear regression models using the `lm()` function in
-R. The unweighted model provides a baseline with equal treatment for all
-polls, while the weighted model adjusts each poll observation based on
-combined factors, including recency, sample size, and poll quality. The
-model specifications are as follows:
-
-#### Unweighted Linear Model
-
-The unweighted model serves as a baseline, treating all polls equally
-without incorporating adjustments for recency, sample size, or poll
-quality. The model is defined as:
+R.
+
+### Mathematical Expressions
+
+Both the unweighted and weighted models share the same mathematical
+expression format:
+
+#### Unweighted Model
+
+The unweighted model for Harris provides a baseline by treating all
+polls equally without adjustments for recency, sample size, or poll
+quality:
 
 $$
-\text{Support_Harris}_i = \beta_0 + \beta_1 \cdot \text{National_Poll}_i + \epsilon_i
+\text{Support\_Harris}_i = \beta_0 + \beta_1 \cdot \text{National\_Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \epsilon_i
 $$
 
-This unweighted model provides a baseline estimate of Harris’s support
-across different polls without considering variations in poll recency,
-sample size, or quality. It allows us to understand Harris’s support
-level with a simplified assumption that all polls are of equal
-relevance.
-
-#### Weighted Linear Model
-
-To enhance the accuracy of our predictions, the weighted model
-incorporates adjustments for recency, sample size, and pollster quality.
-This model is defined as:
+```{r}
+model_harris_unweighted <- lm(pct ~ national_poll + pollster + population, data = harris_data)
+```
+
+#### Weighted Model
+
+The weighted model for Harris incorporates adjustments for recency,
+sample size, and pollster quality:
 
 $$
-\text{Support_Harris}_i = \beta_0 + \beta_1 \cdot \text{National_Poll}_i + \beta_2 \cdot \text{Recency_Weight}_i + \beta_3 \cdot \text{Sample_Size_Weight}_i + \beta_4 \cdot \text{Numeric_Grade}_i + \epsilon_i
+\text{Support\_Harris}_i = \beta_0 + \beta_1 \cdot \text{National\_Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \epsilon_i
 $$
 
-The weighted model applies these additional factors to account for
-variations in data quality and recency, offering a refined view of
-Harris’s support.
-
-## Model Justification
-
-In developing our model to predict support for Kamala Harris, we
-included adjustments based on national polling, recency, sample size,
-and pollster grade. These features were selected to mitigate common
-biases in polling data and to ensure our model reflects up-to-date and
-high-quality information. The decision to incorporate recency as a
-predictor is motivated by the observation that voter sentiment can shift
-rapidly in response to events, such as debates or political
-controversies, especially as the election date approaches (The New York
-Times, 2024). Sample size was also used as a weight, as larger polls
-tend to reduce sampling variability up to a reasonable threshold, set at
-2,300 responses.
-
-Pollster quality, represented through numeric grades, accounts for
-systematic differences in methodology, professionalism, and past
-accuracy. Pollsters with a strong historical performance are given more
-weight, as they are more likely to produce unbiased and reliable
-results. The model structure, however, is based on linear regression,
-meaning it assumes an additive relationship between these predictors and
-voter support. This simplification, while computationally efficient and
-interpretable, may not capture more complex interactions between
-factors, such as shifts in demographic or regional support.
-
-Our model was implemented in R using the `lm()` function for the
-unweighted model and a weighted version for the adjusted model.
-Validation was performed using out-of-sample testing and RMSE
-calculations to assess accuracy. Sensitivity analyses were also
-conducted, examining how the model performed across different subsets of
-data.
-
-The model has several limitations, including the linearity assumption,
-which may not fully capture the dynamic nature of voter support. Its
-effectiveness relies on the assumption that the weights (recency, sample
-size, pollster grade) adequately mitigate biases in polling data.
-Additionally, it does not account for third-party candidates or
-undecided voters, which could affect the election outcome. While
-Bayesian hierarchical models were considered for their capability to
-handle multi-level data, they were ultimately set aside for a simpler,
-more interpretable linear model due to the analysis's scope and
-computational constraints. Future research should explore these more
-complex methods if time and resources permit.
-
-# Results
-
-Our results are summarized in @tbl-modelresults.
+```{r}
+model_harris_weighted <- lm(pct ~ national_poll + pollster + population, data = harris_data, weights = combined_weight)
+```
+
+### Coefficient Explanations
+
+-   $\beta_0$: Intercept of the model, representing the expected support
+    when all predictors are zero.
+-   $\beta_1$: Coefficient for the national poll, indicating how much
+    support changes with a one-unit increase in the national poll
+    percentage.
+-   $\beta_2$: Coefficient for the pollster, reflecting the impact of
+    different polling organizations on support.
+-   $\beta_3$: Coefficient for the population, accounting for the
+    influence of the demographic context on support levels.
+
+### Model Justification
+
+1.  **Use of Weighted Model**: The weighted model is essential for
+    accurately reflecting voter sentiment. By incorporating weights, we
+    adjust for the reliability of the polling data, ensuring that more
+    credible polls have a greater influence on the estimates.
+
+2.  **Calculation of Variables**:
+
+    -   **Combined Weight**: The combined weight is calculated as
+        follows: $$
+        \text{combined\_weight} = \text{recency\_weight} \times \text{sample\_size\_weight} \times \text{poll\_frequency\_weight} \times \text{pollster\_quality\_weight}
+        $$
+
+    -   **Recency Weight**: This weight uses an exponential decay
+        function: $$
+        \text{recency\_weight} = \exp(-\text{Recency}_i \cdot 0.1)
+        $$ This reflects the diminishing influence of older polls, with
+        $\lambda = 0.1$ for the exponential decay.
+
+    -   **Sample Size Weight**: This weight adjusts the significance of
+        each poll based on the number of respondents, capping the
+        weights at a maximum of 2,300 responses to reflect the
+        reliability of larger sample sizes [@nyt_polling_averages].
+
+    -   **Poll Frequency Weight**: This weight considers how often a
+        pollster conducts polls, with higher weights assigned to
+        pollsters with a greater number of recent surveys.
+
+    -   **Pollster Quality Weight**: Based on the historical performance
+        of the pollster, this weight emphasizes the reliability of their
+        polling methods.
+
+### Alternative Models
+
+While this analysis employs linear regression with weighted least
+squares, alternative methods such as Bayesian modeling could provide
+additional insights. However, we opted for the weighted linear
+regression approach to maintain interpretability and ease of
+implementation given the scope and resources of this analysis. The
+Bayesian approach was not chosen primarily due to the complexity
+involved in defining priors and the additional computational
+requirements.
+
+### Weighted Least Squares Estimation
+
+In our analysis, we utilize weighted least squares estimation to account
+for the varying quality of polling data. The weights are crucial in the
+estimation process, leading to the following expression for the
+estimates of the coefficients ($\hat{\beta}$):
+
+$$
+\hat{\beta} = (X^T W X)^{-1} X^T W y
+$$
+
+Where: - $X$ is the design matrix of predictors. - $W$ is the diagonal
+matrix of weights, which incorporates factors such as recency, sample
+size, and pollster quality to enhance the reliability of our estimates.
+
+### Importance of Combined Weights
+
+By incorporating these combined weights, the weighted model offers a
+more nuanced estimation of voter support for both Harris and Trump.
+While the mathematical expression for the models remains consistent, the
+weighted models effectively adjust for variations in data quality and
+recency, leading to more accurate predictions of voter sentiment.
+
+# Result
 
@@
 
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/model_unweighted.rds"))
+#### Load Required Libraries ####
+library(dplyr)
+library(ggplot2)
+library(lubridate)
+harris_data <- harris_data %>%
+  mutate(
+    recency_weight = exp(-recency * 0.1),
+    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
+    predicted_support = predict(model_harris_weighted, newdata = .),
+    candidate = "Harris"
+  )
+
+trump_data <- trump_data %>%
+  mutate(
+    recency_weight = exp(-recency * 0.1),
+    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
+    predicted_support = predict(model_trump_weighted, newdata = .),
+    candidate = "Trump"
+  )
+
+# Combine both datasets
+combined_data <- bind_rows(harris_data, trump_data)
+
+#### Plot Support Trends by State with Reduced Date Labels ####
+# Define states of interest
+selected_states <- c("Pennsylvania", "Nevada", "North Carolina", "Wisconsin", "Michigan", "Georgia", "Arizona")
+
+# Filter data for selected states
+combined_data <- combined_data %>% filter(state %in% selected_states)
+
+# Create the faceted plot with limited x-axis labels
+ggplot(combined_data, aes(x = as.Date(end_date), y = predicted_support, color = candidate, size = combined_weight)) +
+  geom_point(alpha = 0.6) +
+  scale_color_manual(values = c("Harris" = "#1f77b4", "Trump" = "#d62728")) +  # Blue for Harris, Red for Trump
+  scale_size_continuous(range = c(1, 4)) +  # Control point size range for readability
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 month") +  # Show only the first day of each month
+  labs(title = "Support Trends for Harris and Trump Across States",
+       x = "Date", y = "Support (%)", color = "Candidate") +
+  facet_wrap(~ state, ncol = 2, scales = "free_y") +  # Facet by state with free y-scale
+  theme_minimal(base_size = 12) +
+  theme(
+    legend.position = "top",
+    strip.text = element_text(size = 12, face = "bold"),
+    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),  # Slight tilt for x-axis labels
+    panel.grid.major = element_line(size = 0.2, linetype = "dotted", color = "gray80"),
+    panel.grid.minor = element_blank()
+  )
 ```

### 2024-10-30 scripts/05-model_data.R

@@ -11,15 +11,16 @@
 library(dplyr)
 
 # Load Harris and Trump data
-harris_data <- read.csv("data/02-analysis_data/analysis_data_Harris.csv")
-trump_data <- read.csv("data/02-analysis_data/analysis_data_Trump.csv")
+harris_data <- read_parquet("data/02-analysis_data/analysis_data_Harris.parquet")
+trump_data <- read_parquet("data/02-analysis_data/analysis_data_Trump.parquet")
 
 #### Calculate Weights ####
 # Calculate weights for Harris data
 harris_data <- harris_data %>%
   mutate(
     sample_size_weight = pmin(sample_size / 2300, 1),
-    pollster_quality_weight = numeric_grade / 4
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
   ) %>%
   group_by(pollster) %>%
   mutate(
@@ -27,13 +28,14 @@ harris_data <- harris_data %>%
     poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
   ) %>%
   ungroup() %>%
-  mutate(combined_weight = recency * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
 
 # Calculate weights for Trump data
 trump_data <- trump_data %>%
   mutate(
     sample_size_weight = pmin(sample_size / 2300, 1),
-    pollster_quality_weight = numeric_grade / 4
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
   ) %>%
   group_by(pollster) %>%
   mutate(
@@ -41,18 +43,8 @@ trump_data <- trump_data %>%
     poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
   ) %>%
   ungroup() %>%
-  mutate(combined_weight = recency * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
 
-#### Model Preparation ####
-# Define selected states for filtering
-selected_states <- c("Pennsylvania", "Nevada", "North Carolina", "Wisconsin", "Michigan", "Georgia", "Arizona")
-
-# Filter Harris and Trump data by selected states
[…]

### 2024-10-30 scripts/05-model_data.R
merge

@@ -13,6 +13,8 @@ library(dplyr)
 # Load Harris and Trump data
 harris_data <- read.csv("data/02-analysis_data/analysis_data_Harris.csv")
 trump_data <- read.csv("data/02-analysis_data/analysis_data_Trump.csv")
+harris_data <- read_parquet("data/02-analysis_data/analysis_data_Harris.parquet")
+trump_data <- read_parquet("data/02-analysis_data/analysis_data_Trump.parquet")
 
 #### Calculate Weights ####
 # Calculate weights for Harris data
@@ -20,6 +22,8 @@ harris_data <- harris_data %>%
   mutate(
     sample_size_weight = pmin(sample_size / 2300, 1),
     pollster_quality_weight = numeric_grade / 4
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
   ) %>%
   group_by(pollster) %>%
   mutate(
@@ -28,12 +32,15 @@ harris_data <- harris_data %>%
   ) %>%
   ungroup() %>%
   mutate(combined_weight = recency * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
 
 # Calculate weights for Trump data
 trump_data <- trump_data %>%
   mutate(
     sample_size_weight = pmin(sample_size / 2300, 1),
     pollster_quality_weight = numeric_grade / 4
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
   ) %>%
   group_by(pollster) %>%
   mutate(
@@ -46,6 +53,7 @@ trump_data <- trump_data %>%
 #### Model Preparation ####
 # Define selected states for filtering
 selected_states <- c("Pennsylvania", "Nevada", "North Carolina", "Wisconsin", "Michigan", "Georgia", "Arizona")
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
 
 # Filter Harris and Trump data by selected states
 harris_data <- harris_data %>%

### 2024-10-30 paper/paper.qmd
merge conflict

--- 2024-10-30 paper/paper.qmd
@@
 
-In this data-cleaning process, we focus on refining raw polling data to enhance its quality and relevance for subsequent analysis.
-The dataset is initially loaded and cleaned using the janitor package to standardize column names, ensuring consistency throughout.
-We then filter the data to retain only relevant columns and eliminate any rows with missing values in critical fields, including numeric_grade, pct, sample_size, and end_date.
-
-Specifically, we isolate the polling data for Kamala Harris and Donald Trump, applying a condition to include only high-quality polls with a numeric grade of 2 or higher, given that the mean of the numeric grade is 2.175 and the median is 1.9.
-
-For state-level polls, we handle any placeholder states marked as "--" by converting them to NA.
-A national poll indicator is generated, assigning a value of 1 for national polls and 0 for state-specific ones.
-Dates are standardized using the lubridate package to ensure accurate handling in subsequent analyses.
-
-Recency weights are calculated based on the number of days elapsed since the poll ended, utilizing an exponential decay function to give greater weight to more recent polls.
-Additionally, a sample size weight is implemented, capping the weights at a maximum of 2,300 responses to reflect the reliability of larger sample sizes.
-
-Finally, the cleaned datasets for both candidates are saved in CSV format for further modeling and analysis.
-This systematic approach guarantees that the data is accurate, complete, and ready for insightful analysis.
+In this data-cleaning process, we focus on refining raw polling data to
+enhance its quality and relevance for subsequent analysis. The dataset
+is initially loaded and cleaned using the janitor package to standardize
+column names, ensuring consistency throughout. We then filter the data
+to retain only relevant columns and eliminate any rows with missing
+values in critical fields, including numeric_grade, pct, sample_size,
+and end_date.
+
+Specifically, we isolate the polling data for Kamala Harris and Donald
+Trump, applying a condition to include only high-quality polls with a
+numeric grade of 2 or higher, given that the mean of the numeric grade
+is 2.175 and the median is 1.9.
+
+For state-level polls, we handle any placeholder states marked as "--"
+by converting them to NA. A national poll indicator is generated,
+assigning a value of 1 for national polls and 0 for state-specific ones.
+Dates are standardized using the lubridate package to ensure accurate
+handling in subsequent analyses.
+
+Recency weights are calculated based on the number of days elapsed since
+the poll ended, utilizing an exponential decay function to give greater
+weight to more recent polls. Additionally, a sample size weight is
+implemented, capping the weights at a maximum of 2,300 responses to
+reflect the reliability of larger sample sizes.
+
+Finally, the cleaned datasets for both candidates are saved in CSV
+format for further modeling and analysis. This systematic approach
+guarantees that the data is accurate, complete, and ready for insightful
+analysis.
 
@@
 ```{r}
-# Set seed for reproducibility
+#| include: false
+#### Calculate Weights ####
+#harris_data <-read.csv("~/2024 US Election Forecast/data/02-analysis_data/analysis_data_Harris.csv")
+#trump_data <- read.csv("~/2024 US Election Forecast/data/02-analysis_data/analysis_data_Trump.csv")
+## if you haven't run the model script, use this code
+# Calculate weights for Harris data
+# harris_data <- harris_data %>%
+#   mutate(
+#     sample_size_weight = pmin(sample_size / 2300, 1),  # Cap weight at 1
+#     pollster_quality_weight = numeric_grade / 4  # Scale numeric grade to [0, 1]
+#   ) %>%
+#   group_by(pollster) %>%
+#   mutate(
+#     recent_poll_count = sum(recency < 30),  # Count recent polls within the last 30 days
+#     poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)  # Adjust frequency weight
+#   ) %>%
+#   ungroup() %>%
+#   mutate(combined_weight = recency * sample_size_weight * poll_frequency_weight * pollster_quality_weight)  # Combine weights
+
+# Calculate weights for Trump data (similar to Harris)
+# trump_data <- trump_data %>%
+#   mutate(
+#     sample_size_weight = pmin(sample_size / 2300, 1),  # Cap weight at 1
+#     pollster_quality_weight = numeric_grade / 4  # Scale numeric grade to [0, 1]
+#   ) %>%
+#   group_by(pollster) %>%
+#   mutate(
+#     recent_poll_count = sum(recency < 30),  # Count recent polls within the last 30 days
+#     poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)  # Adjust frequency weight
+#   ) %>%
+#   ungroup() %>%
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#### Set Seed for Reproducibility ####
+set.seed(567)
+
+# Sample indices for training and testing sets for Harris data
+train_index_harris <- sample(seq_len(nrow(harris_data)), size = 0.8 * nrow(harris_data))
+
+# Split the data into training and testing sets
+train_data_harris <- harris_data[train_index_harris, ]
+test_data_harris <- harris_data[-train_index_harris, ]
+
+# Convert pollster to factor in the training dataset
+train_data_harris$pollster <- factor(train_data_harris$pollster)
+
+# Get levels from the training dataset
+pollster_levels <- levels(train_data_harris$pollster)
+
+# Set the same levels for pollster in testing data
+test_data_harris$pollster <- factor(test_data_harris$pollster, levels = pollster_levels)
+
+#### Fit the Unweighted Linear Regression Model for Harris ####
+model_harris_unweighted <- lm(pct ~ national_poll + pollster + population, 
+                             data = train_data_harris)
+
+# Predict on test data for unweighted model
+predictions_unweighted <- predict(model_harris_unweighted, newdata = test_data_harris)
+
+# Calculate RMSE for unweighted model
+rmse_unweighted <- sqrt(mean((predictions_unweighted - test_data_harris$pct)^2, na.rm = TRUE))
+cat("Harris Unweighted Model RMSE:", rmse_unweighted, "\n")
+
+#### Fit the Weighted Linear Regression Model for Harris ####
+model_harris_weighted <- lm(pct ~ national_poll + pollster + population, 
+                           data = train_data_harris, weights = combined_weight)
+
+# Predict on test data for weighted model
+predictions_weighted <- predict(model_harris_weighted, newdata = test_data_harris)
+
+# Calculate RMSE for weighted model
+rmse_weighted <- sqrt(mean((predictions_weighted - test_data_harris$pct)^2, na.rm = TRUE))
+cat("Harris Weighted Model RMSE:", rmse_weighted, "\n")
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#### Set Seed for Reproducibility ####
 set.seed(123)
 
-# Sample indices for training and testing sets
-train_index <- sample(seq_len(nrow(data)), size = 0.8 * nrow(data))
+# Sample indices for training and testing sets for Trump data
+train_index_trump <- sample(seq_len(nrow(trump_data)), size = 0.8 * nrow(trump_data))
 
 # Split the data into training and testing sets
-train_data <- data[train_index, ]
-test_data <- data[-train_index, ]
-
-# Fit the weighted linear regression model
-first_model_test <- lm(pct ~ national_poll + pollster + population, 
-                     data = data, 
-                  data = train_data)
-
-# Predict on test data
-predictions <- predict(first_model_test, newdata = test_data)
-
-# Calculate RMSE using the correct outcome variable
-# Assuming 'pct' is the actual observed outcome variable in test_data
-rmse <- sqrt(mean((predictions - test_data$pct)^2, na.rm = TRUE))
-
-# Print RMSE
-print(paste("RMSE:", rmse))
-
+train_data_trump <- trump_data[train_index_trump, ]
+test_data_trump <- trump_data[-train_index_trump, ]
+
+# Convert pollster to factor in the training dataset
+train_data_trump$pollster <- factor(train_data_trump$pollster)
+
+# Get levels from the training dataset
+pollster_levels <- levels(train_data_trump$pollster)
+
+# Set the same levels for pollster in testing data
+test_data_trump$pollster <- factor(test_data_trump$pollster, levels = pollster_levels)
+
+#### Fit the Unweighted Linear Regression Model for Trump ####
+model_trump_unweighted <- lm(pct ~ national_poll + pollster + population, 
+                             data = train_data_trump)
+
+# Predict on test data for unweighted model
+predictions_unweighted <- predict(model_trump_unweighted, newdata = test_data_trump)
+
+# Calculate RMSE for unweighted model
+rmse_unweighted <- sqrt(mean((predictions_unweighted - test_data_trump$pct)^2, na.rm = TRUE))
+cat("Trump Unweighted Model RMSE:", rmse_unweighted, "\n")
+
+#### Fit the Weighted Linear Regression Model for Trump ####
+model_trump_weighted <- lm(pct ~ national_poll + pollster + population, 
+                           data = train_data_trump, weights = combined_weight)
+
+# Predict on test data for weighted model
+predictions_weighted <- predict(model_trump_weighted, newdata = test_data_trump)
+
+# Calculate RMSE for weighted model
+rmse_weighted <- sqrt(mean((predictions_weighted - test_data_trump$pct)^2, na.rm = TRUE))
+cat("Trump Weighted Model RMSE:", rmse_weighted, "\n")
 ```
 
+The RMSE (Root Mean Square Error) values for the models indicate how
+well the models predict the percentage of support for Kamala Harris and
+Donald Trump in the 2024 U.S. presidential election. For the Harris
+models, the unweighted RMSE is approximately 2.24, while the weighted
+model achieves a slightly better performance with an RMSE of about 2.19.
+This improvement in the weighted model suggests that incorporating
+weights—likely reflecting the reliability or relevance of the
+polls—provides a more accurate prediction of Harris's support levels
+compared to the unweighted approach. The smaller RMSE value signifies
+that the predictions made by the weighted model are closer to the actual
+observed percentages, indicating better model performance.
+
+In contrast, the RMSE values for Trump indicate a different scenario.
+The unweighted model for Trump has an RMSE of approximately 2.97, while
+the weighted model has a higher RMSE of about 3.07. This unexpected
+outcome suggests that adding weights to the Trump model may have
+introduced more variability or noise in the predictions rather than
+improving accuracy. The higher RMSE in the weighted model compared to
+the unweighted model indicates that the weighting scheme used might not
+have been effective in capturing the true relationship between the
+predictors and Trump’s support levels, potentially due to factors such
+as multicollinearity or insufficient variation in the data. Overall,
+while the Harris models show consistent improvement with weighting, the
+Trump models demonstrate the need for further investigation into the
+model specifications and the effectiveness of the weighting applied.
+
 ## Diagnostics
 
-@fig-stanareyouokay-1 is a residual plot of un-weighted model. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot. It shows... This suggests...
+@fig-stanareyouokay-1 is a residual plot of un-weighted model. It
+shows... This suggests...
+
+@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot. It
+shows... This suggests...
 
@@
 #| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Harris"
+#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
 #| layout-ncol: 2
-#residual plot
-plot(first_model, which = 1,main ="Residual Plot of unweighted linear regression model residualsmodel" )
-# Q-Q plot for the residuals of the model
-qqnorm(residuals(first_model),main= "Q-Q Plot of unweighted linear regression model residuals
-")
-qqline(residuals(first_model), col = "red")
+
+# Residual plot for unweighted model
+plot(harris_unweighted_model, which = 1, main = "Residual Plot of Unweighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the unweighted model
+qqnorm(residuals(harris_unweighted_model), main = "Q-Q Plot of Unweighted Linear Regression Model Residuals")
+qqline(residuals(harris_unweighted_model), col = "red")
+
+# Residual plot for weighted model
+plot(harris_weighted_model, which = 1, main = "Residual Plot of Weighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the weighted model
+qqnorm(residuals(harris_weighted_model), main = "Q-Q Plot of Weighted Linear Regression Model Residuals")
+qqline(residuals(harris_weighted_model), col = "red")
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-stanareyouokay
+#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Trump"
+#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
+#| layout-ncol: 2
+
+# Residual plot for unweighted model
+plot(trump_unweighted_model, which = 1, main = "Residual Plot of Unweighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the unweighted model
+qqnorm(residuals(trump_unweighted_model), main = "Q-Q Plot of Unweighted Linear Regression Model Residuals")
+qqline(residuals(trump_unweighted_model), col = "red")
+
+# Residual plot for weighted model
+plot(trump_weighted_model, which = 1, main = "Residual Plot of Weighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the weighted model
+qqnorm(residuals(trump_weighted_model), main = "Q-Q Plot of Weighted Linear Regression Model Residuals")
+qqline(residuals(trump_weighted_model), col = "red")
 

### 2024-10-30 paper/paper.qmd
merge conflict

--- 2024-10-30 paper/paper.qmd
@@
 
-In this data-cleaning process, we focus on refining raw polling data to enhance its quality and relevance for subsequent analysis.
-The dataset is initially loaded and cleaned using the janitor package to standardize column names, ensuring consistency throughout.
-We then filter the data to retain only relevant columns and eliminate any rows with missing values in critical fields, including numeric_grade, pct, sample_size, and end_date.
-
-Specifically, we isolate the polling data for Kamala Harris and Donald Trump, applying a condition to include only high-quality polls with a numeric grade of 2 or higher, given that the mean of the numeric grade is 2.175 and the median is 1.9.
-
-For state-level polls, we handle any placeholder states marked as "--" by converting them to NA.
-A national poll indicator is generated, assigning a value of 1 for national polls and 0 for state-specific ones.
-Dates are standardized using the lubridate package to ensure accurate handling in subsequent analyses.
-
-Recency weights are calculated based on the number of days elapsed since the poll ended, utilizing an exponential decay function to give greater weight to more recent polls.
-Additionally, a sample size weight is implemented, capping the weights at a maximum of 2,300 responses to reflect the reliability of larger sample sizes.
-
-Finally, the cleaned datasets for both candidates are saved in CSV format for further modeling and analysis.
-This systematic approach guarantees that the data is accurate, complete, and ready for insightful analysis.
+In this data-cleaning process, we focus on refining raw polling data to
+enhance its quality and relevance for subsequent analysis. The dataset
+is initially loaded and cleaned using the janitor package to standardize
+column names, ensuring consistency throughout. We then filter the data
+to retain only relevant columns and eliminate any rows with missing
+values in critical fields, including numeric_grade, pct, sample_size,
+and end_date.
+
+Specifically, we isolate the polling data for Kamala Harris and Donald
+Trump, applying a condition to include only high-quality polls with a
+numeric grade of 2 or higher, given that the mean of the numeric grade
+is 2.175 and the median is 1.9.
+
+For state-level polls, we handle any placeholder states marked as "--"
+by converting them to NA. A national poll indicator is generated,
+assigning a value of 1 for national polls and 0 for state-specific ones.
+Dates are standardized using the lubridate package to ensure accurate
+handling in subsequent analyses.
+
+Recency weights are calculated based on the number of days elapsed since
+the poll ended, utilizing an exponential decay function to give greater
+weight to more recent polls.
+
+Finally, the cleaned datasets for both candidates are saved in CSV
+format for further modeling and analysis. This systematic approach
+guarantees that the data is accurate, complete, and ready for insightful
+analysis.
 

### 2024-10-30 paper/paper.qmd
Add the result part

--- 2024-10-30 paper/paper.qmd
@@
 
+## Recent 3 Months Support Trends Prediction
+
+The recent three-month support trends for Kamala Harris and Donald Trump across key battleground states—Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, and Wisconsin—show a highly competitive race.
+Each state’s panel displays support percentages over time from August to November 2024, with Harris shown in blue and Trump in red.
+The plot uses point size to represent poll weights, accounting for factors such as recency, pollster quality, and sample size, where larger points indicate higher-weighted polls, emphasizing more reliable data.
+
 ```{r}
 #| echo: false
-#| eval: true
 #| warning: false
 #| message: false
-
-#### Load Required Libraries ####
-library(dplyr)
+#| eval: true
+#| label: fig-support-trends
+#| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States
+
+# Load necessary libraries
+library(tidyverse)
 library(ggplot2)
-library(lubridate)
+
 harris_data <- harris_data %>%
   mutate(
-    recency_weight = exp(-recency * 0.1),
-    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
-    predicted_support = predict(model_harris_weighted, newdata = .),
-    candidate = "Harris"
-  )
-
+    sample_size_weight = pmin(sample_size / 2300, 1),
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
+  ) %>%
+  group_by(pollster) %>%
+  mutate(
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
+  ) %>%
+  ungroup() %>%
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+
+# Calculate weights for Trump data
 trump_data <- trump_data %>%
   mutate(
-    recency_weight = exp(-recency * 0.1),
-    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
-    predicted_support = predict(model_trump_weighted, newdata = .),
-    candidate = "Trump"
-  )
-
-# Combine both datasets
-combined_data <- bind_rows(harris_data, trump_data)
-
-#### Plot Support Trends by State with Reduced Date Labels ####
-# Define states of interest
-selected_states <- c("Pennsylvania", "Nevada", "North Carolina", "Wisconsin", "Michigan", "Georgia", "Arizona")
-
-# Filter data for selected states
-combined_data <- combined_data %>% filter(state %in% selected_states)
-
-# Create the faceted plot with limited x-axis labels
-ggplot(combined_data, aes(x = as.Date(end_date), y = predicted_support, color = candidate, size = combined_weight)) +
-  geom_point(alpha = 0.6) +
-  scale_color_manual(values = c("Harris" = "#1f77b4", "Trump" = "#d62728")) +  # Blue for Harris, Red for Trump
-  scale_size_continuous(range = c(1, 4)) +  # Control point size range for readability
-  scale_x_date(date_labels = "%b %d", date_breaks = "1 month") +  # Show only the first day of each month
-  labs(title = "Support Trends for Harris and Trump Across States",
-       x = "Date", y = "Support (%)", color = "Candidate") +
-  facet_wrap(~ state, ncol = 2, scales = "free_y") +  # Facet by state with free y-scale
-  theme_minimal(base_size = 12) +
+    sample_size_weight = pmin(sample_size / 2300, 1),
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
+  ) %>%
+  group_by(pollster) %>%
+  mutate(
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
+  ) %>%
+  ungroup() %>%
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+
+selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
+recent_date_cutoff <- as.Date("2024-08-01")  # Set cutoff for recent data
+
+harris_filtered <- harris_data %>%
+  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)
+
+trump_filtered <- trump_data %>%
+  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)
+
+# Combine datasets for plotting with a new column for candidate
+harris_filtered <- harris_filtered %>% mutate(candidate = "Harris")
+trump_filtered <- trump_filtered %>% mutate(candidate = "Trump")
+combined_data <- bind_rows(harris_filtered, trump_filtered)
+
+# Plot with recent data, specific axis formatting, and smoother trend lines
+ggplot(combined_data, aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
+  geom_point(alpha = 0.7) + # Adds points with transparency for overlapping data
+  geom_smooth(aes(group = candidate), method = "loess", span = 0.2, se = FALSE, size = 1) + # Smoothed trend line
+  facet_wrap(~ state) +
+  labs(title = "Recent Support Trends for Kamala Harris and Donald Trump Across Selected States",
+       x = "Date", y = "Support (%)") +
+  scale_x_date(date_labels = "%b", date_breaks = "1 month", limits = as.Date(c("2024-08-01", "2024-10-31"))) +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  scale_size_continuous(range = c(0.5, 3), guide = "none") +
+  theme_minimal() +
   theme(
     legend.position = "top",
-    strip.text = element_text(size = 12, face = "bold"),
-    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),  # Slight tilt for x-axis labels
-    panel.grid.major = element_line(size = 0.2, linetype = "dotted", color = "gray80"),
-    panel.grid.minor = element_blank()
-  )
+    axis.text.x = element_text(angle = 0, hjust = 0.5),
+    panel.grid.major = element_line(size = 0.1, color = "grey80")
+  ) +
+  guides(color = guide_legend(title = "Candidate"))
 ```
+@fig-support-trends illustrates the recent support trends for Kamala Harris and Donald Trump across selected battleground states from August to November 2024.
+Each subplot represents a different state, with support percentages for each candidate displayed over time.
+Key features include Harris shown in blue and Trump in red, with smoothed trend lines to capture changes over time.
+The plot's y-axis spans from approximately 30% to 50% support, while the x-axis highlights monthly intervals from August to November.
+For example, in Arizona, Trump maintains a slight lead with support fluctuating around 50% in October, compared to Harris around 48%.
+In Georgia, Trump's support reaches just above 49% in late September, whereas Harris hovers closer to 47%.
+In Wisconsin, both candidates show tightly aligned trends near 48%, highlighting a close race.
+Each point's size reflects the poll weight—calculated using recency, pollster quality, and sample size—indicating the relative importance of each poll.
+This visualization emphasizes recent trends in candidate support across key battleground states.
 

### 2024-10-30 paper/paper.qmd
Add explanation to the graph

@@
 #| eval: true
-#| label: fig-support-trends
+#| label: fig-support-trends-by-state
 #| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States
+
+# Load necessary libraries
+library(tidyverse)
+library(ggplot2)
 
@@
 selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
+
 recent_date_cutoff <- as.Date("2024-08-01")  # Set cutoff for recent data
@@
   filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)
-
-# Combine datasets for plotting with a new column for candidate
-harris_filtered <- harris_filtered %>% mutate(candidate = "Harris")
-trump_filtered <- trump_filtered %>% mutate(candidate = "Trump")
-combined_data <- bind_rows(harris_filtered, trump_filtered)
-
 # Plot with recent data, specific axis formatting, and smoother trend lines
@@
 ```
-@fig-support-trends illustrates the recent support trends for Kamala Harris and Donald Trump across selected battleground states from August to November 2024.
+@fig-support-trends-by-state illustrates the recent support trends for Kamala Harris and Donald Trump across selected battleground states from August to November 2024.
 Each subplot represents a different state, with support percentages for each candidate displayed over time.
@@
 This visualization emphasizes recent trends in candidate support across key battleground states.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| label: fig-national-support-trends
+#| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States
+
+harris_data <- harris_data %>%
+  mutate(
+    sample_size_weight = pmin(sample_size / 2300, 1),
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
+  ) %>%
+  group_by(pollster) %>%
+  mutate(
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
+  ) %>%
+  ungroup() %>%
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+
+# Calculate weights for Trump data
+trump_data <- trump_data %>%
+  mutate(
+    sample_size_weight = pmin(sample_size / 2300, 1),
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
+  ) %>%
+  group_by(pollster) %>%
+  mutate(
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
+  ) %>%
+  ungroup() %>%
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+
+harris_data <- harris_data %>% mutate(candidate = "Harris")
+trump_data <- trump_data %>% mutate(candidate = "Trump")
+combined_data_total <- bind_rows(harris_data, trump_data)
+
+selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
+recent_date_cutoff <- as.Date("2024-08-01")  # Set cutoff for recent data
+
+harris_filtered <- harris_data %>%
+  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)
+
+trump_filtered <- trump_data %>%
+  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)
+
+# Combine datasets for plotting with a new column for candidate
+harris_filtered <- harris_filtered %>% mutate(candidate = "Harris")
+trump_filtered <- trump_filtered %>% mutate(candidate = "Trump")
+combined_data <- bind_rows(harris_filtered, trump_filtered)
+# Plot with recent data, specific axis formatting, and smoother trend lines
+ggplot(combined_data, aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
+  geom_point(alpha = 0.7) + # Adds points with transparency for overlapping data
+  geom_smooth(aes(group = candidate), method = "loess", span = 0.2, se = FALSE, size = 1) + # Smoothed trend line
+  facet_wrap(~ state) +
+  labs(title = "Recent Support Trends for Kamala Harris and Donald Trump Across Selected States",
+       x = "Date", y = "Support (%)") +
+  scale_x_date(date_labels = "%b", date_breaks = "1 month", limits = as.Date(c("2024-08-01", "2024-10-31"))) +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  scale_size_continuous(range = c(0.5, 3), guide = "none") +
+  theme_minimal() +
+  theme(
+    legend.position = "top",
+    axis.text.x = element_text(angle = 0, hjust = 0.5),
+    panel.grid.major = element_line(size = 0.1, color = "grey80")
+  ) +
+  guides(color = guide_legend(title = "Candidate"))
+```
+@fig-support-trends-by-state illustrates the recent support trends for Kamala Harris and Donald Trump across selected battleground states from August to November 2024.
+Each subplot represents a different state, with support percentages for each candidate displayed over time.
+Key features include Harris shown in blue and Trump in red, with smoothed trend lines to capture changes over time.
+The plot's y-axis spans from approximately 30% to 50% support, while the x-axis highlights monthly intervals from August to November.
+For example, in Arizona, Trump maintains a slight lead with support fluctuating around 50% in October, compared to Harris around 48%.
+In Georgia, Trump's support reaches just above 49% in late September, whereas Harris hovers closer to 47%.
+In Wisconsin, both candidates show tightly aligned trends near 48%, highlighting a close race.
+Each point's size reflects the poll weight—calculated using recency, pollster quality, and sample size—indicating the relative importance of each poll.
+This visualization emphasizes recent trends in candidate support across key battleground states.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| label: fig-national-support-trends
+#| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States
+
+# Combine datasets for plotting with a new column for candidate
+harris_filtered <- harris_filtered %>% mutate(candidate = "Harris")
+trump_filtered <- trump_filtered %>% mutate(candidate = "Trump")
+combined_data <- bind_rows(harris_filtered, trump_filtered)
+
+combined_data_total|>filter(national_poll==1)|>ggplot(aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
+  geom_point(alpha = 0.7) + # Adds points with transparency for overlapping data
+  geom_smooth(aes(group = candidate), method = "loess", span = 0.2, se = FALSE, size = 1) + # Smoothed trend line
+  labs(title = "Recent Support Trends for Kamala Harris and Donald Trump Across Country",
+       x = "Date", y = "Support (%)") +
+  scale_x_date(date_labels = "%b", date_breaks = "1 month", limits = as.Date(c("2024-08-01", "2024-10-27"))) +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  scale_size_continuous(range = c(0.5, 3), guide = "none") +
+  theme_minimal() +
+  theme(
+    legend.position = "top",
+    axis.text.x = element_text(angle = 0, hjust = 0.5),
+    panel.grid.major = element_line(size = 0.1, color = "grey80")
+  ) +
+  guides(color = guide_legend(title = "Candidate"))
+
+```
+@fig-national-support-trendsillustrates illustrates the polling support trends for Kamala Harris and Donald Trump across the country from August to October.
+The scatter points represent individual poll results, with blue for Harris and red for Trump, while each dot's size reflects the weight of the poll, accounting for factors like sample size, quality, and recency.
+Harris’s support trend line generally remains above Trump’s, with an average support level around 49%, compared to Trump’s approximate average of 47% over this period.
+Toward the end of October, both candidates show a slight increase, with Harris’s support reaching just over 50% and Trump’s approaching 49%.
+This trend suggests a potential narrowing in support levels as the election approaches, providing a quantitative snapshot of national polling dynamics.
 

### 2024-10-30 paper/paper.qmd
merge outcome

--- 2024-10-30 paper/paper.qmd
@@
 ---
-title: "Based on polling as of 27 October 2024, Harris expects to win on xxx%, leads Trump by xx% in 2024 US election"
+title: "Based on polling as of 27 October 2024, Harris expects to win on 49.2%, leads Trump by 2% in 2024 US election"
 subtitle: "Weighted Linear Regression Analysis of Aggregated Poll Data: Utilizing National Polls indicator, Population, and Pollster as Predictors."
@@
 library(tidyverse)
+library(arrow)
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+harris_data <- read_parquet("~/2024 US Election Forecast/data/02-analysis_data/analysis_data_Harris.parquet")
+trump_data <- read_parquet("~/2024 US Election Forecast/data/02-analysis_data/analysis_data_Trump.parquet")
+
 ```
@@
 
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+harris_unweighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_harris_unweighted.rds")
+harris_weighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_harris_weighted.rds")
+trump_unweighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_trump_unweighted.rds")
+trump_weighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_trump_weighted.rds")
+
+```
+
 #### Unweighted Model
@@
 
-```{r}
-model_harris_unweighted <- lm(pct ~ national_poll + pollster + population, data = harris_data)
-```
-
 #### Weighted Model
@@
 ```{r}
-model_harris_weighted <- lm(pct ~ national_poll + pollster + population, data = harris_data, weights = combined_weight)
-```
-
-### Coefficient Explanations
-
--   $\beta_0$: Intercept of the model, representing the expected support
-    when all predictors are zero.
--   $\beta_1$: Coefficient for the national poll, indicating how much
-    support changes with a one-unit increase in the national poll
-    percentage.
--   $\beta_2$: Coefficient for the pollster, reflecting the impact of
-    different polling organizations on support.
--   $\beta_3$: Coefficient for the population, accounting for the
-    influence of the demographic context on support levels.
-
-### Model Justification
-
-1.  **Use of Weighted Model**: The weighted model is essential for
-    accurately reflecting voter sentiment. By incorporating weights, we
-    adjust for the reliability of the polling data, ensuring that more
-    credible polls have a greater influence on the estimates.
-
-2.  **Calculation of Variables**:
-
-    -   **Combined Weight**: The combined weight is calculated as
-        follows: $$
-        \text{combined\_weight} = \text{recency\_weight} \times \text{sample\_size\_weight} \times \text{poll\_frequency\_weight} \times \text{pollster\_quality\_weight}
-        $$
-
-    -   **Recency Weight**: This weight uses an exponential decay
-        function: $$
-        \text{recency\_weight} = \exp(-\text{Recency}_i \cdot 0.1)
-        $$ This reflects the diminishing influence of older polls, with
-        $\lambda = 0.1$ for the exponential decay.
-
-    -   **Sample Size Weight**: This weight adjusts the significance of
-        each poll based on the number of respondents, capping the
-        weights at a maximum of 2,300 responses to reflect the
-        reliability of larger sample sizes [@nyt_polling_averages].
-
-    -   **Poll Frequency Weight**: This weight considers how often a
-        pollster conducts polls, with higher weights assigned to
-        pollsters with a greater number of recent surveys.
-
-    -   **Pollster Quality Weight**: Based on the historical performance
-        of the pollster, this weight emphasizes the reliability of their
-        polling methods.
-
-### Alternative Models
-
-While this analysis employs linear regression with weighted least
-squares, alternative methods such as Bayesian modeling could provide
-additional insights. However, we opted for the weighted linear
-regression approach to maintain interpretability and ease of
-implementation given the scope and resources of this analysis. The
-Bayesian approach was not chosen primarily due to the complexity
-involved in defining priors and the additional computational
-requirements.
-
-### Weighted Least Squares Estimation
-
-In our analysis, we utilize weighted least squares estimation to account
-for the varying quality of polling data. The weights are crucial in the
-estimation process, leading to the following expression for the
-estimates of the coefficients ($\hat{\beta}$):
-
-$$
-\hat{\beta} = (X^T W X)^{-1} X^T W y
-$$
-
-Where: - $X$ is the design matrix of predictors. - $W$ is the diagonal
-matrix of weights, which incorporates factors such as recency, sample
-size, and pollster quality to enhance the reliability of our estimates.
-
-### Importance of Combined Weights
-
-By incorporating these combined weights, the weighted model offers a
-more nuanced estimation of voter support for both Harris and Trump.
-While the mathematical expression for the models remains consistent, the
-weighted models effectively adjust for variations in data quality and
-recency, leading to more accurate predictions of voter sentiment.
-
-# Result
-
-## Recent 3 Months Support Trends Prediction
-
-The recent three-month support trends for Kamala Harris and Donald Trump across key battleground states—Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, and Wisconsin—show a highly competitive race.
-Each state’s panel displays support percentages over time from August to November 2024, with Harris shown in blue and Trump in red.
-The plot uses point size to represent poll weights, accounting for factors such as recency, pollster quality, and sample size, where larger points indicate higher-weighted polls, emphasizing more reliable data.
-
-```{r}
-#| echo: false
+#| include: false
 #| warning: false
 #| message: false
-#| eval: true
-#| label: fig-support-trends
-#| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States
-
-# Load necessary libraries
-library(tidyverse)
-library(ggplot2)
-
+#### Calculate Weights ####
+# Calculate weights for Harris data
 harris_data <- harris_data %>%
@@
   mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+```
+
+### Coefficient Explanations
+
+-   $\beta_0$: Intercept of the model, representing the expected support
+    when all predictors are zero.
+-   $\beta_1$: Coefficient for the national poll, indicating how much
+    support changes with a one-unit increase in the national poll
+    percentage.
+-   $\beta_2$: Coefficient for the pollster, reflecting the impact of
+    different polling organizations on support.
+-   $\beta_3$: Coefficient for the population, accounting for the
+    influence of the demographic context on support levels.
+
+### Model Justification
+
+1.  **Use of Weighted Model**: The weighted model is essential for
+    accurately reflecting voter sentiment. By incorporating weights, we
+    adjust for the reliability of the polling data, ensuring that more
+    credible polls have a greater influence on the estimates.
+
+2.  **Calculation of Variables**:
+
+    -   **Combined Weight**: The combined weight is calculated as
+        follows: $$
+        \text{combined\_weight} = \text{recency\_weight} \times \text{sample\_size\_weight} \times \text{poll\_frequency\_weight} \times \text{pollster\_quality\_weight}
+        $$
+
+    -   **Recency Weight**: This weight uses an exponential decay
+        function: $$
+        \text{recency\_weight} = \exp(-\text{Recency}_i \cdot 0.1)
+        $$ This reflects the diminishing influence of older polls, with
+        $\lambda = 0.1$ for the exponential decay.
+
+    -   **Sample Size Weight**: This weight adjusts the significance of
+        each poll based on the number of respondents, capping the
+        weights at a maximum of 2,300 responses to reflect the
+        reliability of larger sample sizes [@nyt_polling_averages].
+
+    -   **Poll Frequency Weight**: This weight considers how often a
+        pollster conducts polls, with higher weights assigned to
+        pollsters with a greater number of recent surveys.
+
+    -   **Pollster Quality Weight**: Based on the historical performance
+        of the pollster, this weight emphasizes the reliability of their
+        polling methods.
+
+### Alternative Models
+
+While this analysis employs linear regression with weighted least
+squares, alternative methods such as Bayesian modeling could provide
+additional insights. However, we opted for the weighted linear
+regression approach to maintain interpretability and ease of
+implementation given the scope and resources of this analysis. The
+Bayesian approach was not chosen primarily due to the complexity
+involved in defining priors and the additional computational
+requirements.
+
+### Weighted Least Squares Estimation
+
+In our analysis, we utilize weighted least squares estimation to account
+for the varying quality of polling data. The weights are crucial in the
+estimation process, leading to the following expression for the
+estimates of the coefficients ($\hat{\beta}$):
+
+$$
+\hat{\beta} = (X^T W X)^{-1} X^T W y
+$$
+
+Where: - $X$ is the design matrix of predictors. - $W$ is the diagonal
+matrix of weights, which incorporates factors such as recency, sample
+size, and pollster quality to enhance the reliability of our estimates.
+
+### Importance of Combined Weights
+
+By incorporating these combined weights, the weighted model offers a
+more nuanced estimation of voter support for both Harris and Trump.
+While the mathematical expression for the models remains consistent, the
+weighted models effectively adjust for variations in data quality and
+recency, leading to more accurate predictions of voter sentiment.
+
+# Result
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+harris_data <- harris_data %>%
+  mutate(
+    sample_size_weight = pmin(sample_size / 2300, 1),
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
+  ) %>%
+  group_by(pollster) %>%
+  mutate(
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
+  ) %>%
+  ungroup() %>%
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+
+# Calculate weights for Trump data
+trump_data <- trump_data %>%
+  mutate(
+    sample_size_weight = pmin(sample_size / 2300, 1),
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
+  ) %>%
+  group_by(pollster) %>%
+  mutate(
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
+  ) %>%
+  ungroup() %>%
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+
+harris_data <- harris_data %>% mutate(candidate = "Harris")
+trump_data <- trump_data %>% mutate(candidate = "Trump")
+combined_data_total <- bind_rows(harris_data, trump_data)
 
@@
 
-# Plot with recent data, specific axis formatting, and smoother trend lines
+combined_data_total|>filter(national_poll==1)|>ggplot(aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
+  geom_point(alpha = 0.7) + # Adds points with transparency for overlapping data
+  geom_smooth(aes(group = candidate), method = "loess", span = 0.2, se = FALSE, size = 1) + # Smoothed trend line
+  labs(title = "Recent Support Trends for Kamala Harris and Donald Trump Across Country",
+       x = "Date", y = "Support (%)") +
+  scale_x_date(date_labels = "%b", date_breaks = "1 month", limits = as.Date(c("2024-08-01", "2024-10-27"))) +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  scale_size_continuous(range = c(0.5, 3), guide = "none") +
+  theme_minimal() +
+  theme(
+    legend.position = "top",
+    axis.text.x = element_text(angle = 0, hjust = 0.5),
+    panel.grid.major = element_line(size = 0.1, color = "grey80")
+  )
+```
+
+```{r}
 ggplot(combined_data, aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
@@
 ```
-@fig-support-trends illustrates the recent support trends for Kamala Harris and Donald Trump across selected battleground states from August to November 2024.
-Each subplot represents a different state, with support percentages for each candidate displayed over time.
-Key features include Harris shown in blue and Trump in red, with smoothed trend lines to capture changes over time.
-The plot's y-axis spans from approximately 30% to 50% support, while the x-axis highlights monthly intervals from August to November.
-For example, in Arizona, Trump maintains a slight lead with support fluctuating around 50% in October, compared to Harris around 48%.
-In Georgia, Trump's support reaches just above 49% in late September, whereas Harris hovers closer to 47%.
-In Wisconsin, both candidates show tightly aligned trends near 48%, highlighting a close race.
-Each point's size reflects the poll weight—calculated using recency, pollster quality, and sample size—indicating the relative importance of each poll.
-This visualization emphasizes recent trends in candidate support across key battleground states.
 
@@
 
-## Model validation
+## Model validation: K-Fold Cross-Validation
 
 ```{r}
-# Set seed for reproducibility
-set.seed(123)
-
-# Sample indices for training and testing sets
-train_index <- sample(seq_len(nrow(data)), size = 0.8 * nrow(data))
-
-# Split the data into training and testing sets
-train_data <- data[train_index, ]
-test_data <- data[-train_index, ]
-
-# Fit the weighted linear regression model
-first_model_test <- lm(pct ~ national_poll + pollster + population, 
-                     data = data, 
-                  data = train_data)
-
-# Predict on test data
-predictions <- predict(first_model_test, newdata = test_data)
-
-# Calculate RMSE using the correct outcome variable
-# Assuming 'pct' is the actual observed outcome variable in test_data
-rmse <- sqrt(mean((predictions - test_data$pct)^2, na.rm = TRUE))
-
-# Print RMSE
-print(paste("RMSE:", rmse))
-
+# Load necessary libraries
+library(boot)    # For bootstrapping
+library(caret)   # For cross-validation
+
+# Set up 10-fold cross-validation
+train_control <- trainControl(method = "cv", number = 10)
+# Train the model
+model_formula <- pct ~ national_poll + pollster + population
+model_harris_cv <- train(model_formula, data = harris_data, method = "lm", trControl = train_control)
+# Set up 10-fold cross-validation
+train_control <- trainControl(method = "cv", number = 10)
+# Train the model
+model_harris_cv <- train(model_formula, data = harris_data, method = "lm", trControl = train_control)
+# Print the model results
+print(model_harris_cv)
+
+model_trump_cv <- train(model_formula, data = trump_data, method = "lm", trControl = train_control)
+# Set up 10-fold cross-validation
+train_control <- trainControl(method = "cv", number = 10)
+# Train the model
+model_trump_cv <- train(model_formula, data = trump_data, method = "lm", trControl = train_control)
+# Print the model results
+print(model_trump_cv)
 ```
 
+We use a 10-fold cross-validation on two linear regression models—one for Harris and one for Trump.
+The models use three predictors: national_poll, pollster, and population.
+The output provides key metrics, which breaks down here:
+
+RMSE (Root Mean Square Error): Measures the average magnitude of prediction errors (lower is better).
+
+Harris model: RMSE of 3.47, indicating an average prediction error of around 3.47 percentage points.\
+Trump model: RMSE of 4.39, showing a slightly higher prediction error on average.\
+
+R-squared: Represents the proportion of the variance in the response variable explained by the model (higher is better).\
+Harris model: R-squared of 0.346, meaning the model explains about 34.6% of the variance in Harris's polling data.\
+Trump model: R-squared of 0.346 as well, indicating similar explanatory power for Trump's polling data.
+
+MAE (Mean Absolute Error): Shows the average absolute difference between observed and predicted values (lower is better).\
+Harris model: MAE of 2.50, meaning that, on average, the predictions are off by 2.5 percentage points.\
+Trump model: MAE of 3.13, indicating slightly less precise predictions compared to the Harris model.\
+
+Interpretation Summary
+Predictive Accuracy: The Harris model has slightly better predictive accuracy than the Trump model, as reflected by its lower RMSE and MAE values.\
+Model Fit: Both models explain roughly 34.6% of the variance in their respective datasets.
+This suggests that other factors not included in the model may play a significant role in explaining the remaining variance.\
+This summary indicates the models are moderately predictive, with room for improvement in accuracy and fit, potentially by adding more predictors or adjusting model specifications.\
+
 ## Diagnostics
-
-@fig-stanareyouokay-1 is a residual plot of un-weighted model. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot. It shows... This suggests...
 
@@
 #| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Harris"
+#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
 #| layout-ncol: 2
-#residual plot
-plot(first_model, which = 1,main ="Residual Plot of unweighted linear regression model residualsmodel" )
-# Q-Q plot for the residuals of the model
-qqnorm(residuals(first_model),main= "Q-Q Plot of unweighted linear regression model residuals
-")
-qqline(residuals(first_model), col = "red")
+
+# Residual plot for unweighted model
+plot(harris_unweighted_model, which = 1, main = "Residual Plot of Unweighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the unweighted model
+qqnorm(residuals(harris_unweighted_model), main = "Q-Q Plot of Unweighted Linear Regression Model Residuals")
+qqline(residuals(harris_unweighted_model), col = "red")
+
+# Residual plot for weighted model
+plot(harris_weighted_model, which = 1, main = "Residual Plot of Weighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the weighted model
+qqnorm(residuals(harris_weighted_model), main = "Q-Q Plot of Weighted Linear Regression Model Residuals")
+qqline(residuals(harris_weighted_model), col = "red")
 
 ```
+Generally, we use Residual vs Fitted plot and Q-Q Plot diagnostic our model.
+Residual vs Fitted plot aare Residuals (differences between observed and predicted values) plotted against fitted values.
+Ideally, these residuals should be randomly scattered around the zero line to indicate that the model does not have systematic errors.
+The Q-Q plot for the unweighted model shows how the residuals align with a theoretical normal distribution.
+Ideally, residuals should follow a straight line in this plot if they are normally distributed, which is an assumption of linear regression.
+
+@fig-stanareyouokay-1 is a residual plot of un-weighted model for Harris support. It
+showsthe residuals are generally spread around zero, with no clear pattern.
+This suggests the model is relatively well-specified.
+However, there is a slight curvature, indicating potential non-linearity that the model may not fully capture.
+A few notable outliers with larger residuals might be influencing the model, indicating that some data points have more significant prediction errors.
+
+@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot for Harris support. It
+shows most residuals fall along the line, especially in the middle range.
+This suggests that our model satisfy the normality assumption.
+However, some points at the tails deviate, indicating potential outliers or non-normality in the extreme residual values.
+This slight deviation at the ends suggests the model might have some issues with extreme predictions but performs reasonably well overall.
+
+@fig-stanareyouokay-3 is a residual plot of weighted model for Harris support.It shows residuals are again plotted against fitted values.
+Similar to the unweighted model, the residuals are mostly centered around zero, indicating that the weighted model captures the general trend without significant systematic bias.
+The curvature is slightly reduced compared to the un-weighted model, suggesting that weighting has helped in addressing some of the non-linearity observed in the un-weighted model.
+However, some residuals are still notably large, which may indicate outliers that influence the model despite the weighting scheme.
+This suggests that while the weighted model performs better in terms of capturing non-linearity, further refinement might still be beneficial.
+
+@fig-stanareyouokay-4 is a  Q-Q Plot of weighted model plot for Harris support.The residuals generally align with the theoretical normal distribution line, particularly in the central range, indicating that the residuals of the weighted model are close to normal.
+Similar to the unweighted model, there are deviations at the tails, though they appear less pronounced.
+This suggests that the weighting scheme has slightly improved the distribution of residuals, making the model’s predictions more robust.
+However, some extreme values remain, which could still affect model
+
+In summary, both models show a reasonably good fit, with the weighted model offering slight improvements in handling non-linearity and extreme values.
+However, both models exhibit minor deviations from normality and a few notable outliers, which may warrant further model adjustments for improved prediction accuracy.
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-dia
+#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Trump"
+#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
+#| layout-ncol: 2
+
+# Residual plot for unweighted model
+plot(trump_unweighted_model, which = 1, main = "Residual Plot of Unweighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the unweighted model
+qqnorm(residuals(trump_unweighted_model), main = "Q-Q Plot of Unweighted Linear Regression Model Residuals")
+qqline(residuals(trump_unweighted_model), col = "red")
+
+# Residual plot for weighted model
+plot(trump_weighted_model, which = 1, main = "Residual Plot of Weighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the weighted model
+qqnorm(residuals(trump_weighted_model), main = "Q-Q Plot of Weighted Linear Regression Model Residuals")
+qqline(residuals(trump_weighted_model), col = "red")
+
+```
+
+@fig-dia-1 shows the residuals plotted against the fitted values for the unweighted model.
+It shows that the residuals are generally spread around zero with no clear pattern, suggesting that the model is relatively well-specified.
+However, there is a slight curvature, indicating possible non-linearity that the model may not fully capture.
+Some notable outliers with larger residuals suggest that certain data points have significant prediction errors, potentially influencing the model.
+
+@fig-dia-2 shows the Q-Q plot for the unweighted model, showing that most residuals fall along the line, especially in the middle range, suggesting that the model satisfies the normality assumption.
+However, some points at the tails deviate, indicating potential outliers or non-normality in extreme residual values.
+This deviation at the ends suggests the model may face issues with extreme predictions, though it performs reasonably well overall.
+
+@fig-dia3 shows residuals plotted against fitted values.
+Similar to the unweighted model, the residuals are centered around zero, indicating that the weighted model captures the overall trend without significant systematic bias.
+The slight curvature seen in the unweighted model is reduced here, suggesting that weighting has addressed some of the non-linearity.
+However, some large residuals remain, which could indicate outliers that affect the model even with the weighting scheme.
+This suggests that while the weighted model has improved in handling non-linearity, further refinements could enhance accuracy.
+
+@fig-dia-4 shows the Q-Q plot for the weighted model compares residuals with a theoretical normal distribution.
+Here, the residuals generally align with the theoretical line, especially in the central range, indicating that the residuals of the weighted model are close to normal.
+Similar to the unweighted model, some deviations occur at the tails, though they appear less pronounced, suggesting that the weighting scheme has slightly improved the normality of residuals.
+Nonetheless, some extreme values persist, which may impact model robustness in cases of outliers.
+
+Summary
+Both models exhibit a reasonably good fit, with the weighted model offering slight improvements in managing non-linearity and extreme values.
+Despite this, both models show minor deviations from normality and some notable outliers, suggesting that further model adjustments may be beneficial for improved prediction accuracy.
 

### 2024-10-30 scripts/05-model_data.R

@@ -11,11 +11,6 @@
 library(dplyr)
 
 # Load Harris and Trump data
-<<<<<<< HEAD
-harris_data <- read.csv("data/02-analysis_data/analysis_data_Harris.csv")
-trump_data <- read.csv("data/02-analysis_data/analysis_data_Trump.csv")
-=======
->>>>>>> cce7356b4f7dc558466790ee5c1f91e6d51efaad
 harris_data <- read_parquet("data/02-analysis_data/analysis_data_Harris.parquet")
 trump_data <- read_parquet("data/02-analysis_data/analysis_data_Trump.parquet")
 
@@ -24,10 +19,6 @@ trump_data <- read_parquet("data/02-analysis_data/analysis_data_Trump.parquet")
 harris_data <- harris_data %>%
   mutate(
     sample_size_weight = pmin(sample_size / 2300, 1),
-<<<<<<< HEAD
-    pollster_quality_weight = numeric_grade / 4
-=======
->>>>>>> cce7356b4f7dc558466790ee5c1f91e6d51efaad
     pollster_quality_weight = numeric_grade / 4,
     recency_weight = exp(-recency * 0.1)
   ) %>%
@@ -37,20 +28,12 @@ harris_data <- harris_data %>%
     poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
   ) %>%
   ungroup() %>%
-<<<<<<< HEAD
-  mutate(combined_weight = recency * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
-=======
->>>>>>> cce7356b4f7dc558466790ee5c1f91e6d51efaad
   mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
 
 # Calculate weights for Trump data
 trump_data <- trump_data %>%
   mutate(
     sample_size_weight = pmin(sample_size / 2300, 1),
-<<<<<<< HEAD
-    pollster_quality_weight = numeric_grade / 4
-=======
->>>>>>> cce7356b4f7dc558466790ee5c1f91e6d51efaad
     pollster_quality_weight = numeric_grade / 4,
     recency_weight = exp(-recency * 0.1)
   ) %>%
@@ -62,20 +45,6 @@ trump_data <- trump_data %>%
   ungroup() %>%
   mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
 
-<<<<<<< HEAD
-#### Model Preparation ####
[…]

### 2024-10-30 paper/paper.qmd

@@
 
+## Recent 3 Months Support Trends Prediction
+
+The recent three-month support trends for Kamala Harris and Donald Trump across key battleground states—Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, and Wisconsin—show a highly competitive race.
+Each state’s panel displays support percentages over time from August to November 2024, with Harris shown in blue and Trump in red.
+The plot uses point size to represent poll weights, accounting for factors such as recency, pollster quality, and sample size, where larger points indicate higher-weighted polls, emphasizing more reliable data.
+
 ```{r}
 #| echo: false
-#| eval: true
 #| warning: false
 #| message: false
+#| eval: true
+#| label: fig-support-trends-by-state
+#| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States
+
+# Load necessary libraries
+library(tidyverse)
+library(ggplot2)
 
@@
 
-harris_data <- harris_data %>% mutate(candidate = "Harris")
-trump_data <- trump_data %>% mutate(candidate = "Trump")
-combined_data_total <- bind_rows(harris_data, trump_data)
-
 selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
+
 recent_date_cutoff <- as.Date("2024-08-01")  # Set cutoff for recent data
@@
 harris_filtered <- harris_data %>%
-  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)
-
+  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)|>mutate(candidate = "Harris")
 trump_filtered <- trump_data %>%
-  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)
-
-# Combine datasets for plotting with a new column for candidate
-harris_filtered <- harris_filtered %>% mutate(candidate = "Harris")
-trump_filtered <- trump_filtered %>% mutate(candidate = "Trump")
+  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)|>mutate(candidate = "Trump")
+
 combined_data <- bind_rows(harris_filtered, trump_filtered)
-
-combined_data_total|>filter(national_poll==1)|>ggplot(aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
-  geom_point(alpha = 0.7) + # Adds points with transparency for overlapping data
-  geom_smooth(aes(group = candidate), method = "loess", span = 0.2, se = FALSE, size = 1) + # Smoothed trend line
-  labs(title = "Recent Support Trends for Kamala Harris and Donald Trump Across Country",
-       x = "Date", y = "Support (%)") +
-  scale_x_date(date_labels = "%b", date_breaks = "1 month", limits = as.Date(c("2024-08-01", "2024-10-27"))) +
-  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
-  scale_size_continuous(range = c(0.5, 3), guide = "none") +
-  theme_minimal() +
-  theme(
-    legend.position = "top",
-    axis.text.x = element_text(angle = 0, hjust = 0.5),
-    panel.grid.major = element_line(size = 0.1, color = "grey80")
-  )
-```
-
-```{r}
+# Plot with recent data, specific axis formatting, and smoother trend lines
 ggplot(combined_data, aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
@@
 ```
+@fig-support-trends-by-state illustrates the recent support trends for Kamala Harris and Donald Trump across selected battleground states from August to November 2024.
+Each subplot represents a different state, with support percentages for each candidate displayed over time.
+Key features include Harris shown in blue and Trump in red, with smoothed trend lines to capture changes over time.
+The plot's y-axis spans from approximately 30% to 50% support, while the x-axis highlights monthly intervals from August to November.
+For example, in Arizona, Trump maintains a slight lead with support fluctuating around 50% in October, compared to Harris around 48%.
+In Georgia, Trump's support reaches just above 49% in late September, whereas Harris hovers closer to 47%.
+In Wisconsin, both candidates show tightly aligned trends near 48%, highlighting a close race.
+Each point's size reflects the poll weight—calculated using recency, pollster quality, and sample size—indicating the relative importance of each poll.
+This visualization emphasizes recent trends in candidate support across key battleground states.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| label: fig-national-support-trends
+#| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States
+harris_data<-harris_data|>mutate(candidate = "Harris")
+trump_data<-trump_data |>mutate(candidate= "Trump")
+combined_data_total <- bind_rows(harris_data, trump_data)
+combined_data_total|>filter(national_poll==1)|>ggplot(aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
+  geom_point(alpha = 0.7) + # Adds points with transparency for overlapping data
+  geom_smooth(aes(group = candidate), method = "loess", span = 0.2, se = FALSE, size = 1) + # Smoothed trend line
+  labs(title = "Recent Support Trends for Kamala Harris and Donald Trump Across Country",
+       x = "Date", y = "Support (%)") +
+  scale_x_date(date_labels = "%b", date_breaks = "1 month", limits = as.Date(c("2024-08-01", "2024-10-27"))) +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  scale_size_continuous(range = c(0.5, 3), guide = "none") +
+  theme_minimal() +
+  theme(
+    legend.position = "top",
+    axis.text.x = element_text(angle = 0, hjust = 0.5),
+    panel.grid.major = element_line(size = 0.1, color = "grey80")
+  ) +
+  guides(color = guide_legend(title = "Candidate"))
+
+```
+@fig-national-support-trendsillustrates illustrates the polling support trends for Kamala Harris and Donald Trump across the country from August to October.
+The scatter points represent individual poll results, with blue for Harris and red for Trump, while each dot's size reflects the weight of the poll, accounting for factors like sample size, quality, and recency.
+Harris’s support trend line generally remains above Trump’s, with an average support level around 49%, compared to Trump’s approximate average of 47% over this period.
+Toward the end of October, both candidates show a slight increase, with Harris’s support reaching just over 50% and Trump’s approaching 49%.
+This trend suggests a potential narrowing in support levels as the election approaches, providing a quantitative snapshot of national polling dynamics.
 
@@
 ```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
 # Load necessary libraries
@@
 
-We use a 10-fold cross-validation on two linear regression models—one for Harris and one for Trump.
-The models use three predictors: national_poll, pollster, and population.
-The output provides key metrics, which breaks down here:
-
-RMSE (Root Mean Square Error): Measures the average magnitude of prediction errors (lower is better).
-
-Harris model: RMSE of 3.47, indicating an average prediction error of around 3.47 percentage points.\
-Trump model: RMSE of 4.39, showing a slightly higher prediction error on average.\
-
-R-squared: Represents the proportion of the variance in the response variable explained by the model (higher is better).\
-Harris model: R-squared of 0.346, meaning the model explains about 34.6% of the variance in Harris's polling data.\
-Trump model: R-squared of 0.346 as well, indicating similar explanatory power for Trump's polling data.
-
-MAE (Mean Absolute Error): Shows the average absolute difference between observed and predicted values (lower is better).\
-Harris model: MAE of 2.50, meaning that, on average, the predictions are off by 2.5 percentage points.\
-Trump model: MAE of 3.13, indicating slightly less precise predictions compared to the Harris model.\
-
-Interpretation Summary
-Predictive Accuracy: The Harris model has slightly better predictive accuracy than the Trump model, as reflected by its lower RMSE and MAE values.\
-Model Fit: Both models explain roughly 34.6% of the variance in their respective datasets.
-This suggests that other factors not included in the model may play a significant role in explaining the remaining variance.\
-This summary indicates the models are moderately predictive, with room for improvement in accuracy and fit, potentially by adding more predictors or adjusting model specifications.\
+We use a 10-fold cross-validation on two linear regression models—one
+for Harris and one for Trump. The models use three predictors:
+national_poll, pollster, and population. The output provides key
+metrics, which breaks down here:
+
+RMSE (Root Mean Square Error): Measures the average magnitude of
+prediction errors (lower is better).
+
+Harris model: RMSE of 3.47, indicating an average prediction error of
+around 3.47 percentage points.\
+Trump model: RMSE of 4.39, showing a slightly higher prediction error on
+average.\
+
+R-squared: Represents the proportion of the variance in the response
+variable explained by the model (higher is better).\
+Harris model: R-squared of 0.346, meaning the model explains about 34.6%
+of the variance in Harris's polling data.\
+Trump model: R-squared of 0.346 as well, indicating similar explanatory
+power for Trump's polling data.
+
+MAE (Mean Absolute Error): Shows the average absolute difference between
+observed and predicted values (lower is better).\
+Harris model: MAE of 2.50, meaning that, on average, the predictions are
+off by 2.5 percentage points.\
+Trump model: MAE of 3.13, indicating slightly less precise predictions
+compared to the Harris model.\
+
+Interpretation Summary Predictive Accuracy: The Harris model has
+slightly better predictive accuracy than the Trump model, as reflected
+by its lower RMSE and MAE values.\
+Model Fit: Both models explain roughly 34.6% of the variance in their
+respective datasets. This suggests that other factors not included in
+the model may play a significant role in explaining the remaining
+variance.\
+This summary indicates the models are moderately predictive, with room
+for improvement in accuracy and fit, potentially by adding more
+predictors or adjusting model specifications.\
 
@@
 #| label: fig-stanareyouokay
-#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Harris"
+#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\-Support for Harris"
 #| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
@@
 ```
-Generally, we use Residual vs Fitted plot and Q-Q Plot diagnostic our model.
-Residual vs Fitted plot aare Residuals (differences between observed and predicted values) plotted against fitted values.
-Ideally, these residuals should be randomly scattered around the zero line to indicate that the model does not have systematic errors.
-The Q-Q plot for the unweighted model shows how the residuals align with a theoretical normal distribution.
-Ideally, residuals should follow a straight line in this plot if they are normally distributed, which is an assumption of linear regression.
-
-@fig-stanareyouokay-1 is a residual plot of un-weighted model for Harris support. It
-showsthe residuals are generally spread around zero, with no clear pattern.
-This suggests the model is relatively well-specified.
-However, there is a slight curvature, indicating potential non-linearity that the model may not fully capture.
-A few notable outliers with larger residuals might be influencing the model, indicating that some data points have more significant prediction errors.
-
-@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot for Harris support. It
-shows most residuals fall along the line, especially in the middle range.
-This suggests that our model satisfy the normality assumption.
-However, some points at the tails deviate, indicating potential outliers or non-normality in the extreme residual values.
-This slight deviation at the ends suggests the model might have some issues with extreme predictions but performs reasonably well overall.
-
-@fig-stanareyouokay-3 is a residual plot of weighted model for Harris support.It shows residuals are again plotted against fitted values.
-Similar to the unweighted model, the residuals are mostly centered around zero, indicating that the weighted model captures the general trend without significant systematic bias.
-The curvature is slightly reduced compared to the un-weighted model, suggesting that weighting has helped in addressing some of the non-linearity observed in the un-weighted model.
-However, some residuals are still notably large, which may indicate outliers that influence the model despite the weighting scheme.
-This suggests that while the weighted model performs better in terms of capturing non-linearity, further refinement might still be beneficial.
-
-@fig-stanareyouokay-4 is a  Q-Q Plot of weighted model plot for Harris support.The residuals generally align with the theoretical normal distribution line, particularly in the central range, indicating that the residuals of the weighted model are close to normal.
-Similar to the unweighted model, there are deviations at the tails, though they appear less pronounced.
-This suggests that the weighting scheme has slightly improved the distribution of residuals, making the model’s predictions more robust.
-However, some extreme values remain, which could still affect model
-
-In summary, both models show a reasonably good fit, with the weighted model offering slight improvements in handling non-linearity and extreme values.
-However, both models exhibit minor deviations from normality and a few notable outliers, which may warrant further model adjustments for improved prediction accuracy.
+
+Generally, we use Residual vs Fitted plot and Q-Q Plot diagnostic our
+model. Residual vs Fitted plot aare Residuals (differences between
+observed and predicted values) plotted against fitted values. Ideally,
+these residuals should be randomly scattered around the zero line to
+indicate that the model does not have systematic errors. The Q-Q plot
+for the unweighted model shows how the residuals align with a
+theoretical normal distribution. Ideally, residuals should follow a
+straight line in this plot if they are normally distributed, which is an
+assumption of linear regression.
+
+@fig-stanareyouokay-1 is a residual plot of un-weighted model for Harris
+support. It showsthe residuals are generally spread around zero, with no
+clear pattern. This suggests the model is relatively well-specified.
+However, there is a slight curvature, indicating potential non-linearity
+that the model may not fully capture. A few notable outliers with larger
+residuals might be influencing the model, indicating that some data
+points have more significant prediction errors.
+
+@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot for Harris
+support. It shows most residuals fall along the line, especially in the
+middle range. This suggests that our model satisfy the normality
+assumption. However, some points at the tails deviate, indicating
+potential outliers or non-normality in the extreme residual values. This
+slight deviation at the ends suggests the model might have some issues
+with extreme predictions but performs reasonably well overall.
+
+@fig-stanareyouokay-3 is a residual plot of weighted model for Harris
+support.It shows residuals are again plotted against fitted values.
+Similar to the unweighted model, the residuals are mostly centered
+around zero, indicating that the weighted model captures the general
+trend without significant systematic bias. The curvature is slightly
+reduced compared to the un-weighted model, suggesting that weighting has
+helped in addressing some of the non-linearity observed in the
+un-weighted model. However, some residuals are still notably large,
+which may indicate outliers that influence the model despite the
+weighting scheme. This suggests that while the weighted model performs
+better in terms of capturing non-linearity, further refinement might
+still be beneficial.
+
+@fig-stanareyouokay-4 is a Q-Q Plot of weighted model plot for Harris
+support.The residuals generally align with the theoretical normal
+distribution line, particularly in the central range, indicating that
+the residuals of the weighted model are close to normal. Similar to the
+unweighted model, there are deviations at the tails, though they appear
+less pronounced. This suggests that the weighting scheme has slightly
+improved the distribution of residuals, making the model’s predictions
+more robust. However, some extreme values remain, which could still
+affect model
+
+In summary, both models show a reasonably good fit, with the weighted
+model offering slight improvements in handling non-linearity and extreme
+values. However, both models exhibit minor deviations from normality and
+a few notable outliers, which may warrant further model adjustments for
+improved prediction accuracy.
 
@@
 
-@fig-dia-1 shows the residuals plotted against the fitted values for the unweighted model.
-It shows that the residuals are generally spread around zero with no clear pattern, suggesting that the model is relatively well-specified.
-However, there is a slight curvature, indicating possible non-linearity that the model may not fully capture.
-Some notable outliers with larger residuals suggest that certain data points have significant prediction errors, potentially influencing the model.
-
-@fig-dia-2 shows the Q-Q plot for the unweighted model, showing that most residuals fall along the line, especially in the middle range, suggesting that the model satisfies the normality assumption.
-However, some points at the tails deviate, indicating potential outliers or non-normality in extreme residual values.
-This deviation at the ends suggests the model may face issues with extreme predictions, though it performs reasonably well overall.
-
-@fig-dia3 shows residuals plotted against fitted values.
-Similar to the unweighted model, the residuals are centered around zero, indicating that the weighted model captures the overall trend without significant systematic bias.
-The slight curvature seen in the unweighted model is reduced here, suggesting that weighting has addressed some of the non-linearity.
-However, some large residuals remain, which could indicate outliers that affect the model even with the weighting scheme.
-This suggests that while the weighted model has improved in handling non-linearity, further refinements could enhance accuracy.
-
-@fig-dia-4 shows the Q-Q plot for the weighted model compares residuals with a theoretical normal distribution.
-Here, the residuals generally align with the theoretical line, especially in the central range, indicating that the residuals of the weighted model are close to normal.
-Similar to the unweighted model, some deviations occur at the tails, though they appear less pronounced, suggesting that the weighting scheme has slightly improved the normality of residuals.
-Nonetheless, some extreme values persist, which may impact model robustness in cases of outliers.
-
-Summary
-Both models exhibit a reasonably good fit, with the weighted model offering slight improvements in managing non-linearity and extreme values.
-Despite this, both models show minor deviations from normality and some notable outliers, suggesting that further model adjustments may be beneficial for improved prediction accuracy.
+@fig-dia-1 shows the residuals plotted against the fitted values for the
+unweighted model. It shows that the residuals are generally spread
+around zero with no clear pattern, suggesting that the model is
+relatively well-specified. However, there is a slight curvature,
+indicating possible non-linearity that the model may not fully capture.
+Some notable outliers with larger residuals suggest that certain data
+points have significant prediction errors, potentially influencing the
+model.
+
+@fig-dia-2 shows the Q-Q plot for the unweighted model, showing that
+most residuals fall along the line, especially in the middle range,
+suggesting that the model satisfies the normality assumption. However,
+some points at the tails deviate, indicating potential outliers or
+non-normality in extreme residual values. This deviation at the ends
+suggests the model may face issues with extreme predictions, though it
+performs reasonably well overall.
+
+@fig-dia3 shows residuals plotted against fitted values. Similar to the
+unweighted model, the residuals are centered around zero, indicating
+that the weighted model captures the overall trend without significant
+systematic bias. The slight curvature seen in the unweighted model is
+reduced here, suggesting that weighting has addressed some of the
+non-linearity. However, some large residuals remain, which could
+indicate outliers that affect the model even with the weighting scheme.
+This suggests that while the weighted model has improved in handling
+non-linearity, further refinements could enhance accuracy.
+
+@fig-dia-4 shows the Q-Q plot for the weighted model compares residuals
+with a theoretical normal distribution. Here, the residuals generally
+align with the theoretical line, especially in the central range,
+indicating that the residuals of the weighted model are close to normal.
+Similar to the unweighted model, some deviations occur at the tails,
+though they appear less pronounced, suggesting that the weighting scheme
+has slightly improved the normality of residuals. Nonetheless, some
+extreme values persist, which may impact model robustness in cases of
+outliers.
+
+Summary Both models exhibit a reasonably good fit, with the weighted
+model offering slight improvements in managing non-linearity and extreme
+values. Despite this, both models show minor deviations from normality
+and some notable outliers, suggesting that further model adjustments may
+be beneficial for improved prediction accuracy.
 

### 2024-10-30 paper/paper.qmd
update paper results

@@
 library(arrow)
+library(dplyr)
 ```
@@
 # Calculate weights for Harris data
-harris_data <- harris_data %>%
+harris_data <- harris_data |>
   mutate(
@@
     recency_weight = exp(-recency * 0.1)
-  ) %>%
-  group_by(pollster) %>%
+  ) |>
+  group_by(pollster) |>
   mutate(
@@
     poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) %>%
-  ungroup() %>%
+  ) |>
+  ungroup() |>
   mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
@@
 # Calculate weights for Trump data
-trump_data <- trump_data %>%
+trump_data <- trump_data |>
   mutate(
@@
 
-harris_data <- harris_data %>%
+harris_data <- harris_data |>
   mutate(
@@
 
-harris_filtered <- harris_data %>%
+harris_filtered <- harris_data |>
   filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)|>mutate(candidate = "Harris")
-trump_filtered <- trump_data %>%
+trump_filtered <- trump_data |>
   filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)|>mutate(candidate = "Trump")
@@
   theme_minimal() +
-  theme(
+  theme(theme(panel.spacing = unit(1, "lines"))
     legend.position = "top",
@@
 This trend suggests a potential narrowing in support levels as the election approaches, providing a quantitative snapshot of national polling dynamics.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| include: false
+
+new_data_harris <- data.frame(
+  end_date = seq(
+    min(harris_data$end_date),
+    max(harris_data$end_date),
+    length.out = 1000 
+  ),
+  pollster = factor("YouGov", levels = levels(harris_data$pollster)),  # Ensure it matches training levels
+  national_poll = rep(c(0, 1), length(1000)),  # Create a sequence for national_poll from 0 to 1
+  population = factor("lv", levels = levels(harris_data$population)),  # Use the mean population or any relevant value
+  sample_size = seq(min(0),max(2300),length.out=1000)
+)|>
+  mutate(
+    # Sample size weight (assuming a maximum of 2300 responses)
+    sample_size_weight = pmin(sample_size / 2300, 1),  # Set sample size; adjust accordingly
+
+    # Pollster quality weight (assuming you want to use a dummy numeric grade, e.g., 2)
+    pollster_quality_weight = 2 / 4,  # Example; replace with actual numeric grade if available
+
+    # Recency weight (this can be based on the date difference from a certain cutoff, e.g., "2024-11-05")
+    recency = as.numeric(difftime(as.Date("2024-11-05"), as.Date("2024-08-01") + (1:1000), units = "days")),  # Adjust for the sequence
+    recency_weight = exp(-recency * 0.1),  # Adjust decay rate as needed
+
+    # Poll frequency weight (you can set a condition based on a hypothetical recent poll count)
+    poll_frequency_weight = ifelse(national_poll > 0.5, 1, 0.5),  # Example logic for poll frequency
+
+    # Combine all weights into a final combined weight
+    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight
+  )
+
+new_data_trump <- data.frame(
+  end_date = seq(
+    min(harris_data$end_date),
+    max(harris_data$end_date),
+    length.out = 1000
+  ),
+  pollster = factor("YouGov", levels = levels(harris_data$pollster)),  # Ensure it matches training levels
+  national_poll = rep(c(0, 1), length(1000)),  # Create a sequence for national_poll from 0 to 1
+  population = factor("lv", levels = levels(harris_data$population)),  # Use the mean population or any relevant value
+  sample_size = seq(min(0),max(2300),length.out=1000)
+)|>
+  mutate(
+    # Sample size weight (assuming a maximum of 2300 responses)
+    sample_size_weight = pmin(sample_size / 2300, 1),  # Set sample size; adjust accordingly
+
+    # Pollster quality weight (assuming you want to use a dummy numeric grade, e.g., 2)
+    pollster_quality_weight = 2 / 4,  # Example; replace with actual numeric grade if available
+
+    # Recency weight (this can be based on the date difference from a certain cutoff, e.g., "2024-11-05")
+    recency = as.numeric(difftime(as.Date("2024-11-05"), as.Date("2024-08-01") + (1:1000), units = "days")),  # Adjust for the sequence
+    recency_weight = exp(-recency * 0.1),  # Adjust decay rate as needed
+
+    # Poll frequency weight (you can set a condition based on a hypothetical recent poll count)
+    poll_frequency_weight = ifelse(national_poll > 0.5, 1, 0.5),  # Example logic for poll frequency
+
+    # Combine all weights into a final combined weight
+    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight
+  )
+```
+
+```{r}
+# Predictions for Harris
+new_data_harris <- new_data_harris |>
+  mutate(
+    predicted_unweighted = predict(model_harris_unweighted, newdata = new_data_harris),
+    predicted_weighted = predict(model_harris_weighted, newdata = new_data_harris)
+  )
+
+# Predictions for Trump
+new_data_trump <- new_data_trump |>
+  mutate(
+    predicted_unweighted = predict(model_trump_unweighted, newdata = new_data_trump),
+    predicted_weighted = predict(model_trump_weighted, newdata = new_data_trump)
+  )
+
+# Plot the predictions
+library(dplyr)
+library(ggplot2)
+
+# Define the cutoff date for recent data
+recent_date_cutoff <- as.Date("2024-05-01")
+
+# Filter combined_predictions to include only data from the recent date cutoff onward
+combined_predictions_filtered <- combined_predictions %>%
+  filter(end_date >= recent_date_cutoff)
+
+# Determine the maximum end date for setting the x-axis limit
+max_end_date <- max(combined_predictions_filtered$end_date)
+
+# Plotting with the filtered data
+ggplot(combined_predictions_filtered, aes(x = end_date, color = candidate)) +
+  geom_smooth(aes(y = predicted_unweighted, linetype = "Unweighted"), 
+              method = "loess", se = FALSE, size = 1) +  # Unweighted model with smoothing
+  geom_smooth(aes(y = predicted_weighted, linetype = "Weighted"), 
+              method = "loess", se = FALSE, size = 1) +  # Weighted model with smoothing
+  labs(title = "Predicted Support for Kamala Harris and Donald Trump \n(From August 1, 2024 to October 27, 2024)",
+       subtitle = "predicted using multiple linear regression model ",
+       x = "End Date of the Poll",  # Change x-axis label to End Date
+       y = "Predicted Support (%)",
+       color = "Candidate") +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  scale_linetype_manual(name = "Linear Model Type", values = c("Unweighted" = "dashed", "Weighted" = "solid")) +
+  theme_minimal() +
+  theme(legend.position = "top",
+        axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
+
+```
+The predicted support for Kamala Harris and Donald Trump, as derived from multiple linear regression models, is displayed in the graph above.
+The analysis spans from August 1, 2024, to October 27, 2024, and highlights both unweighted and weighted predictions for each candidate.
+
+For Kamala Harris, the unweighted model predicts her support to remain relatively stable, maintaining an approximate support level of 49%.
+This trend is visually represented by the blue dashed line, which indicates minimal fluctuations over time.
+Conversely, the weighted model shows a more pronounced trend, demonstrating a gradual increase in predicted support, suggesting a potential shift in voter sentiment towards Harris as the election date approaches.
+
+In contrast, Donald Trump's predicted support, represented by the red lines, exhibits a downward trend in both unweighted and weighted models.
+The unweighted model indicates that his support is expected to hover around 48%, while the weighted model predicts a slight decline to approximately 46%.
+This trend may reflect challenges in maintaining voter enthusiasm in the face of changing public sentiment.
+
+At the end of the polling period, we predict that Kamala Harris leads Donald Trump by 2% in the unweighted model (48% vs. 46%) and by about 2% in the weighted model (49.1% vs. 47.3%).
 

### 2024-10-30 paper/paper.qmd
update paper results

@@
   theme_minimal() +
-  theme(theme(panel.spacing = unit(1, "lines"))
+  theme(
     legend.position = "top",

### 2024-10-30 paper/paper.qmd
update with plot caption

@@
 ```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| label: fig-support-predicted
+#| fig-cap: Predicted Support Trends for Kamala Harris and Donald Trump using fitted model
 # Predictions for Harris
@@
               method = "loess", se = FALSE, size = 1) +  # Weighted model with smoothing
-  labs(title = "Predicted Support for Kamala Harris and Donald Trump \n(From August 1, 2024 to October 27, 2024)",
+  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
        subtitle = "predicted using multiple linear regression model ",
@@
        y = "Predicted Support (%)",
-       color = "Candidate") +
+       color = "Candidate",caption = 
+                   "Weights: recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight\nLinear Regression Model: candidate support percentage =national_poll + pollster + population") +
   scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +

### 2024-10-30 paper/paper.qmd
update cross reference

@@
 #| label: fig-support-predicted
-#| fig-cap: Predicted Support Trends for Kamala Harris and Donald Trump using fitted model
+#| fig-cap: Predicted Support Trends for Kamala Harris and Donald Trump using Fitted Linear Model
 # Predictions for Harris
@@
 ```
-The predicted support for Kamala Harris and Donald Trump, as derived from multiple linear regression models, is displayed in the graph above.
+The predicted support for Kamala Harris and Donald Trump, as derived from multiple linear regression models, is displayed in @fig-support-predicted.
 The analysis spans from August 1, 2024, to October 27, 2024, and highlights both unweighted and weighted predictions for each candidate.

### 2024-10-30 paper/paper.qmd
Add discussion point

--- 2024-10-30 paper/paper.qmd
@@
 ---
-title: "Based on polling as of 27 October 2024, Harris expects to win on 49.2%, leads Trump by 2% in 2024 US election"
+title: "Based on polling as of 27 October 2024, Harris expects to win on xxx%, leads Trump by xx% in 2024 US election"
 subtitle: "Weighted Linear Regression Analysis of Aggregated Poll Data: Utilizing National Polls indicator, Population, and Pollster as Predictors."
@@
 library(tidyverse)
-library(arrow)
-library(dplyr)
-```
-
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-harris_data <- read_parquet("~/2024 US Election Forecast/data/02-analysis_data/analysis_data_Harris.parquet")
-trump_data <- read_parquet("~/2024 US Election Forecast/data/02-analysis_data/analysis_data_Trump.parquet")
-
 ```
@@
 
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-harris_unweighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_harris_unweighted.rds")
-harris_weighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_harris_weighted.rds")
-trump_unweighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_trump_unweighted.rds")
-trump_weighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_trump_weighted.rds")
-
-```
-
 #### Unweighted Model
@@
 
+```{r}
+model_harris_unweighted <- lm(pct ~ national_poll + pollster + population, data = harris_data)
+```
+
 #### Weighted Model
@@
 ```{r}
-#| include: false
-#| warning: false
-#| message: false
-#### Calculate Weights ####
-# Calculate weights for Harris data
-harris_data <- harris_data |>
-  mutate(
-    sample_size_weight = pmin(sample_size / 2300, 1),
-    pollster_quality_weight = numeric_grade / 4,
-    recency_weight = exp(-recency * 0.1)
-  ) |>
-  group_by(pollster) |>
-  mutate(
-    recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) |>
-  ungroup() |>
-  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
-
-# Calculate weights for Trump data
-trump_data <- trump_data |>
-  mutate(
-    sample_size_weight = pmin(sample_size / 2300, 1),
-    pollster_quality_weight = numeric_grade / 4,
-    recency_weight = exp(-recency * 0.1)
-  ) |>
-  group_by(pollster) |>
-  mutate(
-    recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) |>
-  ungroup() |>
-  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+model_harris_weighted <- lm(pct ~ national_poll + pollster + population, data = harris_data, weights = combined_weight)
 ```
@@
 
-1.  **Use of Weighted Model**: The weighted model is essential for
-    accurately reflecting voter sentiment. By incorporating weights, we
-    adjust for the reliability of the polling data, ensuring that more
-    credible polls have a greater influence on the estimates.
+1. **Weighted Least Squares Estimation**
+
+In our analysis, we utilize weighted least squares estimation to account
+for the varying quality of polling data. The weights are crucial in the
+estimation process, leading to the following expression for the
+estimates of the coefficients ($\hat{\beta}$):
+
+$$
+\hat{\beta} = (X^T W X)^{-1} X^T W y
+$$
+
+Where: - $X$ is the design matrix of predictors. - $W$ is the diagonal
+matrix of weights, which incorporates factors such as recency, sample
+size, and pollster quality to enhance the reliability of our estimates.
+
+The weighted model is essential for accurately reflecting voter sentiment. 
+By incorporating weights, we adjust for the reliability of the polling data, 
+ensuring that more credible polls have a greater influence on the estimates.
 
@@
 
-### Weighted Least Squares Estimation
-
-In our analysis, we utilize weighted least squares estimation to account
-for the varying quality of polling data. The weights are crucial in the
-estimation process, leading to the following expression for the
-estimates of the coefficients ($\hat{\beta}$):
-
-$$
-\hat{\beta} = (X^T W X)^{-1} X^T W y
-$$
-
-Where: - $X$ is the design matrix of predictors. - $W$ is the diagonal
-matrix of weights, which incorporates factors such as recency, sample
-size, and pollster quality to enhance the reliability of our estimates.
-
 ### Importance of Combined Weights
@@
 
-# Load necessary libraries
-library(tidyverse)
-library(ggplot2)
-
-harris_data <- harris_data |>
+harris_data <- harris_data %>%
   mutate(
@@
     recency_weight = exp(-recency * 0.1)
-  ) |>
-  group_by(pollster) |>
+  ) %>%
+  group_by(pollster) %>%
   mutate(
@@
     poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) |>
-  ungroup() |>
+  ) %>%
+  ungroup() %>%
   mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
@@
 # Calculate weights for Trump data
-trump_data <- trump_data |>
+trump_data <- trump_data %>%
   mutate(
@@
     poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) |>
-  ungroup() |>
+  ) %>%
+  ungroup() %>%
   mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
 
+harris_data <- harris_data %>% mutate(candidate = "Harris")
+trump_data <- trump_data %>% mutate(candidate = "Trump")
+combined_data_total <- bind_rows(harris_data, trump_data)
+
 selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
-
 recent_date_cutoff <- as.Date("2024-08-01")  # Set cutoff for recent data
 
-harris_filtered <- harris_data |>
-  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)|>mutate(candidate = "Harris")
-trump_filtered <- trump_data |>
-  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)|>mutate(candidate = "Trump")
-
+harris_filtered <- harris_data %>%
+  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)
+
+trump_filtered <- trump_data %>%
+  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)
+
+# Combine datasets for plotting with a new column for candidate
+harris_filtered <- harris_filtered %>% mutate(candidate = "Harris")
+trump_filtered <- trump_filtered %>% mutate(candidate = "Trump")
 combined_data <- bind_rows(harris_filtered, trump_filtered)
@@
 #| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States
-harris_data<-harris_data|>mutate(candidate = "Harris")
-trump_data<-trump_data |>mutate(candidate= "Trump")
-combined_data_total <- bind_rows(harris_data, trump_data)
+
+# Combine datasets for plotting with a new column for candidate
+harris_filtered <- harris_filtered %>% mutate(candidate = "Harris")
+trump_filtered <- trump_filtered %>% mutate(candidate = "Trump")
+combined_data <- bind_rows(harris_filtered, trump_filtered)
+
 combined_data_total|>filter(national_poll==1)|>ggplot(aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
@@
 
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| include: false
-
-new_data_harris <- data.frame(
-  end_date = seq(
-    min(harris_data$end_date),
-    max(harris_data$end_date),
-    length.out = 1000 
-  ),
-  pollster = factor("YouGov", levels = levels(harris_data$pollster)),  # Ensure it matches training levels
-  national_poll = rep(c(0, 1), length(1000)),  # Create a sequence for national_poll from 0 to 1
-  population = factor("lv", levels = levels(harris_data$population)),  # Use the mean population or any relevant value
-  sample_size = seq(min(0),max(2300),length.out=1000)
-)|>
-  mutate(
-    # Sample size weight (assuming a maximum of 2300 responses)
-    sample_size_weight = pmin(sample_size / 2300, 1),  # Set sample size; adjust accordingly
-
-    # Pollster quality weight (assuming you want to use a dummy numeric grade, e.g., 2)
-    pollster_quality_weight = 2 / 4,  # Example; replace with actual numeric grade if available
-
-    # Recency weight (this can be based on the date difference from a certain cutoff, e.g., "2024-11-05")
-    recency = as.numeric(difftime(as.Date("2024-11-05"), as.Date("2024-08-01") + (1:1000), units = "days")),  # Adjust for the sequence
-    recency_weight = exp(-recency * 0.1),  # Adjust decay rate as needed
-
-    # Poll frequency weight (you can set a condition based on a hypothetical recent poll count)
-    poll_frequency_weight = ifelse(national_poll > 0.5, 1, 0.5),  # Example logic for poll frequency
-
-    # Combine all weights into a final combined weight
-    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight
-  )
-
-new_data_trump <- data.frame(
-  end_date = seq(
-    min(harris_data$end_date),
-    max(harris_data$end_date),
-    length.out = 1000
-  ),
-  pollster = factor("YouGov", levels = levels(harris_data$pollster)),  # Ensure it matches training levels
-  national_poll = rep(c(0, 1), length(1000)),  # Create a sequence for national_poll from 0 to 1
-  population = factor("lv", levels = levels(harris_data$population)),  # Use the mean population or any relevant value
-  sample_size = seq(min(0),max(2300),length.out=1000)
-)|>
-  mutate(
-    # Sample size weight (assuming a maximum of 2300 responses)
-    sample_size_weight = pmin(sample_size / 2300, 1),  # Set sample size; adjust accordingly
-
-    # Pollster quality weight (assuming you want to use a dummy numeric grade, e.g., 2)
-    pollster_quality_weight = 2 / 4,  # Example; replace with actual numeric grade if available
-
-    # Recency weight (this can be based on the date difference from a certain cutoff, e.g., "2024-11-05")
-    recency = as.numeric(difftime(as.Date("2024-11-05"), as.Date("2024-08-01") + (1:1000), units = "days")),  # Adjust for the sequence
-    recency_weight = exp(-recency * 0.1),  # Adjust decay rate as needed
-
-    # Poll frequency weight (you can set a condition based on a hypothetical recent poll count)
-    poll_frequency_weight = ifelse(national_poll > 0.5, 1, 0.5),  # Example logic for poll frequency
-
-    # Combine all weights into a final combined weight
-    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight
-  )
-```
-
-```{r}
-# Predictions for Harris
-new_data_harris <- new_data_harris |>
-  mutate(
-    predicted_unweighted = predict(model_harris_unweighted, newdata = new_data_harris),
-    predicted_weighted = predict(model_harris_weighted, newdata = new_data_harris)
-  )
-
-# Predictions for Trump
-new_data_trump <- new_data_trump |>
-  mutate(
-    predicted_unweighted = predict(model_trump_unweighted, newdata = new_data_trump),
-    predicted_weighted = predict(model_trump_weighted, newdata = new_data_trump)
-  )
-
-# Plot the predictions
-library(dplyr)
-library(ggplot2)
-
-# Define the cutoff date for recent data
-recent_date_cutoff <- as.Date("2024-05-01")
-
-# Filter combined_predictions to include only data from the recent date cutoff onward
-combined_predictions_filtered <- combined_predictions %>%
-  filter(end_date >= recent_date_cutoff)
-
-# Determine the maximum end date for setting the x-axis limit
-max_end_date <- max(combined_predictions_filtered$end_date)
-
-# Plotting with the filtered data
-ggplot(combined_predictions_filtered, aes(x = end_date, color = candidate)) +
-  geom_smooth(aes(y = predicted_unweighted, linetype = "Unweighted"), 
-              method = "loess", se = FALSE, size = 1) +  # Unweighted model with smoothing
-  geom_smooth(aes(y = predicted_weighted, linetype = "Weighted"), 
-              method = "loess", se = FALSE, size = 1) +  # Weighted model with smoothing
-  labs(title = "Predicted Support for Kamala Harris and Donald Trump \n(From August 1, 2024 to October 27, 2024)",
-       subtitle = "predicted using multiple linear regression model ",
-       x = "End Date of the Poll",  # Change x-axis label to End Date
-       y = "Predicted Support (%)",
-       color = "Candidate") +
-  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
-  scale_linetype_manual(name = "Linear Model Type", values = c("Unweighted" = "dashed", "Weighted" = "solid")) +
-  theme_minimal() +
-  theme(legend.position = "top",
-        axis.text.x = element_text(angle = 45, hjust = 1)) +
-  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
-
-```
-The predicted support for Kamala Harris and Donald Trump, as derived from multiple linear regression models, is displayed in the graph above.
-The analysis spans from August 1, 2024, to October 27, 2024, and highlights both unweighted and weighted predictions for each candidate.
-
-For Kamala Harris, the unweighted model predicts her support to remain relatively stable, maintaining an approximate support level of 49%.
-This trend is visually represented by the blue dashed line, which indicates minimal fluctuations over time.
-Conversely, the weighted model shows a more pronounced trend, demonstrating a gradual increase in predicted support, suggesting a potential shift in voter sentiment towards Harris as the election date approaches.
-
-In contrast, Donald Trump's predicted support, represented by the red lines, exhibits a downward trend in both unweighted and weighted models.
-The unweighted model indicates that his support is expected to hover around 48%, while the weighted model predicts a slight decline to approximately 46%.
-This trend may reflect challenges in maintaining voter enthusiasm in the face of changing public sentiment.
-
-At the end of the polling period, we predict that Kamala Harris leads Donald Trump by 2% in the unweighted model (48% vs. 46%) and by about 2% in the weighted model (49.1% vs. 47.3%).
-
 # Discussion
 
-## First discussion point {#sec-first-point}
+## Key Findings and Real-World Implications {#sec-key-findings}
+Our model reveals a portrait of a nation deeply divided, with Harris holding a narrow 49% edge over Trump’s 47% in national support.
+However, as recent elections have shown, the national popular vote does not always translate into an Electoral College victory.
+The U.S.
+electoral system, which awards each state’s electoral votes to the candidate with the majority of votes in that state, means that winning the popular vote nationally might still leave Harris short of the presidency.
+This structural quirk played a defining role in the 2016 election, where Hillary Clinton’s popular vote win failed to deliver the electoral majority, paving Trump’s path to the White House.
+Our findings underscore this enduring tension: while Harris may have a slight national advantage, the true battle will be fought state by state, in a handful of battlegrounds that could flip the election either way.
+
+In states like Wisconsin and Arizona, our model highlights just how close the race remains.
+Wisconsin, for instance, shows both candidates locked in a near tie around 48% support—a statistical dead heat that brings the state’s significance into sharp relief.
+Arizona, meanwhile, leans modestly toward Trump, a reflection of the unique demographic and political nuances shaping each battleground.
+These state-level insights illuminate a critical truth: while national polls offer a snapshot of overall sentiment, they risk obscuring the specific, local dynamics that will ultimately decide the outcome.
+The stakes are high; these are the states that could swing, the margins that will be watched closely on election night, as even slight changes in turnout or last-minute shifts in opinion could tip the balance.
+
+Yet, as with all models, limitations persist.
+While our weighting system, with its emphasis on recent data, aims to capture a timely snapshot of voter sentiment, it may miss sudden changes sparked by campaign events or unexpected shifts in public discourse.
+The variability in our state projections—ranging from a low estimate of 363 electoral votes for Harris to a high of 471—reflects the inherent uncertainty in polling-based models, particularly given the constraints of our data sources.
+This wide range suggests that while data-driven insights can illuminate trends, they cannot fully account for the unpredictable nature of electoral outcomes.
+Moving forward, incorporating real-time sentiment from social media or demographic-specific insights could offer a more responsive understanding of voter behavior.
+Ultimately, these findings highlight the intricate dance between popular sentiment and the electoral mechanics of American democracy—a system where every vote counts, but some states matter just a bit more than others.
 
@@
 
-In this data-cleaning process, we focus on refining raw polling data to
-enhance its quality and relevance for subsequent analysis. The dataset
-is initially loaded and cleaned using the janitor package to standardize
-column names, ensuring consistency throughout. We then filter the data
-to retain only relevant columns and eliminate any rows with missing
-values in critical fields, including numeric_grade, pct, sample_size,
-and end_date.
-
-Specifically, we isolate the polling data for Kamala Harris and Donald
-Trump, applying a condition to include only high-quality polls with a
-numeric grade of 2 or higher, given that the mean of the numeric grade
-is 2.175 and the median is 1.9.
-
-For state-level polls, we handle any placeholder states marked as "--"
-by converting them to NA. A national poll indicator is generated,
-assigning a value of 1 for national polls and 0 for state-specific ones.
-Dates are standardized using the lubridate package to ensure accurate
-handling in subsequent analyses.
-
-Recency weights are calculated based on the number of days elapsed since
-the poll ended, utilizing an exponential decay function to give greater
-weight to more recent polls.
-
-Finally, the cleaned datasets for both candidates are saved in CSV
-format for further modeling and analysis. This systematic approach
-guarantees that the data is accurate, complete, and ready for insightful
-analysis.
+In this data-cleaning process, we focus on refining raw polling data to enhance its quality and relevance for subsequent analysis.
+The dataset is initially loaded and cleaned using the janitor package to standardize column names, ensuring consistency throughout.
+We then filter the data to retain only relevant columns and eliminate any rows with missing values in critical fields, including numeric_grade, pct, sample_size, and end_date.
+
+Specifically, we isolate the polling data for Kamala Harris and Donald Trump, applying a condition to include only high-quality polls with a numeric grade of 2 or higher, given that the mean of the numeric grade is 2.175 and the median is 1.9.
+
+For state-level polls, we handle any placeholder states marked as "--" by converting them to NA.
+A national poll indicator is generated, assigning a value of 1 for national polls and 0 for state-specific ones.
+Dates are standardized using the lubridate package to ensure accurate handling in subsequent analyses.
+
+Recency weights are calculated based on the number of days elapsed since the poll ended, utilizing an exponential decay function to give greater weight to more recent polls.
+Additionally, a sample size weight is implemented, capping the weights at a maximum of 2,300 responses to reflect the reliability of larger sample sizes.
+
+Finally, the cleaned datasets for both candidates are saved in CSV format for further modeling and analysis.
+This systematic approach guarantees that the data is accurate, complete, and ready for insightful analysis.
 
@@
 
-## Model validation: K-Fold Cross-Validation
+## Model validation
 
 ```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-# Load necessary libraries
-library(boot)    # For bootstrapping
-library(caret)   # For cross-validation
-
-# Set up 10-fold cross-validation
-train_control <- trainControl(method = "cv", number = 10)
-# Train the model
-model_formula <- pct ~ national_poll + pollster + population
-model_harris_cv <- train(model_formula, data = harris_data, method = "lm", trControl = train_control)
-# Set up 10-fold cross-validation
-train_control <- trainControl(method = "cv", number = 10)
-# Train the model
-model_harris_cv <- train(model_formula, data = harris_data, method = "lm", trControl = train_control)
-# Print the model results
-print(model_harris_cv)
-
-model_trump_cv <- train(model_formula, data = trump_data, method = "lm", trControl = train_control)
-# Set up 10-fold cross-validation
-train_control <- trainControl(method = "cv", number = 10)
-# Train the model
-model_trump_cv <- train(model_formula, data = trump_data, method = "lm", trControl = train_control)
-# Print the model results
-print(model_trump_cv)
+# Set seed for reproducibility
+set.seed(123)
+
+# Sample indices for training and testing sets
+train_index <- sample(seq_len(nrow(data)), size = 0.8 * nrow(data))
+
+# Split the data into training and testing sets
+train_data <- data[train_index, ]
+test_data <- data[-train_index, ]
+
+# Fit the weighted linear regression model
+first_model_test <- lm(pct ~ national_poll + pollster + population, 
+                     data = data, 
+                  data = train_data)
+
+# Predict on test data
+predictions <- predict(first_model_test, newdata = test_data)
+
+# Calculate RMSE using the correct outcome variable
+# Assuming 'pct' is the actual observed outcome variable in test_data
+rmse <- sqrt(mean((predictions - test_data$pct)^2, na.rm = TRUE))
+
+# Print RMSE
+print(paste("RMSE:", rmse))
+
 ```
 
-We use a 10-fold cross-validation on two linear regression models—one
-for Harris and one for Trump. The models use three predictors:
-national_poll, pollster, and population. The output provides key
-metrics, which breaks down here:
-
-RMSE (Root Mean Square Error): Measures the average magnitude of
-prediction errors (lower is better).
-
-Harris model: RMSE of 3.47, indicating an average prediction error of
-around 3.47 percentage points.\
-Trump model: RMSE of 4.39, showing a slightly higher prediction error on
-average.\
-
-R-squared: Represents the proportion of the variance in the response
-variable explained by the model (higher is better).\
-Harris model: R-squared of 0.346, meaning the model explains about 34.6%
-of the variance in Harris's polling data.\
-Trump model: R-squared of 0.346 as well, indicating similar explanatory
-power for Trump's polling data.
-
-MAE (Mean Absolute Error): Shows the average absolute difference between
-observed and predicted values (lower is better).\
-Harris model: MAE of 2.50, meaning that, on average, the predictions are
-off by 2.5 percentage points.\
-Trump model: MAE of 3.13, indicating slightly less precise predictions
-compared to the Harris model.\
-
-Interpretation Summary Predictive Accuracy: The Harris model has
-slightly better predictive accuracy than the Trump model, as reflected
-by its lower RMSE and MAE values.\
-Model Fit: Both models explain roughly 34.6% of the variance in their
-respective datasets. This suggests that other factors not included in
-the model may play a significant role in explaining the remaining
-variance.\
-This summary indicates the models are moderately predictive, with room
-for improvement in accuracy and fit, potentially by adding more
-predictors or adjusting model specifications.\
-
 ## Diagnostics
+
+@fig-stanareyouokay-1 is a residual plot of un-weighted model. It shows... This suggests...
+
+@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot. It shows... This suggests...
 
@@
 #| label: fig-stanareyouokay
-#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\-Support for Harris"
-#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
+#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-subcap: ["Trace plot", "Rhat plot"]
 #| layout-ncol: 2
-
-# Residual plot for unweighted model
-plot(harris_unweighted_model, which = 1, main = "Residual Plot of Unweighted Linear Regression Model")
-
-# Q-Q plot for the residuals of the unweighted model
-qqnorm(residuals(harris_unweighted_model), main = "Q-Q Plot of Unweighted Linear Regression Model Residuals")
-qqline(residuals(harris_unweighted_model), col = "red")
-
-# Residual plot for weighted model
-plot(harris_weighted_model, which = 1, main = "Residual Plot of Weighted Linear Regression Model")
-
-# Q-Q plot for the residuals of the weighted model
-qqnorm(residuals(harris_weighted_model), main = "Q-Q Plot of Weighted Linear Regression Model Residuals")
-qqline(residuals(harris_weighted_model), col = "red")
+#residual plot
+plot(first_model, which = 1,main ="Residual Plot of unweighted linear regression model residualsmodel" )
+# Q-Q plot for the residuals of the model
+qqnorm(residuals(first_model),main= "Q-Q Plot of unweighted linear regression model residuals
+")
+qqline(residuals(first_model), col = "red")
 
 ```
-
-Generally, we use Residual vs Fitted plot and Q-Q Plot diagnostic our
-model. Residual vs Fitted plot aare Residuals (differences between
-observed and predicted values) plotted against fitted values. Ideally,
-these residuals should be randomly scattered around the zero line to
-indicate that the model does not have systematic errors. The Q-Q plot
-for the unweighted model shows how the residuals align with a
-theoretical normal distribution. Ideally, residuals should follow a
-straight line in this plot if they are normally distributed, which is an
-assumption of linear regression.
-
-@fig-stanareyouokay-1 is a residual plot of un-weighted model for Harris
-support. It showsthe residuals are generally spread around zero, with no
-clear pattern. This suggests the model is relatively well-specified.
-However, there is a slight curvature, indicating potential non-linearity
-that the model may not fully capture. A few notable outliers with larger
-residuals might be influencing the model, indicating that some data
-points have more significant prediction errors.
-
-@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot for Harris
-support. It shows most residuals fall along the line, especially in the
-middle range. This suggests that our model satisfy the normality
-assumption. However, some points at the tails deviate, indicating
-potential outliers or non-normality in the extreme residual values. This
-slight deviation at the ends suggests the model might have some issues
-with extreme predictions but performs reasonably well overall.
-
-@fig-stanareyouokay-3 is a residual plot of weighted model for Harris
-support.It shows residuals are again plotted against fitted values.
-Similar to the unweighted model, the residuals are mostly centered
-around zero, indicating that the weighted model captures the general
-trend without significant systematic bias. The curvature is slightly
-reduced compared to the un-weighted model, suggesting that weighting has
-helped in addressing some of the non-linearity observed in the
-un-weighted model. However, some residuals are still notably large,
-which may indicate outliers that influence the model despite the
-weighting scheme. This suggests that while the weighted model performs
-better in terms of capturing non-linearity, further refinement might
-still be beneficial.
-
-@fig-stanareyouokay-4 is a Q-Q Plot of weighted model plot for Harris
-support.The residuals generally align with the theoretical normal
-distribution line, particularly in the central range, indicating that
-the residuals of the weighted model are close to normal. Similar to the
-unweighted model, there are deviations at the tails, though they appear
-less pronounced. This suggests that the weighting scheme has slightly
-improved the distribution of residuals, making the model’s predictions
-more robust. However, some extreme values remain, which could still
-affect model
-
-In summary, both models show a reasonably good fit, with the weighted
-model offering slight improvements in handling non-linearity and extreme
-values. However, both models exhibit minor deviations from normality and
-a few notable outliers, which may warrant further model adjustments for
-improved prediction accuracy.
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-dia
-#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Trump"
-#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
-#| layout-ncol: 2
-
-# Residual plot for unweighted model
-plot(trump_unweighted_model, which = 1, main = "Residual Plot of Unweighted Linear Regression Model")
-
-# Q-Q plot for the residuals of the unweighted model
-qqnorm(residuals(trump_unweighted_model), main = "Q-Q Plot of Unweighted Linear Regression Model Residuals")
-qqline(residuals(trump_unweighted_model), col = "red")
-
-# Residual plot for weighted model
-plot(trump_weighted_model, which = 1, main = "Residual Plot of Weighted Linear Regression Model")
-
-# Q-Q plot for the residuals of the weighted model
-qqnorm(residuals(trump_weighted_model), main = "Q-Q Plot of Weighted Linear Regression Model Residuals")
-qqline(residuals(trump_weighted_model), col = "red")
-
-```
-
-@fig-dia-1 shows the residuals plotted against the fitted values for the
-unweighted model. It shows that the residuals are generally spread
-around zero with no clear pattern, suggesting that the model is
-relatively well-specified. However, there is a slight curvature,
-indicating possible non-linearity that the model may not fully capture.
-Some notable outliers with larger residuals suggest that certain data
-points have significant prediction errors, potentially influencing the
-model.
-
-@fig-dia-2 shows the Q-Q plot for the unweighted model, showing that
-most residuals fall along the line, especially in the middle range,
-suggesting that the model satisfies the normality assumption. However,
-some points at the tails deviate, indicating potential outliers or
-non-normality in extreme residual values. This deviation at the ends
-suggests the model may face issues with extreme predictions, though it
-performs reasonably well overall.
-
-@fig-dia3 shows residuals plotted against fitted values. Similar to the
-unweighted model, the residuals are centered around zero, indicating
-that the weighted model captures the overall trend without significant
-systematic bias. The slight curvature seen in the unweighted model is
-reduced here, suggesting that weighting has addressed some of the
-non-linearity. However, some large residuals remain, which could
-indicate outliers that affect the model even with the weighting scheme.
-This suggests that while the weighted model has improved in handling
-non-linearity, further refinements could enhance accuracy.
-
-@fig-dia-4 shows the Q-Q plot for the weighted model compares residuals
-with a theoretical normal distribution. Here, the residuals generally
-align with the theoretical line, especially in the central range,
-indicating that the residuals of the weighted model are close to normal.
-Similar to the unweighted model, some deviations occur at the tails,
-though they appear less pronounced, suggesting that the weighting scheme
-has slightly improved the normality of residuals. Nonetheless, some
-extreme values persist, which may impact model robustness in cases of
-outliers.
-
-Summary Both models exhibit a reasonably good fit, with the weighted
-model offering slight improvements in managing non-linearity and extreme
-values. Despite this, both models show minor deviations from normality
-and some notable outliers, suggesting that further model adjustments may
-be beneficial for improved prediction accuracy.
 

### 2024-10-30 paper/paper.qmd
update paper

--- 2024-10-30 paper/paper.qmd
@@
 weights based on poll quality, sample size, and recency to better
-reflect voter sentiment [@nytimes].
+reflect voter sentiment [@nyt_polling_averages].
+
+The validation and diagnostic details of the model are provided in [Appendix B](#sec-model-details)
 
@@
 
+## Recent 3 Months Support Trends Linear Model Prediction
+
 ```{r}
@@
 #| include: false
-
+set.seed(233)
 new_data_harris <- data.frame(
@@
   ),
-  pollster = factor("YouGov", levels = levels(harris_data$pollster)),  # Ensure it matches training levels
-  national_poll = rep(c(0, 1), length(1000)),  # Create a sequence for national_poll from 0 to 1
-  population = factor("lv", levels = levels(harris_data$population)),  # Use the mean population or any relevant value
-  sample_size = seq(min(0),max(2300),length.out=1000)
+  national_poll = rep(c(0, 1), length(1000)),
+  pollster = factor(sample(levels(harris_data$pollster), size = 1000, replace = TRUE), 
+                    levels = levels(harris_data$pollster)),  
+  population = factor(sample(c("lv","rv"), size = 1000, replace = TRUE)),
+  sample_size = sample(1:2300, size = 1000, replace = TRUE),
+  pollster_quality= sample(2:4, size = 1000, replace = TRUE)
 )|>
@@
     # Pollster quality weight (assuming you want to use a dummy numeric grade, e.g., 2)
-    pollster_quality_weight = 2 / 4,  # Example; replace with actual numeric grade if available
+    pollster_quality_weight = pollster_quality / 4,
 
     # Recency weight (this can be based on the date difference from a certain cutoff, e.g., "2024-11-05")
-    recency = as.numeric(difftime(as.Date("2024-11-05"), as.Date("2024-08-01") + (1:1000), units = "days")),  # Adjust for the sequence
+    recency = as.numeric(difftime( as.Date("2024-11-05"),as.Date(end_date), units = "days")),  # Adjust for the sequence
     recency_weight = exp(-recency * 0.1),  # Adjust decay rate as needed
-
-    # Poll frequency weight (you can set a condition based on a hypothetical recent poll count)
-    poll_frequency_weight = ifelse(national_poll > 0.5, 1, 0.5),  # Example logic for poll frequency
-
+        recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1),
     # Combine all weights into a final combined weight
-    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight
+    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
+    candidate="Harris"
   )
-
 new_data_trump <- data.frame(
   end_date = seq(
-    min(harris_data$end_date),
-    max(harris_data$end_date),
+    min(trump_data$end_date),
+    max(trump_data$end_date),
     length.out = 1000
   ),
-  pollster = factor("YouGov", levels = levels(harris_data$pollster)),  # Ensure it matches training levels
-  national_poll = rep(c(0, 1), length(1000)),  # Create a sequence for national_poll from 0 to 1
-  population = factor("lv", levels = levels(harris_data$population)),  # Use the mean population or any relevant value
-  sample_size = seq(min(0),max(2300),length.out=1000)
+  pollster = factor(sample(levels(trump_data$pollster), size = 1000, replace = TRUE), 
+                    levels = levels(trump_data$pollster)),  
+  population = factor(sample(c("lv","rv"), size = 1000, replace = TRUE)),
+   national_poll = rep(c(0, 1), length(1000)),  
+  sample_size =sample(1:2300, size = 1000, replace = TRUE),
+  pollster_quality= sample(2:4, size = 1000, replace = TRUE)
 )|>
@@
     # Pollster quality weight (assuming you want to use a dummy numeric grade, e.g., 2)
-    pollster_quality_weight = 2 / 4,  # Example; replace with actual numeric grade if available
+    pollster_quality_weight = pollster_quality / 4,
 
     # Recency weight (this can be based on the date difference from a certain cutoff, e.g., "2024-11-05")
-    recency = as.numeric(difftime(as.Date("2024-11-05"), as.Date("2024-08-01") + (1:1000), units = "days")),  # Adjust for the sequence
+    recency = as.numeric(difftime( as.Date("2024-11-05"),as.Date(end_date), units = "days")),  # Adjust for the sequence
     recency_weight = exp(-recency * 0.1),  # Adjust decay rate as needed
@@
     # Poll frequency weight (you can set a condition based on a hypothetical recent poll count)
-    poll_frequency_weight = ifelse(national_poll > 0.5, 1, 0.5),  # Example logic for poll frequency
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1),
 
     # Combine all weights into a final combined weight
-    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight
+    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
+    candidate="Trump"
   )
@@
   mutate(
-    predicted_unweighted = predict(model_harris_unweighted, newdata = new_data_harris),
-    predicted_weighted = predict(model_harris_weighted, newdata = new_data_harris)
+    predicted_unweighted = predict(harris_unweighted_model, newdata = new_data_harris),
+    predicted_weighted = predict(harris_weighted_model, newdata = new_data_harris)
   )
@@
   mutate(
-    predicted_unweighted = predict(model_trump_unweighted, newdata = new_data_trump),
-    predicted_weighted = predict(model_trump_weighted, newdata = new_data_trump)
+    predicted_unweighted = predict(trump_unweighted_model, newdata = new_data_trump),
+    predicted_weighted = predict(trump_weighted_model, newdata = new_data_trump)
   )
 
-# Plot the predictions
-library(dplyr)
-library(ggplot2)
-
 # Define the cutoff date for recent data
-recent_date_cutoff <- as.Date("2024-05-01")
+recent_date_cutoff <- as.Date("2024-08-01")
 
 # Filter combined_predictions to include only data from the recent date cutoff onward
-combined_predictions_filtered <- combined_predictions %>%
-  filter(end_date >= recent_date_cutoff)
-
+combined_predictions<- bind_rows(new_data_harris, new_data_trump)
+combined_predictions_filtered<-combined_predictions|>filter(end_date>=recent_date_cutoff)
 # Determine the maximum end date for setting the x-axis limit
@@
   geom_smooth(aes(y = predicted_unweighted, linetype = "Unweighted"), 
-              method = "loess", se = FALSE, size = 1) +  # Unweighted model with smoothing
+              method = "loess", se = TRUE, size = 1) +  # Unweighted model with smoothing
   geom_smooth(aes(y = predicted_weighted, linetype = "Weighted"), 
-              method = "loess", se = FALSE, size = 1) +  # Weighted model with smoothing
+              method = "loess", se = TRUE, size = 1) +
   labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
@@
 ```
-The predicted support for Kamala Harris and Donald Trump, as derived from multiple linear regression models, is displayed in the graph above.
-The analysis spans from August 1, 2024, to October 27, 2024, and highlights both unweighted and weighted predictions for each candidate.
-
-For Kamala Harris, the unweighted model predicts her support to remain relatively stable, maintaining an approximate support level of 49%.
-This trend is visually represented by the blue dashed line, which indicates minimal fluctuations over time.
-Conversely, the weighted model shows a more pronounced trend, demonstrating a gradual increase in predicted support, suggesting a potential shift in voter sentiment towards Harris as the election date approaches.
-
-In contrast, Donald Trump's predicted support, represented by the red lines, exhibits a downward trend in both unweighted and weighted models.
-The unweighted model indicates that his support is expected to hover around 48%, while the weighted model predicts a slight decline to approximately 46%.
-This trend may reflect challenges in maintaining voter enthusiasm in the face of changing public sentiment.
-
-At the end of the polling period, we predict that Kamala Harris leads Donald Trump by 2% in the unweighted model (48% vs. 46%) and by about 2% in the weighted model (49.1% vs. 47.3%).
+
+The predicted support for Kamala Harris and Donald Trump in the upcoming 2024 U.S.
+presidential election is illustrated in Figure 1.
+This analysis spans the period from August 1, 2024, to October 27, 2024, and uses multiple linear regression models to project voter support.
+
+The un-weighted model predictions indicate that Kamala Harris maintains a consistent support level, with projections hovering around 49%.
+The blue dashed line represents this trend, showing only minor fluctuations throughout the polling period.
+Conversely, the weighted model for Harris, indicated by the solid blue line, suggests a slight upward trend in predicted support, reflecting a potential positive shift in voter sentiment as the election date approaches.
+
+In contrast, Donald Trump's predicted support is represented by the red lines.
+The unweighted model forecasts his support to remain around 48%, while the weighted model predicts a gradual decline to approximately 46%.
+The red dashed line indicates the unweighted prediction, whereas the solid red line shows the weighted prediction.
+This downward trajectory may indicate challenges for Trump in sustaining voter enthusiasm amid changing public opinions.
+
+At the conclusion of the polling period, the models suggest that Kamala Harris leads Donald Trump by approximately 4% in the un-weighted (50% vs. 46%) and 2.5% in weighted models (50% vs. 47.5%).
 
@@
 
-# Additional data details
+# Additional data details{#first-model-details}
 
@@
 #| echo: false
-#| eval: true
 #| message: false
@@
 #| label: fig-stanareyouokay
-#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\-Support for Harris"
+#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Harris"
 #| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]

### 2024-10-30 scripts/02-download_data.R
update script with environment

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from FiveThirtyeight.com
+# Purpose: Downloads and saves the data from FiveThirtyeight,com
 # Author: Diana Shen, Jinyan Wei, Huayan Yu
 # Date: 27 October 2024 
 # Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: no
-# Any other information needed? no
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
 
 
 #### Workspace setup ####

### 2024-10-30 scripts/05-model_data.R

@@ -9,6 +9,7 @@
 
 #### Load cleaned data ####
 library(dplyr)
+library(arrow)
 
 # Load Harris and Trump data
 harris_data <- read_parquet("data/02-analysis_data/analysis_data_Harris.parquet")
@@ -58,6 +59,7 @@ model_trump_unweighted <- lm(pct ~ national_poll + pollster + population, data =
 
 # 4. Weighted model for Trump
 model_trump_weighted <- lm(pct ~ national_poll + pollster + population, data = trump_data, weights = combined_weight)
+
 
 #### Save Models ####
 saveRDS(model_harris_unweighted, "models/model_harris_unweighted.rds")

### 2024-10-30 paper/paper.qmd
Update paper.qmd

--- 2024-10-30 paper/paper.qmd
@@
 ---
-title: "Based on polling as of 27 October 2024, Harris expects to win on xxx%, leads Trump by xx% in 2024 US election"
+title: "Based on polling as of 27 October 2024, Harris expects to win on 50%, leads Trump by about 3% in 2024 US election"
 subtitle: "Weighted Linear Regression Analysis of Aggregated Poll Data: Utilizing National Polls indicator, Population, and Pollster as Predictors."
@@
 results of these polls represent key measures of electoral support and
-voter sentiment, and are therefore the main variables in our analysis.
-
-To ensure that polling data accurately reflect real-world voter
+voter sentiment and are therefore the main variables in our analysis.
+
+To ensure that polling data accurately reflects real-world voter
 preferences, we rely on several key measurement constructs. First, voter
@@
 support for each candidate. Each poll is conducted using different
-sample sizes, sampling methods (e.g., online surveys, IVR calls, etc.),
+sample sizes, and sampling methods (e.g., online surveys, IVR calls, etc.),
 which can inject more variability into the data. To mitigate these
@@
 weights based on poll quality, sample size, and recency to better
-reflect voter sentiment [@nytimes].
+reflect voter sentiment [@nyt_polling_averages].
 
@@
 additional insights. However, we opted for the weighted linear
-regression approach to maintain interpretability and ease of
+a regression approach to maintain interpretability and ease of
 implementation given the scope and resources of this analysis. The
@@
 For example, in Arizona, Trump maintains a slight lead with support fluctuating around 50% in October, compared to Harris around 48%.
-In Georgia, Trump's support reaches just above 49% in late September, whereas Harris hovers closer to 47%.
+In Georgia, Trump's support reached just above 49% in late September, whereas Harris hovers closer to 47%.
 In Wisconsin, both candidates show tightly aligned trends near 48%, highlighting a close race.
@@
 This trend suggests a potential narrowing in support levels as the election approaches, providing a quantitative snapshot of national polling dynamics.
+
+## Recent 3 Months Support Trends Linear Model Prediction
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| include: false
+set.seed(233)
+new_data_harris <- data.frame(
+  end_date = seq(
+    min(harris_data$end_date),
+    max(harris_data$end_date),
+    length.out = 1000 
+  ),
+  national_poll = rep(c(0, 1), length(1000)),
+  pollster = factor(sample(levels(harris_data$pollster), size = 1000, replace = TRUE), 
+                    levels = levels(harris_data$pollster)),  
+  population = factor(sample(c("lv","rv"), size = 1000, replace = TRUE)),
+  sample_size = sample(1:2300, size = 1000, replace = TRUE),
+  pollster_quality= sample(2:4, size = 1000, replace = TRUE)
+)|>
+  mutate(
+    # Sample size weight (assuming a maximum of 2300 responses)
+    sample_size_weight = pmin(sample_size / 2300, 1),  # Set sample size; adjust accordingly
+
+    # Pollster quality weight (assuming you want to use a dummy numeric grade, e.g., 2)
+    pollster_quality_weight = pollster_quality / 4,
+
+    # Recency weight (this can be based on the date difference from a certain cutoff, e.g., "2024-11-05")
+    recency = as.numeric(difftime( as.Date("2024-11-05"),as.Date(end_date), units = "days")),  # Adjust for the sequence
+    recency_weight = exp(-recency * 0.1),  # Adjust decay rate as needed
+        recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1),
+    # Combine all weights into a final combined weight
+    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
+    candidate="Harris"
+  )
+new_data_trump <- data.frame(
+  end_date = seq(
+    min(trump_data$end_date),
+    max(trump_data$end_date),
+    length.out = 1000
+  ),
+  pollster = factor(sample(levels(trump_data$pollster), size = 1000, replace = TRUE), 
+                    levels = levels(trump_data$pollster)),  
+  population = factor(sample(c("lv","rv"), size = 1000, replace = TRUE)),
+   national_poll = rep(c(0, 1), length(1000)),  
+  sample_size =sample(1:2300, size = 1000, replace = TRUE),
+  pollster_quality= sample(2:4, size = 1000, replace = TRUE)
+)|>
+  mutate(
+    # Sample size weight (assuming a maximum of 2300 responses)
+    sample_size_weight = pmin(sample_size / 2300, 1),  # Set sample size; adjust accordingly
+
+    # Pollster quality weight (assuming you want to use a dummy numeric grade, e.g., 2)
+    pollster_quality_weight = pollster_quality / 4,
+
+    # Recency weight (this can be based on the date difference from a certain cutoff, e.g., "2024-11-05")
+    recency = as.numeric(difftime( as.Date("2024-11-05"),as.Date(end_date), units = "days")),  # Adjust for the sequence
+    recency_weight = exp(-recency * 0.1),  # Adjust decay rate as needed
+
+    # Poll frequency weight (you can set a condition based on a hypothetical recent poll count)
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1),
+
+    # Combine all weights into a final combined weight
+    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
+    candidate="Trump"
+  )
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| label: fig-support-predicted
+#| fig-cap: Predicted Support Trends for Kamala Harris and Donald Trump using Fitted Linear Model
+# Predictions for Harris
+new_data_harris <- new_data_harris |>
+  mutate(
+    predicted_unweighted = predict(harris_unweighted_model, newdata = new_data_harris),
+    predicted_weighted = predict(harris_weighted_model, newdata = new_data_harris)
+  )
+
+# Predictions for Trump
+new_data_trump <- new_data_trump |>
+  mutate(
+    predicted_unweighted = predict(trump_unweighted_model, newdata = new_data_trump),
+    predicted_weighted = predict(trump_weighted_model, newdata = new_data_trump)
+  )
+
+# Define the cutoff date for recent data
+recent_date_cutoff <- as.Date("2024-08-01")
+
+# Filter combined_predictions to include only data from the recent date cutoff onward
+combined_predictions<- bind_rows(new_data_harris, new_data_trump)
+combined_predictions_filtered<-combined_predictions|>filter(end_date>=recent_date_cutoff)
+# Determine the maximum end date for setting the x-axis limit
+max_end_date <- max(combined_predictions_filtered$end_date)
+
+# Plotting with the filtered data
+ggplot(combined_predictions_filtered, aes(x = end_date, color = candidate)) +
+  geom_smooth(aes(y = predicted_unweighted, linetype = "Unweighted"), 
+              method = "loess", se = TRUE, size = 1) +  # Unweighted model with smoothing
+  geom_smooth(aes(y = predicted_weighted, linetype = "Weighted"), 
+              method = "loess", se = TRUE, size = 1) +
+  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
+       subtitle = "predicted using multiple linear regression model ",
+       x = "End Date of the Poll",  # Change x-axis label to End Date
+       y = "Predicted Support (%)",
+       color = "Candidate",caption = 
+                   "Weights: recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight\nLinear Regression Model: candidate support percentage =national_poll + pollster + population") +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  scale_linetype_manual(name = "Linear Model Type", values = c("Unweighted" = "dashed", "Weighted" = "solid")) +
+  theme_minimal() +
+  theme(legend.position = "top",
+        axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
+
+```
+
+The predicted support for Kamala Harris and Donald Trump in the upcoming 2024 U.S.
+presidential election is illustrated in Figure 1.
+This analysis spans the period from August 1, 2024, to October 27, 2024, and uses multiple linear regression models to project voter support.
+
+The unweighted model predictions indicate that Kamala Harris maintains a consistent support level, with projections hovering around 49%.
+The blue dashed line represents this trend, showing only minor fluctuations throughout the polling period.
+Conversely, the weighted model for Harris, indicated by the solid blue line, suggests a slight upward trend in predicted support, reflecting a potential positive shift in voter sentiment as the election date approaches.
+
+In contrast, Donald Trump's predicted support is represented by the red lines.
+The unweighted model forecasts his support to remain around 48%, while the weighted model predicts a gradual decline to approximately 46%.
+The red dashed line indicates the unweighted prediction, whereas the solid red line shows the weighted prediction.
+This downward trajectory may indicate challenges for Trump in sustaining voter enthusiasm amid changing public opinions.
+
+At the conclusion of the polling period, the models suggest that Kamala Harris leads Donald Trump by approximately 4% in the un-weighted (50% vs. 46%) and 2.5% in weighted models (50% vs. 47.5%).
 

### 2024-10-30 paper/paper.qmd

@@
 library(tidyverse)
+library(arrow)
+library(dplyr)
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+harris_data <- read_parquet("~/2024 US Election Forecast/data/02-analysis_data/analysis_data_Harris.parquet")
+trump_data <- read_parquet("~/2024 US Election Forecast/data/02-analysis_data/analysis_data_Trump.parquet")
+
 ```
@@
 support for each candidate. Each poll is conducted using different
-sample sizes, and sampling methods (e.g., online surveys, IVR calls, etc.),
-which can inject more variability into the data. To mitigate these
-differences, we aggregate poll results using a “”poll of polls“”
+sample sizes, and sampling methods (e.g., online surveys, IVR calls,
+etc.), which can inject more variability into the data. To mitigate
+these differences, we aggregate poll results using a “”poll of polls“”
 methodology that eliminates anomalies and provides a more comprehensive
@@
 
-## Outcome variables
+## Outcome variables (Estimand)
 
@@
 
+The validation and diagnostic details of the model are provided in
+[Appendix B](#sec-model-details)
+
 ## Model Set-up
@@
 expression format:
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+harris_unweighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_harris_unweighted.rds")
+harris_weighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_harris_weighted.rds")
+trump_unweighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_trump_unweighted.rds")
+trump_weighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_trump_weighted.rds")
+
+```
 
@@
 ```{r}
-model_harris_weighted <- lm(pct ~ national_poll + pollster + population, data = harris_data, weights = combined_weight)
+#| include: false
+#| warning: false
+#| message: false
+#### Calculate Weights ####
+# Calculate weights for Harris data
+harris_data <- harris_data |>
+  mutate(
+    sample_size_weight = pmin(sample_size / 2300, 1),
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
+  ) |>
+  group_by(pollster) |>
+  mutate(
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
+  ) |>
+  ungroup() |>
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+
+# Calculate weights for Trump data
+trump_data <- trump_data |>
+  mutate(
+    sample_size_weight = pmin(sample_size / 2300, 1),
+    pollster_quality_weight = numeric_grade / 4,
+    recency_weight = exp(-recency * 0.1)
+  ) |>
+  group_by(pollster) |>
+  mutate(
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
+  ) |>
+  ungroup() |>
+  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
 ```
@@
 
-The weighted model is essential for accurately reflecting voter sentiment. 
-By incorporating weights, we adjust for the reliability of the polling data, 
-ensuring that more credible polls have a greater influence on the estimates.
+The weighted model is essential for accurately reflecting voter
+sentiment. By incorporating weights, we adjust for the reliability of
+the polling data, ensuring that more credible polls have a greater
+influence on the estimates.
 
@@
 squares, alternative methods such as Bayesian modeling could provide
-additional insights. However, we opted for the weighted linear
-a regression approach to maintain interpretability and ease of
+additional insights. However, we opted for the weighted linear a
+regression approach to maintain interpretability and ease of
 implementation given the scope and resources of this analysis. The
@@
 ```
-@fig-national-support-trendsillustrates illustrates the polling support trends for Kamala Harris and Donald Trump across the country from August to October.
+@fig-national-support-trends illustrates the polling support trends for Kamala Harris and Donald Trump across the country from August to October.
 The scatter points represent individual poll results, with blue for Harris and red for Trump, while each dot's size reflects the weight of the poll, accounting for factors like sample size, quality, and recency.
@@
 )|>
+  group_by(pollster)|>
+  mutate(recency = as.numeric(difftime( as.Date("2024-11-05"),as.Date(end_date), units = "days")),
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
+  ) |>ungroup()|>
   mutate(
@@
 
-    # Recency weight (this can be based on the date difference from a certain cutoff, e.g., "2024-11-05")
-    recency = as.numeric(difftime( as.Date("2024-11-05"),as.Date(end_date), units = "days")),  # Adjust for the sequence
     recency_weight = exp(-recency * 0.1),  # Adjust decay rate as needed
-        recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1),
     # Combine all weights into a final combined weight
@@
   )
+#######
 new_data_trump <- data.frame(
@@
 )|>
+  group_by(pollster)|>
+  mutate(recency = as.numeric(difftime( as.Date("2024-11-05"),as.Date(end_date), units = "days")),
+    recent_poll_count = sum(recency < 30),
+    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
+  ) |>
+  ungroup() |>
   mutate(
     # Sample size weight (assuming a maximum of 2300 responses)
-    sample_size_weight = pmin(sample_size / 2300, 1),  # Set sample size; adjust accordingly
-
-    # Pollster quality weight (assuming you want to use a dummy numeric grade, e.g., 2)
+    sample_size_weight = pmin(sample_size / 2300, 1), 
     pollster_quality_weight = pollster_quality / 4,  
-
-    # Recency weight (this can be based on the date difference from a certain cutoff, e.g., "2024-11-05")
-    recency = as.numeric(difftime( as.Date("2024-11-05"),as.Date(end_date), units = "days")),  # Adjust for the sequence
-    recency_weight = exp(-recency * 0.1),  # Adjust decay rate as needed
-
-    # Poll frequency weight (you can set a condition based on a hypothetical recent poll count)
-    recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1),
-
-    # Combine all weights into a final combined weight
+    recency_weight = exp(-recency * 0.1),  
     combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
@@
 
-The predicted support for Kamala Harris and Donald Trump in the upcoming 2024 U.S.
-presidential election is illustrated in Figure 1.
-This analysis spans the period from August 1, 2024, to October 27, 2024, and uses multiple linear regression models to project voter support.
-
-The unweighted model predictions indicate that Kamala Harris maintains a consistent support level, with projections hovering around 49%.
-The blue dashed line represents this trend, showing only minor fluctuations throughout the polling period.
-Conversely, the weighted model for Harris, indicated by the solid blue line, suggests a slight upward trend in predicted support, reflecting a potential positive shift in voter sentiment as the election date approaches.
-
-In contrast, Donald Trump's predicted support is represented by the red lines.
-The unweighted model forecasts his support to remain around 48%, while the weighted model predicts a gradual decline to approximately 46%.
-The red dashed line indicates the unweighted prediction, whereas the solid red line shows the weighted prediction.
-This downward trajectory may indicate challenges for Trump in sustaining voter enthusiasm amid changing public opinions.
-
-At the conclusion of the polling period, the models suggest that Kamala Harris leads Donald Trump by approximately 4% in the un-weighted (50% vs. 46%) and 2.5% in weighted models (50% vs. 47.5%).
+The predicted support for Kamala Harris and Donald Trump in the upcoming
+2024 U.S. presidential election is illustrated in Figure 1. This
+analysis spans the period from August 1, 2024, to October 27, 2024, and
+uses multiple linear regression models to project voter support.
+
+The unweighted model predictions indicate that Kamala Harris maintains a
+consistent support level, with projections hovering around 49%. The blue
+dashed line represents this trend, showing only minor fluctuations
+throughout the polling period. Conversely, the weighted model for
+Harris, indicated by the solid blue line, suggests a slight upward trend
+in predicted support, reflecting a potential positive shift in voter
+sentiment as the election date approaches.
+
+In contrast, Donald Trump's predicted support is represented by the red
+lines. The unweighted model forecasts his support to remain around 48%,
+while the weighted model predicts a gradual decline to approximately
+46%. The red dashed line indicates the unweighted prediction, whereas
+the solid red line shows the weighted prediction. This downward
+trajectory may indicate challenges for Trump in sustaining voter
+enthusiasm amid changing public opinions.
+
+At the conclusion of the polling period, the models suggest that Kamala
+Harris leads Donald Trump by approximately 4% in the un-weighted (50%
+vs. 46%) and 2.5% in weighted models (50% vs. 47.5%).
 
@@
 ## Key Findings and Real-World Implications {#sec-key-findings}
-Our model reveals a portrait of a nation deeply divided, with Harris holding a narrow 49% edge over Trump’s 47% in national support.
-However, as recent elections have shown, the national popular vote does not always translate into an Electoral College victory.
-The U.S.
-electoral system, which awards each state’s electoral votes to the candidate with the majority of votes in that state, means that winning the popular vote nationally might still leave Harris short of the presidency.
-This structural quirk played a defining role in the 2016 election, where Hillary Clinton’s popular vote win failed to deliver the electoral majority, paving Trump’s path to the White House.
-Our findings underscore this enduring tension: while Harris may have a slight national advantage, the true battle will be fought state by state, in a handful of battlegrounds that could flip the election either way.
-
-In states like Wisconsin and Arizona, our model highlights just how close the race remains.
-Wisconsin, for instance, shows both candidates locked in a near tie around 48% support—a statistical dead heat that brings the state’s significance into sharp relief.
-Arizona, meanwhile, leans modestly toward Trump, a reflection of the unique demographic and political nuances shaping each battleground.
-These state-level insights illuminate a critical truth: while national polls offer a snapshot of overall sentiment, they risk obscuring the specific, local dynamics that will ultimately decide the outcome.
-The stakes are high; these are the states that could swing, the margins that will be watched closely on election night, as even slight changes in turnout or last-minute shifts in opinion could tip the balance.
-
-Yet, as with all models, limitations persist.
-While our weighting system, with its emphasis on recent data, aims to capture a timely snapshot of voter sentiment, it may miss sudden changes sparked by campaign events or unexpected shifts in public discourse.
-The variability in our state projections—ranging from a low estimate of 363 electoral votes for Harris to a high of 471—reflects the inherent uncertainty in polling-based models, particularly given the constraints of our data sources.
-This wide range suggests that while data-driven insights can illuminate trends, they cannot fully account for the unpredictable nature of electoral outcomes.
-Moving forward, incorporating real-time sentiment from social media or demographic-specific insights could offer a more responsive understanding of voter behavior.
-Ultimately, these findings highlight the intricate dance between popular sentiment and the electoral mechanics of American democracy—a system where every vote counts, but some states matter just a bit more than others.
+
+Our model reveals a portrait of a nation deeply divided, with Harris
+holding a narrow 49% edge over Trump’s 47% in national support. However,
+as recent elections have shown, the national popular vote does not
+always translate into an Electoral College victory. The U.S. electoral
+system, which awards each state’s electoral votes to the candidate with
+the majority of votes in that state, means that winning the popular vote
+nationally might still leave Harris short of the presidency. This
+structural quirk played a defining role in the 2016 election, where
+Hillary Clinton’s popular vote win failed to deliver the electoral
+majority, paving Trump’s path to the White House. Our findings
+underscore this enduring tension: while Harris may have a slight
+national advantage, the true battle will be fought state by state, in a
+handful of battlegrounds that could flip the election either way.
+
+In states like Wisconsin and Arizona, our model highlights just how
+close the race remains. Wisconsin, for instance, shows both candidates
+locked in a near tie around 48% support—a statistical dead heat that
+brings the state’s significance into sharp relief. Arizona, meanwhile,
+leans modestly toward Trump, a reflection of the unique demographic and
+political nuances shaping each battleground. These state-level insights
+illuminate a critical truth: while national polls offer a snapshot of
+overall sentiment, they risk obscuring the specific, local dynamics that
+will ultimately decide the outcome. The stakes are high; these are the
+states that could swing, the margins that will be watched closely on
+election night, as even slight changes in turnout or last-minute shifts
+in opinion could tip the balance.
+
+Yet, as with all models, limitations persist. While our weighting
+system, with its emphasis on recent data, aims to capture a timely
+snapshot of voter sentiment, it may miss sudden changes sparked by
+campaign events or unexpected shifts in public discourse. The
+variability in our state projections—ranging from a low estimate of 363
+electoral votes for Harris to a high of 471—reflects the inherent
+uncertainty in polling-based models, particularly given the constraints
+of our data sources. This wide range suggests that while data-driven
+insights can illuminate trends, they cannot fully account for the
+unpredictable nature of electoral outcomes. Moving forward,
+incorporating real-time sentiment from social media or
+demographic-specific insights could offer a more responsive
+understanding of voter behavior. Ultimately, these findings highlight
+the intricate dance between popular sentiment and the electoral
+mechanics of American democracy—a system where every vote counts, but
+some states matter just a bit more than others.
 
@@
 
-# Additional data details
+# Additional data details {#first-model-details}
 
@@
 
-## Model validation
+## Model validation: K-Fold Cross-Validation
 
 ```{r}
-# Set seed for reproducibility
-set.seed(123)
-
-# Sample indices for training and testing sets
-train_index <- sample(seq_len(nrow(data)), size = 0.8 * nrow(data))
-
-# Split the data into training and testing sets
-train_data <- data[train_index, ]
-test_data <- data[-train_index, ]
-
-# Fit the weighted linear regression model
-first_model_test <- lm(pct ~ national_poll + pollster + population, 
-                     data = data, 
-                  data = train_data)
-
-# Predict on test data
-predictions <- predict(first_model_test, newdata = test_data)
-
-# Calculate RMSE using the correct outcome variable
-# Assuming 'pct' is the actual observed outcome variable in test_data
-rmse <- sqrt(mean((predictions - test_data$pct)^2, na.rm = TRUE))
-
-# Print RMSE
-print(paste("RMSE:", rmse))
+#| include: false
+#| message: false
+#| warning: false
+# Load necessary libraries
+library(boot)    # For bootstrapping
+library(caret)   # For cross-validation
+
+# Set up 10-fold cross-validation
+train_control <- trainControl(method = "cv", number = 10)
+# Train the model
+model_formula <- pct ~ national_poll + pollster + population
+model_harris_cv <- train(model_formula, data = harris_data, method = "lm", trControl = train_control)
+# Set up 10-fold cross-validation
+train_control <- trainControl(method = "cv", number = 10)
+# Train the model
+model_harris_cv <- train(model_formula, data = harris_data, method = "lm", trControl = train_control)
+# Print the model results
+
+model_trump_cv <- train(model_formula, data = trump_data, method = "lm", trControl = train_control)
+# Set up 10-fold cross-validation
+train_control <- trainControl(method = "cv", number = 10)
+# Train the model
+model_trump_cv <- train(model_formula, data = trump_data, method = "lm", trControl = train_control)
+# Print the model results
 
@@
 
+```{r}
+#| echo: false
+#| message: false
+#| warning: false
+# Extract RMSE, R-squared, and MAE for Harris model
+harris_rmse <- model_harris_cv$results$RMSE
+harris_r2 <- model_harris_cv$results$Rsquared
+harris_mae <- model_harris_cv$results$MAE
+
+# Print results for Harris model
+cat(sprintf("For the Harris model, the RMSE is %.2f, R-squared is %.2f, and MAE is %.2f.\n", 
+            harris_rmse, harris_r2, harris_mae))
+
+# Extract RMSE, R-squared, and MAE for Trump model
+trump_rmse <- model_trump_cv$results$RMSE
+trump_r2 <- model_trump_cv$results$Rsquared
+trump_mae <- model_trump_cv$results$MAE
+
+# Print results for Trump model
+cat(sprintf("For the Trump model, the RMSE is %.2f, R-squared is %.2f, and MAE is %.2f.\n", 
+            trump_rmse, trump_r2, trump_mae))
+
+```
+
+We use a 10-fold cross-validation on two linear regression models—one
+for Harris and one for Trump. The models use three predictors:
+national_poll, pollster, and population. The output provides key
+metrics, which breaks down here:
+
+RMSE (Root Mean Square Error): Measures the average magnitude of
+prediction errors (lower is better).
+
+Harris model: RMSE of 3.44, indicating an average prediction error of
+around 3.44 percentage points.\
+Trump model: RMSE of 4.40, showing a slightly higher prediction error on
+average.\
+
+R-squared: Represents the proportion of the variance in the response
+variable explained by the model (higher is better).\
+Harris model: R-squared of 0.34, meaning the model explains about 34.6%
+of the variance in Harris's polling data.\
+Trump model: R-squared of 0.34 as well, indicating similar explanatory
+power for Trump's polling data.
+
+MAE (Mean Absolute Error): Shows the average absolute difference between
+observed and predicted values (lower is better).\
+Harris model: MAE of 2.48, meaning that, on average, the predictions are
+off by 2.48 percentage points.\
+Trump model: MAE of 3.15, indicating slightly less precise predictions
+compared to the Harris model.\
+
+Interpretation Summary Predictive Accuracy: The Harris model has
+slightly better predictive accuracy than the Trump model, as reflected
+by its lower RMSE and MAE values.\
+Model Fit: Both models explain roughly 34% of the variance in their
+respective datasets. This suggests that other factors not included in
+the model may play a significant role in explaining the remaining
+variance.\
+This summary indicates the models are moderately predictive, with room
+for improvement in accuracy and fit, potentially by adding more
+predictors or adjusting model specifications.\
+
 ## Diagnostics
-
-@fig-stanareyouokay-1 is a residual plot of un-weighted model. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot. It shows... This suggests...
 
@@
 #| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Harris"
+#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
 #| layout-ncol: 2
-#residual plot
-plot(first_model, which = 1,main ="Residual Plot of unweighted linear regression model residualsmodel" )
-# Q-Q plot for the residuals of the model
-qqnorm(residuals(first_model),main= "Q-Q Plot of unweighted linear regression model residuals
-")
-qqline(residuals(first_model), col = "red")
+
+# Residual plot for unweighted model
+plot(harris_unweighted_model, which = 1, main = "Residual Plot of Unweighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the unweighted model
+qqnorm(residuals(harris_unweighted_model), main = "Q-Q Plot of Unweighted Linear Regression Model Residuals")
+qqline(residuals(harris_unweighted_model), col = "red")
+
+# Residual plot for weighted model
+plot(harris_weighted_model, which = 1, main = "Residual Plot of Weighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the weighted model
+qqnorm(residuals(harris_weighted_model), main = "Q-Q Plot of Weighted Linear Regression Model Residuals")
+qqline(residuals(harris_weighted_model), col = "red")
 
 ```
+
+Generally, we use Residual vs Fitted plot and Q-Q Plot diagnostic our
+model. Residual vs Fitted plot aare Residuals (differences between
+observed and predicted values) plotted against fitted values. Ideally,
+these residuals should be randomly scattered around the zero line to
+indicate that the model does not have systematic errors. The Q-Q plot
+for the unweighted model shows how the residuals align with a
+theoretical normal distribution. Ideally, residuals should follow a
+straight line in this plot if they are normally distributed, which is an
+assumption of linear regression.
+
+@fig-stanareyouokay-1 is a residual plot of un-weighted model for Harris
+support. It showsthe residuals are generally spread around zero, with no
+clear pattern. This suggests the model is relatively well-specified.
+However, there is a slight curvature, indicating potential non-linearity
+that the model may not fully capture. A few notable outliers with larger
+residuals might be influencing the model, indicating that some data
+points have more significant prediction errors.
+
+@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot for Harris
+support. It shows most residuals fall along the line, especially in the
+middle range. This suggests that our model satisfy the normality
+assumption. However, some points at the tails deviate, indicating
+potential outliers or non-normality in the extreme residual values. This
+slight deviation at the ends suggests the model might have some issues
+with extreme predictions but performs reasonably well overall.
+
+@fig-stanareyouokay-3 is a residual plot of weighted model for Harris
+support.It shows residuals are again plotted against fitted values.
+Similar to the unweighted model, the residuals are mostly centered
+around zero, indicating that the weighted model captures the general
+trend without significant systematic bias. The curvature is slightly
+reduced compared to the un-weighted model, suggesting that weighting has
+helped in addressing some of the non-linearity observed in the
+un-weighted model. However, some residuals are still notably large,
+which may indicate outliers that influence the model despite the
+weighting scheme. This suggests that while the weighted model performs
+better in terms of capturing non-linearity, further refinement might
+still be beneficial.
+
+@fig-stanareyouokay-4 is a Q-Q Plot of weighted model plot for Harris
+support.The residuals generally align with the theoretical normal
+distribution line, particularly in the central range, indicating that
+the residuals of the weighted model are close to normal. Similar to the
+unweighted model, there are deviations at the tails, though they appear
+less pronounced. This suggests that the weighting scheme has slightly
+improved the distribution of residuals, making the model’s predictions
+more robust. However, some extreme values remain, which could still
+affect model
+
+In summary, both models show a reasonably good fit, with the weighted
+model offering slight improvements in handling non-linearity and extreme
+values. However, both models exhibit minor deviations from normality and
+a few notable outliers, which may warrant further model adjustments for
+improved prediction accuracy.
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-dia
+#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Trump"
+#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
+#| layout-ncol: 2
+
+# Residual plot for unweighted model
+plot(trump_unweighted_model, which = 1, main = "Residual Plot of Unweighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the unweighted model
+qqnorm(residuals(trump_unweighted_model), main = "Q-Q Plot of Unweighted Linear Regression Model Residuals")
+qqline(residuals(trump_unweighted_model), col = "red")
+
+# Residual plot for weighted model
+plot(trump_weighted_model, which = 1, main = "Residual Plot of Weighted Linear Regression Model")
+
+# Q-Q plot for the residuals of the weighted model
+qqnorm(residuals(trump_weighted_model), main = "Q-Q Plot of Weighted Linear Regression Model Residuals")
+qqline(residuals(trump_weighted_model), col = "red")
+
+```
+
+@fig-dia-1 shows the residuals plotted against the fitted values for the
+unweighted model. It shows that the residuals are generally spread
+around zero with no clear pattern, suggesting that the model is
+relatively well-specified. However, there is a slight curvature,
+indicating possible non-linearity that the model may not fully capture.
+Some notable outliers with larger residuals suggest that certain data
+points have significant prediction errors, potentially influencing the
+model.
+
+@fig-dia-2 shows the Q-Q plot for the unweighted model, showing that
+most residuals fall along the line, especially in the middle range,
+suggesting that the model satisfies the normality assumption. However,
+some points at the tails deviate, indicating potential outliers or
+non-normality in extreme residual values. This deviation at the ends
+suggests the model may face issues with extreme predictions, though it
+performs reasonably well overall.
+
+@fig-dia-3 shows residuals plotted against fitted values. Similar to the
+unweighted model, the residuals are centered around zero, indicating
+that the weighted model captures the overall trend without significant
+systematic bias. The slight curvature seen in the unweighted model is
+reduced here, suggesting that weighting has addressed some of the
+non-linearity. However, some large residuals remain, which could
+indicate outliers that affect the model even with the weighting scheme.
+This suggests that while the weighted model has improved in handling
+non-linearity, further refinements could enhance accuracy.
+
+@fig-dia-4 shows the Q-Q plot for the weighted model compares residuals
+with a theoretical normal distribution. Here, the residuals generally
+align with the theoretical line, especially in the central range,
+indicating that the residuals of the weighted model are close to normal.
+Similar to the unweighted model, some deviations occur at the tails,
+though they appear less pronounced, suggesting that the weighting scheme
+has slightly improved the normality of residuals. Nonetheless, some
+extreme values persist, which may impact model robustness in cases of
+outliers.
+
+Summary Both models exhibit a reasonably good fit, with the weighted
+model offering slight improvements in managing non-linearity and extreme
+values. Despite this, both models show minor deviations from normality
+and some notable outliers, suggesting that further model adjustments may
+be beneficial for improved prediction accuracy.
 
@@
 Target population : The collection of all items about which we would
-like to speak. / The entire group about which we want to draw
+like to speak/ the entire group about which we want to draw.
 conclusions\

### 2024-10-31 paper/paper.qmd
update data cleaning

@@
 
-In this data-cleaning process, we focus on refining raw polling data to
-enhance its quality and relevance for subsequent analysis. The dataset
-is initially loaded and cleaned using the janitor package to standardize
-column names, ensuring consistency throughout. We then filter the data
-to retain only relevant columns and eliminate any rows with missing
-values in critical fields, including numeric_grade, pct, sample_size,
-and end_date.
-
-Specifically, we isolate the polling data for Kamala Harris and Donald
-Trump, applying a condition to include only high-quality polls with a
-numeric grade of 2 or higher, given that the mean of the numeric grade
-is 2.175 and the median is 1.9.
-
-For state-level polls, we handle any placeholder states marked as "--"
-by converting them to NA. A national poll indicator is generated,
-assigning a value of 1 for national polls and 0 for state-specific ones.
-Dates are standardized using the lubridate package to ensure accurate
-handling in subsequent analyses.
-
-Recency weights are calculated based on the number of days elapsed since
-the poll ended, utilizing an exponential decay function to give greater
-weight to more recent polls.
-
-Finally, the cleaned datasets for both candidates are saved in CSV
-format for further modeling and analysis. This systematic approach
-guarantees that the data is accurate, complete, and ready for insightful
-analysis.
+In this data-cleaning process, we focus on refining raw polling data for Kamala Harris and Donald Trump to enhance its quality and relevance for analysis.
+The process begins by loading the dataset and using the janitor package to standardize column names, ensuring consistent naming conventions throughout.
+We then filter the data to retain only essential columns and remove rows with missing values in key fields, including numeric_grade, pct, sample_size, and end_date.
+
+For each candidate, we isolate polls specifically for Kamala Harris and Donald Trump, retaining only high-quality polls with a numeric_grade of 2 or higher—given that the average numeric_grade is approximately 2.175, with a median of 1.9.
+We also handle placeholder values in state information by setting entries marked as "--" to NA, and create a national_poll indicator, assigning a value of 1 for national polls and 0 for state-specific ones.
+Dates are standardized using the lubridate package to facilitate accurate time-based analysis.
+
+Recency weights are calculated based on the days elapsed since the poll's end date, applying an exponential decay function to prioritize more recent polls.
+Weights based on sample size are capped at a maximum of 2,300 responses to maintain balanced representation.
+Additionally, categorical variables, including pollster, state, candidate_name, population, and methodology, are converted to factors to prepare for analysis.
+
+The cleaned datasets for both candidates are then saved as Parquet files for efficient storage and access in further modeling and analysis.
+This structured approach ensures that the data is accurate, complete, and optimized for insightful statistical analysis.
 

### 2024-10-31 paper/paper.qmd
update paper

@@
 
-## Recent 3 Months Support Trends Prediction
+## Recent Three Months Support Trends Prediction
 
@@
   geom_smooth(aes(group = candidate), method = "loess", span = 0.2, se = FALSE, size = 1) + # Smoothed trend line
-  facet_wrap(~ state) +
+  facet_wrap(~ state,ncol = 2,scales = "free_y") +
   labs(title = "Recent Support Trends for Kamala Harris and Donald Trump Across Selected States",
        x = "Date", y = "Support (%)") +
-  scale_x_date(date_labels = "%b", date_breaks = "1 month", limits = as.Date(c("2024-08-01", "2024-10-31"))) +
+  scale_x_date(date_labels = "%b", date_breaks = "1 month", limits = as.Date(c("2024-08-01", "2024-10-25"))) +
   scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
@@
 #| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States
-
 # Combine datasets for plotting with a new column for candidate
@@
   ) +
-  guides(color = guide_legend(title = "Candidate"))
+  guides(color = guide_legend(title = "Candidate")) +  # Vertical line at October 25
+  annotate("text", x = as.Date("2024-10-19"), y = Inf, label = "October 25th", vjust = 1, color = "black", size = 3.5) +
+  geom_vline(xintercept = as.Date("2024-10-25"), linetype = "solid", color = "black", size = 0.8)   # Vertical line at October 25
 
@@
 
-## Recent 3 Months Support Trends Linear Model Prediction
+## Recent Three Months Support Trends Linear Model Prediction
 
@@
 # Determine the maximum end date for setting the x-axis limit
-max_end_date <- max(combined_predictions_filtered$end_date)
+max_end_date <- as.Date("2024-10-30")
 
@@
         axis.text.x = element_text(angle = 45, hjust = 1)) +
-  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
-
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))  +
+  geom_vline(xintercept = as.Date("2024-10-25"), linetype = "solid", color = "black", size = 0.8) +  # Vertical line at October 25
+  annotate("text", x = as.Date("2024-10-19"), y = Inf, label = "October 25th", vjust = 1, color = "black", size = 3.5)+  # Vertical line at October 25
+  geom_text(aes(x = as.Date("2024-10-25"), y = 50, label = "49%"), color = "blue", hjust = -0.1, size = 3) +  # Harris label
+  geom_text(aes(x = as.Date("2024-10-25"), y = 48, label = "48%"),color = "red", hjust = -0.1, size = 3)+  # Harris label
+  geom_text(aes(x = as.Date("2024-10-25"), y = 46.5, label = "46.5%"), color = "red",hjust = -0.1, size = 3)  # Trump label
 ```
@@
 At the conclusion of the polling period, the models suggest that Kamala
-Harris leads Donald Trump by approximately 4% in the un-weighted (50%
-vs. 46%) and 2.5% in weighted models (50% vs. 47.5%).
+Harris leads Donald Trump by approximately 2.5% in the un-weighted (49%
+vs. 46.5%) and 1% in weighted models (49% vs. 48%). Average leading by about 2%.
 

### 2024-10-31 scripts/03-clean_data.R
update data by changeing clean_data script

@@ -33,7 +33,7 @@ just_harris_high_quality <- cleaned_data |>
     numeric_grade >= 2 # mean of numeric_gradeis 2.175, median is 1.9 
   ) |>
   mutate(
-    state = if_else(state == "--", NA_character_, state),
+    state = if_else(is.na(state) | state == "--", "National", state),
     national_poll = if_else(is.na(state), 1, 0)  # 1 for national, 0 for state-specific
   ) |> mutate(
     start_date = mdy(start_date),
@@ -68,7 +68,7 @@ just_trump_high_quality <- cleaned_data|>
     numeric_grade >= 2 # mean of numeric_gradeis 2.175, median is 1.9 
   ) |>
   mutate(
-    state = if_else(state == "--", NA_character_, state),
+    state = if_else(is.na(state) | state == "--", "National", state),
     national_poll = if_else(is.na(state), 1, 0)  # 1 for national, 0 for state-specific
   ) |> mutate(
     start_date = mdy(start_date),
@@ -89,6 +89,7 @@ just_trump_high_quality <- just_trump_high_quality %>%
     population = factor(population),  # Only if appropriate
     methodology = factor(methodology)
   )
+high_quality_combined<-bind_rows(just_harris_high_quality,just_trump_high_quality)
 #### Save data ####
 write_parquet(just_harris_high_quality, "data/02-analysis_data/analysis_data_Harris.parquet")
 write_parquet(just_trump_high_quality, "data/02-analysis_data/analysis_data_Trump.parquet")

### 2024-10-31 paper/paper.qmd
update paper with introduction and data, still working on abstract, discussion and some part of data

@@
 ---
-title: "Based on polling as of 27 October 2024, Harris expects to win on 50%, leads Trump by about 3% in 2024 US election"
+title: "Based on polling as of 27 October 2024, Harris expects to win on 49%, leads Trump by about 2% in 2024 US election"
 subtitle: "Weighted Linear Regression Analysis of Aggregated Poll Data: Utilizing National Polls indicator, Population, and Pollster as Predictors."
@@
 trump_data <- read_parquet("~/2024 US Election Forecast/data/02-analysis_data/analysis_data_Trump.parquet")
-
 ```
@@
 
-Election forecasting has long played a crucial role in understanding
-public opinion and predicting the outcome of political contests. The use
-of data-driven methods, particularly polling data, has become an
-important pre-election analytical tool for political analysts. The
-purpose of this paper is to predict the winner of the upcoming 2024 U.S.
-presidential election by constructing a statistical model based on
-aggregated polling data. The “polling” approach combines results from
-different pollsters to provide a more comprehensive picture of voter
-preferences (Blumenthal 2014; Pasek 2015), and our goal is to predict
-the outcome of the popular vote and the Electoral College. Our analysis,
-based on data collected from multiple polling sources, captures voter
-intentions for the two major candidates, Kamala Harris (Democrat) and
-Donald Trump (Republican).
-
-In addition to constructing and interpreting predictive models, this
-paper dive into the methods used by xx pollsters, analyzing the
-strengths as well as the weaknesses of the methods used against them. At
-the end of the paper, we also propose an idealized survey methodology
-for election forecasting with a budget of \$100,000 USD.
-
-This paper begins with an introduction to data in Section 2. In this
-section, we focus on measurement techniques and the visualization and
-analysis of key variables. Next, in Section 3, we provide an overview of
-the linear model used to analyze the relationships within the dataset.
-The results of the analysis are detailed in Section 4 (Results).
-Finally, in Section 5, we summarize our main conclusions as well as
-suggest some possible future research directions.
-
-# Data {#sec-data}
+Understanding voter sentiment is essential for both political campaigns and analysts, especially with the upcoming U.S.
+election on the horizon.
+Public opinion is highly dynamic and can change swiftly due to various influences, including media coverage, campaign tactics, and major events.
+This study aims to forecast the percentage of support for Kamala Harris, offering insights into the elements that shape voter preferences as the election nears.
+By examining data from multiple polling sources, we intend to pinpoint the key factors influencing support, such as the poll's end date, the polling organization, geographic location, and the poll's score.
+Our research seeks to fill a gap in existing literature that often fails to address the complexities of polling data, thereby enhancing our understanding of voter behavior within the electoral context.
+
+The main focus of our analysis is the percentage of support for Harris, which we will model using various predictor variables.
+We are particularly interested in how the end date, polling organization, state, and poll score affect voter support.
+Using a linear regression framework, we can quantify the relationships between these predictors and the support outcome, providing clarity on how each factor influences overall support for Harris.
+By estimating the coefficients for each predictor, we aim to draw significant conclusions about their respective impacts on voter sentiment.
+
+Our findings reveal a notable positive correlation between the end date and the percentage of support, indicating that as the election approaches, voter support tends to increase.
+We also observed considerable variability in support levels based on the polling organization and state, with certain pollsters consistently reporting higher support for Harris.
+The quality of the polls significantly affected results, with more reputable polls correlating with higher levels of support.
+These insights emphasize the necessity of considering both the timing of polls and the characteristics of different polling firms when analyzing public opinion.
+
+This research is important because precise predictions of voter support are crucial for effective campaign strategies.
+By identifying the main factors influencing support for Harris, campaign teams can customize their outreach and messaging to resonate better with voters.
+Furthermore, recognizing the differences across various polling organizations and states can assist in resource allocation and strategic focus during the campaign.
+Given that elections can be decided by narrow margins, having trustworthy insights into voter preferences can substantially influence the final outcomes.
+
+The structure of this paper is organized as follows: @sec-data provides details on the data sources and variables used in our analysis.
+@sec-model explains the modeling approach, including the assumptions and specifications of our linear regression framework.
+In @sec-results, we present our findings, emphasizing the key predictors of Harris's support.
+Finally, @sec-discussion explores the implications of our results and suggests potential directions for future research.
+# Estimand
+
+The estimand of our analysis is the true percentage of voter support for Kamala Harris in the upcoming U.S. presidential election.
+
+# Data {#third-data}
 
@@
 
-The data for this paper was sourced from ABC News (xxxxx). The
-statistical software R (R Core Team, 2023) was employed to retrieve,
-clean, and process the dataset. Specifically, the tidyverse package
-(Wickham et al., 2019) was used for data acquisition, cleaning, and
-processing. The ggplot2 (Wickham, 2016) package was utilized to generate
-the visualizations.
+We conduct our polling data analysis using the R programming language [@citeR].
+Our dataset, obtained from FiveThirtyEight [@fivethirtyeight2024], provides a detailed overview of public opinion in the lead-up to the election.
+Adhering to the guidelines presented in @tellingstories, we explore various factors that influence voter support percentages, including the timing of the polls, the traits of polling organizations, and regional differences.
+
+In this study, we utilized several R packages to enhance our data manipulation, modeling, and visualization capabilities.
+The tidyverse package offered a comprehensive set of tools for data wrangling and analysis, improving workflow efficiency (@thereferencecanbewhatever).
+The here package aided in managing file paths, allowing for easy access to our data files (@citehere).
+We relied on janitor to perform data cleaning, as it provides functionalities to identify and rectify quality issues within the dataset (@citejanitor).
+For handling date-related operations, the lubridate package proved invaluable, simplifying the manipulation of time variables (@citelubridate).
+Lastly, arrow supported efficient data input and output in a performance-oriented format, essential for managing larger datasets (@citearrow).
+Our coding practices and file organization were informed by the structure outlined in @tellingstories.
 
@@
 
-The data used to predict the outcome of the 2024 U.S. presidential
-election in this study came from a variety of polling sources. The
-results of these polls represent key measures of electoral support and
-voter sentiment and are therefore the main variables in our analysis.
-
-To ensure that polling data accurately reflects real-world voter
-preferences, we rely on several key measurement constructs. First, voter
-preferences are measured by the percentage of respondents who indicated
-support for each candidate. Each poll is conducted using different
-sample sizes, and sampling methods (e.g., online surveys, IVR calls,
-etc.), which can inject more variability into the data. To mitigate
-these differences, we aggregate poll results using a “”poll of polls“”
-methodology that eliminates anomalies and provides a more comprehensive
-picture of voter preferences (Blumenthal 2014; Pasek 2015).
-
-In this study, we recognize the measurement problems inherent in polling
-data. Polls rely on sample data to represent the entire voting
-population, and therefore, there may be potential biases in the data.
-For example, there may be no-response bias due to the potential under
-representation of certain populations, or because of the wording of the
-questions and thus the influence of respondents to report their
-preferences. Therefore, in this study, we chose to analyze aggregated
-data from multiple pollsters and adjust for sampling variability and
-response rates in an effort to be able to provide a more robust measure
-of electoral support. We believe that our aggregated dataset can serve
-as a reliable basis for our predictive model to help us translate the
-data into quantitative metrics that can be used to predict election
-outcomes.
-
-## Outcome variables (Estimand)
+The process of translating real-world events into our dataset requires a systematic approach to measurement and data gathering.
+In this research, we aim to assess public opinion regarding Kamala Harris as the upcoming U.S.
+presidential election approaches.
+Polling agencies formulate surveys featuring specific questions designed to capture voters' attitudes, including their likelihood of supporting Harris and their views on prevailing political issues.
+
+Once the survey items are established, a representative sample is selected through stratified random sampling methods, ensuring a diverse demographic representation.
+Respondents are reached using various techniques, such as telephone interviews and online questionnaires.
+
+After gathering the responses, the data is subjected to thorough cleaning and validation procedures to rectify inconsistencies and handle any missing information.
+This step is crucial for ensuring that the dataset accurately mirrors the electorate's sentiments.
+Each entry in the finalized dataset reflects an individual's viewpoint at a given moment, enabling a detailed analysis of the factors that shape public opinion as the election nears.
+This structured methodology effectively converts subjective opinions into measurable data, providing valuable insights into voter behavior and preferences.
+
+## Outcome variable
+
+### The support percentage of Kamala Harris.
+
+@fig-percentage illustrates the distribution of percentage support for Kamala Harris based on polling data, where support reflects the proportion of respondents favoring Harris in each survey.
+Most polls report support clustered around 50%, with the majority of values falling between 40% and 55%.
+This central peak suggests moderate, consistent support levels among respondents, with fewer instances of higher support levels above 55%.
+The right-skew in the distribution indicates occasional polls with elevated support, though these are less common.
+Overall, this visualization highlights the general sentiment and variability in support for Harris as captured across multiple polls.
+
+```{r}
+#| label: fig-percentage
+#| fig-cap: Distribution of support percentage of Kamala Harris
+#| echo: false
+#| warning: false
+#| message: false
+ggplot(harris_data, aes(x = pct)) +
+  geom_histogram(binwidth = 1, fill = "gold", color = "grey50") +
+  labs(
+    x = "Support Percentage",
+    y = "Count"
+  ) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5))
+```
 
 ## Predictor variables
+
+### End Date
+
+The end date is the final day of data collection for a poll, indicating when the survey period concluded.
+This date provides crucial context for the poll results, as public opinion may change over time in response to events, campaign actions, or other influencing factors.
+
+### State
+
+@fig-state displays the distribution of polls by state, showing how frequently polling organizations conducted surveys across various U.S.
+states and at the national level.
+The "National" category has the highest number of polls, indicating a strong emphasis on capturing overall U.S.
+sentiment.
+Certain states, such as Pennsylvania, Wisconsin, North Carolina, Arizona, Georgia, and Michigan, also show higher polling frequencies, likely because these are battleground states with the potential to influence the election outcome significantly.
+Toward the right side of the chart, states with minimal polling activity, including South Carolina, Iowa, and Washington, appear less frequently, possibly due to their historically predictable or less competitive nature.
+This distribution reflects the strategic focus of polling efforts, with organizations prioritizing both national sentiment and swing states where public opinion is more volatile.
+Overall, the chart provides insight into where polling resources are allocated as election day nears, emphasizing areas that could sway the final result.
+
+```{r}
+#| label: fig-state
+#| fig-cap: Count of polls by state
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(harris_data, aes(x = fct_infreq(state))) +
+  geom_bar(fill = "gold", color = "black") +
+  labs(
+    x = "State",
+    y = "Number of Polls"
+  ) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+### Pollster
+
+@fig-pollster displays the frequency of polls conducted by different pollsters.
+Each bar represents a pollster, with the height indicating the number of polls they conducted.
+Siena/NYT has the highest count, followed by YouGov and Emerson.
+Pollsters to the right have conducted significantly fewer polls, with some showing only one or two entries.
+
+The pollster is the organization or firm that conducts the surveys, gathering and analyzing public opinion data on voter preferences.
+In this context, each pollster's count reflects its level of polling activity related to the election.
+
+```{r}
+#| label: fig-pollster
+#| fig-cap: Frequency of Polls by Pollster"
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(harris_data, aes(x = fct_infreq(pollster))) +
+  geom_bar(fill = "gold", color = "grey30") +
+  labs(
+    x = "Pollster",
+    y = "Poll Count"
+  ) +
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 6))
+```
+
+### Numeric Grade
+
+@fig-numericgrade displays the distribution of numeric grades assigned to various pollsters, with the x-axis representing the numeric grade values and the y-axis indicating the frequency of each grade.
+The numeric grade is a metric that evaluates the quality or reliability of a pollster, taking into account factors such as methodology, historical accuracy, sample size, and pollster reputation.
+In this chart, we observe that the most common numeric grades are concentrated around 2.75 and 3.00, with a large spike at these values, suggesting that a significant number of polls are conducted by highly-rated pollsters.
+Fewer polls have grades below 2.5, indicating a relatively lower occurrence of polls from less-reliable pollsters in this dataset.
+This distribution underscores the emphasis on high-quality pollsters within the dataset, ensuring a more reliable and consistent source of polling data for subsequent analysis.
+
+```{r}
+#| label: fig-numericgrade
+#| fig-cap: Distribution of numeric grade
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(harris_data, aes(x = numeric_grade)) +
+  geom_histogram(binwidth = 0.05, fill = "gold", color = "grey30") +
+  labs(
+    x = "Numeric Grade",
+    y = "Frequency"
+  ) +
+  theme_minimal()
+```
+
+## Relationships between key varaibles
+
+@fig-pollstertime shows the trend of percentage support for Kamala Harris over time, with data points and smoothed trend lines for each pollster.
+The x-axis represents the dates from August through October, while the y-axis indicates the percentage of respondents supporting Harris.
+Each color corresponds to a specific polling organization, with prominent pollsters such as Beacon/Shaw, Ipsos, Siena/NYT, Emerson, Quinnipiac, and YouGov.
+The smoothed lines reveal subtle trends over time, with some pollsters like Emerson and Beacon/Shaw showing a slight upward trend, while others like Siena/NYT display a downward trend.
+@fig-pollstertime highlights the variability in poll results across different organizations, reflecting each pollster's methodology and sample.
+
+```{r}
+#| label: fig-pollstertime
+#| fig-cap: Harris Support Over Time by Pollster (Top 6 Pollsters)
+#| echo: false
+#| warning: false
+#| message: false
+
+top_pollsters <- harris_data %>%
+  count(pollster, sort = TRUE) %>%
+  top_n(6, n) %>%
+  pull(pollster)
+
+filtered_data <- harris_data %>%
+  filter(pollster %in% top_pollsters)
+
+ggplot(filtered_data, aes(x = end_date, y = pct, color = pollster)) +
+  geom_point(alpha = 0.7) +
+  geom_smooth(se = FALSE)+
+  scale_color_viridis_d() +
+  labs(y = "Harris Support Percent", x = "Date") +
+  theme_classic() +
+  theme(legend.position = "bottom", legend.title = element_blank())
+```
+
+@fig-numericgradetime illustrates Harris's support percentages over time, with each data point representing poll results colored by the numeric grade of the pollster.
+The smoothing lines for each numeric grade remain subtle, indicating minor variations in support trends over time across different pollster quality levels.
+Most points are clustered around the 50% support level, suggesting a generally stable voter sentiment for Harris, with only slight fluctuations across numeric grades.
+By limiting the y-axis, outliers and extreme variations are minimized, resulting in a clearer and more interpretable visualization.
+This approach emphasizes the central trend, allowing for clearer comparisons of support levels across pollsters of varying reliability without distraction from extreme values.
+
+```{r}
+#| label: fig-numericgradetime
+#| fig-cap: Harris Support Over Time by Numeric Grade
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(harris_data %>% filter(pct <= 100), aes(x = end_date, y = pct, color = factor(numeric_grade))) +
+  geom_point(alpha = 0.7) +
+  geom_smooth(se = FALSE, span = 0.3) +
+  labs(y = "Harris Percent", x = "Date", color = "Numeric Grade") +
+  scale_color_viridis_d() +
+  theme_classic() +
+  theme(legend.position = "bottom") +
+  coord_cartesian(ylim = c(0, 100))
+```
 

### 2024-10-31 paper/paper.qmd
update paper on data end date

@@
 We conduct our polling data analysis using the R programming language [@citeR].
-Our dataset, obtained from FiveThirtyEight [@fivethirtyeight2024], provides a detailed overview of public opinion in the lead-up to the election.
+Our dataset, obtained from FiveThirtyEight [@fivethirtyeight2024],based on polling as of 27 October 2024, provides a detailed overview of public opinion in the lead-up to the election.
 Adhering to the guidelines presented in @tellingstories, we explore various factors that influence voter support percentages, including the timing of the polls, the traits of polling organizations, and regional differences.

### 2024-11-01 scripts/02-download_data.R
update model

@@ -22,8 +22,6 @@ raw_elections_data <- read_csv(
 #### Save data ####
 write_csv(
   x = raw_elections_data,
-  file = "~/2024 US Election Forecast/data/01-raw_data/raw_election_24.csv"
+  file = "data/01-raw_data/raw_election_24.csv"
 )
 
-head(raw_elections_data)
-raw_elections_data<-read.csv("~/2024 US Election Forecast/data/01-raw_data/raw_election_24.csv")

### 2024-11-01 scripts/03-clean_data.R

@@ -17,7 +17,6 @@ raw_data <- read_csv("data/01-raw_data/raw_election_24.csv")
 
 cleaned_data <- raw_data |>
   clean_names()
-summary(cleaned_data)##check summary statistics of raw cleaned data
 
 # Filter data to Harris estimates based on high-quality polls after she declared
 just_harris_high_quality <- cleaned_data |>
@@ -25,12 +24,12 @@ just_harris_high_quality <- cleaned_data |>
   select(
     pollster, numeric_grade, state, candidate_name, pct, sample_size, 
     population, methodology, start_date, end_date
-  )|>
+  )|>filter(population %in% c("lv", "rv"))|>
   # Drop rows with missing values in essential columns
   drop_na(numeric_grade, pct, sample_size, end_date)|>
   filter(
     candidate_name == "Kamala Harris",
-    numeric_grade >= 2 # mean of numeric_gradeis 2.175, median is 1.9 
+    numeric_grade >= 2 # mean of numeric_grade is 2.175, median is 1.9 
   ) |>
   mutate(
     state = if_else(is.na(state) | state == "--", "National", state),
@@ -39,14 +38,9 @@ just_harris_high_quality <- cleaned_data |>
     start_date = mdy(start_date),
     end_date = mdy(end_date)
   )|>
-  # Calculate recency weight using exponential decay (more recent polls get higher weight)
   mutate(
-    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
-    recency_weight = exp(-recency*0.1)  # Adjust decay rate as needed
+    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days"))
   ) |>
-  # Apply sample size weight, capped at a maximum of 2,300 responses
-  mutate(sample_size_weight = pmin(sample_size / 2300, 1))
-just_harris_high_quality <- just_harris_high_quality %>%
   mutate(
     pollster = factor(pollster),
     state = factor(state),

### 2024-11-01 paper/paper.qmd
update paper

@@
 ---
-title: "Based on polling as of 27 October 2024, Harris expects to win on 49%, leads Trump by about 2% in 2024 US election"
-subtitle: "Weighted Linear Regression Analysis of Aggregated Poll Data: Utilizing National Polls indicator, Population, and Pollster as Predictors."
+title: "Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach"
+subtitle: "Harris expects to win on 49%, leads Trump by about 2% in 2024 US election"
 author: 
@@
 #| message: false
-harris_data <- read_parquet("~/2024 US Election Forecast/data/02-analysis_data/analysis_data_Harris.parquet")
-trump_data <- read_parquet("~/2024 US Election Forecast/data/02-analysis_data/analysis_data_Trump.parquet")
+harris_data <- read_parquet(here::here("data", "02-analysis_data", "analysis_data_Harris.parquet"))
+trump_data <- read_parquet(here::here("data", "02-analysis_data", "analysis_data_Trump.parquet"))
 ```
@@
 
-Understanding voter sentiment is essential for both political campaigns and analysts, especially with the upcoming U.S.
-election on the horizon.
-Public opinion is highly dynamic and can change swiftly due to various influences, including media coverage, campaign tactics, and major events.
-This study aims to forecast the percentage of support for Kamala Harris, offering insights into the elements that shape voter preferences as the election nears.
-By examining data from multiple polling sources, we intend to pinpoint the key factors influencing support, such as the poll's end date, the polling organization, geographic location, and the poll's score.
-Our research seeks to fill a gap in existing literature that often fails to address the complexities of polling data, thereby enhancing our understanding of voter behavior within the electoral context.
-
-The main focus of our analysis is the percentage of support for Harris, which we will model using various predictor variables.
-We are particularly interested in how the end date, polling organization, state, and poll score affect voter support.
-Using a linear regression framework, we can quantify the relationships between these predictors and the support outcome, providing clarity on how each factor influences overall support for Harris.
-By estimating the coefficients for each predictor, we aim to draw significant conclusions about their respective impacts on voter sentiment.
-
-Our findings reveal a notable positive correlation between the end date and the percentage of support, indicating that as the election approaches, voter support tends to increase.
-We also observed considerable variability in support levels based on the polling organization and state, with certain pollsters consistently reporting higher support for Harris.
-The quality of the polls significantly affected results, with more reputable polls correlating with higher levels of support.
-These insights emphasize the necessity of considering both the timing of polls and the characteristics of different polling firms when analyzing public opinion.
-
-This research is important because precise predictions of voter support are crucial for effective campaign strategies.
-By identifying the main factors influencing support for Harris, campaign teams can customize their outreach and messaging to resonate better with voters.
-Furthermore, recognizing the differences across various polling organizations and states can assist in resource allocation and strategic focus during the campaign.
-Given that elections can be decided by narrow margins, having trustworthy insights into voter preferences can substantially influence the final outcomes.
-
-The structure of this paper is organized as follows: @sec-data provides details on the data sources and variables used in our analysis.
-@sec-model explains the modeling approach, including the assumptions and specifications of our linear regression framework.
-In @sec-results, we present our findings, emphasizing the key predictors of Harris's support.
-Finally, @sec-discussion explores the implications of our results and suggests potential directions for future research.
-# Estimand
-
-The estimand of our analysis is the true percentage of voter support for Kamala Harris in the upcoming U.S. presidential election.
+Understanding voter sentiment is essential for both political campaigns
+and analysts, especially with the upcoming U.S. election on the horizon.
+Public opinion is highly dynamic and can change swiftly due to various
+influences, including media coverage, campaign tactics, and major
+events. This study aims to forecast the percentage of support for Kamala
+Harris, offering insights into the elements that shape voter preferences
+as the election nears. By examining data from multiple polling sources,
+we intend to pinpoint the key factors influencing support, such as the
+poll's end date, the polling organization, geographic location, and the
+poll's score. Our research seeks to fill a gap in existing literature
+that often fails to address the complexities of polling data, thereby
+enhancing our understanding of voter behavior within the electoral
+context.
+
+The estimand of our analysis is the true percentage of voter support for
+Kamala Harris in the upcoming U.S. presidential election.
+
+The main focus of our analysis is the percentage of support for Harris,
+which we will model using various predictor variables. We are
+particularly interested in how the end date, polling organization,
+state, and poll score affect voter support. Using a linear regression
+framework, we can quantify the relationships between these predictors
+and the support outcome, providing clarity on how each factor influences
+overall support for Harris. By estimating the coefficients for each
+predictor, we aim to draw significant conclusions about their respective
+impacts on voter sentiment.
+
+Our findings reveal a notable positive correlation between the end date
+and the percentage of support, indicating that as the election
+approaches, voter support tends to increase. We also observed
+considerable variability in support levels based on the polling
+organization and state, with certain pollsters consistently reporting
+higher support for Harris. The quality of the polls significantly
+affected results, with more reputable polls correlating with higher
+levels of support. These insights emphasize the necessity of considering
+both the timing of polls and the characteristics of different polling
+firms when analyzing public opinion.
+
+This research is important because precise predictions of voter support
+are crucial for effective campaign strategies. By identifying the main
+factors influencing support for Harris, campaign teams can customize
+their outreach and messaging to resonate better with voters.
+Furthermore, recognizing the differences across various polling
+organizations and states can assist in resource allocation and strategic
+focus during the campaign. Given that elections can be decided by narrow
+margins, having trustworthy insights into voter preferences can
+substantially influence the final outcomes.
+
+The structure of this paper is organized as follows: @third-data provides
+details on the data sources and variables used in our analysis.
+@forth-model explains the modeling approach, including the assumptions and
+specifications of our linear regression framework. In @fifth-results, we
+present our findings, emphasizing the key predictors of Harris's
+support. Finally, @sixth-discussion explores the implications of our
+results and suggests potential directions for future research.
+@appendix-a provide external data detail, @appendix-b provide model detail, @appendix-c provide a exploration for pollster methodology, @appendix-d provide a idealized methodology.
 
@@
 
-We conduct our polling data analysis using the R programming language [@citeR].
-Our dataset, obtained from FiveThirtyEight [@fivethirtyeight2024],based on polling as of 27 October 2024, provides a detailed overview of public opinion in the lead-up to the election.
-Adhering to the guidelines presented in @tellingstories, we explore various factors that influence voter support percentages, including the timing of the polls, the traits of polling organizations, and regional differences.
-
-In this study, we utilized several R packages to enhance our data manipulation, modeling, and visualization capabilities.
-The tidyverse package offered a comprehensive set of tools for data wrangling and analysis, improving workflow efficiency (@thereferencecanbewhatever).
-The here package aided in managing file paths, allowing for easy access to our data files (@citehere).
-We relied on janitor to perform data cleaning, as it provides functionalities to identify and rectify quality issues within the dataset (@citejanitor).
-For handling date-related operations, the lubridate package proved invaluable, simplifying the manipulation of time variables (@citelubridate).
-Lastly, arrow supported efficient data input and output in a performance-oriented format, essential for managing larger datasets (@citearrow).
-Our coding practices and file organization were informed by the structure outlined in @tellingstories.
+We conduct our polling data analysis using the R programming language
+[@citeR]. Our dataset, obtained from FiveThirtyEight
+[@fivethirtyeight2024],based on polling as of 27 October 2024, provides
+a detailed overview of public opinion in the lead-up to the election.
+Adhering to the guidelines presented in @tellingstories, we explore
+various factors that influence voter support percentages, including the
+timing of the polls, the traits of polling organizations, and regional
+differences.
+
+In this study, we utilized several R packages to enhance our data
+manipulation, modeling, and visualization capabilities. The tidyverse
+package offered a comprehensive set of tools for data wrangling and
+analysis, improving workflow efficiency [@thereferencecanbewhatever].
+The here package aided in managing file paths, allowing for easy access
+to our data files [@citehere]. We relied on janitor to perform data
+cleaning, as it provides functionalities to identify and rectify quality
+issues within the dataset [@citejanitor]. For handling date-related
+operations, the lubridate package proved invaluable, simplifying the
+manipulation of time variables [@citelubridate]. Lastly, arrow supported
+efficient data input and output in a performance-oriented format,
+essential for managing larger datasets [@citearrow]. Our coding
+practices and file organization were informed by the structure outlined
+in @tellingstories.
 
@@
 
-The process of translating real-world events into our dataset requires a systematic approach to measurement and data gathering.
-In this research, we aim to assess public opinion regarding Kamala Harris as the upcoming U.S.
-presidential election approaches.
-Polling agencies formulate surveys featuring specific questions designed to capture voters' attitudes, including their likelihood of supporting Harris and their views on prevailing political issues.
-
-Once the survey items are established, a representative sample is selected through stratified random sampling methods, ensuring a diverse demographic representation.
-Respondents are reached using various techniques, such as telephone interviews and online questionnaires.
-
-After gathering the responses, the data is subjected to thorough cleaning and validation procedures to rectify inconsistencies and handle any missing information.
-This step is crucial for ensuring that the dataset accurately mirrors the electorate's sentiments.
-Each entry in the finalized dataset reflects an individual's viewpoint at a given moment, enabling a detailed analysis of the factors that shape public opinion as the election nears.
-This structured methodology effectively converts subjective opinions into measurable data, providing valuable insights into voter behavior and preferences.
+The process of translating real-world events into our dataset requires a
+systematic approach to measurement and data gathering. In this research,
+we aim to assess public opinion regarding Kamala Harris as the upcoming
+U.S. presidential election approaches. Polling agencies formulate
+surveys featuring specific questions designed to capture voters'
+attitudes, including their likelihood of supporting Harris and their
+views on prevailing political issues.
+
+Once the survey items are established, a representative sample is
+selected through stratified random sampling methods, ensuring a diverse
+demographic representation. Respondents are reached using various
+techniques, such as telephone interviews and online questionnaires.
+
+After gathering the responses, the data is subjected to thorough
+cleaning and validation procedures to rectify inconsistencies and handle
+any missing information. This step is crucial for ensuring that the
+dataset accurately mirrors the electorate's sentiments. Each entry in
+the finalized dataset reflects an individual's viewpoint at a given
+moment, enabling a detailed analysis of the factors that shape public
+opinion as the election nears. This structured methodology effectively
+converts subjective opinions into measurable data, providing valuable
+insights into voter behavior and preferences.
 
@@
 
-@fig-percentage illustrates the distribution of percentage support for Kamala Harris based on polling data, where support reflects the proportion of respondents favoring Harris in each survey.
-Most polls report support clustered around 50%, with the majority of values falling between 40% and 55%.
-This central peak suggests moderate, consistent support levels among respondents, with fewer instances of higher support levels above 55%.
-The right-skew in the distribution indicates occasional polls with elevated support, though these are less common.
-Overall, this visualization highlights the general sentiment and variability in support for Harris as captured across multiple polls.
+@fig-percentage illustrates the distribution of percentage support for
+Kamala Harris based on polling data, where support reflects the
+proportion of respondents favoring Harris in each survey. Most polls
+report support clustered around 50%, with the majority of values falling
+between 40% and 55%. This central peak suggests moderate, consistent
+support levels among respondents, with fewer instances of higher support
+levels above 55%. The right-skew in the distribution indicates
+occasional polls with elevated support, though these are less common.
+Overall, this visualization highlights the general sentiment and
+variability in support for Harris as captured across multiple polls.
 
@@
 
-The end date is the final day of data collection for a poll, indicating when the survey period concluded.
-This date provides crucial context for the poll results, as public opinion may change over time in response to events, campaign actions, or other influencing factors.
+The end date is the final day of data collection for a poll, indicating
+when the survey period concluded. This date provides crucial context for
+the poll results, as public opinion may change over time in response to
+events, campaign actions, or other influencing factors.
 
@@
 
-@fig-state displays the distribution of polls by state, showing how frequently polling organizations conducted surveys across various U.S.
-states and at the national level.
-The "National" category has the highest number of polls, indicating a strong emphasis on capturing overall U.S.
-sentiment.
-Certain states, such as Pennsylvania, Wisconsin, North Carolina, Arizona, Georgia, and Michigan, also show higher polling frequencies, likely because these are battleground states with the potential to influence the election outcome significantly.
-Toward the right side of the chart, states with minimal polling activity, including South Carolina, Iowa, and Washington, appear less frequently, possibly due to their historically predictable or less competitive nature.
-This distribution reflects the strategic focus of polling efforts, with organizations prioritizing both national sentiment and swing states where public opinion is more volatile.
-Overall, the chart provides insight into where polling resources are allocated as election day nears, emphasizing areas that could sway the final result.
+@fig-state displays the distribution of polls by state, showing how
+frequently polling organizations conducted surveys across various U.S.
+states and at the national level. The "National" category has the
+highest number of polls, indicating a strong emphasis on capturing
+overall U.S. sentiment. Certain states, such as Pennsylvania, Wisconsin,
+North Carolina, Arizona, Georgia, and Michigan, also show higher polling
+frequencies, likely because these are battleground states with the
+potential to influence the election outcome significantly. Toward the
+right side of the chart, states with minimal polling activity, including
+South Carolina, Iowa, and Washington, appear less frequently, possibly
+due to their historically predictable or less competitive nature. This
+distribution reflects the strategic focus of polling efforts, with
+organizations prioritizing both national sentiment and swing states
+where public opinion is more volatile. Overall, the chart provides
+insight into where polling resources are allocated as election day
+nears, emphasizing areas that could sway the final result.
 
@@
 
-@fig-pollster displays the frequency of polls conducted by different pollsters.
-Each bar represents a pollster, with the height indicating the number of polls they conducted.
-Siena/NYT has the highest count, followed by YouGov and Emerson.
-Pollsters to the right have conducted significantly fewer polls, with some showing only one or two entries.
-
-The pollster is the organization or firm that conducts the surveys, gathering and analyzing public opinion data on voter preferences.
-In this context, each pollster's count reflects its level of polling activity related to the election.
+@fig-pollster displays the frequency of polls conducted by different
+pollsters. Each bar represents a pollster, with the height indicating
+the number of polls they conducted. Siena/NYT has the highest count,
+followed by YouGov and Emerson. Pollsters to the right have conducted
+significantly fewer polls, with some showing only one or two entries.
+
+The pollster is the organization or firm that conducts the surveys,
+gathering and analyzing public opinion data on voter preferences. In
+this context, each pollster's count reflects its level of polling
+activity related to the election.
 
@@
 
-@fig-numericgrade displays the distribution of numeric grades assigned to various pollsters, with the x-axis representing the numeric grade values and the y-axis indicating the frequency of each grade.
-The numeric grade is a metric that evaluates the quality or reliability of a pollster, taking into account factors such as methodology, historical accuracy, sample size, and pollster reputation.
-In this chart, we observe that the most common numeric grades are concentrated around 2.75 and 3.00, with a large spike at these values, suggesting that a significant number of polls are conducted by highly-rated pollsters.
-Fewer polls have grades below 2.5, indicating a relatively lower occurrence of polls from less-reliable pollsters in this dataset.
-This distribution underscores the emphasis on high-quality pollsters within the dataset, ensuring a more reliable and consistent source of polling data for subsequent analysis.
+@fig-numericgrade displays the distribution of numeric grades assigned
+to various pollsters, with the x-axis representing the numeric grade
+values and the y-axis indicating the frequency of each grade. The
+numeric grade is a metric that evaluates the quality or reliability of a
+pollster, taking into account factors such as methodology, historical
+accuracy, sample size, and pollster reputation. In this chart, we
+observe that the most common numeric grades are concentrated around 2.75
+and 3.00, with a large spike at these values, suggesting that a
+significant number of polls are conducted by highly-rated pollsters.
+Fewer polls have grades below 2.5, indicating a relatively lower
+occurrence of polls from less-reliable pollsters in this dataset. This
+distribution underscores the emphasis on high-quality pollsters within
+the dataset, ensuring a more reliable and consistent source of polling
+data for subsequent analysis.
 
@@
 
-@fig-pollstertime shows the trend of percentage support for Kamala Harris over time, with data points and smoothed trend lines for each pollster.
-The x-axis represents the dates from August through October, while the y-axis indicates the percentage of respondents supporting Harris.
-Each color corresponds to a specific polling organization, with prominent pollsters such as Beacon/Shaw, Ipsos, Siena/NYT, Emerson, Quinnipiac, and YouGov.
-The smoothed lines reveal subtle trends over time, with some pollsters like Emerson and Beacon/Shaw showing a slight upward trend, while others like Siena/NYT display a downward trend.
-@fig-pollstertime highlights the variability in poll results across different organizations, reflecting each pollster's methodology and sample.
+@fig-pollstertime shows the trend of percentage support for Kamala
+Harris over time, with data points and smoothed trend lines for each
+pollster. The x-axis represents the dates from August through October,
+while the y-axis indicates the percentage of respondents supporting
+Harris. Each color corresponds to a specific polling organization, with
+prominent pollsters such as Beacon/Shaw, Ipsos, Siena/NYT, Emerson,
+Quinnipiac, and YouGov. The smoothed lines reveal subtle trends over
+time, with some pollsters like Emerson and Beacon/Shaw showing a slight
+upward trend, while others like Siena/NYT display a downward trend.
+@fig-pollstertime highlights the variability in poll results across
+different organizations, reflecting each pollster's methodology and
+sample.
 
@@
 
-@fig-numericgradetime illustrates Harris's support percentages over time, with each data point representing poll results colored by the numeric grade of the pollster.
-The smoothing lines for each numeric grade remain subtle, indicating minor variations in support trends over time across different pollster quality levels.
-Most points are clustered around the 50% support level, suggesting a generally stable voter sentiment for Harris, with only slight fluctuations across numeric grades.
-By limiting the y-axis, outliers and extreme variations are minimized, resulting in a clearer and more interpretable visualization.
-This approach emphasizes the central trend, allowing for clearer comparisons of support levels across pollsters of varying reliability without distraction from extreme values.
+@fig-numericgradetime illustrates Harris's support percentages over
+time, with each data point representing poll results colored by the
+numeric grade of the pollster. The smoothing lines for each numeric
+grade remain subtle, indicating minor variations in support trends over
+time across different pollster quality levels. Most points are clustered
+around the 50% support level, suggesting a generally stable voter
+sentiment for Harris, with only slight fluctuations across numeric
+grades. By limiting the y-axis, outliers and extreme variations are
+minimized, resulting in a clearer and more interpretable visualization.
+This approach emphasizes the central trend, allowing for clearer
+comparisons of support levels across pollsters of varying reliability
+without distraction from extreme values.
 
@@
 
-## Model
+## Model{#forth-model}
 
@@
 #| message: false
-harris_unweighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_harris_unweighted.rds")
-harris_weighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_harris_weighted.rds")
-trump_unweighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_trump_unweighted.rds")
-trump_weighted_model <-readRDS(file = "~/2024 US Election Forecast/models/model_trump_weighted.rds")
-
+harris_unweighted_model <- readRDS(here::here("models", "model_harris_unweighted.rds"))
+harris_weighted_model <- readRDS(here::here("models", "model_harris_weighted.rds"))
+trump_unweighted_model <- readRDS(here::here("models", "model_trump_unweighted.rds"))
+trump_weighted_model <- readRDS(here::here("models", "model_trump_weighted.rds"))
 ```
@@
 
-## Recent Three Months Support Trends Prediction
-
-The recent three-month support trends for Kamala Harris and Donald Trump across key battleground states—Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, and Wisconsin—show a highly competitive race.
-Each state’s panel displays support percentages over time from August to November 2024, with Harris shown in blue and Trump in red.
-The plot uses point size to represent poll weights, accounting for factors such as recency, pollster quality, and sample size, where larger points indicate higher-weighted polls, emphasizing more reliable data.
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| eval: true
-#| label: fig-support-trends-by-state
-#| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States
-
-harris_data <- harris_data %>%
-  mutate(
-    sample_size_weight = pmin(sample_size / 2300, 1),
-    pollster_quality_weight = numeric_grade / 4,
-    recency_weight = exp(-recency * 0.1)
-  ) %>%
-  group_by(pollster) %>%
-  mutate(
-    recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) %>%
-  ungroup() %>%
-  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
-
-# Calculate weights for Trump data
-trump_data <- trump_data %>%
-  mutate(
-    sample_size_weight = pmin(sample_size / 2300, 1),
-    pollster_quality_weight = numeric_grade / 4,
-    recency_weight = exp(-recency * 0.1)
-  ) %>%
-  group_by(pollster) %>%
-  mutate(
-    recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) %>%
-  ungroup() %>%
-  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
-
-harris_data <- harris_data %>% mutate(candidate = "Harris")
-trump_data <- trump_data %>% mutate(candidate = "Trump")
-combined_data_total <- bind_rows(harris_data, trump_data)
-
-selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
-recent_date_cutoff <- as.Date("2024-08-01")  # Set cutoff for recent data
-
-harris_filtered <- harris_data %>%
-  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)
-
-trump_filtered <- trump_data %>%
-  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)
-
-# Combine datasets for plotting with a new column for candidate
-harris_filtered <- harris_filtered %>% mutate(candidate = "Harris")
-trump_filtered <- trump_filtered %>% mutate(candidate = "Trump")
-combined_data <- bind_rows(harris_filtered, trump_filtered)
-# Plot with recent data, specific axis formatting, and smoother trend lines
-ggplot(combined_data, aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
-  geom_point(alpha = 0.7) + # Adds points with transparency for overlapping data
-  geom_smooth(aes(group = candidate), method = "loess", span = 0.2, se = FALSE, size = 1) + # Smoothed trend line
-  facet_wrap(~ state,ncol = 2,scales = "free_y") +
-  labs(title = "Recent Support Trends for Kamala Harris and Donald Trump Across Selected States",
-       x = "Date", y = "Support (%)") +
-  scale_x_date(date_labels = "%b", date_breaks = "1 month", limits = as.Date(c("2024-08-01", "2024-10-25"))) +
-  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
-  scale_size_continuous(range = c(0.5, 3), guide = "none") +
-  theme_minimal() +
-  theme(
-    legend.position = "top",
-    axis.text.x = element_text(angle = 0, hjust = 0.5),
-    panel.grid.major = element_line(size = 0.1, color = "grey80")
-  ) +
-  guides(color = guide_legend(title = "Candidate"))
-```
-@fig-support-trends-by-state illustrates the recent support trends for Kamala Harris and Donald Trump across selected battleground states from August to November 2024.
-Each subplot represents a different state, with support percentages for each candidate displayed over time.
-Key features include Harris shown in blue and Trump in red, with smoothed trend lines to capture changes over time.
-The plot's y-axis spans from approximately 30% to 50% support, while the x-axis highlights monthly intervals from August to November.
-For example, in Arizona, Trump maintains a slight lead with support fluctuating around 50% in October, compared to Harris around 48%.
-In Georgia, Trump's support reached just above 49% in late September, whereas Harris hovers closer to 47%.
-In Wisconsin, both candidates show tightly aligned trends near 48%, highlighting a close race.
-Each point's size reflects the poll weight—calculated using recency, pollster quality, and sample size—indicating the relative importance of each poll.
-This visualization emphasizes recent trends in candidate support across key battleground states.
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| eval: true
-#| label: fig-national-support-trends
-#| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States
-# Combine datasets for plotting with a new column for candidate
-harris_filtered <- harris_filtered %>% mutate(candidate = "Harris")
-trump_filtered <- trump_filtered %>% mutate(candidate = "Trump")
-combined_data <- bind_rows(harris_filtered, trump_filtered)
-
-combined_data_total|>filter(national_poll==1)|>ggplot(aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
-  geom_point(alpha = 0.7) + # Adds points with transparency for overlapping data
-  geom_smooth(aes(group = candidate), method = "loess", span = 0.2, se = FALSE, size = 1) + # Smoothed trend line
-  labs(title = "Recent Support Trends for Kamala Harris and Donald Trump Across Country",
-       x = "Date", y = "Support (%)") +
-  scale_x_date(date_labels = "%b", date_breaks = "1 month", limits = as.Date(c("2024-08-01", "2024-10-27"))) +
-  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
-  scale_size_continuous(range = c(0.5, 3), guide = "none") +
-  theme_minimal() +
-  theme(
-    legend.position = "top",
-    axis.text.x = element_text(angle = 0, hjust = 0.5),
-    panel.grid.major = element_line(size = 0.1, color = "grey80")
-  ) +
-  guides(color = guide_legend(title = "Candidate")) +  # Vertical line at October 25
-  annotate("text", x = as.Date("2024-10-19"), y = Inf, label = "October 25th", vjust = 1, color = "black", size = 3.5) +
-  geom_vline(xintercept = as.Date("2024-10-25"), linetype = "solid", color = "black", size = 0.8)   # Vertical line at October 25
-
-```
-@fig-national-support-trends illustrates the polling support trends for Kamala Harris and Donald Trump across the country from August to October.
-The scatter points represent individual poll results, with blue for Harris and red for Trump, while each dot's size reflects the weight of the poll, accounting for factors like sample size, quality, and recency.
-Harris’s support trend line generally remains above Trump’s, with an average support level around 49%, compared to Trump’s approximate average of 47% over this period.
-Toward the end of October, both candidates show a slight increase, with Harris’s support reaching just over 50% and Trump’s approaching 49%.
-This trend suggests a potential narrowing in support levels as the election approaches, providing a quantitative snapshot of national polling dynamics.
-
-## Recent Three Months Support Trends Linear Model Prediction
+## Predicted Voting Outcomes
+
+```{r}
+modelsummary::msummary(list(
+  "Harris Unweighted" = harris_unweighted_model, 
+  "Harris Weighted" = harris_weighted_model,
+  "Trump Unweighted" = trump_unweighted_model,
+  "Trump Weighted" = trump_weighted_model))
+
+```
 
@@
 set.seed(233)
+
 new_data_harris <- data.frame(
@@
     max(harris_data$end_date),
-    length.out = 1000 
+    length.out = 2000
   ),
-  national_poll = rep(c(0, 1), length(1000)),
-  pollster = factor(sample(levels(harris_data$pollster), size = 1000, replace = TRUE), 
+  state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE)), 
+  pollster = factor(sample(levels(harris_data$pollster), size = 2000, replace = TRUE), 
                     levels = levels(harris_data$pollster)), 
-  population = factor(sample(c("lv","rv"), size = 1000, replace = TRUE)),
-  sample_size = sample(1:2300, size = 1000, replace = TRUE),
-  pollster_quality= sample(2:4, size = 1000, replace = TRUE)
+  population = factor(sample(levels(harris_data$population), size = 2000, replace = TRUE), 
+                    levels = levels(harris_data$population)),
+  sample_size = sample(1:2300, size = 2000, replace = TRUE)
 )|>
-  group_by(pollster)|>
-  mutate(recency = as.numeric(difftime( as.Date("2024-11-05"),as.Date(end_date), units = "days")),
-    recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) |>ungroup()|>
   mutate(
-    # Sample size weight (assuming a maximum of 2300 responses)
-    sample_size_weight = pmin(sample_size / 2300, 1),  # Set sample size; adjust accordingly
-
-    # Pollster quality weight (assuming you want to use a dummy numeric grade, e.g., 2)
-    pollster_quality_weight = pollster_quality / 4,
-
-    recency_weight = exp(-recency * 0.1),  # Adjust decay rate as needed
-    # Combine all weights into a final combined weight
-    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
+    national_poll = if_else(state == "National", 1, 0),
+    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
+    sample_size_weight = pmin(sample_size / 2300, 1),
+    recency_weight = exp(-recency * 0.1),
+    combined_weight = recency_weight * sample_size_weight,
     candidate="Harris"
   )
-#######
+
+####### Prediction for Trump ######
 new_data_trump <- data.frame(
@@
     max(trump_data$end_date),
-    length.out = 1000
+    length.out = 2000
   ),
-  pollster = factor(sample(levels(trump_data$pollster), size = 1000, replace = TRUE), 
+  pollster = factor(sample(levels(trump_data$pollster), size = 2000, replace = TRUE), 
                     levels = levels(trump_data$pollster)),
-  population = factor(sample(c("lv","rv"), size = 1000, replace = TRUE)),
-   national_poll = rep(c(0, 1), length(1000)),  
-  sample_size =sample(1:2300, size = 1000, replace = TRUE),
-  pollster_quality= sample(2:4, size = 1000, replace = TRUE)
+ population= factor(sample(levels(trump_data$population), size = 2000, replace = TRUE), 
+                    levels = levels(trump_data$population)),
+   state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE), 
+                    levels = levels(trump_data$state)),  
+  sample_size =sample(1:2300, size = 2000, replace = TRUE),
+  pollster_quality= sample(2:4, size = 2000, replace = TRUE)
 )|>
-  group_by(pollster)|>
-  mutate(recency = as.numeric(difftime( as.Date("2024-11-05"),as.Date(end_date), units = "days")),
-    recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) |>
-  ungroup() |>
   mutate(
-    # Sample size weight (assuming a maximum of 2300 responses)
+   national_poll = if_else(state == "National", 1, 0),
+      recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
     sample_size_weight = pmin(sample_size / 2300, 1),
-    pollster_quality_weight = pollster_quality / 4,  
     recency_weight = exp(-recency * 0.1),  
-    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
+    combined_weight = recency_weight * sample_size_weight,
     candidate="Trump"
@@
 #| message: false
-#| eval: true
-#| label: fig-support-predicted
-#| fig-cap: Predicted Support Trends for Kamala Harris and Donald Trump using Fitted Linear Model
+#| include: false
 # Predictions for Harris
@@
 # Determine the maximum end date for setting the x-axis limit
-max_end_date <- as.Date("2024-10-30")
-
-# Plotting with the filtered data
-ggplot(combined_predictions_filtered, aes(x = end_date, color = candidate)) +
-  geom_smooth(aes(y = predicted_unweighted, linetype = "Unweighted"), 
-              method = "loess", se = TRUE, size = 1) +  # Unweighted model with smoothing
-  geom_smooth(aes(y = predicted_weighted, linetype = "Weighted"), 
-              method = "loess", se = TRUE, size = 1) +
+max_end_date <- as.Date("2024-10-26")
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using Fitted Linear Model"
+#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
+#| layout-ncol: 2
+#| label: fig-support-trend
+ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
+  geom_point(alpha = 0.7,color="grey")+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
+  facet_wrap(~ candidate,ncol = 2) +
   labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
-       subtitle = "predicted using multiple linear regression model ",
+       subtitle = "predicted using unweighted multiple linear regression model ",
        x = "End Date of the Poll",  # Change x-axis label to End Date
@@
        color = "Candidate",caption = 
-                   "Weights: recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight\nLinear Regression Model: candidate support percentage =national_poll + pollster + population") +
+                   "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
   scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
-  scale_linetype_manual(name = "Linear Model Type", values = c("Unweighted" = "dashed", "Weighted" = "solid")) +
-  theme_minimal() +
+  theme_classic() +
   theme(legend.position = "top",
-        axis.text.x = element_text(angle = 45, hjust = 1)) +
-  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))  +
-  geom_vline(xintercept = as.Date("2024-10-25"), linetype = "solid", color = "black", size = 0.8) +  # Vertical line at October 25
-  annotate("text", x = as.Date("2024-10-19"), y = Inf, label = "October 25th", vjust = 1, color = "black", size = 3.5)+  # Vertical line at October 25
-  geom_text(aes(x = as.Date("2024-10-25"), y = 50, label = "49%"), color = "blue", hjust = -0.1, size = 3) +  # Harris label
-  geom_text(aes(x = as.Date("2024-10-25"), y = 48, label = "48%"),color = "red", hjust = -0.1, size = 3)+  # Harris label
-  geom_text(aes(x = as.Date("2024-10-25"), y = 46.5, label = "46.5%"), color = "red",hjust = -0.1, size = 3)  # Trump label
+        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
+
+# Plotting with the filtered data
+ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
+  geom_point(alpha = 0.7,color="grey")+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
+  facet_wrap(~ candidate,ncol = 2) +
+  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
+       subtitle = "predicted using weighted multiple linear regression model ",
+       x = "End Date of the Poll",  # Change x-axis label to End Date
+       y = "Predicted Support (%)",
+       color = "Candidate",
+       size="Weight",
+       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red"))  +
+  theme_classic() +
+  theme(legend.position = "top",
+        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
+```
+## Predicted Voting Outcomes for Recent Three Months by Respondent Group
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Fitted Linear Model"
+#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
+#| layout-ncol: 2
+#| label: fig-support-respondent
+custom_labels <- c("lv" = "Likely Voters", "rv" = "Registered Voters")
+### unweighted
+ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
+  geom_point(alpha = 0.7,color="grey")+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
+  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
+  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
+       subtitle = "predicted using unweighted multiple linear regression model ",
+       x = "End Date of the Poll",  # Change x-axis label to End Date
+       y = "Predicted Support (%)",
+       color = "Candidate",
+       size="Weight",
+       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  theme_classic() +
+  theme(legend.position = "top",
+        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
+### weighted
+ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
+  geom_point(alpha = 0.7,color="grey")+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
+  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
+  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
+       subtitle = "predicted using weighted multiple linear regression model ",
+       x = "End Date of the Poll",  # Change x-axis label to End Date
+       y = "Predicted Support (%)",
+       color = "Candidate",
+       size="Weight",
+       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  theme_classic() +
+  theme(legend.position = "top",
+        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
+```
+## Predicted Voting Outcomes for Recent Three Months by State
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Fitted Linear Model"
+#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
+#| layout-ncol: 2
+#| label: fig-support-respondent
+## unweighted
+selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
+combined_data_total<-combined_data_total|>filter(state %in% selected_states)
+combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
+ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
+  geom_point(alpha = 0.7,color="grey")+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
+  facet_wrap(~ state,ncol = 4) +
+  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
+       subtitle = "predicted using unweighted multiple linear regression model ",
+       x = "End Date of the Poll",  # Change x-axis label to End Date
+       y = "Predicted Support (%)",
+       color = "Candidate",
+       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  theme_classic() +
+  theme(legend.position = "top",
+        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
+## weighetd
+ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
+  geom_point(alpha = 0.7,color="grey")+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
+  facet_wrap(~ state,ncol = 4) +
+  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
+       subtitle = "predicted using weighted multiple linear regression model ",
+       x = "End Date of the Poll",  # Change x-axis label to End Date
+       y = "Predicted Support (%)",
+       color = "Candidate",
+       size="Weight",
+       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  theme_classic() +
+  theme(legend.position = "top",
+        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
+```
+
+```{r}
+# Load necessary package
+library(knitr)
+library(kableExtra)
+
+# Example: Assume `predicted_results` is your data frame
+# Ensure column names match this format
+# Example structure:
+# predicted_results <- data.frame(
+#   State = c("Arizona", "California", ...),
+#   Trump_Predicted_Percentage = c(48.94, 33.80, ...),
+#   Electoral_Votes = c(11, 55, ...),
+#   Winner = c("Harris", "Harris", ...)
+# )
+
+# Rename columns to match the desired table format
+colnames(predicted_results) <- c("State", "Harris Predicted %", "Vote Share", "Winner")
+
+# Generate table
+predicted_results %>%
+  kbl(caption = "Prediction Vote share for Trump and Harris", format = "html") %>%
+  kable_styling(full_width = FALSE, position = "center") %>%
+  column_spec(2, width = "5em") %>%
+  column_spec(3, width = "5em") %>%
+  column_spec(4, width = "5em") %>%
+  add_header_above(c(" " = 1, "Trump Predicted %" = 1, "Electoral Votes" = 1, "Winner" = 1))
+
 ```
@@
 Harris leads Donald Trump by approximately 2.5% in the un-weighted (49%
-vs. 46.5%) and 1% in weighted models (49% vs. 48%). Average leading by about 2%.
+vs. 46.5%) and 1% in weighted models (49% vs. 48%). Average leading by
+about 2%.
 
@@
 
-# Additional data details {#first-model-details}
+# Additional data details {#appendix-a}
 
@@
 
-In this data-cleaning process, we focus on refining raw polling data for Kamala Harris and Donald Trump to enhance its quality and relevance for analysis.
-The process begins by loading the dataset and using the janitor package to standardize column names, ensuring consistent naming conventions throughout.
-We then filter the data to retain only essential columns and remove rows with missing values in key fields, including numeric_grade, pct, sample_size, and end_date.
-
-For each candidate, we isolate polls specifically for Kamala Harris and Donald Trump, retaining only high-quality polls with a numeric_grade of 2 or higher—given that the average numeric_grade is approximately 2.175, with a median of 1.9.
-We also handle placeholder values in state information by setting entries marked as "--" to NA, and create a national_poll indicator, assigning a value of 1 for national polls and 0 for state-specific ones.
-Dates are standardized using the lubridate package to facilitate accurate time-based analysis.
-
-Recency weights are calculated based on the days elapsed since the poll's end date, applying an exponential decay function to prioritize more recent polls.
-Weights based on sample size are capped at a maximum of 2,300 responses to maintain balanced representation.
-Additionally, categorical variables, including pollster, state, candidate_name, population, and methodology, are converted to factors to prepare for analysis.
-
-The cleaned datasets for both candidates are then saved as Parquet files for efficient storage and access in further modeling and analysis.
-This structured approach ensures that the data is accurate, complete, and optimized for insightful statistical analysis.
+In this data-cleaning process, we focus on refining raw polling data for
+Kamala Harris and Donald Trump to enhance its quality and relevance for
+analysis. The process begins by loading the dataset and using the
+janitor package to standardize column names, ensuring consistent naming
+conventions throughout. We then filter the data to retain only essential
+columns and remove rows with missing values in key fields, including
+numeric_grade, pct, sample_size, and end_date.
+
+For each candidate, we isolate polls specifically for Kamala Harris and
+Donald Trump, retaining only high-quality polls with a numeric_grade of
+2 or higher—given that the average numeric_grade is approximately 2.175,
+with a median of 1.9. We also handle placeholder values in state
+information by setting entries marked as "--" to NA, and create a
+national_poll indicator, assigning a value of 1 for national polls and 0
+for state-specific ones. Dates are standardized using the lubridate
+package to facilitate accurate time-based analysis.
+
+Recency weights are calculated based on the days elapsed since the
+poll's end date, applying an exponential decay function to prioritize
+more recent polls. Weights based on sample size are capped at a maximum
+of 2,300 responses to maintain balanced representation. Additionally,
+categorical variables, including pollster, state, candidate_name,
+population, and methodology, are converted to factors to prepare for
+analysis.
+
+The cleaned datasets for both candidates are then saved as Parquet files
+for efficient storage and access in further modeling and analysis. This
+structured approach ensures that the data is accurate, complete, and
+optimized for insightful statistical analysis.
 
@@
 
-# Model details {#sec-model-details}
+# Model details {#appendix-b}
 
@@
 
-Harris model: RMSE of 3.44, indicating an average prediction error of
+Harris model: RMSE of 3.42, indicating an average prediction error of
 around 3.44 percentage points.\
-Trump model: RMSE of 4.40, showing a slightly higher prediction error on
+Trump model: RMSE of 4.30, showing a slightly higher prediction error on
 average.\
@@
 variable explained by the model (higher is better).\
-Harris model: R-squared of 0.34, meaning the model explains about 34.6%
+Harris model: R-squared of 0.33, meaning the model explains about 34.6%
 of the variance in Harris's polling data.\
-Trump model: R-squared of 0.34 as well, indicating similar explanatory
+Trump model: R-squared of 0.27 as well, indicating similar explanatory
 power for Trump's polling data.
@@
 by its lower RMSE and MAE values.\
-Model Fit: Both models explain roughly 34% of the variance in their
-respective datasets. This suggests that other factors not included in
+Model Fit: Harris' model explain roughly 33% of the variance in their
+respective datasets. Trump's models explain roughly 33% of the variance in their
+respective datasets.This suggests that other factors not included in
 the model may play a significant role in explaining the remaining
@@
 
-# The New York Times/Siena College Polling Methodology {#third-poll}
+# The New York Times/Siena College Polling Methodology {#appendix-c}
 
@@
 political polling and is particularly recognized for its work in
-understanding voter sentiment during elections.
-
-Established in 1980 at Siena College in New York's Capital District, the
-Siena College Research Institute (SCRI) conducts surveys at regional,
-state, and national levels on various topics, including business,
-economics, politics, voter behavior, social issues, academics, and
-history. The institute carries out both expert and public opinion polls.
-
-Students from Siena and other colleges participate in every survey,
-gaining hands-on experience in fields such as political science,
-computing, communications, sociology, and psychology. SCRI also hires
-interns for special projects involving event planning, in-depth
-research, report writing, and analysis. The results of SCRI's surveys
-are featured in major regional and national publications, including The
-Wall Street Journal and The New York Times, as well as in academic
-journals, books, and encyclopedias, both in print and online. Their
-findings are regularly highlighted in local and national television and
-radio broadcasts. SCRI conducts the Siena New York Poll, a monthly
-survey that captures the opinions of registered voters across New York
-State on current political issues, along with the New York State Index
-of Consumer Sentiment, which offers a quarterly assessment of New
-Yorkers' spending intentions. SCRI adheres to the American Association
-of Public Opinion Research (AAPOR) Code of Professional Ethics and
-Practices. The institute is often commissioned to carry out surveys for
-various organizations, businesses, and local and state government
-agencies. [@aboutsiena]
+understanding voter sentiment during elections. Established in 1980 at
+Siena College in New York's Capital District, the institute carries out
+both expert and public opinion polls. [@aboutsiena].
 
@@
 
-In essence, statistics is about collecting data and making informed
-conclusions, even though we can never access every piece of
-information.\
-From @tellingstories, we defined three key terms as:\
+Refer from @tellingstories, we defined three key terms as:\
 Target population : The collection of all items about which we would
@@
 The target population for Siena’s polls includes registered voters
-eligible to vote in Michigan, Wisconsin, and Ohio. The sampling frame
-consists of a comprehensive list of registered voters, which includes
-demographic information for each voter. This enables the pollsters to
-ensure an appropriate representation of voters across various parties,
-races, and regions [@poll]. The sample of registered voters sourced from
-the voter file maintained by L2, a nonpartisan vendor, and supplemented
-with additional cellular phone numbers matched from Marketing Systems
-Group. The sample for the poll totals 2,055 likely voters, with 688 from
-Michigan, 687 from Ohio, and 680 from Wisconsin, surveyed from September
-21 to 26, 2024.\
+eligible to vote in Michigan, Wisconsin, and Ohio.
+
+The sampling frame is a comprehensive list of registered voters, which
+includes demographic information for each voter. This enables the
+pollsters to ensure an appropriate representation of voters across
+various parties, races, and regions [@poll].
+
+The sample of registered voters sourced from the voter file maintained
+by L2, a nonpartisan vendor, and supplemented with additional cellular
+phone numbers matched from Marketing Systems Group. The sample for the
+poll totals 2,055 likely voters, with 688 from Michigan, 687 from Ohio,
+and 680 from Wisconsin, surveyed from September 21 to 26, 2024.
 
@@
 
-Siena use phone poll to recruit sample. Telephone polling is a common
-method for gathering public opinion and assessing voter sentiment by
-contacting individuals via landlines and mobile phones. This approach
-uses live interviewers to enhance data quality, allowing for
-clarification and nuanced responses. By utilizing random digit dialing
-or national voter registration databases, researchers can ensure a
-representative sample across various demographics. Despite its
-effectiveness in reaching diverse audiences quickly, telephone polling
-must address potential biases, such as nonresponse and shifts in
-communication habits, to maintain the reliability of its findings.[^1]
-
-[^1]: Phone polls, once considered the gold standard in survey research,
-    now compete with methods like online panels and text messaging.
-    Their advantages have diminished due to declining response rates,
-    which increase costs and may affect representativeness, raising
-    concerns about their future viability. However, they still
-    effectively reach a random selection of voters quickly, as there is
-    no national email database and postal mail can be slow. Other
-    methods, such as recruiting panelists by mail, risk attracting only
-    the most politically engaged individuals. Recent elections have
-    shown that telephone polls, including The Times/Siena Poll, continue
-    to perform well due to the reliability of voter registration files
-    in balancing party representation.
-
-According to @freqqa, the polls are conducted by live interviewers at
-call centers located in Florida, New York, South Carolina, Texas, and
-Virginia. The respondents are randomly selected from a national database
-of registered voters and are contacted via both landlines and
-cellphones.
-
-Siena polls are conducted over the phone in both English and Spanish.
-For these polls, interviewers made nearly 260,000 calls to just over
-140,000 voters. Overall, about 97 percent of respondents were contacted
-on a cellphone for these polls.
+Siena use phone poll to recruit sample. Telephone polling is a way to
+gather public opinion by contacting individuals via landlines and mobile
+phones, using live interviewers to improve data quality and capture
+nuanced responses. Through random digit dialing or voter registration
+databases, researchers achieve a representative sample across
+demographics.
+
+According to @freqqa, the polls are conducted in both English and
+Spanish by live interviewers at call centers located in Florida, New
+York, South Carolina, Texas, and Virginia. The respondents are randomly
+selected from a national database of registered voters and are contacted
+via both landlines and cellphones.
 
@@
 us to categorize the population into mutually exclusive and collectively
-exhaustive sub-populations known as "strata".
-
-Stratification is employed to enhance sampling efficiency and ensure
-balance within the survey. For example, the population of the United
-States is approximately 335 million, with around 40 million residents in
-California and roughly half a million in Wyoming. In a survey with
-10,000 responses, we would expect to receive only about 15 responses
-from Wyoming, which could complicate any inferences about that state. By
-implementing stratification, we could ensure, for instance, that there
-are 200 responses from each state. Within each state, we could then use
-random sampling to select individuals for data collection
-[@tellingstories].
+exhaustive sub-populations known as "strata"[@tellingstories].
 
@@
 by political party, race, and region, and screened by M.S.G. to ensure
-that the cellular phone numbers were active. The Siena College Research
-Institute conducted the survey, with additional support from various
-institutions, including ReconMR, the Public Opinion Research Laboratory
-at the University of North Florida, the Institute for Policy and Opinion
-Research at Roanoke College, the Center for Public Opinion and Policy
-Research at Winthrop University in South Carolina, and the Survey Center
-at the University of New Hampshire. Interviewers sought to speak with
-the individuals listed on the voter file and would terminate the
-interview if those persons were unavailable. Overall, 97 percent of
-respondents across all four samples were reached via cellular phones.
-
-The survey instrument was translated into Spanish by ReconMR, and
-bilingual interviewers began in English, following the respondent's
-preference for either language. Among self-reported Hispanics, 11
-percent of interviews were conducted in Spanish, with this percentage
-rising to 15 percent in the weighted sample of registered voters. An
-interview was considered complete for inclusion in the voting questions
-if the respondent did not drop out after answering the two self-reported
-variables used for weighting—age and education—and responded to at least
-one question related to age, education, or presidential candidate
-preference.
-
-Stratified sampling enhances the representativeness of the sample by
-ensuring that smaller subgroups, which might otherwise be
-underrepresented, are adequately included. A significant advantage of
-this method is that it allows for more efficient resource allocation,
-enabling researchers to target specific groups and gather more
-insightful data. However, this focus can lead to **higher overall
-costs**, particularly due to the comprehensive data collection and
-analysis required when sampling large states or countries. Additionally,
-while stratified sampling provides richer insights into the
-characteristics and opinions of different subgroups, it introduces
-**complexity in data analysis**, necessitating advanced statistical
-techniques to interpret the results accurately. Consequently,
-researchers must have sufficient evidence to determine how to weight
-each stratum appropriately. Lastly, if the strata are not well-defined
-or if there is an imbalance in sampling, it could still result in
-sampling bias. Overall, while stratified sampling offers substantial
-benefits in terms of representation and analytical depth, it also
-presents challenges related to complexity, cost, and potential bias if
-not executed carefully.
+that the cellular phone numbers were active.
+
+### Strength and Weakness
+
+Stratified sampling enhances sample representativeness by ensuring that
+smaller subgroups are adequately included, allowing researchers to
+allocate resources more efficiently and gain deeper insights into
+specific groups. However, this method can lead to **higher costs** due
+to the extensive data collection and analysis needed, especially when
+sampling large regions. Stratified sampling also introduces **complexity
+in data analysis**, requiring advanced techniques to accurately
+interpret subgroup data and appropriate weighting for each stratum.
+Additionally, poorly defined strata or imbalanced sampling can lead to
+sampling bias. While stratified sampling provides strong representation
+and analytical depth, it also brings challenges related to cost,
+complexity, and potential bias if not executed with care.
 
@@
 reliability of the results. The weighting process was conducted by The
-Times using the R survey package and involved multiple adjustments.
-Initially, the samples were adjusted for the unequal probability of
-selection by stratum. Subsequently, the first-stage weight was modified
-to account for the likelihood that a registrant would vote in the 2024
-election, based on a model derived from turnout data in the 2020
-election.
-
-To create a composition that reflects the likely electorate, the sample
-was further weighted to match specific targets. These targets were
-developed by aggregating individual-level turnout estimates from the L2
-voter file, with categories aligning with those used for registered
-voters. Additionally, the initial likely electorate weight was adjusted
-to incorporate self-reported voting intentions. In this final
-adjustment, four-fifths of the probability that a registrant would vote
-in the 2024 election was based on their ex ante modeled turnout score,
-while one-fifth relied on their self-reported intentions, adjusted for
-the tendency of survey respondents to have higher turnout rates than
-nonrespondents.
-
-The final likely electorate weight was calculated by multiplying the
-modeled electorate rake weight by the final turnout probability and then
-dividing by the ex ante modeled turnout probability. This comprehensive
-approach to weighting helps mitigate nonresponse bias by ensuring that
-the sample reflects both the characteristics of the general population
-and the expected behavior of likely voters. As a result, the sample of
-respondents who completed all questions in the survey was adjusted to
-accurately represent the likely electorate, enhancing the overall
-validity of the findings.
+New York Times using the R survey package and involved multiple
+adjustments. Siena’s weighting process involved adjusting samples for
+unequal selection probabilities and turnout likelihood, based on 2020
+data. Further adjustments aligned the sample with likely electorate
+targets from the L2 voter file. The final weight combined modeled
+turnout (80%) and self-reported intentions (20%), mitigating nonresponse
+bias and ensuring the sample accurately reflected the characteristics
+and behaviors of likely voters, thereby enhancing result validity.
 
@@
 
-The questionnaire is crafted to be concise and straightforward,
-effectively minimizing respondent fatigue and maximizing clarity in
-question phrasing. This design is essential for maintaining participant
-engagement, especially in surveys that may include a wide array of
-questions. Additionally, the use of a mix of closed and open-ended
-formats allows for a comprehensive analysis of voter sentiment.
-Closed-ended questions yield quantifiable data, enabling researchers to
-identify trends and patterns, while open-ended questions provide rich
-qualitative insights that contextualize these trends.
-
-The careful structuring of questions also plays a crucial role in
-reducing moderacy bias, where respondents might lean towards neutral
-options when unsure. By providing clear response categories, the
-questionnaire encourages participants to express their opinions more
-decisively. For each of the degree question, Siena designed at least 4
-options to help the respondents not only choose extreme or moderate
-answer in the question.
-
-Furthermore, the inclusion of diverse question types can mitigate
-acquiescence bias, which occurs when respondents habitually agree with
-statements instead of reflecting their true feelings. By framing
-questions in a balanced manner and avoiding leading language, the design
-helps ensure that participants feel comfortable expressing varied
-opinions.
+The questionnaire is concise and straightforward, reducing respondent
+fatigue and enhancing clarity, which is crucial for maintaining
+engagement. By incorporating both closed- and open-ended questions, it
+allows for both quantifiable data and rich qualitative insights. Clear
+response categories help reduce moderacy bias, encouraging participants
+to choose decisively rather than defaulting to neutral answers.
+Additionally, varied question types help mitigate acquiescence bias by
+encouraging honest responses and avoiding leading language.
 
@@
 
-However, the questionnaire is not without its weaknesses. Critics
-highlight that the reliance on agree-disagree, yes-no formats can lead
-to acquiescence bias, where respondents might select favorable options
-rather than accurately expressing their true opinions. This tendency
-skews the results, potentially misrepresenting genuine voter sentiment
-and leading to misleading conclusions.
-
-Moreover, the questionnaire may not adequately address the nuances that
-are important to specific demographic groups, resulting in potential
-gaps in understanding voter motivations. For instance, certain groups
-may have distinct issues or concerns that are not adequately captured by
-the survey's questions. This limitation can contribute to nonresponse
-bias, where individuals from underrepresented groups choose not to
-participate or drop out of the survey, further skewing the results.
-
-Additionally, since we don’t know whether they use randomization when
-interviewers ask the respondents, there might be response order bias
-with the occurrence of recency effect, in which respondents choose one
-of the last items presented to them ( as telephone survey is orally
-presented surveys). This bias can be exacerbated by the order of
-response options in a list or a rating scale influences the response
-chosen [@survey].
-
-Furthermore, as the questionnaire hasn't been provided, we haven't found
-an assured of complete anonymity in the survey landing and consent page
-(record of interviewers' words) in the posted questionnaire. This might
-cause social desirability bias, which typically stems from the desire of
-respondents to avoid embarrassment and project a favorable image to
-others, resulting in respondents not revealing their actual attitudes.
-Thus Siena cannot get the true polls from their sample.
-
-Finally, we noticed that the questionnaire is quite long, with more than
-50 questions. It will significantly increase the attribution rate of the
-questionnaires, especially in a telephone survey which takes more time
-than the online panel. This will increase the possibility of the
-occurrence of non-response bias.
-
-In summary, the questionnaire exhibits strengths such as clarity and a
-mixed-format approach that promotes engagement and nuanced responses.
-However, it faces significant challenges related to biases including
-acquiescence, nonresponse, social desirability, and ordering effects. To
-enhance its effectiveness, future iterations should incorporate a
-broader range of question types, ensure demographic representation, and
-carefully consider question order and phrasing. Addressing these issues
-is crucial for minimizing bias and improving the overall validity of the
-findings.
-
-# Idealized Methodology for US Presidential Election Forecast
+However, the questionnaire has some limitations. Its reliance on
+agree-disagree and yes-no formats may increase acquiescence bias, as
+respondents may lean toward favorable answers. Furthermore, some
+demographic nuances may be inadequately addressed, potentially leading
+to nonresponse bias from underrepresented groups. The risk of response
+order bias is also present, especially if randomization of options is
+not implemented, increasing the chance of recency effects in
+verbally-administered surveys.
+
+Additionally, the absence of assured anonymity could lead to social
+desirability bias, where respondents alter answers to project a
+favorable image. Lastly, with over 50 questions, the length of the
+survey may increase dropout rates, especially in time-intensive formats
+like telephone surveys, thereby raising nonresponse bias.
+
+In summary, while the questionnaire is clear and well-structured, it
+faces challenges from potential biases including acquiescence,
+nonresponse, social desirability, and order effects. Future improvements
+should focus on diversifying question types, ensuring demographic
+inclusivity, and refining question phrasing to reduce bias and enhance
+validity.
+
+# Idealized Methodology for US Presidential Election Forecast {#appendix-d}
 
@@
 To ensure a representative sample of likely voters, I will employ a
-Composite Measure sampling method based on past voter turnout data from
+Composite Measure sampling method based on past ballots cast data from
 the 2020 U.S. elections. After determining the sample size for each
@@
 have 1 million eligible voters, State B consistently shows a higher
-voter turnout in past elections. Therefore, we will increase the
+ballots cast in past elections. Therefore, we will increase the
 proportion of polls conducted in State B. In this scenario, State A has
@@
 have an equal chance of being selected for polls: 50% for State A and
-50% for State B. However, by incorporating voter turnout, we modify
-these probabilities to increase the likelihood of selecting State B due
-to its higher historical turnout.
-
-In the subsequent steps, we will detail how to utilize **voter turnout**
+50% for State B. However, by incorporating ballots cast, we modify these
+probabilities to increase the likelihood of selecting State B due to its
+higher historical turnout.
+
+In the subsequent steps, we will detail how to utilize **ballots cast**
 as a crucial factor in creating a **composite measure of size** for
@@
 
-We begin by collecting the **eligible voter population** and
-**historical voter turnout rates** for different states. In this
-simplified example, we will focus on two states: **State A** and **State
-B**.
-
-| State   | Eligible Voters | Turnout Rate |
+We begin by gathering data on the **eligible voter population** and
+**historical ballots cast** for different states. For simplicity, we'll
+focus on two states: **State A** and **State B**.
+
+| State   | Eligible Voters | Ballots Cast |
 |---------|-----------------|--------------|
-| State A | 1,000,000       | 50%          |
-| State B | 1,000,000       | 70%          |
-
-### Step 2: Calculate Actual Voters
-
-Next, we calculate the **number of actual voters** in each state by
-multiplying the eligible voters by the turnout rate:
-$$\text{Actual Voters} = \text{Eligible Voters} \times \text{Turnout Rate}$$\
-Actual voters in State A:
-$\text{Actual Voters}_A = 1,000,000 \times 0.50 = 500,000$\
-Actual voters in State B:
-$\text{Actual Voters}_B = 1,000,000 \times 0.70 = 700,000$\
-Total actual voters:
-$\text{Actual Voters}_A+\text{Actual Voters}_B= 500,000 + 700,000 = 1,200,000$\
+| State A | 1,000,000       | 500,000      |
+| State B | 1,000,000       | 700,000      |
+
+### Step 2: Calculate Total Ballots Cast
+
+The **total ballots cast** across both states is the sum of ballots cast
+in each state:
+
+Total Ballots Cast = $Ballots Cast_A$ + $Ballots Cast_B$
+
+Total Ballots Cast= 500,000 + 700,000 = 1,200,000
 
@@
 
-We now calculate the **total number of voters** across both states and
-determine the **proportion** of each state's turnout relative to the
-total. This forms the basis of the composite measure of size, which we
-will use to adjust the sampling weights.
-
-The total voters in two states are 1,200,000. Therefore, the sampling
-proportion for State A is:
-$\text{Sampling Proportion}_A = \frac{500,000}{1,200,000} \approx 0.417$,
-and for State B is:
-$\text{Sampling Proportion}_B = \frac{700,000}{1,200,000} \approx 0.583$
-
-### Step 4: Allocate Sample Based on Turnout
-
-Finally, we allocate the sample size according to the calculated
-sampling proportions. For instance, if we are conducting 1,000 polls, we
-would allocate State A with
-$\text{Polls for State A} = 1,000 \times 0.417 \approx 417 \text{polls}$
-and State B with
-$\text{Polls for State B} = 1,000 \times 0.583 \approx 583 \text{polls}$
-
-By using historical voter turnout to adjust our polling sample, we
-ensure that regions with higher voter engagement have a greater
-influence on the polling results. This composite measure of size ensures
-that our polling sample better reflects the actual voting patterns and
-preferences in different regions. Consequently, we can produce more
-accurate and representative poll outcomes that account for the varying
-levels of voter participation across the country.
+Using the total ballots cast across both states, we calculate the
+**proportion** of each state’s ballots relative to the total. This
+proportion serves as the composite measure of size, which will guide our
+sample allocation.
+
+For State A:
+
+$\text{Sampling Proportion_A}$ =
+$\frac{500,000}{1,200,000} \approx0.417$
+
+For State B:
+
+$\text{Sampling Proportion_B}$ =
+$\frac{700,000}{1,200,000} \approx0.583$
+
+### Step 4: Allocate Sample Based on Ballots Cast
+
+Finally, we allocate the sample size according to these calculated
+sampling proportions. For example, if conducting 1,000 surveys, the
+allocation would be:
+
+-   **Polls for State A**:
+
+\$ \text{Polls for State A} = 1,000 \times 0.417 \approx 417\$
+
+-   **Polls for State B**:
+
+$\text{Polls for State B} = 1,000 \times 0.583 \approx 583$
+
+By using the number of ballots cast, we ensure that the sample
+allocation reflects historical voting participation, giving each state
+an influence proportional to its voter turnout in previous elections.
+
+By using historical ballots cast to adjust our polling sample, we ensure
+that regions with higher voter engagement have a greater influence on
+the polling results. Consequently, we can produce more accurate and
+representative poll outcomes that account for the varying levels of
+voter participation across the country.
 
@@
 
-After determining the number of respondents to be sampled from each
-region, stratified sampling will be employed across key demographic
-categories, including age, gender, race/ethnicity, and education level.
-This approach ensures that the final sample accurately reflects the
-diversity of the U.S. voting population by proportionally representing
-each subgroup within every region. To mitigate potential non-response
-bias, post-stratification weighting\[\^2\] will be applied, correcting
-for any imbalances caused by variations in response rates among
-different demographic groups. The sample will be stratified based on
-several critical demographic and geographic variables to guarantee
-proportional representation of the U.S. voting population. Strata
-information will be sourced from U.S. census data obtained through IPUMS
-USA [@ruggles2024ipums].
-
-\[\^2\]: Post-stratification weighting adjusts survey data by applying
-weights to under- or over-represented demographic groups in the sample,
-ensuring the final results align with the true population distribution
-and reducing biases such as non-response bias.
-
-These variables include age, with categories such as 18-24 (12%), 25-34
-(17%), 35-44 (16%), 45-54 (16%), 55-64 (16%), and 65+ (23%); gender,
-split into male (48%), female (52%), and non-binary/other (less than
-1%); and race/ethnicity, covering groups like White/Caucasian (67%),
-Black/African American (13%), Hispanic/Latino (13%), Asian/Pacific
-Islander (5%), Native American/Alaskan Native (1%), and Other/Mixed Race
-(1%). Additionally, education level will be stratified into high school
-diploma or less (36%), some college, no degree (17%), Associate’s degree
-(9%), Bachelor’s degree (23%), and graduate or professional degree
-(15%). Geographic region will also be a key factor, ensuring
-representation from the Midwest (21%), Northeast (17%), South (38%), and
-West (24%). For each variable, U.S. Census or voter turnout data will be
-used to proportionally allocate respondents, ensuring that the final
-sample closely mirrors the demographic and regional composition of the
-actual voting population. Post-stratification weighting will be applied
-to adjust for any imbalances that may occur during data collection.
+After determining the sample size for each region, we will use
+stratified sampling across key demographic categories, such as age,
+gender, race/ethnicity, and education level. This method ensures that
+our final sample proportionally represents each subgroup within every
+region, accurately reflecting the diversity of the U.S. voting
+population. To achieve this, the sample will be stratified according to
+critical demographic and geographic variables, with strata information
+sourced from U.S. Census data available through IPUMS USA
+[@ruggles2024ipums].
 
@@
 
-We plan to survey 300 respondents, which will provide a margin of error
-of approximately ±1.7 percentage points, ensuring a high level of
-confidence in the results. Given the limited sample size and to enhance
-the effectiveness of stratified sampling, the states will be grouped
-into four regions: Midwest, Northeast, South, and West. The sample size
-for each region will be allocated based on the proportion of total
-ballots cast in each region during the 2020 election. The regional
-grouping of states is shown in @tbl-region.
+We plan to survey 400 respondents. To optimize the limited sample size
+and enhance the stratified sampling approach, we will group states into
+four regions: Midwest, Northeast, South, and West. Sample sizes for each
+region will be allocated according to the proportion of total ballots
+cast in each region during the 2020 election. This regional allocation
+ensures representative sampling while aligning with past voting
+patterns, as outlined in @tbl-region.
 
@@
 |--------------------------|----------------------------------------------|
-| **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
-| **NORTHEAST** | Connecticut, Delaware, District of Columbia, Maine, Maryland, Massachusetts, New Hampshire, New Jersey, New York, Pennsylvania, Rhode Island, Vermont      |
-| **SOUTH**     | Alabama, Arkansas, Florida, Georgia, Kentucky, Louisiana, Mississippi, North Carolina, Oklahoma, South Carolina, Tennessee, Texas, Virginia, West Virginia |
-| **WEST**      | Alaska, Arizona, California, Colorado, Hawaii, Idaho, Montana, Nevada, New Mexico, Oregon, Utah, Washington, Wyoming                                       |
+| Midwest    | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
+| Northeast  | Connecticut, Delaware, District of Columbia, Maine, Maryland, Massachusetts, New Hampshire, New Jersey, New York, Pennsylvania, Rhode Island, Vermont      |
+| South      | Alabama, Arkansas, Florida, Georgia, Kentucky, Louisiana, Mississippi, North Carolina, Oklahoma, South Carolina, Tennessee, Texas, Virginia, West Virginia |
+| West       | Alaska, Arizona, California, Colorado, Hawaii, Idaho, Montana, Nevada, New Mexico, Oregon, Utah, Washington, Wyoming                                       |
 
@@
 
-| **Region**    | **Voter Turnout (%)** | **Total Ballots Cast** | **VEP**    | **Composite Measure Sampling Proportion** | **Sample Size** |
-|------------|------------|------------|------------|------------|------------|
-| **MIDWEST**   | 69%                   | 35,134,960             | 50,932,439 | 0.214805579                               | 86              |
-| **NORTHEAST** | 68%                   | 32,262,303             | 47,473,317 | 0.200216867                               | 80              |
-| **SOUTH**     | 65%                   | 54,746,770             | 84,563,831 | 0.356644666                               | 143             |
-| **WEST**      | 69%                   | 37,594,304             | 54,139,892 | 0.228332888                               | 91              |
+| **Region** | **Total Ballots Cast** | **VEP**    | **Composite Measure Sampling Proportion** | **Sample Size** |
+|---------------|---------------|---------------|---------------|---------------|
+| Midwest    | 35,134,960             | 50,932,439 | 0.214805579                               | 86              |
+| Northeast  | 32,262,303             | 47,473,317 | 0.200216867                               | 80              |
+| South      | 54,746,770             | 84,563,831 | 0.356644666                               | 143             |
+| West       | 37,594,304             | 54,139,892 | 0.228332888                               | 91              |
 
@@
 Composite Measure Sampling Proportion based on 2020 US Election regional
-voter turnout (%) {#tbl-samplesize}
+ballots cast {#tbl-samplesize}
 
 @tbl-samplesize shows the regional breakdown of the 2020 election data,
-sourced from [@wikivote], including voter turnout, total ballots cast,
-and Voting Eligible Population (VEP). The sample size for each region
-shown in @tbl-samplesize was determined based on the **Composite Measure
-Sampling Proportion**.
+sourced from [@wikivote], including total ballots cast, and Voting
+Eligible Population (VEP). The sample size for each region shown in
+@tbl-samplesize was determined based on the **Composite Measure Sampling
+Proportion**.
 
@@
 
-Due to budget constraints, we will focus on online recruitment methods,
-which offer a cost-effective and efficient way to reach a diverse and
-representative sample of voters across the country.
-
-Online Recruitment: With the objective of surveying 400 respondents, we
-will focus our resources on implementing the survey and ensuring
-high-quality data collection. The survey will be developed in-house, and
-respondents will be recruited using online survey platforms. The
-recruitment approach is as follows:
-
-Sample Size Distribution Across Platforms
-
-Online Panel Providers (Qualtrics, YouGov): 200 respondents will be
-recruited through reputable online panel providers like Qualtrics and
-YouGov, known for high-quality samples with verified voter registration
-status. This recruitment source provides a strong base of quality data,
-given the stringent participant verification process in place.
-
-Social Media Recruitment: We plan to recruit 400 respondents through
-targeted social media panels on platforms such as Facebook and
-Instagram. Given the typically lower data quality from social media
-recruitment, we anticipate that 50% of responses may be invalid. To
-compensate, we will oversample from this group, aiming to gather a
-sufficient number of valid and high-quality responses. To attract
-participants, each respondent will receive a small monetary reward (such
-as a gift card) for completing the survey. Targeted ads and eligibility
-screening will be used to reach respondents who meet key criteria, such
-as age and U.S. voter registration status. This approach helps ensure
-that those recruited are likely to be eligible voters.
+To maximize our budget, we will concentrate on online recruitment
+methods, which provide a cost-effective and efficient means of reaching
+a diverse and representative sample of voters nationwide.
+
+Online Recruitment Strategy: Aiming for a total of 400 respondents, we
+will focus our resources on survey implementation and high-quality data
+collection, developing the survey in-house and recruiting participants
+through online survey platforms.
+
+Online Panel Providers (Qualtrics, YouGov): We will recruit 200
+respondents via reputable panel providers like Qualtrics and YouGov.
+These platforms ensure high-quality samples by verifying voter
+registration, offering a solid foundation of reliable data due to their
+strict participant verification protocols.
+
+Social Media Recruitment: An additional 400 respondents will be
+recruited through targeted ads on platforms like Facebook and Instagram.
+Given the typically lower data quality from social media sources, we
+anticipate that about 50% of responses may be invalid, and we will
+oversample accordingly to secure a sufficient number of valid responses.
+To incentivize participation, respondents will receive a small monetary
+reward, such as a gift card, upon survey completion. We will also use
+targeted ads and eligibility screening (e.g., age and U.S. voter
+registration status) to ensure that respondents are likely to be
+eligible voters.
 
@@
 Nonresponse bias occurs when participants are unwilling or unable to
-respond to specific questions or complete the entire survey. For
-example, since our survey takes about 15 minutes to finish, there is a
-potential for nonresponse bias to arise. To address this concern, as
-highlighted by @surveymonkey, we strive to establish clear expectations
-regarding the survey's objectives and the estimated time required for
-completion. Furthermore, we utilize post-stratification, which changes
-the survey weights to make sure the group that answered fits well with
-the actual population characteristics [@surveylab].
+answer certain questions or complete the survey. Given that our survey
+takes approximately 15 minutes to complete, there is a risk of
+nonresponse bias. To mitigate this,as highlighted by @surveymonkey, we
+set clear expectations about the survey's purpose and estimated
+completion time, encouraging participants to stay engaged. Additionally,
+we apply post-stratification, adjusting survey weights to ensure that
+our respondent group aligns closely with the actual population
+characteristics, reducing bias and improving representativeness
+[@surveylab].
 
@@
 
-To ensure high data quality and accuracy, respondent validation will be
-conducted through multiple checks and verification processes. This
-process ensures that only eligible and relevant participants are
-included in the survey, maintaining the integrity of the sample.
-
-Voter Registration Verification:
-
-Respondents will be required to confirm their voter registration status,
-with a portion of the sample cross-referenced against voter registration
-databases or verified through reputable online panel providers like
-Qualtrics or YouGov. This step ensures that the survey includes only
-registered and likely voters, crucial for representing the target
-population accurately. Screening and Eligibility Questions:
-
-Respondents will complete a set of screening questions to verify
-eligibility criteria, such as age (18 or older) and U.S. citizenship.
-Only those meeting these criteria will be allowed to proceed with the
-survey. Attention Checks:
-
-To detect and filter out inattentive or disengaged participants,
-attention-check questions will be embedded throughout the survey (e.g.,
-asking respondents to select a specific answer to verify attentiveness).
-Respondents who fail these checks may be excluded from the final sample.
-Duplicate Prevention:
-
-Unique identifiers such as IP addresses and email addresses will be
-tracked to prevent multiple submissions from the same individual,
-ensuring that each response represents a unique participant. Post-Survey
-Data Cleaning:
-
-After data collection, responses will be reviewed for consistency and
-completeness. Inconsistent responses or incomplete surveys will be
-removed, maintaining the quality and reliability of the dataset. By
-implementing these respondent validation steps, the survey methodology
-ensures that data collected reflects only eligible, registered, and
-attentive respondents, thereby enhancing the validity and accuracy of
-the survey results.
+To ensure high data quality and accuracy, we will conduct rigorous
+respondent validation through several verification steps, ensuring only
+eligible and relevant participants are included. Respondents will
+confirm their voter registration status, with a portion cross-referenced
+against voter databases or verified via reliable panel providers like
+Qualtrics and YouGov, thus focusing the survey on registered and likely
+voters. Eligibility will also be confirmed through screening questions
+verifying age (18+) and U.S. citizenship, allowing only those who meet
+these criteria to proceed. Attention-check questions embedded throughout
+the survey will filter out inattentive participants, with non-compliant
+responses excluded from the final sample. Additionally, unique
+identifiers such as IP and email addresses will be tracked to prevent
+duplicate submissions, ensuring each response is unique. Finally,
+post-survey data cleaning will address any inconsistent or incomplete
+responses to maintain dataset reliability. These validation steps are
+essential for producing data that accurately reflects the opinions of
+eligible, registered, and attentive respondents, thereby enhancing the
+survey's overall validity.
 
@@
 
-After getting the survey response, we will aggregate polls from two
-recruitment sources: online panel providers and social media
-platforms.To weight the two panels effectively, we will first identify
-key demographic variables for stratification, such as age, gender,
-race/ethnicity, and education level, and establish population
-proportions using U.S. Census data or other reliable sources. For the
-online panel (200 respondents), we will compare the demographic
-distribution of respondents to these population benchmarks, calculating
-weights based on the degree of under- or over-representation. Similarly,
-we will perform this analysis for the social media panel (400
-respondents) to determine its weights. Once we have calculated weights
-for each panel, we will combine them into a single weighting scheme that
-reflects the overall demographic composition of the target population.
-During data analysis, we will apply these weights to the responses,
-ensuring that underrepresented groups have a greater influence on the
-results while adjusting for those that are overrepresented. Finally, we
-will conduct post-stratification adjustments to confirm that the
-combined sample accurately mirrors the true characteristics of the U.S.
-voting population, providing reliable insights into voter preferences
-and behaviors.
+After collecting survey responses, we will aggregate data from our two
+recruitment sources: online panel providers and social media platforms.
+To weight these panels accurately, we’ll first identify key demographic
+variables (e.g., age, gender, race/ethnicity, education level) and
+establish population benchmarks using U.S. Census data
+[@ruggles2024ipums]. For the online panel (200 respondents) and social
+media panel (400 respondents), we will calculate weights by comparing
+each panel's demographic distribution to these benchmarks, adjusting for
+under- and over-represented groups.
+
+Once individual weights are calculated for each panel, we will integrate
+them into a single weighting scheme that aligns with the target
+population's demographic makeup. These weights will then be applied
+during data analysis, allowing underrepresented groups to have an
+appropriate influence on the results. Finally, we’ll conduct
+post-stratification adjustments to ensure that the combined sample
+accurately reflects the U.S. voting population, yielding reliable
+insights into voter preferences and behaviors.
 
@@
 
-Addressing Extreme/Moderacy Bias: We customize the scale and response
-options with differentiated alternatives. Three-point answer scales can
-lead to extreme response bias or moderacy bias due to insufficient
-options. Therefore, for every scale question, we designed at least five
-response options, which reduces the likelihood of respondents choosing
-the middle answers because of a lack of alternatives.
-
-Mitigating Response Order Bias: We implement a solution involving
-seemingly open-ended questions and randomizing the order of response
-options for unordered (nominal) questions. For ordinal questions, we
-invert the order. For example, instead of asking, "Will you choose
-candidate A or candidate B?" we ask, "Who would you vote for? \[pause\]
-Candidate A or Candidate B?" Additionally, using Google Forms, we
-randomize the order of options for all unordered questions to further
-reduce response order bias.
-
-Minimizing Social Desirability Bias (SDB): Given that our survey is
-conducted online, we employ a minimized SDB format. A recommended
-strategy for recruiting respondents is to provide only basic information
-about the survey's purpose at the outset, which engages participants
-without overwhelming them. Therefore, in the introduction, we state that
-the survey aims for academic research in Statistics, omitting details
-about our affiliations or the specific use of the data. We simply inform
-participants that, "This survey is for nonpartisan researchers in
-academic research in Statistics." At the end of the survey, we include a
-feedback section to gauge attitudes toward the surveyor or entity.
-
-Ensuring Anonymity (Minimizing SDB): The complete anonymity of
-respondents is a crucial aspect of our survey. We guarantee this
-anonymity as stated on the survey landing and consent page. Before
-sensitive questions, we will reinforce that all answers are confidential
-and anonymous, reminding participants of their privacy. We will
-strategically place sensitive items within the survey to minimize the
-risk of social desirability bias (SDB).
-
-Reducing Acquiescence Bias: To tackle acquiescence bias, we avoid
-agree-disagree, true-false, and yes-no question formats. Instead of
-using agree-disagree questions, we formulate inquiries that utilize
-direct, item-specific scales tailored to the question. For instance,
-when asking for respondents' views on candidates, we use options like
-"very unfavorable, unfavorable, moderate, favorable, very favorable"
-instead of simple yes or no. Furthermore, we ensure that our questions
-offer answer options that encompass all possible views. For example, in
-the question "Do you approve or disapprove of the job Joe Biden is doing
-as President?", we provide the options "Approve, Disapprove, Neutral or
-no opinion" rather than just yes or no.
+Addressing Extreme/Moderacy Bias: We use a minimum of five response
+options for scale questions to provide more nuanced choices, reducing
+the likelihood of respondents defaulting to extreme or middle answers.
+
+Mitigating Response Order Bias: For nominal questions, we randomize
+response options, and for ordinal questions, we vary the order.
+Open-ended formats and pauses (e.g., "Who would you vote for? \[pause\]
+Candidate A or Candidate B?") further minimize order effects.
+
+Minimizing Social Desirability Bias (SDB): Our online survey format and
+minimal introductory information (only stating it’s for academic
+research in Statistics) reduce SDB. We guarantee respondent anonymity on
+the survey landing page and before sensitive questions, reminding
+participants that all answers are confidential. Additionally, a feedback
+section at the end allows respondents to express any concerns.
+
+Reducing Acquiescence Bias: We avoid agree-disagree formats, instead
+using direct scales (e.g., "very unfavorable" to "very favorable") and
+item-specific options (e.g., "Approve, Disapprove, Neutral") to capture
+a full range of views.
 
@@
 
-Survey Design and Development: \$2,000 This portion covers the design
-and development of the survey, including question formatting, testing,
-and integration with online platforms like Qualtrics and social media
-platforms. Ensuring the survey is user-friendly and addresses key
-research questions is essential for high-quality data collection. Online
-Panel Providers (Qualtrics, YouGov): \$80,000 (200 respondents at \$400
-per respondent) We will recruit 100 respondents via reputable online
-panel providers like Qualtrics and YouGov. These platforms ensure
-high-quality responses through verified voter registration, but they
-come at a higher cost per respondent due to their validation processes.
-
-Social Media Recruitment (Facebook, Instagram): \$12,000 (400
-respondents at \$30 per respondent) 400 respondents will be recruited
-using targeted social media ads. Since we expect 50% of responses to be
-invalid, oversampling will allow us to achieve a final valid sample of
-200 respondents. The cost per respondent is lower than online panel
-providers, but rigorous validation and filtering are required to ensure
-data quality.
-
-Data Validation and Quality Control: \$6,000 This covers voter
-registration verification, attention checks within the survey, and
-extensive post-collection filtering, particularly for social media
-responses. Ensuring the integrity and accuracy of the data is crucial to
-minimize biases and errors.
+Survey Design and Development: \$2,000 Covers question formatting,
+testing, and online integration (e.g., Qualtrics) to ensure
+user-friendly and relevant survey design.
+
+Online Panel Providers (Qualtrics, YouGov): \$80,000 200 respondents
+recruited at \$400 each, leveraging verified voter panels for
+high-quality data.
+
+Social Media Recruitment (Facebook, Instagram): \$12,000 400 respondents
+recruited via targeted ads (\$30 each). Anticipating a 50% invalid rate,
+allowing for 200 valid responses after validation.
+
+Data Validation and Quality Control: \$6,000 Includes voter registration
+checks, attention filters, and post-collection quality review,
+especially for social media responses, to ensure data integrity.
 
@@
 
-1.  **Do you approve or disapprove of the job Joe Biden is doing as
-    President?**
-
-    -   Approve
-    -   Disapprove
-    -   Neutral or no opinion
-
-2.  **What is your party registration or affiliation?**
+## Survey Questions
+
+1.  **What is your party registration or affiliation?**
 
@@
     -   Republican
-    -   Independent/ Other
+    -   Independent/Other
     -   Prefer not to say
@@
 
-3.  **If the Presidential Election were held today, would you vote for
+2.  **If the Presidential Election were held today, would you vote for
     Kamala Harris or Donald Trump?**
@@
 
-4.  **Although you are undecided, which candidate do you lean
-    toward?**(Jump to this question only if responders choose undecided
-    in Question 3)
+3.  **Although you are undecided, which candidate do you lean toward?**
+    (Only answer if you chose "Undecided" in Question 2)
 
@@
 
-5.  **How favorable are you towards the following candidates?**
+4.  **How favorable are you towards the following candidates?**
 
@@
 
-6.  **How likely are you going to vote in the 2024 election**
-
-    Definitely not to vote
+5.  **How likely are you going to vote in the 2024 election?** (1 = Definitely
+    not to vote, 10 = Definitely will vote)
 
@@
     -   9
-    -   10 Definitely will vote
-
-7.  **How do you plan to cast your vote?**
+    -   10
+
+6.  **How do you plan to cast your vote?**
 
@@
 
-8.  **Did you vote in the 2020 U.S. presidential election?**
+7.  **Did you vote in the 2020 U.S. presidential election?**
 
@@
 
-9.  **If you voted in 2020, who did you vote for?**
+8.  **If you voted in 2020, who did you vote for?**
 
@@
 
-10. **Imagine the following candidates: Candidate A favors cutting taxes
+9.  **Imagine the following candidates: Candidate A favors cutting taxes
     but has a weak stance on climate change, and Candidate B focuses on
-    healthcare but supports increased military spending.Who would you
-    vote for? Candidate A or Candidate B?**
+    healthcare but supports increased military spending. Who would you
+    vote for?**
 
@@
 
-11. **Imagine two candidates: Candidate A supports education reform but
-    plans to cut social security, and Candidate B focuses on green
-    energy but raises taxes. Who would you vote for? Candidate A or
-    Candidate B?**
-
-    -   Candidate A
-    -   Candidate B
-
-12. **What do you think is the most important issue facing the United
-    States?**
+10. **What do you think is the most important issue facing the United
+    States?** [Select at most 3]
 
@@
 
-13. **Select option 3 from the list below:**
+11. **Select option 3 from the list below:**
 
@@
 
-14. **How important is the economy in deciding your vote?**
-
-    Not important
-
-    -   1
-    -   2
-    -   3
-    -   4
-    -   5 Very important
-
-15. **How important is climate change in deciding your vote?**
-
-    Not important
-
-    -   1
-    -   2
-    -   3
-    -   4
-    -   5 Very important
-
-16. **How important is healthcare in deciding your vote?**
-
-    Not important
-
-    -   1
-    -   2
-    -   3
-    -   4
-    -   5 Very important
-
-17. **How closely are you following news about the 2024 U.S.
-    presidential election?**
-
-    -   Very closely
-    -   Somewhat closely
-    -   Not closely
-
-18. **Which social media platforms do you use to get political news?**
+12. **Which social media platforms do you use to get political news?**
     (Select all that apply)
@@
     -   Graduate degree
-6.  **What is your household annual income level?**
-    -   Less than \$50,000
-    -   \$50,000 - \$100,000
-    -   Over \$100,000
-    -   Prefer not to say
 

### 2024-11-01 paper/paper.qmd
update paper

@@
 trump_data <- read_parquet(here::here("data", "02-analysis_data", "analysis_data_Trump.parquet"))
+####### Model ######
+harris_unweighted_model <- readRDS(here::here("models", "model_harris_unweighted.rds"))
+harris_weighted_model <- readRDS(here::here("models", "model_harris_weighted.rds"))
+trump_unweighted_model <- readRDS(here::here("models", "model_trump_unweighted.rds"))
+trump_weighted_model <- readRDS(here::here("models", "model_trump_weighted.rds"))
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+trump_data<-trump_data |>mutate(candidate="Trump")
+harris_data<-harris_data|>mutate(candidat="Harris")
+combined_data_total<-bind_rows(harris_data,trump_data)
+combined_data_total<-combined_data_total|>
+  mutate(
+    sample_size_weight = pmin(sample_size / 2300, 1),
+    recency_weight = exp(-recency * 0.1),
+    combined_weight = recency_weight * sample_size_weight
+  ) 
 ```
@@
 
-The structure of this paper is organized as follows: @third-data provides
-details on the data sources and variables used in our analysis.
-@forth-model explains the modeling approach, including the assumptions and
-specifications of our linear regression framework. In @fifth-results, we
-present our findings, emphasizing the key predictors of Harris's
-support. Finally, @sixth-discussion explores the implications of our
-results and suggests potential directions for future research.
-@appendix-a provide external data detail, @appendix-b provide model detail, @appendix-c provide a exploration for pollster methodology, @appendix-d provide a idealized methodology.
+The structure of this paper is organized as follows: @third-data
+provides details on the data sources and variables used in our analysis.
+@forth-model explains the modeling approach, including the assumptions
+and specifications of our linear regression framework. In
+@fifth-results, we present our findings, emphasizing the key predictors
+of Harris's support. Finally, @sixth-discussion explores the
+implications of our results and suggests potential directions for future
+research. @appendix-a provide external data detail, @appendix-b provide
+model detail, @appendix-c provide a exploration for pollster
+methodology, @appendix-d provide a idealized methodology.
 
@@
 
-## Model{#forth-model}
-
-We conducted a regression analysis to predict support for Kamala Harris
-and Donald Trump in the 2024 U.S. presidential election, including
-models for Trump for comparison. Our analysis includes four models:
-**unweighted linear models** and **weighted linear models** for both
-candidates. These models predict each candidate’s support as a
-continuous outcome across different states, using **pollster**,
-**national poll**, and **population** as key predictors. The weighted
-models additionally incorporate adjustments for recency, sample size,
-and poll quality to account for potential biases. This setup aligns with
-the New York Times methodology for election polling, which assigns
-weights based on poll quality, sample size, and recency to better
-reflect voter sentiment [@nyt_polling_averages].
-
-The validation and diagnostic details of the model are provided in
-[Appendix B](#sec-model-details)
-
-## Model Set-up
-
-We implemented our linear regression models using the `lm()` function in
-R.
-
-### Mathematical Expressions
-
-Both the unweighted and weighted models share the same mathematical
-expression format:
-
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-harris_unweighted_model <- readRDS(here::here("models", "model_harris_unweighted.rds"))
-harris_weighted_model <- readRDS(here::here("models", "model_harris_weighted.rds"))
-trump_unweighted_model <- readRDS(here::here("models", "model_trump_unweighted.rds"))
-trump_weighted_model <- readRDS(here::here("models", "model_trump_weighted.rds"))
-```
+## Model {#forth-model}
+
+Our modeling approach aims to quantify the relationship between various
+polling metrics and the percentage of support for each candidate, Kamala
+Harris and Donald Trump. For this analysis, we employ a linear model
+(LM) to examine how factors such as national polling trends, poll
+quality scores, and population size influence support percentages. The
+model is implemented using the `lm` function in R, with a Gaussian
+distribution to capture the variability in support rates.
+
+In this analysis, we use predictors that capture both the methodological
+quality and structural aspects of each poll. Specifically, we include
+variables such as `national_poll`, which reflects national support
+trends; `pollster`, which represents differences in methodology and
+reliability across polling organizations; and `population`, which
+accounts for demographic and regional characteristics associated with
+each poll. Our combined weighting approach further integrates factors
+like recency and sample size to ensure that more recent, larger-sample
+polls have a greater impact on the model's predictions, providing a
+balanced and comprehensive assessment of candidate support.
+
+The model assumes that the distribution of support percentage, given
+these polling characteristics, follows a normal distribution. This
+Gaussian assumption enables effective parameter estimation, a standard
+approach in linear regression. By applying moderate priors, we balance
+interpretability with the model’s stability, allowing us to assess the
+impact of polling characteristics on candidate support with greater
+reliability.
+
+### 3.1 Model Set-Up
+
+The model predicts Harris's support percentage using the following
+predictor variables:
+
+-   **National Poll (`national_poll`)**: Represents the national trend
+    in support for the candidate.
+-   **Pollster (`pollster`)**: Categorical variable identifying the
+    organization conducting the poll, accounting for differences in
+    methodology and reliability.
+-   **Population (`population`)**: Reflects demographic or regional
+    characteristics associated with each poll.
 
@@
 polls equally without adjustments for recency, sample size, or poll
-quality:
+quality: The model takes the form:
 
 $$
-\text{Support\_Harris}_i = \beta_0 + \beta_1 \cdot \text{National\_Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \epsilon_i
-$$
-
-#### Weighted Model
-
-The weighted model for Harris incorporates adjustments for recency,
-sample size, and pollster quality:
-
-$$
-\text{Support\_Harris}_i = \beta_0 + \beta_1 \cdot \text{National\_Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \epsilon_i
-$$
-
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-#### Calculate Weights ####
-# Calculate weights for Harris data
-harris_data <- harris_data |>
-  mutate(
-    sample_size_weight = pmin(sample_size / 2300, 1),
-    pollster_quality_weight = numeric_grade / 4,
-    recency_weight = exp(-recency * 0.1)
-  ) |>
-  group_by(pollster) |>
-  mutate(
-    recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) |>
-  ungroup() |>
-  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
-
-# Calculate weights for Trump data
-trump_data <- trump_data |>
-  mutate(
-    sample_size_weight = pmin(sample_size / 2300, 1),
-    pollster_quality_weight = numeric_grade / 4,
-    recency_weight = exp(-recency * 0.1)
-  ) |>
-  group_by(pollster) |>
-  mutate(
-    recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) |>
-  ungroup() |>
-  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
-```
-
-### Coefficient Explanations
-
--   $\beta_0$: Intercept of the model, representing the expected support
-    when all predictors are zero.
--   $\beta_1$: Coefficient for the national poll, indicating how much
-    support changes with a one-unit increase in the national poll
-    percentage.
--   $\beta_2$: Coefficient for the pollster, reflecting the impact of
-    different polling organizations on support.
--   $\beta_3$: Coefficient for the population, accounting for the
-    influence of the demographic context on support levels.
-
-### Model Justification
-
-1.  **Weighted Least Squares Estimation**
-
-In our analysis, we utilize weighted least squares estimation to account
-for the varying quality of polling data. The weights are crucial in the
-estimation process, leading to the following expression for the
-estimates of the coefficients ($\hat{\beta}$):
+y_i | \mu_i, \sigma \sim \text{Normal}(\mu_i, \sigma)
+$$ $$
+\mu_i = \beta_0 + \beta_1 \cdot \text{National Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \epsilon_i
+$$ $$
+\epsilon_i \sim \text{Normal}(0, \sigma^2)$$ Where:
+
+-   $\beta_0$ is the intercept term, representing the baseline level of
+    support.
+-   $\beta_1, \beta_2, \beta_3$ are the coefficients for each predictor,
+    indicating their influence on Harris's support percentage.
+-   $\sigma^2$ is the variance of the error term, representing
+    unobserved variability in support.
+
+The model is executed in R, using the `lm` function for a linear
+regression model. We apply weights based on `combined_weight` to account
+for the importance of each poll, incorporating factors such as recency
+and sample size. This approach helps ensure that more recent and
+reliable polls have a greater influence on the model’s predictions.
+
+### 3.1.1 Weighted Model Explanation
+
+Our model uses a weighted approach to estimate candidate support more
+accurately by emphasizing higher-quality and more recent polls. The
+weighting scheme integrates factors like poll recency, sample size,
+pollster quality, and frequency, as inspired by the New York Times’
+methodology [@nyt_polling_averages] for polling averages.
+
+In this model, weights are applied directly to each poll’s contribution
+in the **Weighted Least Squares (WLS)** estimation process, modifying
+the influence of each poll on the outcome. This results in the following
+expression for the estimated coefficients ($\hat{\beta}$):
 
@@
 
-Where: - $X$ is the design matrix of predictors. - $W$ is the diagonal
-matrix of weights, which incorporates factors such as recency, sample
-size, and pollster quality to enhance the reliability of our estimates.
-
-The weighted model is essential for accurately reflecting voter
-sentiment. By incorporating weights, we adjust for the reliability of
-the polling data, ensuring that more credible polls have a greater
-influence on the estimates.
-
-2.  **Calculation of Variables**:
-
-    -   **Combined Weight**: The combined weight is calculated as
-        follows: $$
-        \text{combined\_weight} = \text{recency\_weight} \times \text{sample\_size\_weight} \times \text{poll\_frequency\_weight} \times \text{pollster\_quality\_weight}
-        $$
-
-    -   **Recency Weight**: This weight uses an exponential decay
-        function: $$
-        \text{recency\_weight} = \exp(-\text{Recency}_i \cdot 0.1)
-        $$ This reflects the diminishing influence of older polls, with
-        $\lambda = 0.1$ for the exponential decay.
-
-    -   **Sample Size Weight**: This weight adjusts the significance of
-        each poll based on the number of respondents, capping the
-        weights at a maximum of 2,300 responses to reflect the
-        reliability of larger sample sizes [@nyt_polling_averages].
-
-    -   **Poll Frequency Weight**: This weight considers how often a
-        pollster conducts polls, with higher weights assigned to
-        pollsters with a greater number of recent surveys.
-
-    -   **Pollster Quality Weight**: Based on the historical performance
-        of the pollster, this weight emphasizes the reliability of their
-        polling methods.
-
-### Alternative Models
-
-While this analysis employs linear regression with weighted least
-squares, alternative methods such as Bayesian modeling could provide
-additional insights. However, we opted for the weighted linear a
-regression approach to maintain interpretability and ease of
-implementation given the scope and resources of this analysis. The
-Bayesian approach was not chosen primarily due to the complexity
-involved in defining priors and the additional computational
-requirements.
-
-### Importance of Combined Weights
-
-By incorporating these combined weights, the weighted model offers a
-more nuanced estimation of voter support for both Harris and Trump.
-While the mathematical expression for the models remains consistent, the
-weighted models effectively adjust for variations in data quality and
-recency, leading to more accurate predictions of voter sentiment.
+Where:
+
+- **Sample Size Weight**: Calculated as the sample size divided by 2300, capped at 1.
+This emphasizes larger, more reliable polls while preventing extremely large samples from disproportionately impacting the analysis.
+
+- **Recency Weight**: Applied through an exponential decay function, `exp(-recency * 0.1)`, where "recency" represents the days since the poll was conducted.
+This ensures that more recent data carries more weight, while older polls have reduced influence.
+
+- **Combined Weight**: The final weight is the product of all individual weights: $$
+\text{Combined Weight} =\text{Recency Weight} \times \text{Sample Size Weight}
+$$.
+This comprehensive weight prioritizes recent, large-sample, high-quality, and moderately frequent polls, creating a balanced and reliable dataset that reflects both current sentiment and credible data sources.
+
+The **combined weight** for each poll is thus:
+
+By incorporating these weights, we adjust the model’s estimates to give
+more importance to recent, credible, and representative polls, enhancing
+the reliability of our predictions.
+
+### 3.1.2 Model Justification
+
+Existing research and political science theories suggest that factors
+such as sample size, recency, pollster reliability, and local
+demographics can significantly impact support percentages for candidates
+like Harris and Trump. Larger sample sizes are generally more reliable,
+while recent polls capture the latest shifts in public opinion. The
+methodology and timing of each poll also play a role: for instance,
+online surveys and telephone interviews may capture different segments
+of the population, and polling conducted during or near key political
+events often reflects more immediate public sentiment. Additionally,
+regional factors, such as local political dynamics or demographic
+characteristics, can influence support patterns.
+
+Our model incorporates a combined weighting scheme inspired by the
+methodology outlined by the New York Times in their election polling
+averages. This weighting system integrates factors like recency and
+sample size, ensuring that more recent and larger-sample polls exert a
+greater influence on our model's predictions. By applying this weighting
+approach, we aim to achieve a balanced and representative dataset that
+reflects up-to-date trends while mitigating potential biases from older
+or smaller-sample polls.
+
+A linear regression model was chosen to predict support percentages
+because the dependent variable is continuous and tends to approximate a
+normal distribution. Linear regression is an accessible and
+interpretable method for assessing how multiple factors contribute to an
+outcome, with each coefficient offering a straightforward interpretation
+of predictor influence. This model framework allows us to quantify the
+effects of various polling characteristics on candidate support.
+
+Further justification for using this model stems from its alignment with
+the central limit theorem, which indicates that, given a sufficiently
+large sample, the distribution of support percentages should approximate
+normality. Moreover, the relationships between predictors like sample
+size and recency align with established theories in political behavior,
+providing a theoretical basis for the model. The linear regression
+approach also reduces the risk of overfitting, enhancing the
+generalizability of our results to a wider set of polling data.
+
+Finally, to ensure the robustness and accuracy of our model, we conduct
+model validation and diagnostics, which are detailed in Appendix B.
+These procedures help confirm that the model assumptions are met and
+that the predictions are reliable across different polling scenarios.
 
@@
 
+## Recent Three Months Support Trends Linear Model Prediction
+
 ```{r}
@@
 #| include: false
+####### Prediction and Plot ######
 set.seed(233)
-
+####### Prediction for Harris ######
 new_data_harris <- data.frame(
@@
 ```
+
 ## Predicted Voting Outcomes for Recent Three Months by Respondent Group
@@
 ```
+
 ## Predicted Voting Outcomes for Recent Three Months by State
@@
 #| layout-ncol: 2
-#| label: fig-support-respondent
+#| label: fig-support-state
 ## unweighted
@@
 
-```{r}
-# Load necessary package
-library(knitr)
-library(kableExtra)
-
-# Example: Assume `predicted_results` is your data frame
-# Ensure column names match this format
-# Example structure:
-# predicted_results <- data.frame(
-#   State = c("Arizona", "California", ...),
-#   Trump_Predicted_Percentage = c(48.94, 33.80, ...),
-#   Electoral_Votes = c(11, 55, ...),
-#   Winner = c("Harris", "Harris", ...)
-# )
-
-# Rename columns to match the desired table format
-colnames(predicted_results) <- c("State", "Harris Predicted %", "Vote Share", "Winner")
-
-# Generate table
-predicted_results %>%
-  kbl(caption = "Prediction Vote share for Trump and Harris", format = "html") %>%
-  kable_styling(full_width = FALSE, position = "center") %>%
-  column_spec(2, width = "5em") %>%
-  column_spec(3, width = "5em") %>%
-  column_spec(4, width = "5em") %>%
-  add_header_above(c(" " = 1, "Trump Predicted %" = 1, "Electoral Votes" = 1, "Winner" = 1))
-
-```
-
 The predicted support for Kamala Harris and Donald Trump in the upcoming
@@
 about 2%.
+
+@fig-national-support-trendsillustrates illustrates the polling support
+trends for Kamala Harris and Donald Trump across the country from August
+to October. The scatter points represent individual poll results, with
+blue for Harris and red for Trump, while each dot's size reflects the
+weight of the poll, accounting for factors like sample size, quality,
+and recency. Harris’s support trend line generally remains above
+Trump’s, with an average support level around 49%, compared to Trump’s
+approximate average of 47% over this period. Toward the end of October,
+both candidates show a slight increase, with Harris’s support reaching
+just over 50% and Trump’s approaching 49%. This trend suggests a
+potential narrowing in support levels as the election approaches,
+providing a quantitative snapshot of national polling dynamics.
 
@@
 Model Fit: Harris' model explain roughly 33% of the variance in their
-respective datasets. Trump's models explain roughly 33% of the variance in their
-respective datasets.This suggests that other factors not included in
-the model may play a significant role in explaining the remaining
-variance.\
+respective datasets. Trump's models explain roughly 33% of the variance
+in their respective datasets.This suggests that other factors not
+included in the model may play a significant role in explaining the
+remaining variance.\
 This summary indicates the models are moderately predictive, with room
@@
 
-$\text{Sampling Proportion_A}$ =
-$\frac{500,000}{1,200,000} \approx0.417$
+Sampling Proportion A = $\frac{500,000}{1,200,000} \approx0.417$
 
@@
 
-$\text{Sampling Proportion_B}$ =
-$\frac{700,000}{1,200,000} \approx0.583$
+Sampling Proportion B = $\frac{700,000}{1,200,000} \approx0.583$
 
@@
 
-\$ \text{Polls for State A} = 1,000 \times 0.417 \approx 417\$
+Polls for State A = $1,000 {\times} 0.417 {\approx} 417$
 
@@
 
-$\text{Polls for State B} = 1,000 \times 0.583 \approx 583$
+Polls for State B  = $1,000{\times} 0.583{\approx} 583$
 
@@
 
-5.  **How likely are you going to vote in the 2024 election?** (1 = Definitely
-    not to vote, 10 = Definitely will vote)
+5.  **How likely are you going to vote in the 2024 election?** (1 =
+    Definitely not to vote, 10 = Definitely will vote)
 
@@
 10. **What do you think is the most important issue facing the United
-    States?** [Select at most 3]
+    States?** \[Select at most 3\]
 

### 2024-11-01 scripts/03-clean_data.R

@@ -33,7 +33,7 @@ just_harris_high_quality <- cleaned_data |>
   ) |>
   mutate(
     state = if_else(is.na(state) | state == "--", "National", state),
-    national_poll = if_else(is.na(state), 1, 0)  # 1 for national, 0 for state-specific
+    national_poll = if_else(state == "National", 1, 0)  # 1 for national, 0 for state-specific
   ) |> mutate(
     start_date = mdy(start_date),
     end_date = mdy(end_date)
@@ -54,7 +54,7 @@ just_trump_high_quality <- cleaned_data|>
   select(
     pollster, numeric_grade, state, candidate_name, pct, sample_size, 
     population, methodology, start_date, end_date
-  )|>
+  )|>filter(population %in% c("lv", "rv"))|>
   # Drop rows with missing values in essential columns
   drop_na(numeric_grade, pct, sample_size, end_date)|>
   filter(
@@ -63,19 +63,15 @@ just_trump_high_quality <- cleaned_data|>
   ) |>
   mutate(
     state = if_else(is.na(state) | state == "--", "National", state),
-    national_poll = if_else(is.na(state), 1, 0)  # 1 for national, 0 for state-specific
+    national_poll = if_else(state == "National", 1, 0)  # 1 for national, 0 for state-specific
   ) |> mutate(
     start_date = mdy(start_date),
     end_date = mdy(end_date)
   )|>
   # Calculate recency weight using exponential decay (more recent polls get higher weight)
   mutate(
-    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
-    recency_weight = exp(-recency*0.1)  # Adjust decay rate as needed
+    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days"))
   ) |>
-  # Apply sample size weight, capped at a maximum of 2,300 responses
-  mutate(sample_size_weight = pmin(sample_size / 2300, 1)) 
-just_trump_high_quality <- just_trump_high_quality %>%
   mutate(
     pollster = factor(pollster),
     state = factor(state),
@@ -83,7 +79,6 @@ just_trump_high_quality <- just_trump_high_quality %>%
     population = factor(population),  # Only if appropriate
     methodology = factor(methodology)
   )
-high_quality_combined<-bind_rows(just_harris_high_quality,just_trump_high_quality)
 #### Save data ####
[…]

### 2024-11-01 scripts/05-model_data.R

@@ -20,45 +20,31 @@ trump_data <- read_parquet("data/02-analysis_data/analysis_data_Trump.parquet")
 harris_data <- harris_data %>%
   mutate(
     sample_size_weight = pmin(sample_size / 2300, 1),
-    pollster_quality_weight = numeric_grade / 4,
     recency_weight = exp(-recency * 0.1)
-  ) %>%
-  group_by(pollster) %>%
-  mutate(
-    recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) %>%
-  ungroup() %>%
-  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+  )  %>%
+  mutate(combined_weight = recency_weight * sample_size_weight)
 
 # Calculate weights for Trump data
 trump_data <- trump_data %>%
   mutate(
     sample_size_weight = pmin(sample_size / 2300, 1),
-    pollster_quality_weight = numeric_grade / 4,
     recency_weight = exp(-recency * 0.1)
   ) %>%
-  group_by(pollster) %>%
-  mutate(
-    recent_poll_count = sum(recency < 30),
-    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
-  ) %>%
-  ungroup() %>%
-  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
+  mutate(combined_weight = recency_weight * sample_size_weight)
 
 
 #### Build Models ####
 # 1. Unweighted model for Harris
-model_harris_unweighted <- lm(pct ~ national_poll + pollster + population, data = harris_data)
+model_harris_unweighted <- lm(pct ~ national_poll + pollster + population+state, data = harris_data)
 
 # 2. Weighted model for Harris
-model_harris_weighted <- lm(pct ~ national_poll + pollster + population, data = harris_data, weights = combined_weight)
+model_harris_weighted <- lm(pct ~ national_poll + pollster + population+state, data = harris_data, weights = combined_weight)
 
 # 3. Unweighted model for Trump
-model_trump_unweighted <- lm(pct ~ national_poll + pollster + population, data = trump_data)
+model_trump_unweighted <- lm(pct ~ national_poll + pollster + population+state, data = trump_data)
 
 # 4. Weighted model for Trump
[…]

### 2024-11-01 paper/paper.qmd
Update paper.qmd
added reference to intro

@@
 poll's end date, the polling organization, geographic location, and the
-poll's score. Our research seeks to fill a gap in existing literature
-that often fails to address the complexities of polling data, thereby
-enhancing our understanding of voter behavior within the electoral
-context.
+poll's score.
+
+Research by Gelman and King (1993) underscores that while polls can exhibit
+variability over a campaign period, they can provide reliable predictions 
+when adjusted for temporal changes and fundamental factors. Additionally,
+Erikson and Wlezien (2008) highlight the importance of timing in polling,
+showing that data closer to election day tends to stabilize and therefore
+becomes more predictive. Our research seeks to fill a gap in existing
+literature that often fails to address the complexities of polling
+data, thereby enhancing our understanding of voter behavior within the
+electoral context.
 
@@
 and the support outcome, providing clarity on how each factor influences
-overall support for Harris. By estimating the coefficients for each
-predictor, we aim to draw significant conclusions about their respective
-impacts on voter sentiment.
+overall support for Harris. As Silver (2012) argues, leveraging aggregated
+data from multiple reputable sources and adjusting for sample quality
+and methodology is crucial for achieving accurate predictions.
+By estimating the coefficients for each predictor, we aim to draw
+significant conclusions about their respective impacts on voter
+sentiment.
 

### 2024-11-01 paper/paper.qmd
Update paper.qmd

@@
 and the support outcome, providing clarity on how each factor influences
-overall support for Harris. As Silver (2012) argues, leveraging aggregated
-data from multiple reputable sources and adjusting for sample quality
-and methodology is crucial for achieving accurate predictions.
-By estimating the coefficients for each predictor, we aim to draw
-significant conclusions about their respective impacts on voter
-sentiment.
+overall support for Harris. By estimating the coefficients for each 
+predictor, we aim to drawn significant conclusions about their respective
+impacts on voter sentiment.
 

### 2024-11-01 paper/paper.qmd
merge

--- 2024-11-01 paper/paper.qmd
@@
 
-- **Recency Weight**: Applied through an exponential decay function, `exp(-recency * 0.1)`, where "recency" represents the days since the poll was conducted.
+- **Recency Weight**: Applied through an exponential decay function, exp(-recency * 0.1), where "recency" represents the days since the poll was conducted.
 This ensures that more recent data carries more weight, while older polls have reduced influence.
@@
 ```{r}
-modelsummary::msummary(list(
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| tbl-colwidths: [45,15]
+#| tbl-cap: "Summary of the Linear Regression Model for Predicting Polling Outcomes"
+#| layout-ncol: 2
+#| label: tbl-summary
+modelsummary::msummary(
+  list(
     "Harris Unweighted" = harris_unweighted_model, 
@@
     "Trump Unweighted" = trump_unweighted_model,
-  "Trump Weighted" = trump_weighted_model))
-
+    "Trump Weighted" = trump_weighted_model
+  ))
 ```
@@
 
-This appendix provides a comprehensive overview of the methodology
-employed by the Siena College Polling Institute in conducting its
-surveys.Siena College is renowned for its methodologically rigorous
-approach to political polling, focusing on accurately capturing voter
-sentiment during elections. Siena College has conducted polls in three
-key states: Michigan, Wisconsin, and Ohio.
-
-In this section, we will delve into the key components of Siena's
-polling methodology, including the target population, sampling frame,
-recruitment processes, and the sampling strategies used. We will also
-address how non-response is managed and evaluate the strengths and
-weaknesses of the questionnaire design. By exploring these elements,
-this appendix aims to clarify how Siena College ensures the reliability
-and validity of its polling results, contributing valuable insights to
-the understanding of voter behavior and election outcomes.
+This appendix outlines the methodology used by the Siena College Polling Institute for conducting its surveys.
+Known for its methodological rigor, Siena College focuses on accurately capturing voter sentiment during elections and has conducted polls in key states such as Michigan, Wisconsin, and Ohio.
+
+In this section, we examine the main components of Siena's polling methodology, including the target population, sampling frame, recruitment processes, and sampling strategies.
+Additionally, we discuss how Siena addresses non-response and review the strengths and weaknesses of its questionnaire design.
+By detailing these elements, this appendix clarifies how Siena College ensures the reliability and validity of its polling results, offering valuable insights into voter behavior and election dynamics.
 
@@
 This appendix details the methodology and design for conducting a U.S.
-presidential election forecast survey with a budget of \$100,000. The
+presidential election forecast survey with a budget of $\$100,000$. The
 objective is to generate an accurate and reliable prediction of the
@@
 Our target population is all U.S. citizens eligible to vote in the 2024
-U.S. presidential election (age\>=18).
+U.S. presidential election (age>=18).
 
@@
 response options, and for ordinal questions, we vary the order.
-Open-ended formats and pauses (e.g., "Who would you vote for? \[pause\]
+Open-ended formats and pauses (e.g., "Who would you vote for? [pause]
 Candidate A or Candidate B?") further minimize order effects.
@@
 
-Budget Breakdown With a total budget of \$100,000, the allocation for
+Budget Breakdown With a total budget of $\$100,000$, the allocation for
 various components of the survey implementation and data collection is
@@
 
-Survey Design and Development: \$2,000 Covers question formatting,
+Survey Design and Development: $\$2,000$ Covers question formatting,
 testing, and online integration (e.g., Qualtrics) to ensure
@@
 
-Online Panel Providers (Qualtrics, YouGov): \$80,000 200 respondents
-recruited at \$400 each, leveraging verified voter panels for
+Online Panel Providers (Qualtrics, YouGov): $\$80,000$ 200 respondents
+recruited at $\$400$ each, leveraging verified voter panels for
 high-quality data.
 
-Social Media Recruitment (Facebook, Instagram): \$12,000 400 respondents
-recruited via targeted ads (\$30 each). Anticipating a 50% invalid rate,
+Social Media Recruitment (Facebook, Instagram): $\$12,000$ 400 respondents
+recruited via targeted ads ($\$30$ each). Anticipating a 50% invalid rate,
 allowing for 200 valid responses after validation.
 
-Data Validation and Quality Control: \$6,000 Includes voter registration
+Data Validation and Quality Control: $\$6,000$ Includes voter registration
 checks, attention filters, and post-collection quality review,

### 2024-11-01 paper/paper.qmd
merge

@@
 library(dplyr)
+library(ggplot2)
 ```
@@
 #| message: false
-trump_data<-trump_data |>mutate(candidate="Trump")
-harris_data<-harris_data|>mutate(candidat="Harris")
 combined_data_total<-bind_rows(harris_data,trump_data)
@@
   mutate(
+    candidate = candidate_name,
     sample_size_weight = pmin(sample_size / 2300, 1),
@@
 #| eval: true
-#| tbl-colwidths: [45,15]
-#| tbl-cap: "Summary of the Linear Regression Model for Predicting Polling Outcomes"
-#| layout-ncol: 2
-#| label: tbl-summary
+#| tbl-cap: "Summary of the Linear Regression Model for Predicting Harris' Voting Outcomes by polling results"
+#| label: tbl-summary1
 modelsummary::msummary(
@@
     "Harris Unweighted" = harris_unweighted_model, 
-    "Harris Weighted" = harris_weighted_model,
+    "Harris Weighted" = harris_weighted_model
+  ), 
+  options = list("longtable" = TRUE))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| tbl-cap: "Summary of the Linear Regression Model for Predicting Trump's Voting Outcomes by polling results"
+#| label: tbl-summary2
+modelsummary::msummary(
+  list(
     "Trump Unweighted" = trump_unweighted_model,
     "Trump Weighted" = trump_weighted_model
-  ))
+  ), 
+  options = list("longtable" = TRUE))
 ```
@@
     combined_weight = recency_weight * sample_size_weight,
-    candidate="Harris"
+    candidate="Kamala Harris"
   )
@@
     combined_weight = recency_weight * sample_size_weight,
-    candidate="Trump"
+    candidate="Donald Trump"
   )
@@
 #| eval: true
-#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using Fitted Linear Model"
-#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
-#| layout-ncol: 2
-#| label: fig-support-trend
+#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using unweighted fitted Linear Model"
+#| label: fig-support-trend1
 ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
@@
                    "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
-  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
   theme_classic() +
@@
   scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
-
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using weighted fitted Linear Model"
+#| label: fig-support-trend2
 # Plotting with the filtered data
@@
        caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
-  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red"))  +
+  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red"))  +
   theme_classic() +
@@
 #| eval: true
-#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Fitted Linear Model"
-#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
-#| layout-ncol: 2
-#| label: fig-support-respondent
+#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Unweighted Fitted Linear Model"
+#| label: fig-support-respondent1
 custom_labels <- c("lv" = "Likely Voters", "rv" = "Registered Voters")
@@
        caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
-  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
   theme_classic() +
@@
   scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Weighted Fitted Linear Model"
+#| label: fig-support-respondent2
 ### weighted
@@
        caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
-  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
+  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
   theme_classic() +
@@
 #| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Fitted Linear Model"
-#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
-#| layout-ncol: 2
 #| label: fig-support-state
@@
   scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Weighted Fitted Linear Model"
+#| label: fig-support-state2
 ## weighetd

### 2024-11-01 paper/paper.qmd

@@
 overall support for Harris. By estimating the coefficients for each 
-predictor, we aim to draw significant conclusions about their respective
+predictor, we aim to drawn significant conclusions about their respective
 impacts on voter sentiment.

### 2024-11-01 paper/paper.qmd
update paper

@@
 ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
-  geom_point(alpha = 0.7,color="grey")+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
-  facet_wrap(~ candidate,ncol = 2) +
+  geom_point(alpha = 0.1)+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+
   labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
@@
 ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
-  geom_point(alpha = 0.7,color="grey")+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
-  facet_wrap(~ candidate,ncol = 2) +
+  geom_point(alpha = 0.1)+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+
   labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
@@
 ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
-  geom_point(alpha = 0.7,color="grey")+ 
+  geom_point(alpha = 0.1)+ 
   geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
@@
 ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
-  geom_point(alpha = 0.7,color="grey")+ 
+  geom_point(alpha = 0.1)+ 
   geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
@@
 ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
-  geom_point(alpha = 0.7,color="grey")+ 
+  geom_point(alpha = 0.1)+ 
   geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
@@
   scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
+```
+
+## Predicted Support for Harris and Trump by Major Pollsters
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by Pollster using Unweighted Fitted Linear Model"
+#| label: fig-support-pollster1
+
+# Calculate the top 10 pollsters by frequency in the data
+top_pollsters <- combined_data_total %>%
+  count(pollster) %>%
+  top_n(5, n) %>%
+  pull(pollster)
+
+# Create a new variable to label the top pollsters and others as "Other"
+combined_data_total <- combined_data_total %>%
+  mutate(pollster_group = ifelse(pollster %in% top_pollsters, as.character(pollster), "Other"))
+
+ggplot(combined_data_total, aes(x = end_date, y = pct, size = combined_weight)) +
+  geom_point(aes(fill = pollster_group), alpha = 0.5, shape = 21, color = "black") + 
+  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
+            aes(x = end_date, y = predicted_unweighted), color = "blue", size = 1) +
+  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
+            aes(x = end_date, y = predicted_unweighted), color = "red", size = 1) +
+  facet_wrap(~ candidate, ncol = 2) +
+  labs(
+    title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election by Top 5 Pollster \n(From August 1, 2024 to October 27, 2024)",
+    subtitle = "predicted using weighted multiple linear regression model",
+    x = "End Date of the Poll",
+    y = "Predicted Support (%)",
+    size = "Weight",
+    fill = "Pollster",
+    caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population"
+  ) +
+  scale_fill_manual(values = c(setNames(rep("grey", length(unique(combined_data_total$pollster_group))), "Other"),
+                               setNames(rainbow(10), top_pollsters))) + # Assign colors to top pollsters and grey to others
+  theme_classic() +
+  theme(
+    legend.position = "bottom",
+    legend.box = "horizontal",  # Place legends in a horizontal row
+    legend.title.align = 0.5,   # Center-align legend titles for better appearance
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    strip.background = element_rect(colour = "black", fill = "white")
+  ) +
+  guides(
+    size = guide_legend(order = 1, title.position = "top", label.position = "left"),
+    fill = guide_legend(order = 2)
+  ) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| eval: true
+#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by Pollster using Weighted Fitted Linear Model"
+#| label: fig-support-pollster2
+
+ggplot(combined_data_total, aes(x = end_date, y = pct, size = combined_weight)) +
+  geom_point(aes(fill = pollster_group), alpha = 0.5, shape = 21, color = "black") + 
+  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
+            aes(x = end_date, y = predicted_weighted), color = "blue", size = 1) +
+  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
+            aes(x = end_date, y = predicted_weighted), color = "red", size = 1) +
+  facet_wrap(~ candidate, ncol = 2) +
+  labs(
+    title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election by Top 5 Pollster \n(From August 1, 2024 to October 27, 2024)",
+    subtitle = "predicted using weighted multiple linear regression model",
+    x = "End Date of the Poll",
+    y = "Predicted Support (%)",
+    size = "Weight",
+    fill = "Pollster",
+    caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population"
+  ) +
+  scale_fill_manual(values = c(setNames(rep("grey", length(unique(combined_data_total$pollster_group))), "Other"),
+                               setNames(rainbow(10), top_pollsters))) + # Assign colors to top pollsters and grey to others
+  theme_classic() +
+  theme(
+    legend.position = "bottom",
+    legend.box = "horizontal",  # Place legends in a horizontal row
+    legend.title.align = 0.5,   # Center-align legend titles for better appearance
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    strip.background = element_rect(colour = "black", fill = "white")
+  ) +
+  guides(
+    size = guide_legend(order = 1, title.position = "top", label.position = "left"),
+    fill = guide_legend(order = 2)
+  ) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
+
 ```
@@
 
-Harris model: RMSE of 3.42, indicating an average prediction error of
+Harris model: RMSE of 3.41, indicating an average prediction error of
 around 3.44 percentage points.\
-Trump model: RMSE of 4.30, showing a slightly higher prediction error on
+Trump model: RMSE of 4.28, showing a slightly higher prediction error on
 average.\
@@
 variable explained by the model (higher is better).\
-Harris model: R-squared of 0.33, meaning the model explains about 34.6%
+Harris model: R-squared of 0.34, meaning the model explains about 34.6%
 of the variance in Harris's polling data.\
-Trump model: R-squared of 0.27 as well, indicating similar explanatory
+Trump model: R-squared of 0.28 as well, indicating similar explanatory
 power for Trump's polling data.
@@
 observed and predicted values (lower is better).\
-Harris model: MAE of 2.48, meaning that, on average, the predictions are
+Harris model: MAE of 2.40, meaning that, on average, the predictions are
 off by 2.48 percentage points.\
-Trump model: MAE of 3.15, indicating slightly less precise predictions
+Trump model: MAE of 3.09, indicating slightly less precise predictions
 compared to the Harris model.\
@@
 by its lower RMSE and MAE values.\
-Model Fit: Harris' model explain roughly 33% of the variance in their
-respective datasets. Trump's models explain roughly 33% of the variance
+Model Fit: Harris' model explain roughly 34% of the variance in their
+respective datasets. Trump's models explain roughly 28% of the variance
 in their respective datasets.This suggests that other factors not

### 2024-11-01 paper/paper.qmd
Update paper.qmd

@@
 Nonresponse bias occurs when participants are unwilling or unable to
-answer certain questions or complete the survey. Given that our survey
+answer certain questions or complete the survey.
+Handling non-response bias matters because it can skew survey results, leading to inaccurate conclusions that do not accurately represent the entire population's views or characteristics.
+Given that our survey
 takes approximately 15 minutes to complete, there is a risk of
-nonresponse bias. To mitigate this,as highlighted by @surveymonkey, we
+nonresponse bias. To mitigate this, as highlighted by @surveymonkey, we
 set clear expectations about the survey's purpose and estimated
@@
 our respondent group aligns closely with the actual population
-characteristics, reducing bias and improving representativeness
+characteristics, reducing bias, and improving representativeness
 [@surveylab].
@@
 
-### Defination of the response bias
+### Definition of the response bias
 

### 2024-11-01 paper/paper.qmd
added reference to measurement

@@
 any missing information. This step is crucial for ensuring that the
-dataset accurately mirrors the electorate's sentiments. Each entry in
-the finalized dataset reflects an individual's viewpoint at a given
-moment, enabling a detailed analysis of the factors that shape public
-opinion as the election nears. This structured methodology effectively
-converts subjective opinions into measurable data, providing valuable
-insights into voter behavior and preferences.
+dataset accurately mirrors the electorate's sentiments. Following data
+cleaning, polling results are aggregated to smooth out individual poll
+biases and mitigate random error. This aggregation process leverages
+weighting based on poll quality, sample size, recency, and the historical
+accuracy of each polling agency, as seen in FiveThirtyEight’s approach
+(Silver, 2018; Jackman, 2005). By combining multiple polls, the aggregation
+method produces a more reliable picture of public opinion trends over time.
+
+Each entry in the finalized dataset reflects an individual's viewpoint
+at a given moment, enabling a detailed analysis of the factors that
+shape public opinion as the election nears. This structured methodology
+effectively converts subjective opinions into measurable data, providing
+valuable insights into voter behavior and preferences.
 

### 2024-11-02 paper/paper.qmd
update estimand
Add more result

@@
 format: pdf
+toc: true
 number-sections: true
@@
 
-# Introduction
+# Introduction {#sec-introduction}
 
@@
 
-# Data {#third-data}
-
-## Overview
+# Data {#sec-data}
+
+## Overview {#sec-data-overview}
 
@@
 
-## Measurement
+## Measurement {#sec-data-measurement}
 
@@
 
-## Outcome variable
-
-### The support percentage of Kamala Harris.
+## Outcome variable {#sec-outcome-variable}
+
+### The support percentage of Kamala Harris.{#sec-harris-support}
 
@@
 
-## Predictor variables
-
-### End Date
+## Predictor variables {#sec-predictor-variables}
+
+### End Date {#sec-end-date}
 
@@
 
-### State
+### State {#sec-state}
 
@@
 
-### Pollster
+### Pollster {#sec-pollster}
 
@@
 
-### Numeric Grade
+### Numeric Grade {#sec-numberic-grade}
 
@@
 
-## Relationships between key varaibles
+## Relationships between key varaibles {#sec-data-relationship}
 
@@
 
-## Model {#forth-model}
+# Model{#sec-model}
 
@@
 
-### 3.1 Model Set-Up
+## Model Set-Up {#sec-model-setup}
 
@@
     methodology and reliability.
--   **Population (`population`)**: Reflects demographic or regional
-    characteristics associated with each poll.
-
-#### Unweighted Model
+-   **Population (`population`)**: Variable provides an abbreviated description
+    of the respondent group, usually indicating their voting status
+    (e.g., "lv" for likely voters or "rv" for registered voters).
+-   **State (`state`)**: The U.S. state where the poll was conducted or focused,
+    if applicable.
+
+### Unweighted Model {#sec-unweighted-model}
 
@@
 $$ $$
-\mu_i = \beta_0 + \beta_1 \cdot \text{National Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \epsilon_i
+\mu_i = \beta_0 + \beta_1 \cdot \text{National Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \beta_4 \cdot \text{State}_i + \epsilon_i
 $$ $$
@@
     support.
--   $\beta_1, \beta_2, \beta_3$ are the coefficients for each predictor,
+-   $\beta_1, \beta_2, \beta_3, \beta_4$ are the coefficients for each predictor,
     indicating their influence on Harris's support percentage.
@@
 
-### 3.1.1 Weighted Model Explanation
+### Weighted Model Explanation {#sec-weighted-explain}
 
@@
 $$.
-This comprehensive weight prioritizes recent, large-sample, high-quality, and moderately frequent polls, creating a balanced and reliable dataset that reflects both current sentiment and credible data sources.
-
-The **combined weight** for each poll is thus:
-
-By incorporating these weights, we adjust the model’s estimates to give
-more importance to recent, credible, and representative polls, enhancing
+
+By incorporating these weights, we adjust the model’s estimates to give more importance to recent, credible, and representative polls, enhancing
 the reliability of our predictions.
 
-### 3.1.2 Model Justification
+## Model Justification {#sec-model-justify}
 
@@
 
-# Result
-
-## Predicted Voting Outcomes
+# Result {#sec-result}
+
+This section examines the relationship between national polling trends, pollster effects, population demographics, and other factors with respect to the predicted support levels for Kamala Harris and Donald Trump in the 2024 U.S.
+Presidential Election.
+Using a dataset comprising polling data from various states and organizations, we applied both unweighted and weighted linear regression models to identify the key predictors influencing each candidate's support.
+Below, we present the results of our models along with their implications.
+
+Predictions were generated based on our test dataset.
+However, due to incomplete data for certain states, we were unable to make predictions across the entire U.S.
+This limitation arises from states with missing values in the dataset, which are consequently not represented in the model, affecting forecast accuracy in those regions.
+
+## Model Results and Interpretation {#sec-result-explain}
+
+The linear regression models constructed for predicting support for Kamala Harris and Donald Trump in the 2024 U.S.
+Presidential Election utilized both unweighted and weighted configurations.
+As shown in **Table 1** and **Table 2**, the intercepts for Harris and Trump, estimated at 45.10 and 59.28 respectively in the unweighted models, represent their baseline support levels when all predictors are at reference values.
+The high \( R^2 \) values of 0.738 for Harris’s unweighted model and 0.860 for her weighted model, along with similar values of 0.635 and 0.890 for Trump, indicate that a significant portion of the variation in support can be explained by the model's predictors.
+The relatively low Root Mean Square Error (RMSE) values further suggest that the models provide reasonably accurate predictions of support levels.
+
+The results underscore the significance of **national_poll** and **pollster** as key predictors for both candidates' support, highlighting how national trends and pollster differences impact the reported support levels.
+The **population** predictor further reveals that demographic and regional characteristics contribute meaningfully to support variations, especially in battleground states.
+These findings enhance our understanding of the dynamics influencing voter sentiment, with methodological and regional factors proving essential in shaping support for each candidate.
 
@@
 
-## Recent Three Months Support Trends Linear Model Prediction
+## Predicted Voting Outcomes {#sec-model-predicted-outcome}
+
+@fig-support-trend1 and @fig-support-trend2 illustrate the predicted support for Kamala Harris and Donald Trump from August 1, 2024, to October 27, 2024, using both unweighted and weighted linear regression models.
+In the unweighted model, we see that Trump's predicted support generally hovers between 45% and 50%, while Harris's support ranges from 35% to 45%.
+Both candidates' support levels appear relatively stable across the polling period, with minor fluctuations.
+This model, which treats all polls equally, suggests a consistent lead for Trump, albeit within a fairly close range, as shown by the overlapping grey points representing individual poll results.
+
+The weighted model refines these predictions by applying weights based on recency and sample size, which reduces the influence of older or smaller polls.
+This approach results in smoother trend lines for both candidates, with less apparent variability compared to the unweighted model.
+Trump's support remains around the mid-40% range, while Harris’s support stays in the high 30% range.
+The weighting emphasizes more recent and larger polls, likely providing a more accurate reflection of current public opinion.
+Overall, both models consistently indicate a lead for Trump, with the weighted model slightly stabilizing the predictions.
 
@@
 #| include: false
-####### Prediction and Plot ######
+#| 
 set.seed(233)
@@
     sample_size_weight = pmin(sample_size / 2300, 1),
+   pollster_quality_weight = pollster_quality / 4,  
     recency_weight = exp(-recency * 0.1),  
@@
 
-## Predicted Voting Outcomes for Recent Three Months by Respondent Group
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| eval: true
-#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Unweighted Fitted Linear Model"
-#| label: fig-support-respondent1
-custom_labels <- c("lv" = "Likely Voters", "rv" = "Registered Voters")
-### unweighted
-ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
-  geom_point(alpha = 0.1)+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
-  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
-  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
-       subtitle = "predicted using unweighted multiple linear regression model ",
-       x = "End Date of the Poll",  # Change x-axis label to End Date
-       y = "Predicted Support (%)",
-       color = "Candidate",
-       size="Weight",
-       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
-  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
-  theme_classic() +
-  theme(legend.position = "top",
-        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
-  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| eval: true
-#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Weighted Fitted Linear Model"
-#| label: fig-support-respondent2
-### weighted
-ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
-  geom_point(alpha = 0.1)+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
-  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
-  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
-       subtitle = "predicted using weighted multiple linear regression model ",
-       x = "End Date of the Poll",  # Change x-axis label to End Date
-       y = "Predicted Support (%)",
-       color = "Candidate",
-       size="Weight",
-       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
-  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
-  theme_classic() +
-  theme(legend.position = "top",
-        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
-  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
-```
-
 ## Predicted Voting Outcomes for Recent Three Months by State
 
+@fig-support-state and @fig-support-state2 compare the predicted support for Kamala Harris and Donald Trump in key battleground states (Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, and Wisconsin) for the 2024 U.S.
+election.
+@fig-support-state uses an unweighted multiple linear regression model, while @fig-support-state2 applies a weighted model, giving greater influence to polls with higher weights based on recency and sample size.
+In both figures, Trump’s support, represented by red lines, and Harris’s support, shown in blue, show close competition across most states, with slight variations in trends across the polling period from August to October 2024.
+
+The weighted model in @fig-support-state2 introduces subtle shifts, with larger circles indicating polls with greater influence on the predicted trend.
+This approach captures more recent or higher-quality polls, offering a potentially more accurate representation of voter sentiment shifts over time.
+The close alignment of support lines for both candidates suggests tight races in these states, which are crucial for the election outcome.
+The use of weighted and unweighted models highlights the importance of data weighting in enhancing the reliability of electoral forecasts in dynamic political environments.
 ```{r}
@@
 ## Predicted Support for Harris and Trump by Major Pollsters
+
+@fig-support-pollster1 and @fig-support-pollster2 depict the predicted support for Kamala Harris and Donald Trump in the 2024 U.S.
+election, from August 1, 2024, to October 27, 2024, using a weighted multiple linear regression model.
+The red line shows fluctuations in Trump’s support, generally between 40% and 55%, with some noticeable peaks and dips, indicating variability over time.
+In contrast, Harris’s support, represented by the blue line, remains more stable, consistently ranging around 40% to 50%, suggesting less volatility in voter sentiment for her.
+
+Pollsters such as AtlasIntel, Emerson, Beacon/Shaw, Siena/NY, and YouGov are represented by different colors, with circle sizes reflecting weights based on factors like recency and sample size.
+Larger circles correspond to higher-weighted polls, indicating they had a greater influence on the predictions.
+The model incorporates national poll data, adjustments for pollster effects, and population considerations, allowing for a refined prediction approach.
+This approach ensures that more recent and larger polls play a more significant role, capturing shifts in voter sentiment as the election approaches.
 ```{r}
@@
 
-The predicted support for Kamala Harris and Donald Trump in the upcoming
-2024 U.S. presidential election is illustrated in Figure 1. This
-analysis spans the period from August 1, 2024, to October 27, 2024, and
-uses multiple linear regression models to project voter support.
-
-The unweighted model predictions indicate that Kamala Harris maintains a
-consistent support level, with projections hovering around 49%. The blue
-dashed line represents this trend, showing only minor fluctuations
-throughout the polling period. Conversely, the weighted model for
-Harris, indicated by the solid blue line, suggests a slight upward trend
-in predicted support, reflecting a potential positive shift in voter
-sentiment as the election date approaches.
-
-In contrast, Donald Trump's predicted support is represented by the red
-lines. The unweighted model forecasts his support to remain around 48%,
-while the weighted model predicts a gradual decline to approximately
-46%. The red dashed line indicates the unweighted prediction, whereas
-the solid red line shows the weighted prediction. This downward
-trajectory may indicate challenges for Trump in sustaining voter
-enthusiasm amid changing public opinions.
-
-At the conclusion of the polling period, the models suggest that Kamala
-Harris leads Donald Trump by approximately 2.5% in the un-weighted (49%
-vs. 46.5%) and 1% in weighted models (49% vs. 48%). Average leading by
-about 2%.
-
-@fig-national-support-trendsillustrates illustrates the polling support
-trends for Kamala Harris and Donald Trump across the country from August
-to October. The scatter points represent individual poll results, with
-blue for Harris and red for Trump, while each dot's size reflects the
-weight of the poll, accounting for factors like sample size, quality,
-and recency. Harris’s support trend line generally remains above
-Trump’s, with an average support level around 49%, compared to Trump’s
-approximate average of 47% over this period. Toward the end of October,
-both candidates show a slight increase, with Harris’s support reaching
-just over 50% and Trump’s approaching 49%. This trend suggests a
-potential narrowing in support levels as the election approaches,
-providing a quantitative snapshot of national polling dynamics.
-
 # Discussion

### 2024-11-02 scripts/05-model_data.R

@@ -35,16 +35,16 @@ trump_data <- trump_data %>%
 
 #### Build Models ####
 # 1. Unweighted model for Harris
-model_harris_unweighted <- lm(pct ~ national_poll + pollster + population+state, data = harris_data)
+model_harris_unweighted <- lm(pct ~ national_poll + pollster + population + state, data = harris_data)
 
 # 2. Weighted model for Harris
-model_harris_weighted <- lm(pct ~ national_poll + pollster + population+state, data = harris_data, weights = combined_weight)
+model_harris_weighted <- lm(pct ~ national_poll + pollster + population + state, data = harris_data, weights = combined_weight)
 
 # 3. Unweighted model for Trump
-model_trump_unweighted <- lm(pct ~ national_poll + pollster + population+state, data = trump_data)
+model_trump_unweighted <- lm(pct ~ national_poll + pollster + population + state, data = trump_data)
 
 # 4. Weighted model for Trump
-model_trump_weighted <- lm(pct ~ national_poll + pollster + population+state, data = trump_data, weights = combined_weight)
+model_trump_weighted <- lm(pct ~ national_poll + pollster + population + state, data = trump_data, weights = combined_weight)
 
 
 #### Save Models ####

### 2024-11-02 paper/paper.qmd
update paper

--- 2024-11-01 paper/paper.qmd
@@
 format: pdf
+header-includes:
+- \usepackage{caption}
+- \usepackage{longtable}
+- \usepackage{booktabs}
 number-sections: true
@@
 library(ggplot2)
+library(modelsummary)
 ```
@@
 The estimand of our analysis is the true percentage of voter support for
-Kamala Harris in the upcoming U.S. presidential election.
+Kamala Harris in the upcoming U.S.
+presidential election.
+The object of the estimation is forecasting the percentage of Kamala’s vote share based on an aggregated polling data using a multiple linear regression model.
+Our goal is to track shifts in public opinion over time, offering a clearer pattern of voter’s choice and potential election outcomes.
 
@@
 #| label: tbl-summary1
-modelsummary::msummary(
+
+msummary(
   list(
-    "Harris Unweighted" = harris_unweighted_model, 
-    "Harris Weighted" = harris_weighted_model
-  ), 
+    "Unweighted" = harris_unweighted_model,
+    "Weighted" = harris_weighted_model
+  ), fmt = fmt_significant(4),
   options = list("longtable" = TRUE))
+
 ```
@@
   list(
-    "Trump Unweighted" = trump_unweighted_model,
-    "Trump Weighted" = trump_weighted_model
+    "Unweighted" = trump_unweighted_model,
+    "Weighted" = trump_weighted_model
   ), 
@@
        color = "Candidate",caption = 
-                   "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+                   "Linear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
        size="Weight",
-       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red"))  +
@@
        size="Weight",
-       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+       caption = "Linear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
        size="Weight",
-       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
        color = "Candidate",
-       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+       caption = "Linear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
     fill = "Pollster",
-    caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population"
+    caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state"
   ) +
@@
 
-@fig-national-support-trendsillustrates illustrates the polling support
+ illustrates the polling support
 trends for Kamala Harris and Donald Trump across the country from August
@@
 # Train the model
-model_formula <- pct ~ national_poll + pollster + population
+model_formula <- pct ~ national_poll + pollster + population + state
 model_harris_cv <- train(model_formula, data = harris_data, method = "lm", trControl = train_control)

### 2024-11-02 paper/paper.qmd

--- 2024-11-02 paper/paper.qmd
@@
 library(ggplot2)
+library(modelsummary)
+library(RColorBrewer)
+library(gt)
+library(future)
 ```
@@
 
-Research by Gelman and King (1993) underscores that while polls can exhibit
-variability over a campaign period, they can provide reliable predictions 
-when adjusted for temporal changes and fundamental factors. Additionally,
-Erikson and Wlezien (2008) highlight the importance of timing in polling,
-showing that data closer to election day tends to stabilize and therefore
-becomes more predictive. Our research seeks to fill a gap in existing
-literature that often fails to address the complexities of polling
-data, thereby enhancing our understanding of voter behavior within the
-electoral context.
+Research by Gelman and King (1993) underscores that while polls can
+exhibit variability over a campaign period, they can provide reliable
+predictions when adjusted for temporal changes and fundamental factors.
+Additionally, Erikson and Wlezien (2008) highlight the importance of
+timing in polling, showing that data closer to election day tends to
+stabilize and therefore becomes more predictive. Our research seeks to
+fill a gap in existing literature that often fails to address the
+complexities of polling data, thereby enhancing our understanding of
+voter behavior within the electoral context.
 
 The estimand of our analysis is the true percentage of voter support for
-Kamala Harris in the upcoming U.S. presidential election.
+Kamala Harris in the upcoming U.S. presidential election. The object of
+the estimation is forecasting the percentage of Kamala’s vote share
+based on an aggregated polling data using a multiple linear regression
+model. Our goal is to track shifts in public opinion over time, offering
+a clearer pattern of voter’s choice and potential election outcomes.
 
@@
 overall support for Harris. By estimating the coefficients for each
-predictor, we aim to drawn significant conclusions about their respective
-impacts on voter sentiment.
+predictor, we aim to drawn significant conclusions about their
+respective impacts on voter sentiment.
 
@@
 biases and mitigate random error. This aggregation process leverages
-weighting based on poll quality, sample size, recency, and the historical
-accuracy of each polling agency, as seen in FiveThirtyEight’s approach
-(Silver, 2018; Jackman, 2005). By combining multiple polls, the aggregation
-method produces a more reliable picture of public opinion trends over time.
+weighting based on poll quality, sample size, recency, and the
+historical accuracy of each polling agency, as seen in FiveThirtyEight’s
+approach (Silver, 2018; Jackman, 2005). By combining multiple polls, the
+aggregation method produces a more reliable picture of public opinion
+trends over time.
 
@@
 
-### The support percentage of Kamala Harris.{#sec-harris-support}
+### The support percentage of Kamala Harris. {#sec-harris-support}
 
@@
 
-# Model{#sec-model}
+# Model {#sec-model}
 
@@
 
-The model predicts Harris's support percentage using the following
-predictor variables:
+The model predicts Harris's support percentage by constructing multiple
+linear regression model using the following predictor variables:
 
@@
     methodology and reliability.
--   **Population (`population`)**: Variable provides an abbreviated description
-    of the respondent group, usually indicating their voting status
-    (e.g., "lv" for likely voters or "rv" for registered voters).
--   **State (`state`)**: The U.S. state where the poll was conducted or focused,
-    if applicable.
+-   **Population (`population`)**: Variable provides an abbreviated
+    description of the respondent group, usually indicating their voting
+    status (e.g., "lv" for likely voters or "rv" for registered voters).
+-   **State (`state`)**: The U.S. state where the poll was conducted or
+    focused, if applicable.
+
+We include Pollster and State variables as controls to account for potential biases introduced by different polling organizations and regional variations in voter preferences.
 
@@
     support.
--   $\beta_1, \beta_2, \beta_3, \beta_4$ are the coefficients for each predictor,
-    indicating their influence on Harris's support percentage.
+-   $\beta_1, \beta_2, \beta_3, \beta_4$ are the coefficients for each
+    predictor, indicating their influence on Harris's support
+    percentage.
 -   $\sigma^2$ is the variance of the error term, representing
@@
 
-Where:
-
-- **Sample Size Weight**: Calculated as the sample size divided by 2300, capped at 1.
-This emphasizes larger, more reliable polls while preventing extremely large samples from disproportionately impacting the analysis.
-
-- **Recency Weight**: Applied through an exponential decay function, exp(-recency * 0.1), where "recency" represents the days since the poll was conducted.
-This ensures that more recent data carries more weight, while older polls have reduced influence.
-
-- **Combined Weight**: The final weight is the product of all individual weights: $$
+Where: $W$ is the weight parameters calculated from the product of
+**sample size weight** and recency **weight**.
+
+-   **Sample Size Weight**: Calculated as the sample size divided by
+    2300, capped at 1. This emphasizes larger, more reliable polls while
+    preventing extremely large samples from disproportionately impacting
+    the analysis.
+
+-   **Recency Weight**: Applied through an exponential decay function,
+    exp(-recency \* 0.1), where "recency" represents the days since the
+    poll was conducted. This ensures that more recent data carries more
+    weight, while older polls have reduced influence.
+
+-   **Combined Weight**: The final weight is the product of all
+    individual weights: $$
     \text{Combined Weight} =\text{Recency Weight} \times \text{Sample Size Weight}
@@
 
-By incorporating these weights, we adjust the model’s estimates to give more importance to recent, credible, and representative polls, enhancing
+By incorporating these weights, we adjust the model’s estimates to give
+more importance to recent, credible, and representative polls, enhancing
 the reliability of our predictions.
@@
 Finally, to ensure the robustness and accuracy of our model, we conduct
-model validation and diagnostics, which are detailed in Appendix B.
-These procedures help confirm that the model assumptions are met and
-that the predictions are reliable across different polling scenarios.
+model validation and diagnostics, which are detailed in Appendix B. We
+use K-Fold Cross-Validation to validate the model, use Q-Q Plot and
+Residuals vs fitted diagram to diagnostic the model. These procedures
+help confirm that the model assumptions are met and that the predictions
+are reliable across different polling scenarios.
 
@@
 
-This section examines the relationship between national polling trends, pollster effects, population demographics, and other factors with respect to the predicted support levels for Kamala Harris and Donald Trump in the 2024 U.S.
-Presidential Election.
-Using a dataset comprising polling data from various states and organizations, we applied both unweighted and weighted linear regression models to identify the key predictors influencing each candidate's support.
-Below, we present the results of our models along with their implications.
-
-Predictions were generated based on our test dataset.
-However, due to incomplete data for certain states, we were unable to make predictions across the entire U.S.
-This limitation arises from states with missing values in the dataset, which are consequently not represented in the model, affecting forecast accuracy in those regions.
-
-## Model Results and Interpretation {#sec-result-explain}
-
-The linear regression models constructed for predicting support for Kamala Harris and Donald Trump in the 2024 U.S.
-Presidential Election utilized both unweighted and weighted configurations.
-As shown in **Table 1** and **Table 2**, the intercepts for Harris and Trump, estimated at 45.10 and 59.28 respectively in the unweighted models, represent their baseline support levels when all predictors are at reference values.
-The high \( R^2 \) values of 0.738 for Harris’s unweighted model and 0.860 for her weighted model, along with similar values of 0.635 and 0.890 for Trump, indicate that a significant portion of the variation in support can be explained by the model's predictors.
-The relatively low Root Mean Square Error (RMSE) values further suggest that the models provide reasonably accurate predictions of support levels.
-
-The results underscore the significance of **national_poll** and **pollster** as key predictors for both candidates' support, highlighting how national trends and pollster differences impact the reported support levels.
-The **population** predictor further reveals that demographic and regional characteristics contribute meaningfully to support variations, especially in battleground states.
-These findings enhance our understanding of the dynamics influencing voter sentiment, with methodological and regional factors proving essential in shaping support for each candidate.
+This section examines the relationship between national polling trends,
+pollster effects, population demographics, and other factors with
+respect to the predicted support levels for Kamala Harris and Donald
+Trump in the 2024 U.S. Presidential Election. Using a dataset comprising
+polling data from various states and organizations, we applied both
+unweighted and weighted linear regression models to identify the key
+predictors influencing each candidate's support. Below, we present the
+results of our models along with their implications.
+
+Predictions were generated based on our test dataset. However, due to
+incomplete data for certain states, we were unable to make predictions
+across the entire U.S. This limitation arises from states with missing
+values in the dataset, which are consequently not represented in the
+model, affecting forecast accuracy in those regions.
+
+## Model Results
+
+The linear regression models constructed for predicting support for
+Kamala Harris and Donald Trump in the 2024 U.S. Presidential Election
+utilized both unweighted and weighted configurations.The model summary of support for Harris is shown in @tbl-summary1, support for Trump is shown in @tbl-summary2. As shown in
+@tbl-summary1 and @tbl-summary2, the intercepts for Harris and Trump,
+estimated at 45.10 and 59.28 respectively in the unweighted models,
+represent their baseline support levels when all predictors are at
+reference values. The high ( R\^2 ) values of 0.738 for Harris’s
+unweighted model and 0.860 for her weighted model, along with similar
+values of 0.635 and 0.890 for Trump, indicate that a significant portion
+of the variation in support can be explained by the model's predictors.
+The relatively low Root Mean Square Error (RMSE) values further suggest
+that the models provide reasonably accurate predictions of support
+levels.
 
@@
 #| eval: true
-#| tbl-cap: "Summary of the Linear Regression Model for Predicting Harris' Voting Outcomes by polling results"
+#| tbl-cap: "Summary of Multiple Linear Regression Model Predicting Harris Support Based on Polling Data"
 #| label: tbl-summary1
-modelsummary::msummary(
-  list(
-    "Harris Unweighted" = harris_unweighted_model, 
-    "Harris Weighted" = harris_weighted_model
-  ), 
-  options = list("longtable" = TRUE))
+msummary(
+  list("Unweighted" = harris_unweighted_model, "Weighted" = harris_weighted_model),
+  fmt = fmt_significant(3),coef_omit="state|pollster",notes = "Note.
+All models include a control for state and pollsters.
+The reference level of state is Alaska, the reference level of population is likely voter, and the reference level of pollsters is Alaska is Angus Reid.")
 ```
@@
 #| eval: true
-#| tbl-cap: "Summary of the Linear Regression Model for Predicting Trump's Voting Outcomes by polling results"
+#| tbl-cap: "Summary of Multiple Linear Regression Model Predicting Trump Support Based on Polling Data"
 #| label: tbl-summary2
-modelsummary::msummary(
-  list(
-    "Trump Unweighted" = trump_unweighted_model,
-    "Trump Weighted" = trump_weighted_model
-  ), 
-  options = list("longtable" = TRUE))
+msummary(
+  list("Unweighted" = trump_unweighted_model, "Weighted" = trump_weighted_model),
+  fmt = fmt_significant(3),coef_omit="state|pollster",notes = "Note.
+All models include a control for state and pollsters.
+The reference level of state is Alaska,the reference level of population is likely voter, and the reference level of pollsters is Alaska is ABC/Washington Post.")
 ```
 
+The results underscore the significance of **national_poll** as key predictors for both candidates' support, highlighting how national trends and pollster differences impact the
+reported support levels, as polls from the National level increase the
+support of Harris by 3.262%, decrease the support for Trump by 7.943%.
+The **population** predictor indicates that the type of respondent group
+contributes meaningfully to variations in support. With "likely voters"
+as the baseline level, the coefficient for "registered voters"
+(populationrv) suggests a lower level of support for both Harris and
+Trump in this group compared to likely voters. Specifically, the support
+of registered voters is 2.1095 (unweighted model) and 1.0322 (weighted
+model) lower than the likely voters. This implies that, on average,
+support among registered voters is lower than that among likely voters.
+
 ## Predicted Voting Outcomes {#sec-model-predicted-outcome}
 
-@fig-support-trend1 and @fig-support-trend2 illustrate the predicted support for Kamala Harris and Donald Trump from August 1, 2024, to October 27, 2024, using both unweighted and weighted linear regression models.
-In the unweighted model, we see that Trump's predicted support generally hovers between 45% and 50%, while Harris's support ranges from 35% to 45%.
-Both candidates' support levels appear relatively stable across the polling period, with minor fluctuations.
-This model, which treats all polls equally, suggests a consistent lead for Trump, albeit within a fairly close range, as shown by the overlapping grey points representing individual poll results.
-
-The weighted model refines these predictions by applying weights based on recency and sample size, which reduces the influence of older or smaller polls.
-This approach results in smoother trend lines for both candidates, with less apparent variability compared to the unweighted model.
-Trump's support remains around the mid-40% range, while Harris’s support stays in the high 30% range.
-The weighting emphasizes more recent and larger polls, likely providing a more accurate reflection of current public opinion.
-Overall, both models consistently indicate a lead for Trump, with the weighted model slightly stabilizing the predictions.
+@fig-support-trend illustrate the predicted support for Kamala Harris
+and Donald Trump from August 1, 2024, to October 27, 2024, using both
+unweighted and weighted linear regression models. In the
+@fig-support-trend-1 unweighted model, we see that Trump's predicted
+support generally hovers between 45% and 50%, while Harris's support
+ranges from 35% to 45%. Both candidates' support levels appear
+relatively stable across the polling period, with minor fluctuations.
+This model, which treats all polls equally, suggests a consistent lead
+for Trump, albeit within a fairly close range, as shown by the
+overlapping grey points representing individual poll results.
+
+The weighted model @fig-support-trend-2 refines these predictions by
+applying weights based on recency and sample size, which reduces the
+influence of older or smaller polls. This approach results in smoother
+trend lines for both candidates, with less apparent variability compared
+to the unweighted model @fig-support-trend-1. Trump's support remains
+around the mid-40% range, while Harris’s support stays in the high 30%
+range. The weighting emphasizes more recent and larger polls, likely
+providing a more accurate reflection of current public opinion. Overall,
+both models consistently indicate a lead for Trump, with the weighted
+model slightly stabilizing the predictions.
 
@@
 #| include: false
-#| 
+
 set.seed(233)
+plan(multisession)
 ####### Prediction for Harris ######
@@
 # Predictions for Harris
+plan(multisession)
 new_data_harris <- new_data_harris |>
@@
 #| eval: true
-#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using unweighted fitted Linear Model"
-#| label: fig-support-trend1
+#| fig-cap: "Harris Kamala leads Donald Trump an average 5% in Predicted Support in the 2024 US Election (From August 1, 2024, to October 27, 2024)"
+#| fig-subcap: ["Unweighted","Weighted"]
+#| layout-ncol: 2
+#| label: fig-support-trend
+# Plotting with the filtered data
+plan(multisession)
+##unweighted
 ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
@@
   geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+
-  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
-       subtitle = "predicted using unweighted multiple linear regression model ",
+  labs(
        x = "End Date of the Poll",  # Change x-axis label to End Date
@@
        color = "Candidate",caption = 
-                   "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+                   "Linear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state") +
+  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
+  theme_classic() +
+  theme(legend.position = "top",
+        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
+##weighted
+ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
+  geom_point(alpha = 0.1)+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+
+  labs(x = "End Date of the Poll",
+       y = "Predicted Support (%)",
+       color = "Candidate",
+       size="Weight",
+       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red"))  +
@@
 
+## Predicted Voting Outcomes for Recent Three Months by State
+
+@fig-support-state compare the predicted support for Kamala Harris and
+Donald Trump in key battleground states (Arizona, Georgia, Michigan,
+Nevada, North Carolina, Pennsylvania, and Wisconsin) for the 2024 U.S.
+election. @fig-support-state-1 uses an unweighted multiple linear
+regression model, while @fig-support-state-2 applies a weighted model,
+giving greater influence to polls with higher weights based on recency
+and sample size. In both figures, Trump’s support, represented by red
+lines, and Harris’s support, shown in blue, show close competition
+across most states, with slight variations in trends across the polling
+period from August to October 2024.
+
+In the @fig-support-state-1 , support for Kamala Harris and Donald Trump
+fluctuates widely across battleground states, with Harris holding slight
+leads in Pennsylvania and North Carolina but facing tight competition
+overall. Without weighting, polls contribute equally, creating more
+volatility.
+
+The @fig-support-state-2 stabilizes these trends by emphasizing recent,
+larger polls. Harris's support becomes more consistent, particularly in
+Pennsylvania, North Carolina, and Nevada, where she shows a clearer
+lead. This weighted approach provides a more refined snapshot,
+highlighting Harris’s likely advantage in these key states.
+
 ```{r}
@@
 #| eval: true
-#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using weighted fitted Linear Model"
-#| label: fig-support-trend2
-# Plotting with the filtered data
+#| fig-subcap: ["Unweighted","Weighted"]
+#| layout-ncol: 2
+#| fig-cap: "Harris is likely to lead Trump in Pennsylvania, North Carolina, and Nevada by Model Prediction"
+#| label: fig-support-state
+## unweighted
+plan(multisession)
+selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
+combined_data_total<-combined_data_total|>filter(state %in% selected_states)
+combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
+
+ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
+  geom_point(alpha = 0.1)+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 0.5)+ # Smoothed trend line
+  facet_wrap(~ state,ncol = 4) +
+  labs(
+       x = "End Date of the Poll",  # Change x-axis label to End Date
+       y = "Predicted Support (%)",
+       color = "Candidate",
+       caption = "Candidate Support Percentage = national_poll + pollster + population + state") +
+  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
+  theme_classic() +
+  theme(legend.position = "top",
+        axis.text.x = element_text(angle = 90, hjust = 1),
+        legend.box = "vertical",
+        strip.background = element_rect(colour = "black", fill = "white")) +
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
+
+## weighetd
 ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
   geom_point(alpha = 0.1)+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+
-  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
-       subtitle = "predicted using weighted multiple linear regression model ",
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 0.5)+ # Smoothed trend line
+  facet_wrap(~ state,ncol = 4) +
+  labs(
        x = "End Date of the Poll",  # Change x-axis label to End Date
@@
        size="Weight",
-       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
+       caption = "Weights: recency_weight * sample_size_weight\nCandidate Support Percentage = national_poll + pollster + population + state") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
   theme(legend.position = "top",
-        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
+        axis.text.x = element_text(angle = 90, hjust = 1),
+        legend.box = "vertical",
+        strip.background = element_rect(colour = "black", fill = "white")) +
   scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
@@
 
-## Predicted Voting Outcomes for Recent Three Months by State
-
-@fig-support-state and @fig-support-state2 compare the predicted support for Kamala Harris and Donald Trump in key battleground states (Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, and Wisconsin) for the 2024 U.S.
-election.
-@fig-support-state uses an unweighted multiple linear regression model, while @fig-support-state2 applies a weighted model, giving greater influence to polls with higher weights based on recency and sample size.
-In both figures, Trump’s support, represented by red lines, and Harris’s support, shown in blue, show close competition across most states, with slight variations in trends across the polling period from August to October 2024.
-
-The weighted model in @fig-support-state2 introduces subtle shifts, with larger circles indicating polls with greater influence on the predicted trend.
-This approach captures more recent or higher-quality polls, offering a potentially more accurate representation of voter sentiment shifts over time.
-The close alignment of support lines for both candidates suggests tight races in these states, which are crucial for the election outcome.
-The use of weighted and unweighted models highlights the importance of data weighting in enhancing the reliability of electoral forecasts in dynamic political environments.
+## Predicted Support for Harris and Trump by Major Pollsters
+
+@fig-support-pollster depict the predicted support for Kamala Harris and
+Donald Trump in the 2024 U.S. election, from August 1, 2024, to October
+27, 2024, using a weighted multiple linear regression model. The red
+line shows fluctuations in Trump’s support, generally between 40% and
+55%, with some noticeable peaks and dips, indicating variability over
+time. In contrast, Harris’s support, represented by the blue line,
+remains more stable, consistently ranging around 40% to 50%, suggesting
+less volatility in voter sentiment for her.
+
+Major Pollsters are represented by different colors, with circle sizes
+reflecting weights based on factors like recency and sample size. Larger
+circles correspond to higher-weighted polls, indicating they had a
+greater influence on the predictions. The model incorporates national
+poll data, adjustments for pollster effects, and population
+considerations, allowing for a refined prediction approach. This
+approach ensures that more recent and larger polls play a more
+significant role, capturing shifts in voter sentiment as the election
+approaches.
+
+Siena/NYT and Quinnipiac consistently show stronger support for Harris,
+with Siena/NYT polls placing her around or above 50%. In contrast,
+Emerson polls display a closer race, often showing near-equal support
+for both candidates. AtlasIntel and Beacon/Shaw lean toward Trump, with
+AtlasIntel showing more volatility and Beacon/Shaw stabilizing near
+45-50% for Trump. Polls from other organizations, in grey, introduce
+variability but hold less influence in the model. Overall, Siena/NYT and
+Quinnipiac favor Harris, while Emerson, AtlasIntel, and Beacon/Shaw
+present a more competitive picture.
+
 ```{r}
@@
 #| eval: true
-#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Fitted Linear Model"
-#| label: fig-support-state
-## unweighted
-selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
-combined_data_total<-combined_data_total|>filter(state %in% selected_states)
-combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
-ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
-  geom_point(alpha = 0.1)+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
-  facet_wrap(~ state,ncol = 4) +
-  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
-       subtitle = "predicted using unweighted multiple linear regression model ",
-       x = "End Date of the Poll",  # Change x-axis label to End Date
-       y = "Predicted Support (%)",
-       color = "Candidate",
-       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
-  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
-  theme_classic() +
-  theme(legend.position = "top",
-        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
-  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| eval: true
-#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Weighted Fitted Linear Model"
-#| label: fig-support-state2
-## weighetd
-ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
-  geom_point(alpha = 0.1)+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
-  facet_wrap(~ state,ncol = 4) +
-  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
-       subtitle = "predicted using weighted multiple linear regression model ",
-       x = "End Date of the Poll",  # Change x-axis label to End Date
-       y = "Predicted Support (%)",
-       color = "Candidate",
-       size="Weight",
-       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
-  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
-  theme_classic() +
-  theme(legend.position = "top",
-        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
-  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
-```
-
-## Predicted Support for Harris and Trump by Major Pollsters
-
-@fig-support-pollster1 and @fig-support-pollster2 depict the predicted support for Kamala Harris and Donald Trump in the 2024 U.S.
-election, from August 1, 2024, to October 27, 2024, using a weighted multiple linear regression model.
-The red line shows fluctuations in Trump’s support, generally between 40% and 55%, with some noticeable peaks and dips, indicating variability over time.
-In contrast, Harris’s support, represented by the blue line, remains more stable, consistently ranging around 40% to 50%, suggesting less volatility in voter sentiment for her.
-
-Pollsters such as AtlasIntel, Emerson, Beacon/Shaw, Siena/NY, and YouGov are represented by different colors, with circle sizes reflecting weights based on factors like recency and sample size.
-Larger circles correspond to higher-weighted polls, indicating they had a greater influence on the predictions.
-The model incorporates national poll data, adjustments for pollster effects, and population considerations, allowing for a refined prediction approach.
-This approach ensures that more recent and larger polls play a more significant role, capturing shifts in voter sentiment as the election approaches.
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| eval: true
-#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by Pollster using Unweighted Fitted Linear Model"
-#| label: fig-support-pollster1
-
+#| fig-subcap: ["Unweighted","Weighted"]
+#| layout-ncol: 2
+#| fig-cap: "Major Pollsters Siena/NYT and Quinnipiac favor Harris, while Emerson, AtlasIntel, and Beacon/Shaw present a more competitive picture"
+#| label: fig-support-pollster
+plan(multisession)
 # Calculate the top 10 pollsters by frequency in the data
@@
 
-ggplot(combined_data_total, aes(x = end_date, y = pct, size = combined_weight)) +
-  geom_point(aes(fill = pollster_group), alpha = 0.5, shape = 21, color = "black") + 
+ggplot(combined_data_total, aes(x = end_date, y = pct)) +
+  geom_point(aes(fill = pollster_group), alpha = 0.7, shape = 21) + 
   geom_line(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
@@
             aes(x = end_date, y = predicted_unweighted), color = "red", size = 1) +
-  facet_wrap(~ candidate, ncol = 2) +
   labs(
-    title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election by Top 5 Pollster \n(From August 1, 2024 to October 27, 2024)",
-    subtitle = "predicted using weighted multiple linear regression model",
     x = "End Date of the Poll",
     y = "Predicted Support (%)",
-    size = "Weight",
-    fill = "Pollster",
-    caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population"
-  ) +
+    color = "Candidate",
+    fill = "Top 5 Pollster",
+    caption = "Candidate Support Percentage = national_poll + pollster + population + state"
+  )+ # Smoothed trend line
+  facet_wrap(~ candidate,ncol = 2) +
   scale_fill_manual(values = c(setNames(rep("grey", length(unique(combined_data_total$pollster_group))), "Other"),
-                               setNames(rainbow(10), top_pollsters))) + # Assign colors to top pollsters and grey to others
+                               setNames(brewer.pal(10, "Set1"), top_pollsters))) + 
   theme_classic() +
   theme(
-    legend.position = "bottom",
-    legend.box = "horizontal",  # Place legends in a horizontal row
+    legend.position = "right",
+    legend.box = "vertical",  # Place legends in a horizontal row
     legend.title.align = 0.5,   # Center-align legend titles for better appearance
@@
 
-```
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-#| eval: true
-#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by Pollster using Weighted Fitted Linear Model"
-#| label: fig-support-pollster2
-
 ggplot(combined_data_total, aes(x = end_date, y = pct, size = combined_weight)) +
-  geom_point(aes(fill = pollster_group), alpha = 0.5, shape = 21, color = "black") + 
+  geom_point(aes(fill = pollster_group), alpha = 0.7, shape = 21) + 
   geom_line(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
@@
   geom_line(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
-            aes(x = end_date, y = predicted_weighted), color = "red", size = 1) +
-  facet_wrap(~ candidate, ncol = 2) +
+            aes(x = end_date, y = predicted_weighted), color = "red", size = 1)+
   labs(
-    title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election by Top 5 Pollster \n(From August 1, 2024 to October 27, 2024)",
-    subtitle = "predicted using weighted multiple linear regression model",
     x = "End Date of the Poll",
@@
     size = "Weight",
-    fill = "Pollster",
-    caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population"
-  ) +
+    color = "Candidate",
+    fill = "Top 5 Pollster",
+    caption = "Weights: recency_weight * sample_size_weight \nCandidate Support Percentage = national_poll + pollster + population + state"
+  )+ # Smoothed trend line
+  facet_wrap(~ candidate,ncol = 2) +
   scale_fill_manual(values = c(setNames(rep("grey", length(unique(combined_data_total$pollster_group))), "Other"),
-                               setNames(rainbow(10), top_pollsters))) + # Assign colors to top pollsters and grey to others
+                               setNames(brewer.pal(10, "Set1"), top_pollsters))) +
   theme_classic() +
   theme(
-    legend.position = "bottom",
-    legend.box = "horizontal",  # Place legends in a horizontal row
+    legend.position = "right",
+    legend.box = "vertical",  # Place legends in a horizontal row
     legend.title.align = 0.5,   # Center-align legend titles for better appearance
@@
 
-# Additional data details {#appendix-a}
+# Additional data details {#first-data-details}
 
@@
 
-# Model details {#appendix-b}
+# Model details {#sec-model-details}
 
@@
 # Residual plot for unweighted model
-plot(harris_unweighted_model, which = 1, main = "Residual Plot of Unweighted Linear Regression Model")
+plot(harris_unweighted_model, which = 1)
 
 # Q-Q plot for the residuals of the unweighted model
-qqnorm(residuals(harris_unweighted_model), main = "Q-Q Plot of Unweighted Linear Regression Model Residuals")
+qqnorm(residuals(harris_unweighted_model) )
 qqline(residuals(harris_unweighted_model), col = "red")
@@
 # Residual plot for weighted model
-plot(harris_weighted_model, which = 1, main = "Residual Plot of Weighted Linear Regression Model")
+plot(harris_weighted_model, which = 1)
 
 # Q-Q plot for the residuals of the weighted model
-qqnorm(residuals(harris_weighted_model), main = "Q-Q Plot of Weighted Linear Regression Model Residuals")
+qqnorm(residuals(harris_weighted_model))
 qqline(residuals(harris_weighted_model), col = "red")
@@
 clear pattern. This suggests the model is relatively well-specified.
-However, there is a slight curvature, indicating potential non-linearity
-that the model may not fully capture. A few notable outliers with larger
-residuals might be influencing the model, indicating that some data
-points have more significant prediction errors.
 
@@
 middle range. This suggests that our model satisfy the normality
-assumption. However, some points at the tails deviate, indicating
+assumption. However, some points at the head deviate, indicating
 potential outliers or non-normality in the extreme residual values. This
@@
 around zero, indicating that the weighted model captures the general
-trend without significant systematic bias. The curvature is slightly
-reduced compared to the un-weighted model, suggesting that weighting has
-helped in addressing some of the non-linearity observed in the
-un-weighted model. However, some residuals are still notably large,
-which may indicate outliers that influence the model despite the
-weighting scheme. This suggests that while the weighted model performs
-better in terms of capturing non-linearity, further refinement might
-still be beneficial.
+trend without significant systematic bias.
 
@@
 the residuals of the weighted model are close to normal. Similar to the
-unweighted model, there are deviations at the tails, though they appear
+unweighted model, there are deviations at the heads, though they appear
 less pronounced. This suggests that the weighting scheme has slightly
@@
 # Residual plot for unweighted model
-plot(trump_unweighted_model, which = 1, main = "Residual Plot of Unweighted Linear Regression Model")
+plot(trump_unweighted_model, which = 1)
 
 # Q-Q plot for the residuals of the unweighted model
-qqnorm(residuals(trump_unweighted_model), main = "Q-Q Plot of Unweighted Linear Regression Model Residuals")
+qqnorm(residuals(trump_unweighted_model))
 qqline(residuals(trump_unweighted_model), col = "red")
@@
 # Residual plot for weighted model
-plot(trump_weighted_model, which = 1, main = "Residual Plot of Weighted Linear Regression Model")
+plot(trump_weighted_model, which = 1)
 
 # Q-Q plot for the residuals of the weighted model
-qqnorm(residuals(trump_weighted_model), main = "Q-Q Plot of Weighted Linear Regression Model Residuals")
+qqnorm(residuals(trump_weighted_model))
 qqline(residuals(trump_weighted_model), col = "red")
@@
 unweighted model. It shows that the residuals are generally spread
-around zero with no clear pattern, suggesting that the model is
-relatively well-specified. However, there is a slight curvature,
-indicating possible non-linearity that the model may not fully capture.
-Some notable outliers with larger residuals suggest that certain data
-points have significant prediction errors, potentially influencing the
-model.
+around zero with no clear pattern, suggesting that the model is well-specified.
 
@@
 suggesting that the model satisfies the normality assumption. However,
-some points at the tails deviate, indicating potential outliers or
-non-normality in extreme residual values. This deviation at the ends
-suggests the model may face issues with extreme predictions, though it
-performs reasonably well overall.
+some points at the head deviate, indicating potential outliers or
+non-normality in extreme residual values.
 
@@
 that the weighted model captures the overall trend without significant
-systematic bias. The slight curvature seen in the unweighted model is
-reduced here, suggesting that weighting has addressed some of the
-non-linearity. However, some large residuals remain, which could
-indicate outliers that affect the model even with the weighting scheme.
-This suggests that while the weighted model has improved in handling
-non-linearity, further refinements could enhance accuracy.
+systematic bias.
 
 @fig-dia-4 shows the Q-Q plot for the weighted model compares residuals
-with a theoretical normal distribution. Here, the residuals generally
-align with the theoretical line, especially in the central range,
-indicating that the residuals of the weighted model are close to normal.
-Similar to the unweighted model, some deviations occur at the tails,
-though they appear less pronounced, suggesting that the weighting scheme
-has slightly improved the normality of residuals. Nonetheless, some
-extreme values persist, which may impact model robustness in cases of
-outliers.
+with a theoretical normal distribution. Here, the residuals almost fully
+align with the theoretical line,suggest that our data is almost normally distributed.
 
@@
 
-This appendix outlines the methodology used by the Siena College Polling Institute for conducting its surveys.
-Known for its methodological rigor, Siena College focuses on accurately capturing voter sentiment during elections and has conducted polls in key states such as Michigan, Wisconsin, and Ohio.
-
-In this section, we examine the main components of Siena's polling methodology, including the target population, sampling frame, recruitment processes, and sampling strategies.
-Additionally, we discuss how Siena addresses non-response and review the strengths and weaknesses of its questionnaire design.
-By detailing these elements, this appendix clarifies how Siena College ensures the reliability and validity of its polling results, offering valuable insights into voter behavior and election dynamics.
+This appendix outlines the methodology used by the Siena College Polling
+Institute for conducting its surveys. Known for its methodological
+rigor, Siena College focuses on accurately capturing voter sentiment
+during elections and has conducted polls in key states such as Michigan,
+Wisconsin, and Ohio.
+
+In this section, we examine the main components of Siena's polling
+methodology, including the target population, sampling frame,
+recruitment processes, and sampling strategies. Additionally, we discuss
+how Siena addresses non-response and review the strengths and weaknesses
+of its questionnaire design. By detailing these elements, this appendix
+clarifies how Siena College ensures the reliability and validity of its
+polling results, offering valuable insights into voter behavior and
+election dynamics.
 
@@
 have larger populations, we aim to adjust the sampling to reflect higher
-turnout rates.
+anticipation rates.
 
@@
 Our target population is all U.S. citizens eligible to vote in the 2024
-U.S. presidential election (age>=18).
+U.S. presidential election (age\>=18).
 
@@
 Nonresponse bias occurs when participants are unwilling or unable to
-answer certain questions or complete the survey.
-Handling non-response bias matters because it can skew survey results, leading to inaccurate conclusions that do not accurately represent the entire population's views or characteristics.
-Given that our survey
-takes approximately 15 minutes to complete, there is a risk of
-nonresponse bias. To mitigate this, as highlighted by @surveymonkey, we
-set clear expectations about the survey's purpose and estimated
-completion time, encouraging participants to stay engaged. Additionally,
-we apply post-stratification, adjusting survey weights to ensure that
-our respondent group aligns closely with the actual population
+answer certain questions or complete the survey. Handling non-response
+bias matters because it can skew survey results, leading to inaccurate
+conclusions that do not accurately represent the entire population's
+views or characteristics. Given that our survey takes approximately 15
+minutes to complete, there is a risk of nonresponse bias. To mitigate
+this, as highlighted by @surveymonkey, we set clear expectations about
+the survey's purpose and estimated completion time, encouraging
+participants to stay engaged. Additionally, we apply
+post-stratification, adjusting survey weights to ensure that our
+respondent group aligns closely with the actual population
 characteristics, reducing bias, and improving representativeness
@@
 response options, and for ordinal questions, we vary the order.
-Open-ended formats and pauses (e.g., "Who would you vote for? [pause]
+Open-ended formats and pauses (e.g., "Who would you vote for? \[pause\]
 Candidate A or Candidate B?") further minimize order effects.
@@
 
-Social Media Recruitment (Facebook, Instagram): $\$12,000$ 400 respondents
-recruited via targeted ads ($\$30$ each). Anticipating a 50% invalid rate,
-allowing for 200 valid responses after validation.
-
-Data Validation and Quality Control: $\$6,000$ Includes voter registration
-checks, attention filters, and post-collection quality review,
-especially for social media responses, to ensure data integrity.
+Social Media Recruitment (Facebook, Instagram): $\$12,000$ 400
+respondents recruited via targeted ads ($\$30$ each). Anticipating a 50%
+invalid rate, allowing for 200 valid responses after validation.
+
+Data Validation and Quality Control: $\$6,000$ Includes voter
+registration checks, attention filters, and post-collection quality
+review, especially for social media responses, to ensure data integrity.
 
@@
 Section 1: Survey Questions
-
-## Survey Questions
 

### 2024-11-03 paper/paper.qmd
update paper

@@
   theme_classic() +
-  theme(legend.position = "top",
+  theme(legend.position = "right",
         axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
@@
 with a median of 1.9. We also handle placeholder values in state
-information by setting entries marked as "--" to NA, and create a
-national_poll indicator, assigning a value of 1 for national polls and 0
-for state-specific ones. Dates are standardized using the lubridate
+information by setting entries marked as NA to National, and create a
+national_poll indicator, assigning a value of 1 for value in state equals to National and 0 for others. Dates are standardized using the lubridate
 package to facilitate accurate time-based analysis.
 
-Recency weights are calculated based on the days elapsed since the
-poll's end date, applying an exponential decay function to prioritize
-more recent polls. Weights based on sample size are capped at a maximum
-of 2,300 responses to maintain balanced representation. Additionally,
-categorical variables, including pollster, state, candidate_name,
+Recency are calculated based on the days elapsed since the
+poll's end date.Additionally,categorical variables, including pollster, state, candidate_name,
 population, and methodology, are converted to factors to prepare for

### 2024-11-03 paper/paper.qmd
Update discussion part, modified structure, added limitation section

@@
 
+Ultimately, these findings highlight the intricate dance between popular
+sentiment and the electoral mechanics of American democracy—a system where
+every vote counts, but some states matter just a bit more than others.
+
+## Limitations of the Dataset and Model
+
 Yet, as with all models, limitations persist. While our weighting
@@
 insights can illuminate trends, they cannot fully account for the
-unpredictable nature of electoral outcomes. Moving forward,
-incorporating real-time sentiment from social media or
-demographic-specific insights could offer a more responsive
-understanding of voter behavior. Ultimately, these findings highlight
-the intricate dance between popular sentiment and the electoral
-mechanics of American democracy—a system where every vote counts, but
-some states matter just a bit more than others.
-
-## Second discussion point
+unpredictable nature of electoral outcomes. While the dataset provides
+an overall approval rating for Harris, it lacks a breakdown by factors
+such as age, gender, income, and education, which are critical to
+understanding the preferences of different groups of voters. Without
+them, our analysis may have overlooked significant changes in specific
+groups that could affect overall trends.
 

### 2024-11-03 paper/paper.qmd
added future steps section in discussion part

@@
 
-## Weaknesses and next steps
+## Next Steps
+
+To enhance the predictive power of the model, historical voting data, economic
+indicators and major news events can be used as background variables. By analyzing
+the impact of similar factors on voter sentiment in past elections, we can gain
+insight into patterns and trends that may apply to the current campaign. For
+example, high-profile events have historically influenced voter opinion, and
+understanding these influences can provide a more complete picture of the factors
+that drive support for each candidate. Given the underlying conditions that influence
+voter preferences over time, this additional context would allow the model to make
+more informed predictions.
+
+Another possible improvement is the addition of detailed demographic information, such as age,
+gender, income level, and educational background, which would allow us to identify trends among
+specific groups of voters and thus greatly enhance our analysis. Different demographics often
+have unique responses to campaign issues and activities; for example, younger voters may
+prioritize different issues compared to older voters, and income level and educational
+attainment may influence political preferences in complex ways. By incorporating this level
+of granularity, future analyses can provide deeper insights into voter behavior and help
+develop more targeted campaign strategies.
 

### 2024-11-03 paper/paper.qmd
added recency in data

@@
 events, campaign actions, or other influencing factors.
+
+## Recency {#sec-recency}
+
+Recency is a newly created predictor variable in our dataset, specifically
+for use in our model. It is calculated as follows Recency = Election Date - End Date,
+where Election Date is set to November 5th. This variable quantifies the time
+interval between the poll's end date and the election date as a measure of the poll's
+relevance and potential impact on voter behavior. In general, polls conducted closer
+to the election date provide a more accurate picture of public opinion. The original
+dataset includes only dates, and by mutating this variable, we can more intuitively
+interpret the number of days before the election that each data point was collected.
+Converting this to discrete data enhances its usefulness in constructing predictive models.
+
+## National Poll {#sec-national-poll}
 

### 2024-11-03 paper/paper.qmd
added national poll in data

@@
 ## National Poll {#sec-national-poll}
+
+National polls is another newly created variable in our dataset, represented by a binary
+indicator (1 for national polls, 0 otherwise). This distinction is important because
+not all polls are conducted nationally; some are state-specific and may reflect the
+region's preference for a particular presidential candidate. Ignoring this distinction
+may introduce significant bias into our model. By labeling each poll as national or
+non-national, we can give higher weight to national polls, which are more representative
+of overall public opinion, and thus improve the accuracy of our predictive model.
 

### 2024-11-03 paper/paper.qmd
Update paper.qmd

@@
 This section examines the relationship between national polling trends,
-pollster effects, population demographics, and other factors with
+pollster effects, population(respondent group), and other factors with
 respect to the predicted support levels for Kamala Harris and Donald

### 2024-11-03 paper/paper.qmd
added population to data

@@
 of overall public opinion, and thus improve the accuracy of our predictive model.
+
+## Population {#population}
+
+The “population” variable in the dataset represents the status of each
+entry, categorizing participants as “lv” (likely voters) or “rv”
+(registered voters). They represent different levels of participation
+and potential voting behavior. Likely voters are individuals who are not
+only registered but are statistically more likely to vote based on historical
+data or survey responses. In contrast, registered voters include all
+individuals who are eligible to vote, regardless of their likelihood
+of participation.
 

### 2024-11-03 paper/paper.qmd
Update paper.qmd

@@
 The “population” variable in the dataset represents the status of each
-entry, categorizing participants as “lv” (likely voters) or “rv”
-(registered voters). They represent different levels of participation
-and potential voting behavior. Likely voters are individuals who are not
-only registered but are statistically more likely to vote based on historical
-data or survey responses. In contrast, registered voters include all
-individuals who are eligible to vote, regardless of their likelihood
-of participation.
+entry. it is the abbreviated description of the respondent group, categorizing
+participants as “lv” (likely voters) or “rv” (registered voters). They represent
+different levels of participation and potential voting behavior. Likely voters
+are individuals who are not only registered but are statistically more likely
+to vote based on historical data or survey responses. In contrast, registered
+voters include all individuals who are eligible to vote, regardless of their
+likelihood of participation.
 

### 2024-11-03 paper/paper.qmd
update paper with new model data

--- 2024-11-03 paper/paper.qmd
@@
 Harris over time, with data points and smoothed trend lines for each
-pollster. The x-axis represents the dates from August through October,
-while the y-axis indicates the percentage of respondents supporting
-Harris. Each color corresponds to a specific polling organization, with
+pollster. The graph shows the trend of the percentage of respondents supporting
+Harris from August through October. Each color corresponds to a specific polling organization, with
 prominent pollsters such as Beacon/Shaw, Ipsos, Siena/NYT, Emerson,
@@
 sentiment for Harris, with only slight fluctuations across numeric
-grades. By limiting the y-axis, outliers and extreme variations are
-minimized, resulting in a clearer and more interpretable visualization.
+grades. By limiting the maximum value of support at 80%, outliers and extreme variations are minimized, resulting in a clearer and more interpretable visualization.
 This approach emphasizes the central trend, allowing for clearer
@@
 
-ggplot(harris_data %>% filter(pct <= 100), aes(x = end_date, y = pct, color = factor(numeric_grade))) +
+ggplot(harris_data %>% filter(pct <= 80), aes(x = end_date, y = pct, color = factor(numeric_grade))) +
   geom_point(alpha = 0.7) +
   geom_smooth(se = FALSE, span = 0.3) +
-  labs(y = "Harris Percent", x = "Date", color = "Numeric Grade") +
+  labs(y = "Support for Harris", x = "Date", color = "Numeric Grade") +
   scale_color_viridis_d() +
@@
 @tbl-summary1 and @tbl-summary2, the intercepts for Harris and Trump,
-estimated at 45.10 and 59.28 respectively in the unweighted models,
+estimated at 44.70 and 59.28 respectively in the unweighted models, while in weighted models, it's estimated at 45.2 and 54.8,
 represent their baseline support levels when all predictors are at
-reference values. The high ( R\^2 ) values of 0.738 for Harris’s
-unweighted model and 0.860 for her weighted model, along with similar
-values of 0.635 and 0.890 for Trump, indicate that a significant portion
+reference values. The high ( R\^2 ) values of 0.824 for Harris’s
+unweighted model and 0.892 for her weighted model, along with similar
+values of 0.849 and 0.916 for Trump, indicate that a significant portion
 of the variation in support can be explained by the model's predictors.
@@
 reported support levels, as polls from the National level increase the
-support of Harris by 3.262%, decrease the support for Trump by 7.943%.
+support of Harris by 3.47%/4.27% , decrease the support for Trump by 7.61%/7.17%.
 The **population** predictor indicates that the type of respondent group
@@
 (populationrv) suggests a lower level of support for both Harris and
-Trump in this group compared to likely voters. Specifically, the support
-of registered voters is 2.1095 (unweighted model) and 1.0322 (weighted
+Trump in this group compared to likely voters. Specifically, the support for Harris
+of registered voters is 1.372 (unweighted model) or 0.529 (weighted
 model) lower than the likely voters. This implies that, on average,
@@
 @fig-support-trend-1 unweighted model, we see that Trump's predicted
-support generally hovers between 45% and 50%, while Harris's support
-ranges from 35% to 45%. Both candidates' support levels appear
+support generally hovers between 40% and 50%, while Harris's support
+ranges from 45% to 50%. Both candidates' support levels appear
 relatively stable across the polling period, with minor fluctuations.
-This model, which treats all polls equally, suggests a consistent lead
-for Trump, albeit within a fairly close range, as shown by the
-overlapping grey points representing individual poll results.
+This model, which treats all polls equally, suggests a consistent lead for Harris, albeit within a fairly close range.
 
@@
 to the unweighted model @fig-support-trend-1. Trump's support remains
-around the mid-40% range, while Harris’s support stays in the high 30%
-range. The weighting emphasizes more recent and larger polls, likely
-providing a more accurate reflection of current public opinion. Overall,
-both models consistently indicate a lead for Trump, with the weighted
-model slightly stabilizing the predictions.
+around the 40% to 50% range, while Harris’s support stays in about 45% to 52%  range. The weighting emphasizes more recent and larger polls, likely
+providing a more accurate reflection of current public opinion.
+Overall, both models consistently indicate a lead for Harris, with the weighted model slightly stabilizing the predictions.
+The average support for Harris and Trump are both consist for two models, which predicts that Harris will win on about 49%, leads Trump by about 2%.
 
@@
     max(harris_data$end_date),
-    length.out = 2000
+    length.out = 700
   ),
-  state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE)), 
-  pollster = factor(sample(levels(harris_data$pollster), size = 2000, replace = TRUE), 
+  state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 700, replace = TRUE)), 
+  pollster = factor(sample(levels(harris_data$pollster), size = 700, replace = TRUE), 
                     levels = levels(harris_data$pollster)), 
-  population = factor(sample(levels(harris_data$population), size = 2000, replace = TRUE), 
+  population = factor(sample(levels(harris_data$population), size = 700, replace = TRUE), 
                     levels = levels(harris_data$population)),
-  sample_size = sample(1:2300, size = 2000, replace = TRUE)
+  sample_size = sample(1:2300, size = 700, replace = TRUE)
 )|>
@@
     max(trump_data$end_date),
-    length.out = 2000
+    length.out = 700
   ),
-  pollster = factor(sample(levels(trump_data$pollster), size = 2000, replace = TRUE), 
+  pollster = factor(sample(levels(trump_data$pollster), size = 700, replace = TRUE), 
                     levels = levels(trump_data$pollster)),
- population= factor(sample(levels(trump_data$population), size = 2000, replace = TRUE), 
+ population= factor(sample(levels(trump_data$population), size = 700, replace = TRUE), 
                     levels = levels(trump_data$population)),
-   state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE), 
+   state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 700, replace = TRUE), 
                     levels = levels(trump_data$state)),  
-  sample_size =sample(1:2300, size = 2000, replace = TRUE),
-  pollster_quality= sample(2:4, size = 2000, replace = TRUE)
+  sample_size =sample(1:2300, size = 700, replace = TRUE)
 )|>
@@
     sample_size_weight = pmin(sample_size / 2300, 1),
-   pollster_quality_weight = pollster_quality / 4,  
     recency_weight = exp(-recency * 0.1),  
@@
 #| include: false
-# Predictions for Harris
-plan(multisession)
 new_data_harris <- new_data_harris |>
@@
   geom_point(alpha = 0.1)+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+
+  geom_smooth(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), method = "lm",size = 1)+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted),size = 0.2)+
   labs(
@@
   geom_point(alpha = 0.1)+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+
+  geom_smooth(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), method = "lm",size = 1)+ 
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 0.2)+
   labs(x = "End Date of the Poll",
@@
 In the @fig-support-state-1 , support for Kamala Harris and Donald Trump
-fluctuates widely across battleground states, with Harris holding slight
-leads in Pennsylvania and North Carolina but facing tight competition
-overall. Without weighting, polls contribute equally, creating more
+fluctuates widely across battleground states, with Harris holding significant
+leads in Michigan, and Pennsylvania.  Harris also hold advantage in Wisconsin but facing tight competition. Overall, without weighting, polls contribute equally, creating more
 volatility.
@@
 larger polls. Harris's support becomes more consistent, particularly in
-Pennsylvania, North Carolina, and Nevada, where she shows a clearer
+Pennsylvania, Michigan, and Wiscosin, where she shows a clearer
 lead. This weighted approach provides a more refined snapshot,
@@
 #| layout-ncol: 2
-#| fig-cap: "Harris is likely to lead Trump in Pennsylvania, North Carolina, and Nevada by Model Prediction"
+#| fig-cap: "Harris is likely to lead Trump in Pennsylvania, North Carolina, and Wisconsin by Model Prediction"
 #| label: fig-support-state
@@
 Donald Trump in the 2024 U.S. election, from August 1, 2024, to October
-27, 2024, using a weighted multiple linear regression model. The red
-line shows fluctuations in Trump’s support, generally between 40% and
-55%, with some noticeable peaks and dips, indicating variability over
-time. In contrast, Harris’s support, represented by the blue line,
-remains more stable, consistently ranging around 40% to 50%, suggesting
+27, 2024, using the unweighted and weighted multiple linear regression model. The red
+line shows average fluctuations in Trump’s support, generally between 46% and
+48%, with some noticeable peaks and dips, indicating variability over
+time. In contrast,the average Harris’s support, represented by the blue line,
+remains more stable, consistently ranging around 47% to 48%, suggesting
 less volatility in voter sentiment for her.
@@
 Major Pollsters are represented by different colors, with circle sizes
-reflecting weights based on factors like recency and sample size. Larger
+reflecting weights based on factors like recency and sample size. In the weighted model, larger
 circles correspond to higher-weighted polls, indicating they had a
@@
   geom_point(aes(fill = pollster_group), alpha = 0.7, shape = 21) + 
-  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
+  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
             aes(x = end_date, y = predicted_unweighted), color = "blue", size = 1) +
-  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
+  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
             aes(x = end_date, y = predicted_unweighted), color = "red", size = 1) +
@@
   geom_point(aes(fill = pollster_group), alpha = 0.7, shape = 21) + 
-  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
+  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
             aes(x = end_date, y = predicted_weighted), color = "blue", size = 1) +
-  geom_line(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
+  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
             aes(x = end_date, y = predicted_weighted), color = "red", size = 1)+

### 2024-11-03 paper/paper.qmd

@@
 of overall public opinion, and thus improve the accuracy of our predictive model.
+
+## Population {#population}
+
+The “population” variable in the dataset represents the status of each
+entry. it is the abbreviated description of the respondent group, categorizing
+participants as “lv” (likely voters) or “rv” (registered voters). They represent
+different levels of participation and potential voting behavior. Likely voters
+are individuals who are not only registered but are statistically more likely
+to vote based on historical data or survey responses. In contrast, registered
+voters include all individuals who are eligible to vote, regardless of their
+likelihood of participation.
 

### 2024-11-03 paper/paper.qmd
update paper

@@
 title: "Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach"
-subtitle: "Harris expects to win on 49%, leads Trump by about 2% in 2024 US election"
+subtitle: "Kamala Harris expects to win on 47.5%, leads Donald Trump by about 1% in 2024 US election"
 author: 
@@
 date-format: long
-abstract: "This paper predicts the outcome of the 2024 U.S.
-presidential election using a statistical model based on aggregated polling data for Kamala Harris and Donald Trump.
-We employ multi-level regression with post-stratification (MRP) using demographic predictors to estimate voter support.
-The analysis addresses polling biases and proposes an idealized survey methodology with a $100,000 budget.
-Our results offer insights into voter behavior and suggest improvements for future election forecasting models."
+abstract: "This study models the 2024 U.S.
+Presidential Election by analyzing polling data with adjustments for factors like recency and sample size, simulating an approach that captures up-to-date voter sentiment.
+Using recent 4 months aggregated poll data, the model identifies shifts in candidate support across key battleground states, providing a nuanced view of evolving preferences as election day approaches.
+By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering insights that could inform campaign strategies and public discourse.
+These findings highlight the value of weighting and time-sensitive adjustments in forecasting methods, balancing accuracy with responsiveness to the latest trends."
 format: pdf
@@
 library(RColorBrewer)
-library(gt)
 library(future)
+library(boot)    # For bootstrapping
+library(caret)   # For cross-validation
 ```
@@
 
-Research by Gelman and King (1993) underscores that while polls can
+Research by @GelKin93 underscores that while polls can
 exhibit variability over a campaign period, they can provide reliable
 predictions when adjusted for temporal changes and fundamental factors.
-Additionally, Erikson and Wlezien (2008) highlight the importance of
+Additionally, @politic highlight the importance of
 timing in polling, showing that data closer to election day tends to
@@
 
-The structure of this paper is organized as follows: @third-data
+The structure of this paper is organized as follows: @sec-data 
 provides details on the data sources and variables used in our analysis.
-@forth-model explains the modeling approach, including the assumptions
+@sec-model explains the modeling approach, including the assumptions
 and specifications of our linear regression framework. In
-@fifth-results, we present our findings, emphasizing the key predictors
-of Harris's support. Finally, @sixth-discussion explores the
+@sec-result, we present our findings, emphasizing the key predictors
+of Harris's support. Finally, @sec-discussion explores the
 implications of our results and suggests potential directions for future
-research. @appendix-a provide external data detail, @appendix-b provide
-model detail, @appendix-c provide a exploration for pollster
-methodology, @appendix-d provide a idealized methodology.
+research. @sec-a provide external data detail, @sec-b provide
+model detail, @sec-c provide a exploration for pollster Siena College's
+methodology, and  @sec-d provide a idealized methodology for polling the poll.
 
@@
 [@citeR]. Our dataset, obtained from FiveThirtyEight
-[@fivethirtyeight2024],based on polling as of 27 October 2024, provides
+[@fivethirtyeight2024],based on polling as of 2 November 2024, provides
 a detailed overview of public opinion in the lead-up to the election.
@@
 operations, the lubridate package proved invaluable, simplifying the
-manipulation of time variables [@citelubridate]. Lastly, arrow supported
+manipulation of time variables [@citelubridate]. Arrow supported
 efficient data input and output in a performance-oriented format,
-essential for managing larger datasets [@citearrow]. Our coding
-practices and file organization were informed by the structure outlined
+essential for managing larger datasets [@citearrow].
+We use ggplot2 [@citeggplot2] to visualize the analysis of data.
+In addition to the core packages, we employed several specialized libraries to facilitate specific analytical tasks.
+The modelsummary package enabled us to generate clean, interpretable model summaries, streamlining the reporting of regression and other statistical results [@citemodelsummary].
+RColorBrewer provided color palettes for visualizations, enhancing clarity and visual appeal in our plots [@citeRColorBrewer].
+The future package supported parallel processing, optimizing the runtime of intensive computations, especially beneficial in model training [@citefuture].
+Finally,for resampling and bootstrapping techniques, we utilized the boot package, which allowed us to assess model stability and reliability [@citeboot1;@citeboot2].
+caret facilitated model training and validation, offering a unified interface for cross-validation and performance metrics [@citecaret].
+Our coding practices and file organization were informed by the structure outlined
 in @tellingstories.
@@
 
+## Variables
+
+### End Date {#sec-end-date}
+
+The end date is the final day of data collection for a poll, indicating
+when the survey period concluded. This date provides crucial context for
+the poll results, as public opinion may change over time in response to
+events, campaign actions, or other influencing factors. In our analysis, we only choose the polls with end date after July 21 2024, which Kamala Harris first declared in the election.
+
+### Recency {#sec-recency}
+```{r}
+#| label: fig-recency
+#| fig-cap: Distribution of the recency of the polls after July 21 2024
+#| echo: false
+#| warning: false
+#| message: false
+ggplot(harris_data, aes(x = recency)) +
+  geom_histogram(binwidth = 1, fill = "gold", color = "grey50") +
+  labs(
+    x = "Recency (days)",
+    y = "Count"
+  ) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5))
+```
+
+Recency is a newly created predictor variable in our dataset, specifically
+for use in our model. It is calculated as follows Recency = Election Date - End Date,
+where Election Date is set to November 5th. This variable quantifies the time
+interval between the poll's end date and the election date as a measure of the poll's
+relevance and potential impact on voter behavior. In general, polls conducted closer
+to the election date provide a more accurate picture of public opinion. The original
+dataset includes only dates, and by mutating this variable, we can more intuitively
+interpret the number of days before the election that each data point was collected.
+Converting this to discrete data enhances its usefulness in constructing predictive models.
+@fig-recency reveals a strong focus on recent polling data, with the highest frequency of polls occurring within the first few days and gradually declining as recency increases.
+Periodic peaks around 30, 60, and 90 days suggest some regularity in polling schedules, though the overall trend emphasizes newer data.
+This distribution highlights the prioritization of recent polls in the dataset.
+
 ## Outcome variable {#sec-outcome-variable}
@@
   labs(
-    x = "Support Percentage",
+    x = "Support Percentage (%)",
     y = "Count"
@@
 
-### End Date {#sec-end-date}
-
-The end date is the final day of data collection for a poll, indicating
-when the survey period concluded. This date provides crucial context for
-the poll results, as public opinion may change over time in response to
-events, campaign actions, or other influencing factors.
-
-## Recency {#sec-recency}
-
-Recency is a newly created predictor variable in our dataset, specifically
-for use in our model. It is calculated as follows Recency = Election Date - End Date,
-where Election Date is set to November 5th. This variable quantifies the time
-interval between the poll's end date and the election date as a measure of the poll's
-relevance and potential impact on voter behavior. In general, polls conducted closer
-to the election date provide a more accurate picture of public opinion. The original
-dataset includes only dates, and by mutating this variable, we can more intuitively
-interpret the number of days before the election that each data point was collected.
-Converting this to discrete data enhances its usefulness in constructing predictive models.
-
-## National Poll {#sec-national-poll}
+```{r}
+#| label: tbl-category
+#| tbl-cap: Summary Statistics of categorical variable population and national_pull
+#| echo: false
+#| warning: false
+#| message: false
+harris_data|>select(population,national_poll)|>
+  datasummary_skim(type = "categorical")
+```
+
+### National Poll {#sec-national-poll}
 
 National polls is another newly created variable in our dataset, represented by a binary
-indicator (1 for national polls, 0 otherwise). This distinction is important because
+indicator (1 for polls at national level, 0 otherwise). This distinction is important because
 not all polls are conducted nationally; some are state-specific and may reflect the
@@
 of overall public opinion, and thus improve the accuracy of our predictive model.
-
-## Population {#population}
-
-The “population” variable in the dataset represents the status of each
+@tbl-category shows that for the national_poll variable, non-national polls (coded as 0) account for 681 cases (75.0%), whereas national polls (coded as 1) represent 227 cases (25.0%).
+This distribution highlights a focus on likely voters and a predominance of non-national polling data in the sample.
+
+### Population {#population}
+
+The "population" variable in the dataset represents the status of each
 entry. it is the abbreviated description of the respondent group, categorizing
@@
 voters include all individuals who are eligible to vote, regardless of their
-likelihood of participation.
+likelihood of participation. @tbl-category shows that likely voters (lv) constitute the majority with 620 cases (68.3%), while registered voters (rv) make up 288 cases (31.7%).
 
@@
 #| label: fig-state
-#| fig-cap: Count of polls by state
+#| fig-cap: Count of polls by the US state 
 #| echo: false
@@
 #| label: fig-pollster
-#| fig-cap: Frequency of Polls by Pollster"
+#| fig-cap: Frequency of Polls by Pollster
 #| echo: false
@@
 @tbl-summary1 and @tbl-summary2, the intercepts for Harris and Trump,
-estimated at 44.70 and 59.28 respectively in the unweighted models, while in weighted models, it's estimated at 45.2 and 54.8,
+estimated at 44.70% and 59.28% respectively in the unweighted models, while in weighted models, it's estimated at 45.2% and 54.8%,
 represent their baseline support levels when all predictors are at
@@
 @fig-support-trend illustrate the predicted support for Kamala Harris
-and Donald Trump from August 1, 2024, to October 27, 2024, using both
+and Donald Trump from August 1, 2024, to November 2, 2024, using both
 unweighted and weighted linear regression models. In the
@@
 Overall, both models consistently indicate a lead for Harris, with the weighted model slightly stabilizing the predictions.
-The average support for Harris and Trump are both consist for two models, which predicts that Harris will win on about 49%, leads Trump by about 2%.
+The average support for Harris and Trump are both consist for two models, which predicts that Harris will win on about 47%, leads Trump by about 1%.
 
@@
   mutate(
-    national_poll = if_else(state == "National", 1, 0),
+    national_poll = factor(if_else(state == "National", 1, 0)),
     recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
@@
   mutate(
-   national_poll = if_else(state == "National", 1, 0),
+   national_poll = factor(if_else(state == "National", 1, 0)),
       recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
@@
 # Determine the maximum end date for setting the x-axis limit
-max_end_date <- as.Date("2024-10-26")
+max_end_date <- as.Date("2024-11-2")
 ```
@@
 #| eval: true
-#| fig-cap: "Harris Kamala leads Donald Trump an average 5% in Predicted Support in the 2024 US Election (From August 1, 2024, to October 27, 2024)"
+#| fig-cap: "Harris Kamala leads Donald Trump an average 2% in Predicted Support in the 2024 US Election (From August 1, 2024, to November 2, 2024)"
 #| fig-subcap: ["Unweighted","Weighted"]
-#| layout-ncol: 2
+#| layout-ncol: 1
 #| label: fig-support-trend
@@
   theme_classic() +
-  theme(legend.position = "right",
+  theme(legend.position = "bottom",
         axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
-  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) +
+  annotate("text", x = max(combined_predictions_filtered$end_date) -0.5, y = 48, 
+           label = "47.5%", color = "blue", hjust = -0.2, size = 2) +  # Adjust size here
+  annotate("text", x = max(combined_predictions_filtered$end_date) - 0.5, y = 46, 
+           label = "46.5%", color = "red", hjust = -0.2, size = 2)
+
 ##weighted
@@
   theme_classic() +
-  theme(legend.position = "right",
+  theme(legend.position = "bottom",
         axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
-  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
+  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) +
+  annotate("text", x = max(combined_predictions_filtered$end_date) -0.5, y = 48, 
+           label = "47.5%", color = "blue", hjust = -0.2, size = 2) +  # Adjust size here
+  annotate("text", x = max(combined_predictions_filtered$end_date) - 0.5, y = 46, 
+           label = "46.5%", color = "red", hjust = -0.2, size = 2)
 ```
@@
 across most states, with slight variations in trends across the polling
-period from August to October 2024.
+period from August to November 2024.
 
@@
 larger polls. Harris's support becomes more consistent, particularly in
-Pennsylvania, Michigan, and Wiscosin, where she shows a clearer
+Pennsylvania, Michigan, and Wisconsin, where she shows a clearer
 lead. This weighted approach provides a more refined snapshot,
@@
 #| fig-subcap: ["Unweighted","Weighted"]
-#| layout-ncol: 2
-#| fig-cap: "Harris is likely to lead Trump in Pennsylvania, North Carolina, and Wisconsin by Model Prediction"
+#| layout-ncol: 1
+#| fig-cap: "Harris is likely to lead Trump in Pennsylvania, Michigan, and Wisconsin by Model Prediction"
 #| label: fig-support-state
@@
 combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
-
-ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
+late<-combined_predictions_filtered[which.max(combined_predictions_filtered$end_date), ]
+ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate))+
   geom_point(alpha = 0.1)+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 0.5)+ # Smoothed trend line
+  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 0.5)+
   facet_wrap(~ state,ncol = 4) +
@@
   theme_classic() +
-  theme(legend.position = "top",
-        axis.text.x = element_text(angle = 90, hjust = 1),
+  theme(legend.position = "bottom",
+        axis.text.x = element_text(angle = 90, hjust = 1, size =6),
         legend.box = "vertical",
@@
   theme_classic() +
-  theme(legend.position = "top",
-        axis.text.x = element_text(angle = 90, hjust = 1),
+  theme(legend.position = "bottom",
+        axis.text.x = element_text(angle = 90, hjust = 1,size=6),
         legend.box = "vertical",
@@
 @fig-support-pollster depict the predicted support for Kamala Harris and
-Donald Trump in the 2024 U.S. election, from August 1, 2024, to October
-27, 2024, using the unweighted and weighted multiple linear regression model. The red
+Donald Trump in the 2024 U.S. election, from August 1, 2024, to November
+2, 2024, using the unweighted and weighted multiple linear regression model. The red
 line shows average fluctuations in Trump’s support, generally between 46% and
@@
 #| fig-subcap: ["Unweighted","Weighted"]
-#| layout-ncol: 2
+#| layout-ncol: 1
 #| fig-cap: "Major Pollsters Siena/NYT and Quinnipiac favor Harris, while Emerson, AtlasIntel, and Beacon/Shaw present a more competitive picture"
@@
   theme(
-    legend.position = "right",
+    legend.position = "bottom",
     legend.box = "vertical",  # Place legends in a horizontal row
     legend.title.align = 0.5,   # Center-align legend titles for better appearance
-    axis.text.x = element_text(angle = 45, hjust = 1),
+    axis.text.x = element_text(angle = 45, hjust = 1,size=8),
     strip.background = element_rect(colour = "black", fill = "white")
@@
     size = "Weight",
-    color = "Candidate",
     fill = "Top 5 Pollster",
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
@@
 
-In states like Wisconsin and Arizona, our model highlights just how
-close the race remains. Wisconsin, for instance, shows both candidates
-locked in a near tie around 48% support—a statistical dead heat that
-brings the state’s significance into sharp relief. Arizona, meanwhile,
+In states like Nevada and North Carolina, our model highlights just how
+close the race remains. North Carolina, for instance, shows both candidates
+locked in a near tie around 47% support—a statistical dead heat that
+brings the state’s significance into sharp relief. Neveda, meanwhile,
 leans modestly toward Trump, a reflection of the unique demographic and
@@
 election night, as even slight changes in turnout or last-minute shifts
-in opinion could tip the balance.
+in opinion could tip the balance. improve the number based on the graph results
 
@@
 every vote counts, but some states matter just a bit more than others.
+
+## Influence of Weighting Methodology in Analyzing Voters' Preference
+
+In our analysis and shown result, we find out that the use of a weighted model helps to reduce volatility in predicted support trends by assigning greater importance to polls that are both recent and based on larger sample sizes.
+This approach effectively smooths out abrupt fluctuations that might otherwise result from older or smaller polls, providing a more stable and coherent view of voter sentiment.
+hough our data filtered with recent polls after Harris's candidacy announcement, voter sentiment remains fluid, with ongoing debates and events likely to influence preferences.
+By emphasizing recent polls, the model is more responsive to the latest shifts in public opinion, which is especially relevant as election day approaches and voters’ preferences may crystallize.
+Larger-sample polls, often conducted by established pollsters like Siena/NYT or Emerson, are assumed to be more reliable, and their increased weight in the model further reduces the likelihood of erratic changes driven by smaller, less consistent polls.
+This decreased volatility allows the model to present a clearer picture of the general support trend for each candidate, reducing noise and highlighting true shifts in sentiment.
+However, this smoothing effect may also mask some of the localized or short-term dynamics captured by less frequent or smaller-sample polls, which could provide unique insights into specific voter groups or state-level shifts.
 
@@
 
-## Third discussion point
-
 ## Next Steps
@@
 
-# Additional data details {#first-data-details}
+# Additional data details {#sec-a}
 
@@
 
-# Model details {#sec-model-details}
+# Model details {#sec-b}
 
@@
 # Load necessary libraries
-library(boot)    # For bootstrapping
-library(caret)   # For cross-validation
 
@@
 
-Harris model: RMSE of 3.41, indicating an average prediction error of
-around 3.44 percentage points.\
-Trump model: RMSE of 4.28, showing a slightly higher prediction error on
+Harris model: RMSE of 2.43, indicating an average prediction error of
+around 2.43 percentage points.\
+Trump model: RMSE of 2.57, showing a slightly average prediction error on
 average.\
@@
 variable explained by the model (higher is better).\
-Harris model: R-squared of 0.34, meaning the model explains about 34.6%
+Harris model: R-squared of 0.63, meaning the model explains about 63%
 of the variance in Harris's polling data.\
-Trump model: R-squared of 0.28 as well, indicating similar explanatory
-power for Trump's polling data.
+Trump model: R-squared of 0.66, meaning the model explains about 66%
+of the variance in Trump's polling data.
 
@@
 observed and predicted values (lower is better).\
-Harris model: MAE of 2.40, meaning that, on average, the predictions are
-off by 2.48 percentage points.\
-Trump model: MAE of 3.09, indicating slightly less precise predictions
+Harris model: MAE of 1.6, meaning that, on average, the predictions are
+off by 1.62 percentage points.\
+Trump model: MAE of 1.62, indicating slightly higher precise predictions
 compared to the Harris model.\
@@
 by its lower RMSE and MAE values.\
-Model Fit: Harris' model explain roughly 34% of the variance in their
-respective datasets. Trump's models explain roughly 28% of the variance
+Model Fit: Harris' model explain roughly 63% of the variance in their
+respective datasets. Trump's models explain roughly 66% of the variance
 in their respective datasets.This suggests that other factors not
@@
 
-@fig-stanareyouokay-1 is a residual plot of un-weighted model for Harris
+@fig-stanareyouokay-1 and @fig-stanareyouokay-3 are residual plots of un-weighted model for Harris
 support. It showsthe residuals are generally spread around zero, with no
@@
 
-@fig-stanareyouokay-2 is a Q-Q plot of un-weighted model plot for Harris
-support. It shows most residuals fall along the line, especially in the
+@fig-stanareyouokay-2 and @fig-stanareyouokay-4 is are Q-Q plots of un-weighted and weighted model plot for Harris support. It shows most residuals fall along the line, especially in the
 middle range. This suggests that our model satisfy the normality
-assumption. However, some points at the head deviate, indicating
+assumption. However, some points at the head and tail deviate, indicating
 potential outliers or non-normality in the extreme residual values. This
@@
 
-@fig-stanareyouokay-3 is a residual plot of weighted model for Harris
-support.It shows residuals are again plotted against fitted values.
-Similar to the unweighted model, the residuals are mostly centered
-around zero, indicating that the weighted model captures the general
-trend without significant systematic bias.
-
-@fig-stanareyouokay-4 is a Q-Q Plot of weighted model plot for Harris
-support.The residuals generally align with the theoretical normal
-distribution line, particularly in the central range, indicating that
-the residuals of the weighted model are close to normal. Similar to the
-unweighted model, there are deviations at the heads, though they appear
-less pronounced. This suggests that the weighting scheme has slightly
-improved the distribution of residuals, making the model’s predictions
-more robust. However, some extreme values remain, which could still
-affect model
-
-In summary, both models show a reasonably good fit, with the weighted
-model offering slight improvements in handling non-linearity and extreme
-values. However, both models exhibit minor deviations from normality and
-a few notable outliers, which may warrant further model adjustments for
+In summary, both models show a reasonably good fit. Both models exhibit minor deviations from normality and a few notable outliers, which may warrant further model adjustments for
 improved prediction accuracy.
@@
 
-@fig-dia-1 shows the residuals plotted against the fitted values for the
-unweighted model. It shows that the residuals are generally spread
-around zero with no clear pattern, suggesting that the model is well-specified.
-
-@fig-dia-2 shows the Q-Q plot for the unweighted model, showing that
+@fig-dia-1 and @fig-dia-3 shows the residuals plotted against the fitted values for the
+unweighted model for Trump's Support. It shows that the residuals are generally spread
+around zero with no clear pattern for both model, suggesting that the model is well-specified.
+
+@fig-dia-2 and @fig-dia-4 shows the Q-Q plot for the unweighted and weighted model for Trump's Support, showing that
 most residuals fall along the line, especially in the middle range,
 suggesting that the model satisfies the normality assumption. However,
-some points at the head deviate, indicating potential outliers or
+some points at the head and tail deviate, indicating potential outliers or
 non-normality in extreme residual values.
-
-@fig-dia-3 shows residuals plotted against fitted values. Similar to the
-unweighted model, the residuals are centered around zero, indicating
-that the weighted model captures the overall trend without significant
-systematic bias.
-
-@fig-dia-4 shows the Q-Q plot for the weighted model compares residuals
-with a theoretical normal distribution. Here, the residuals almost fully
-align with the theoretical line,suggest that our data is almost normally distributed.
 
@@
 
-# The New York Times/Siena College Polling Methodology {#appendix-c}
+# The New York Times/Siena College Polling Methodology {#sec-c}
 
@@
 
-# Idealized Methodology for US Presidential Election Forecast {#appendix-d}
+# Idealized Methodology for US Presidential Election Forecast {#sec-d}
 
@@
 
-We have defined the bias we want to solve in [Appendix C](#third-poll).
+We have defined the bias we want to solve in @sec-pollster.
 

### 2024-11-03 scripts/00-simulate_data.R
update script

@@ -1,52 +1,54 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates a dataset of 2024 US election poll of polls.
+# Author: Diana Shen, Jinyan Wei, Huayan Yu
+# Date: 3 November 2024 
+# Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `tidyverse` package must be installed
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
-
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
+library(lubridate)
 
+#### Data expected structure ####
+# Simulated Data Harris:
+# - Columns: pollscore, end_date, pollster, numeric_grade, national_poll, recency, state, population, sample_size, pct, candidate, sample_size_weight, recency_weight, combined_weight
+# - pollscore should be between -1.5 and 2
+# - end_date should be between 2024-07-21 and 2024-11-2
+# - pollster should be one of: "Pollster A", "Pollster B", "Pollster C", "Pollster D".
+# - numeric_grade should be between 0.5 and 3
+# - national_poll should be one of: 0 and 1.
+# - state should be valid US state abbreviations
+# - population should be one of: "lv", "rv"
+# - recency should greater than 0.
+# - candidate should be one of: "Donald Trump", "Kamala Harris"
+# - pct should be between 30 and 80
+# - sample_size should be between 0 and 2300
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
-)
+# Define states, candidates, and other factors
+states <- c("National", "Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
+candidates <- c("Kamala Harris", "Donald Trump")
+pollsters <- c("Pollster A", "Pollster B", "Pollster C", "Pollster D")
+populations <- c("rv", "lv")
 
-# Political parties
[…]

### 2024-11-03 scripts/01-test_simulated_data.R

@@ -1,89 +1,149 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the 2024 US election poll of polls
+# simulated dataset.
+# Author: Diana Shen, Jinyan Wei, Huayan Yu
+# Date: 3 November 2024 
+# Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
+# - The `tidyverse`, `testthat`,`lubridate`,`arrow` package must be installed and loaded
+# - 03-clean_data.R must have been run
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(testthat)
+library(lubridate)
+library(arrow)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
-
+simulated_data <- read_csv("data/00-simulated_data/simulated_data.csv")
 # Test if the data was successfully loaded
-if (exists("analysis_data")) {
+if (exists("simulated_data")) {
   message("Test Passed: The dataset was successfully loaded.")
 } else {
   stop("Test Failed: The dataset could not be loaded.")
 }
 
-
 #### Test data ####
+## test simulated data has correct structure
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
+test_that("Simulated Harris data has correct structure", {
+  expect_true(is.numeric(simulated_data$poll_score))
+  expect_true(inherits(simulated_data$end_date, "Date"))
+  expect_true(is.character(simulated_data$pollster))
+  expect_true(is.numeric(simulated_data$numeric_grade))
+  expect_true(is.numeric(simulated_data$national_poll))
+  expect_true(is.numeric(simulated_data$recency))
+  expect_true(is.character(simulated_data$state))
+  expect_true(is.character(simulated_data$population))
+  expect_true(is.numeric(simulated_data$sample_size))
+  expect_true(is.numeric(simulated_data$pct))
[…]

### 2024-11-03 scripts/02-download_data.R

@@ -1,11 +1,12 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from FiveThirtyeight,com
+# Purpose: Downloads and saves the data from FiveThirtyeight.com of 2024 US election poll of polls.
 # Author: Diana Shen, Jinyan Wei, Huayan Yu
-# Date: 27 October 2024 
+# Date: 2 November 2024 
 # Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites:
+# - Packages `tidyverse` must be installed and loaded
+# Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Workspace setup ####

### 2024-11-03 scripts/03-clean_data.R

@@ -1,11 +1,13 @@
 #### Preamble ####
-# Purpose: Cleans the raw poll data recorded
+# Purpose: Cleans the raw 2024 US election poll of polls data recorded as of 2 November 2024.
 # Author: Diana Shen, Jinyan Wei, Huayan Yu
-# Date: 27 October 2024 
+# Date: 2 November 2024
 # Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: not needed
-# Any other information needed? not needed
+# Pre-requisites:  
+# - The `tidyverse`, `janitor`,`lubridate`,`arrow` package must be installed and loaded
+# - 02-download_data.R must have been run
+# Any other information needed? Make sure you are in the `starter_folder` rproj
 
 #### Workspace setup ####
 library(tidyverse)
@@ -22,8 +24,8 @@ cleaned_data <- raw_data |>
 just_harris_high_quality <- cleaned_data |>
   # Select relevant columns for analysis
   select(
-    pollster, numeric_grade, state, candidate_name, pct, sample_size, 
-    population, methodology, start_date, end_date
+    pollster, numeric_grade, state, candidate_name, pct, sample_size, pollscore,
+    population, end_date
   )|>filter(population %in% c("lv", "rv"))|>
   # Drop rows with missing values in essential columns
   drop_na(numeric_grade, pct, sample_size, end_date)|>
@@ -35,9 +37,9 @@ just_harris_high_quality <- cleaned_data |>
     state = if_else(is.na(state) | state == "--", "National", state),
     national_poll = if_else(state == "National", 1, 0)  # 1 for national, 0 for state-specific
   ) |> mutate(
-    start_date = mdy(start_date),
     end_date = mdy(end_date)
   )|>
+  filter(end_date >= as.Date("2024-07-21"))|>
   mutate(
     recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days"))
   ) |>
@@ -46,14 +48,14 @@ just_harris_high_quality <- cleaned_data |>
     state = factor(state),
     candidate_name = factor(candidate_name),
     population = factor(population),  # Only if appropriate
-    methodology = factor(methodology)
+    national_poll = factor(national_poll)
   )
 
 just_trump_high_quality <- cleaned_data|>
   # Select relevant columns for analysis
   select(
[…]

### 2024-11-03 scripts/04-test_analysis_data.R

@@ -1,92 +1,125 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the structure and validity of the cleaned 2024 US election poll of polls
+# analysis dataset.
+# Author: Diana Shen, Jinyan Wei, Huayan Yu
+# Date: 3 November 2024 
+# Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+# - The `tidyverse`, `testthat`,`lubridate`,`dplyr` package must be installed and loaded
+# - 03-clean_data.R must have been run
+# Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
+library(lubridate)
+library(dplyr)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
-
-raw_igme_data <-
-  read_csv(
-    file = "data/01-raw_data/raw_election_24.csv",
-    col_select = c(`Geographic area`, TIME_PERIOD, OBS_VALUE),
-    col_types = cols(
-      `Geographic area` = col_character(),
-      TIME_PERIOD = col_character(),
-      OBS_VALUE = col_double(),
-    )
-  )
+analysis_data_harris <- read_csv("data/02-analysis_data/analysis_data_Harris.csv")
+analysis_data_trump <- read_csv("data/02-analysis_data/analysis_data_Trump.csv")
+#### combined two dataset to test together
+combined_data <- bind_rows(analysis_data_harris, analysis_data_trump)
+# Test if the data was successfully loaded
+if (exists("combined_data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
+## test analysis data has correct structure
[…]

### 2024-11-03 scripts/05-model_data.R

@@ -1,10 +1,13 @@
 #### Preamble ####
-# Purpose: Model Harris's support in the 2024 U.S. presidential election using weighted and unweighted linear models.
-# Author: [Your Name]
-# Date: [Today's Date]
-# Contact: [Your Email]
+# Purpose: Model Harris' and Trump's support in the 2024 U.S. presidential election using weighted and unweighted linear models.
+# Author: Diana Shen, Jinyan Wei, Huayan Yu
+# Date: 3 November 2024 
+# Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Cleaned data file `cleaned_harris_support.csv` should be available in the `data/02-analysis_data/` directory.
+# Pre-requisites: 
+# - Cleaned data file `analysis_data_Harris.parquet` and `analysis_data_Trump.parquet` should be available in the `data/02-analysis_data/` directory.
+# - Packages `arrow`, and `dplyr` must be installed and loaded
+# Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Load cleaned data ####

### 2024-11-03 paper/paper.qmd
update paper

@@
 Using recent 4 months aggregated poll data, the model identifies shifts in candidate support across key battleground states, providing a nuanced view of evolving preferences as election day approaches.
-By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering insights that could inform campaign strategies and public discourse.
+By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering understanding that could inform campaign strategies and public discourse.
 These findings highlight the value of weighting and time-sensitive adjustments in forecasting methods, balancing accuracy with responsiveness to the latest trends."
@@
 events. This study aims to forecast the percentage of support for Kamala
-Harris, offering insights into the elements that shape voter preferences
+Harris, offering understanding into the elements that shape voter preferences
 as the election nears. By examining data from multiple polling sources,
@@
 timing in polling, showing that data closer to election day tends to
-stabilize and therefore becomes more predictive. Our research seeks to
-fill a gap in existing literature that often fails to address the
-complexities of polling data, thereby enhancing our understanding of
-voter behavior within the electoral context.
+stabilize and therefore becomes more predictive.
+Our research addresses aspects of the literature that often overlook the detailed complexities of polling data, enriching our understanding of voter behavior within the electoral context.
 
@@
 
-Our findings reveal a notable positive correlation between the end date
+Our findings demonstrate a notable positive correlation between the end date
 and the percentage of support, indicating that as the election
@@
 affected results, with more reputable polls correlating with higher
-levels of support. These insights emphasize the necessity of considering
+levels of support. These results emphasize the necessity of considering
 both the timing of polls and the characteristics of different polling
@@
 This research is important because precise predictions of voter support
-are crucial for effective campaign strategies. By identifying the main
+are necessary for effective campaign strategies. By identifying the main
 factors influencing support for Harris, campaign teams can customize
@@
 focus during the campaign. Given that elections can be decided by narrow
-margins, having trustworthy insights into voter preferences can
+margins, having trustworthy understanding into voter preferences can
 substantially influence the final outcomes.
@@
 research. @sec-a provide external data detail, @sec-b provide
-model detail, @sec-c provide a exploration for pollster Siena College's
+model detail, @sec-c provide a investigation for pollster Siena College's
 methodology, and  @sec-d provide a idealized methodology for polling the poll.
@@
 manipulation, modeling, and visualization capabilities. The tidyverse
-package offered a comprehensive set of tools for data wrangling and
+package offered a detailed set of tools for data wrangling and
 analysis, improving workflow efficiency [@thereferencecanbewhatever].
@@
 cleaning and validation procedures to rectify inconsistencies and handle
-any missing information. This step is crucial for ensuring that the
+any missing information. This step is necessary for ensuring that the
 dataset accurately mirrors the electorate's sentiments. Following data
 cleaning, polling results are aggregated to smooth out individual poll
-biases and mitigate random error. This aggregation process leverages
+biases and mitigate random error. This aggregation process employs
 weighting based on poll quality, sample size, recency, and the
@@
 effectively converts subjective opinions into measurable data, providing
-valuable insights into voter behavior and preferences.
+valuable understanding into voter behavior and preferences.
 
@@
 The end date is the final day of data collection for a poll, indicating
-when the survey period concluded. This date provides crucial context for
+when the survey period concluded. This date provides necessary context for
 the poll results, as public opinion may change over time in response to
@@
 Converting this to discrete data enhances its usefulness in constructing predictive models.
-@fig-recency reveals a strong focus on recent polling data, with the highest frequency of polls occurring within the first few days and gradually declining as recency increases.
+@fig-recency demonstrates a strong focus on recent polling data, with the highest frequency of polls occurring within the first few days and gradually declining as recency increases.
 Periodic peaks around 30, 60, and 90 days suggest some regularity in polling schedules, though the overall trend emphasizes newer data.
@@
 organizations prioritizing both national sentiment and swing states
-where public opinion is more volatile. Overall, the chart provides
-insight into where polling resources are allocated as election day
+where public opinion is more volatile. Overall, the chart illustrates how polling resources are allocated as election day
 nears, emphasizing areas that could sway the final result.
@@
 prominent pollsters such as Beacon/Shaw, Ipsos, Siena/NYT, Emerson,
-Quinnipiac, and YouGov. The smoothed lines reveal subtle trends over
+Quinnipiac, and YouGov. The smoothed lines demonstrate subtle trends over
 time, with some pollsters like Emerson and Beacon/Shaw showing a slight
@@
 polls have a greater impact on the model's predictions, providing a
-balanced and comprehensive assessment of candidate support.
+balanced and detailed assessment of candidate support.
 
@@
 
-Our model reveals a portrait of a nation deeply divided, with Harris
+Our model demonstrates a portrait of a nation deeply divided, with Harris
 holding a narrow 49% edge over Trump’s 47% in national support. However,
@@
 leans modestly toward Trump, a reflection of the unique demographic and
-political nuances shaping each battleground. These state-level insights
-illuminate a critical truth: while national polls offer a snapshot of
+political nuances shaping each battleground. These state-level results
+illuminate a significant truth: while national polls offer a snapshot of
 overall sentiment, they risk obscuring the specific, local dynamics that
@@
 
-Ultimately, these findings highlight the intricate dance between popular
+Ultimately, these findings highlight the complex dance between popular
 sentiment and the electoral mechanics of American democracy—a system where
@@
 This decreased volatility allows the model to present a clearer picture of the general support trend for each candidate, reducing noise and highlighting true shifts in sentiment.
-However, this smoothing effect may also mask some of the localized or short-term dynamics captured by less frequent or smaller-sample polls, which could provide unique insights into specific voter groups or state-level shifts.
+However, this smoothing effect may also mask some of the localized or short-term dynamics captured by less frequent or smaller-sample polls, which could provide unique understanding into specific voter groups or state-level shifts.
 
@@
 
-Yet, as with all models, limitations persist. While our weighting
-system, with its emphasis on recent data, aims to capture a timely
-snapshot of voter sentiment, it may miss sudden changes sparked by
-campaign events or unexpected shifts in public discourse. The
-variability in our state projections—ranging from a low estimate of 363
-electoral votes for Harris to a high of 471—reflects the inherent
-uncertainty in polling-based models, particularly given the constraints
-of our data sources. This wide range suggests that while data-driven
-insights can illuminate trends, they cannot fully account for the
-unpredictable nature of electoral outcomes. While the dataset provides
-an overall approval rating for Harris, it lacks a breakdown by factors
-such as age, gender, income, and education, which are critical to
-understanding the preferences of different groups of voters. Without
-them, our analysis may have overlooked significant changes in specific
-groups that could affect overall trends.
+Despite the strengths of our model, limitations remain.
+Our weighting system prioritizes recent data to reflect current voter sentiment; however, it may miss abrupt shifts triggered by campaign events or changing public opinion.
+While our model can capture trends, it may not fully anticipate unpredictable electoral dynamics.
+Additionally, our dataset lacks demographic breakdowns by age, gender, income, and education, which are essential for understanding the preferences of specific voter groups.
+This absence may obscure meaningful trends within key demographic segments, affecting the model’s precision in reflecting voter sentiment shifts across diverse populations.
 
@@
 indicators and major news events can be used as background variables. By analyzing
-the impact of similar factors on voter sentiment in past elections, we can gain
-insight into patterns and trends that may apply to the current campaign. For
+the impact of similar factors on voter sentiment in past elections, we can understand the patterns and trends that may apply to the current campaign. For
 example, high-profile events have historically influenced voter opinion, and
@@
 attainment may influence political preferences in complex ways. By incorporating this level
-of granularity, future analyses can provide deeper insights into voter behavior and help
+of granularity, future analyses can provide deeper understanding into voter behavior and help
 develop more targeted campaign strategies.
@@
 structured approach ensures that the data is accurate, complete, and
-optimized for insightful statistical analysis.
+optimized for the following statistical analysis.
 
@@
 clarifies how Siena College ensures the reliability and validity of its
-polling results, offering valuable insights into voter behavior and
+polling results, offering valuable understanding into voter behavior and
 election dynamics.
@@
 Siena College Polling Institute is a prominent pollster known for its
-comprehensive and methodologically rigorous surveys. It specializes in
+detailed and methodologically rigorous surveys. It specializes in
 political polling and is particularly recognized for its work in
@@
 
-The sampling frame is a comprehensive list of registered voters, which
+The sampling frame is a detailed list of registered voters, which
 includes demographic information for each voter. This enables the
@@
 phones, using live interviewers to improve data quality and capture
-nuanced responses. Through random digit dialing or voter registration
+subtle responses. Through random digit dialing or voter registration
 databases, researchers achieve a representative sample across
@@
 smaller subgroups are adequately included, allowing researchers to
-allocate resources more efficiently and gain deeper insights into
+allocate resources more efficiently and gain deeper understanding into
 specific groups. However, this method can lead to **higher costs** due
@@
     respondents to avoid embarrassment and project a favorable image to
-    others, resulting in respondents not revealing their actual
+    others, resulting in respondents not demonstrateing their actual
     attitudes. The prevalence of this bias will depend on the topic,
@@
 The questionnaire is concise and straightforward, reducing respondent
-fatigue and enhancing clarity, which is crucial for maintaining
+fatigue and enhancing clarity, which is necessary for maintaining
 engagement. By incorporating both closed- and open-ended questions, it
-allows for both quantifiable data and rich qualitative insights. Clear
+allows for both quantifiable data and rich qualitative results. Clear
 response categories help reduce moderacy bias, encouraging participants
@@
 objective is to generate an accurate and reliable prediction of the
-election outcome while ensuring data quality through meticulous
+election outcome while ensuring data quality through careful
 sampling, recruitment, validation, and aggregation of results.\
@@
 In the subsequent steps, we will detail how to utilize **ballots cast**
-as a crucial factor in creating a **composite measure of size** for
+as a necessary factor in creating a **composite measure of size** for
 sampling U.S. election polls. Rather than relying solely on population
@@
 population. To achieve this, the sample will be stratified according to
-critical demographic and geographic variables, with strata information
+significant demographic and geographic variables, with strata information
 sourced from U.S. Census data available through IPUMS USA
@@
 accurately reflects the U.S. voting population, yielding reliable
-insights into voter preferences and behaviors.
+understanding into voter preferences and behaviors.
 
@@
 
-The survey is designed to capture essential insights into voting
+The survey is designed to capture essential understanding into voting
 intentions, candidate favorability, and the issues influencing voter
@@
 In our survey, several questions are adapted from the Emerson College
-Polling data [@emerson]. We apply insights from @survey to minimize
+Polling data [@emerson]. We draw on recommendations from @survey to minimize
 response biases. Common response biases identified in survey design

### 2024-11-03 paper/paper.qmd
update paper with grammar error

@@
 ---
-title: "Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach"
+title: "Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach with Poll-of-Polls Data"
 subtitle: "Kamala Harris expects to win on 47.5%, leads Donald Trump by about 1% in 2024 US election"
@@
 Presidential Election by analyzing polling data with adjustments for factors like recency and sample size, simulating an approach that captures up-to-date voter sentiment.
-Using recent 4 months aggregated poll data, the model identifies shifts in candidate support across key battleground states, providing a nuanced view of evolving preferences as election day approaches.
-By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering understanding that could inform campaign strategies and public discourse.
+Using the recent 4 months of aggregated poll data, the model identifies shifts in candidate support across key battleground states, providing a nuanced view of evolving preferences as election day approaches.
+By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering an understanding that could inform campaign strategies and public discourse.
 These findings highlight the value of weighting and time-sensitive adjustments in forecasting methods, balancing accuracy with responsiveness to the latest trends."
@@
 events. This study aims to forecast the percentage of support for Kamala
-Harris, offering understanding into the elements that shape voter preferences
+Harris offers an understanding of the elements that shape voter preferences
 as the election nears. By examining data from multiple polling sources,
@@
 predictions when adjusted for temporal changes and fundamental factors.
-Additionally, @politic highlight the importance of
+Additionally, @politic highlights the importance of
 timing in polling, showing that data closer to election day tends to
@@
 Kamala Harris in the upcoming U.S. presidential election. The object of
-the estimation is forecasting the percentage of Kamala’s vote share
-based on an aggregated polling data using a multiple linear regression
+the estimation is to forecast the percentage of Kamala’s vote share
+based on aggregated polling data using a multiple linear regression
 model. Our goal is to track shifts in public opinion over time, offering
-a clearer pattern of voter’s choice and potential election outcomes.
+a clearer pattern of voters’ choices and potential election outcomes.
 
@@
 overall support for Harris. By estimating the coefficients for each
-predictor, we aim to drawn significant conclusions about their
+predictor, we aim to draw significant conclusions about their
 respective impacts on voter sentiment.
@@
 focus during the campaign. Given that elections can be decided by narrow
-margins, having trustworthy understanding into voter preferences can
+margins, having a trustworthy understanding of voter preferences can
 substantially influence the final outcomes.
@@
 implications of our results and suggests potential directions for future
-research. @sec-a provide external data detail, @sec-b provide
-model detail, @sec-c provide a investigation for pollster Siena College's
-methodology, and  @sec-d provide a idealized methodology for polling the poll.
+research. @sec-a provides external data detail, @sec-b provides
+model detail, @sec-c provides an investigation for pollster Siena College's
+methodology, and  @sec-d provides an idealized methodology for polling the poll.
 
@@
 [@citeR]. Our dataset, obtained from FiveThirtyEight
-[@fivethirtyeight2024],based on polling as of 2 November 2024, provides
+[@fivethirtyeight2024], based on polling as of 2 November 2024, provides
 a detailed overview of public opinion in the lead-up to the election.
@@
 RColorBrewer provided color palettes for visualizations, enhancing clarity and visual appeal in our plots [@citeRColorBrewer].
-The future package supported parallel processing, optimizing the runtime of intensive computations, especially beneficial in model training [@citefuture].
+The future package supported parallel processing, optimizing the runtime of intensive computations, which is especially beneficial in model training [@citefuture].
 Finally,for resampling and bootstrapping techniques, we utilized the boot package, which allowed us to assess model stability and reliability [@citeboot1;@citeboot2].
@@
 cleaning, polling results are aggregated to smooth out individual poll
-biases and mitigate random error. This aggregation process employs
+biases and mitigate random errors. This aggregation process employs
 weighting based on poll quality, sample size, recency, and the
@@
 effectively converts subjective opinions into measurable data, providing
-valuable understanding into voter behavior and preferences.
+valuable understanding of voter behavior and preferences.
 
@@
 The end date is the final day of data collection for a poll, indicating
-when the survey period concluded. This date provides necessary context for
+when the survey period concluded. This data provides necessary context for
 the poll results, as public opinion may change over time in response to
-events, campaign actions, or other influencing factors. In our analysis, we only choose the polls with end date after July 21 2024, which Kamala Harris first declared in the election.
+events, campaign actions, or other influencing factors. In our analysis, we only choose the polls with the end date after July 21 2024, which Kamala Harris first declared in the election.
 
@@
 
-National polls is another newly created variable in our dataset, represented by a binary
-indicator (1 for polls at national level, 0 otherwise). This distinction is important because
+National poll is another newly created variable in our dataset, represented by a binary
+indicator (1 for polls at the national level, 0 otherwise). This distinction is important because
 not all polls are conducted nationally; some are state-specific and may reflect the
@@
 right side of the chart, states with minimal polling activity, including
-South Carolina, Iowa, and Washington, appear less frequently, possibly
+South Carolina, Iowa, and Washington appear less frequently, possibly
 due to their historically predictable or less competitive nature. This
@@
 to various pollsters, with the x-axis representing the numeric grade
-values and the y-axis indicating the frequency of each grade. The
+values and the y-axis indicates the frequency of each grade. The
 numeric grade is a metric that evaluates the quality or reliability of a
@@
 and 3.00, with a large spike at these values, suggesting that a
-significant number of polls are conducted by highly-rated pollsters.
+significant number of polls are conducted by highly rated pollsters.
 Fewer polls have grades below 2.5, indicating a relatively lower
@@
 sentiment for Harris, with only slight fluctuations across numeric
-grades. By limiting the maximum value of support at 80%, outliers and extreme variations are minimized, resulting in a clearer and more interpretable visualization.
-This approach emphasizes the central trend, allowing for clearer
-comparisons of support levels across pollsters of varying reliability
-without distraction from extreme values.
+grades.
 
@@
 
-ggplot(harris_data %>% filter(pct <= 80), aes(x = end_date, y = pct, color = factor(numeric_grade))) +
+ggplot(harris_data, aes(x = end_date, y = pct, color = factor(numeric_grade))) +
   geom_point(alpha = 0.7) +
@@
 -   **National Poll (`national_poll`)**: Represents the national trend
-    in support for the candidate.
+    in support of the candidate.
 -   **Pollster (`pollster`)**: Categorical variable identifying the
-    organization conducting the poll, accounting for differences in
+    the organization conducting the poll, accounting for differences in
     methodology and reliability.
@@
 weighting scheme integrates factors like poll recency, sample size,
-pollster quality, and frequency, as inspired by the New York Times’
-methodology [@nyt_polling_averages] for polling averages.
+pollster quality, and frequency, as inspired by the New York Times' methodology [@nyt_polling_averages] for polling averages.
 
@@
 of the population, and polling conducted during or near key political
-events often reflects more immediate public sentiment. Additionally,
+events often reflect more immediate public sentiment. Additionally,
 regional factors, such as local political dynamics or demographic
-characteristics, can influence support patterns.
+characteristics can influence support patterns.
 
@@
 averages. This weighting system integrates factors like recency and
-sample size, ensuring that more recent and larger-sample polls exert a
+sample size, ensuring that more recent and larger sample polls exert a
 greater influence on our model's predictions. By applying this weighting
@@
 use K-Fold Cross-Validation to validate the model, use Q-Q Plot and
-Residuals vs fitted diagram to diagnostic the model. These procedures
+Residuals vs fitted diagram to diagnose the model. These procedures
 help confirm that the model assumptions are met and that the predictions
@@
 incomplete data for certain states, we were unable to make predictions
-across the entire U.S. This limitation arises from states with missing
+across the entire U.S., This limitation arises from states with missing
 values in the dataset, which are consequently not represented in the
@@
 Kamala Harris and Donald Trump in the 2024 U.S. Presidential Election
-utilized both unweighted and weighted configurations.The model summary of support for Harris is shown in @tbl-summary1, support for Trump is shown in @tbl-summary2. As shown in
+utilized both unweighted and weighted configurations. The model summary of support for Harris is shown in @tbl-summary1, and support for Trump is shown in @tbl-summary2. As shown in
 @tbl-summary1 and @tbl-summary2, the intercepts for Harris and Trump,
@@
 reference values. The high ( R\^2 ) values of 0.824 for Harris’s
-unweighted model and 0.892 for her weighted model, along with similar
+unweighted model and 0.892 for her weighted model, along with a similar
 values of 0.849 and 0.916 for Trump, indicate that a significant portion
@@
 reported support levels, as polls from the National level increase the
-support of Harris by 3.47%/4.27% , decrease the support for Trump by 7.61%/7.17%.
+support of Harris by 3.47%/4.27%, decrease the support for Trump by 7.61%/7.17%.
 The **population** predictor indicates that the type of respondent group
@@
 
-@fig-support-trend illustrate the predicted support for Kamala Harris
+@fig-support-trend illustrates the predicted support for Kamala Harris
 and Donald Trump from August 1, 2024, to November 2, 2024, using both
@@
 Overall, both models consistently indicate a lead for Harris, with the weighted model slightly stabilizing the predictions.
-The average support for Harris and Trump are both consist for two models, which predicts that Harris will win on about 47%, leads Trump by about 1%.
+The average support for Harris and Trump both consist of two models, which predict that Harris will win by about 47%, and lead Trump by about 1%.
 
@@
 and sample size. In both figures, Trump’s support, represented by red
-lines, and Harris’s support, shown in blue, show close competition
+lines, and Harris’s support, shown in blue, shows close competition
 across most states, with slight variations in trends across the polling
-period from August to November 2024.
-
-In the @fig-support-state-1 , support for Kamala Harris and Donald Trump
+the period from August to November 2024.
+
+In the @fig-support-state-1, support for Kamala Harris and Donald Trump
 fluctuates widely across battleground states, with Harris holding significant
-leads in Michigan, and Pennsylvania.  Harris also hold advantage in Wisconsin but facing tight competition. Overall, without weighting, polls contribute equally, creating more
+leads in Michigan and Pennsylvania.  Harris also holds the advantage in Wisconsin but facing tight competition. Overall, without weighting, polls contribute equally, creating more
 volatility.
@@
 
-@fig-support-pollster depict the predicted support for Kamala Harris and
+@fig-support-pollster depicts the predicted support for Kamala Harris and
 Donald Trump in the 2024 U.S. election, from August 1, 2024, to November
@@
 48%, with some noticeable peaks and dips, indicating variability over
-time. In contrast,the average Harris’s support, represented by the blue line,
+time. In contrast, the average Harris’s support, represented by the blue line,
 remains more stable, consistently ranging around 47% to 48%, suggesting
@@
 variability but hold less influence in the model. Overall, Siena/NYT and
-Quinnipiac favor Harris, while Emerson, AtlasIntel, and Beacon/Shaw
+Quinnipiac favors Harris, while Emerson, AtlasIntel, and Beacon/Shaw
 present a more competitive picture.
@@
 locked in a near tie around 47% support—a statistical dead heat that
-brings the state’s significance into sharp relief. Neveda, meanwhile,
+brings the state’s significance into sharp relief. Nevada, meanwhile,
 leans modestly toward Trump, a reflection of the unique demographic and
@@
 This approach effectively smooths out abrupt fluctuations that might otherwise result from older or smaller polls, providing a more stable and coherent view of voter sentiment.
-hough our data filtered with recent polls after Harris's candidacy announcement, voter sentiment remains fluid, with ongoing debates and events likely to influence preferences.
+hough our data was filtered with recent polls after Harris's candidacy announcement, voter sentiment remains fluid, with ongoing debates and events likely to influence preferences.
 By emphasizing recent polls, the model is more responsive to the latest shifts in public opinion, which is especially relevant as election day approaches and voters’ preferences may crystallize.
@@
 This decreased volatility allows the model to present a clearer picture of the general support trend for each candidate, reducing noise and highlighting true shifts in sentiment.
-However, this smoothing effect may also mask some of the localized or short-term dynamics captured by less frequent or smaller-sample polls, which could provide unique understanding into specific voter groups or state-level shifts.
+However, this smoothing effect may also mask some of the localized or short-term dynamics captured by less frequent or smaller-sample polls, which could provide a unique understanding of specific voter groups or state-level shifts.
 
@@
 To enhance the predictive power of the model, historical voting data, economic
-indicators and major news events can be used as background variables. By analyzing
+indicators, and major news events can be used as background variables. By analyzing
 the impact of similar factors on voter sentiment in past elections, we can understand the patterns and trends that may apply to the current campaign. For
@@
 attainment may influence political preferences in complex ways. By incorporating this level
-of granularity, future analyses can provide deeper understanding into voter behavior and help
+of granularity, future analyses can provide a deeper understanding of voter behavior and help
 develop more targeted campaign strategies.
@@
 Sketches depicting both the desired dataset and the graphs generated in
-this analysis are available in the GitHub Repository `other/sketches`.
+this analysis is available in the GitHub Repository `other/sketches`.
 
@@
 with a median of 1.9. We also handle placeholder values in state
-information by setting entries marked as NA to National, and create a
-national_poll indicator, assigning a value of 1 for value in state equals to National and 0 for others. Dates are standardized using the lubridate
+information by setting entries marked as NA to National, and creating a
+national_poll indicator, assigning a value of 1 for value in state equal to National and 0 for others. Dates are standardized using the lubridate
 package to facilitate accurate time-based analysis.
 
-Recency are calculated based on the days elapsed since the
-poll's end date.Additionally,categorical variables, including pollster, state, candidate_name,
+Recency is calculated based on the days elapsed since the
+poll's end date.Additionally, categorical variables, including pollster, state, candidate_name,
 population, and methodology, are converted to factors to prepare for
@@
 The cleaned datasets for both candidates are then saved as Parquet files
-for efficient storage and access in further modeling and analysis. This
+for efficient storage and access to further modeling and analysis. This
 structured approach ensures that the data is accurate, complete, and
@@
 national_poll, pollster, and population. The output provides key
-metrics, which breaks down here:
+metrics, which are breaking down here:
 
@@
 
-Harris model: RMSE of 2.43, indicating an average prediction error of
+Harris Model: RMSE of 2.43, indicating an average prediction error of
 around 2.43 percentage points.\
-Trump model: RMSE of 2.57, showing a slightly average prediction error on
+Trump Model: RMSE of 2.57, showing a slightly average prediction error on
 average.\
@@
 variable explained by the model (higher is better).\
-Harris model: R-squared of 0.63, meaning the model explains about 63%
+Harris Model: R-squared of 0.63, meaning the model explains about 63%
 of the variance in Harris's polling data.\
-Trump model: R-squared of 0.66, meaning the model explains about 66%
+Trump Model: R-squared of 0.66, meaning the model explains about 66%
 of the variance in Trump's polling data.
@@
 observed and predicted values (lower is better).\
-Harris model: MAE of 1.6, meaning that, on average, the predictions are
+Harris Model: MAE of 1.6, meaning that, on average, the predictions are
 off by 1.62 percentage points.\
-Trump model: MAE of 1.62, indicating slightly higher precise predictions
+Trump Model: MAE of 1.62, indicating slightly higher precise predictions
 compared to the Harris model.\
@@
 by its lower RMSE and MAE values.\
-Model Fit: Harris' model explain roughly 63% of the variance in their
+Model Fit: Harris' model explains roughly 63% of the variance in their
 respective datasets. Trump's models explain roughly 66% of the variance
-in their respective datasets.This suggests that other factors not
+in their respective datasets. This suggests that other factors not
 included in the model may play a significant role in explaining the
@@
 
-Generally, we use Residual vs Fitted plot and Q-Q Plot diagnostic our
-model. Residual vs Fitted plot aare Residuals (differences between
+Generally, we use the Residual vs Fitted plot and Q-Q Plot diagnostic for our
+model. Residual vs Fitted plots are Residuals (differences between
 observed and predicted values) plotted against fitted values. Ideally,
@@
 
-@fig-stanareyouokay-1 and @fig-stanareyouokay-3 are residual plots of un-weighted model for Harris
-support. It showsthe residuals are generally spread around zero, with no
+@fig-stanareyouokay-1 and @fig-stanareyouokay-3 are residual plots of the un-weighted model for Harris
+support. It shows residuals are generally spread around zero, with no
 clear pattern. This suggests the model is relatively well-specified.
 
-@fig-stanareyouokay-2 and @fig-stanareyouokay-4 is are Q-Q plots of un-weighted and weighted model plot for Harris support. It shows most residuals fall along the line, especially in the
-middle range. This suggests that our model satisfy the normality
+@fig-stanareyouokay-2 and @fig-stanareyouokay-4 are Q-Q plots of un-weighted and weighted model plots for Harris support. It shows most residuals fall along the line, especially in the
+middle range. This suggests that our model satisfies the normality
 assumption. However, some points at the head and tail deviate, indicating
@@
 
-@fig-dia-1 and @fig-dia-3 shows the residuals plotted against the fitted values for the
+@fig-dia-1 and @fig-dia-3 show the residuals plotted against the fitted values for the
 unweighted model for Trump's Support. It shows that the residuals are generally spread
-around zero with no clear pattern for both model, suggesting that the model is well-specified.
-
-@fig-dia-2 and @fig-dia-4 shows the Q-Q plot for the unweighted and weighted model for Trump's Support, showing that
+around zero with no clear pattern for both models, suggesting that the model is well-specified.
+
+@fig-dia-2 and @fig-dia-4 show the Q-Q plot for the unweighted and weighted model for Trump's Support, showing that
 most residuals fall along the line, especially in the middle range,
@@
 recruitment processes, and sampling strategies. Additionally, we discuss
-how Siena addresses non-response and review the strengths and weaknesses
+how Siena addresses non-response and reviews the strengths and weaknesses
 of its questionnaire design. By detailing these elements, this appendix
 clarifies how Siena College ensures the reliability and validity of its
-polling results, offering valuable understanding into voter behavior and
+polling results, offering a valuable understanding of voter behavior and
 election dynamics.
@@
 
-## Population, Frame and sample
-
-Refer from @tellingstories, we defined three key terms as:\
-Target population : The collection of all items about which we would
-like to speak/ the entire group about which we want to draw.
+## Population, Frame, and sample
+
+Refer to @tellingstories, we defined three key terms as:\
+Target population: The collection of all items about which we would
+like to speak/to the entire group about which we want to draw.
 conclusions\
-Sampling frame : A list of all the items from the target population that
+Sampling frame: A list of all the items from the target population that
 we could get data about.\
-Sample : The items from the sampling frame that we get data about.\
+Sample: The items from the sampling frame that we get data about.\
 
@@
 
-The sample of registered voters sourced from the voter file maintained
-by L2, a nonpartisan vendor, and supplemented with additional cellular
-phone numbers matched from Marketing Systems Group. The sample for the
-poll totals 2,055 likely voters, with 688 from Michigan, 687 from Ohio,
+The sample for the Siena's poll is a total of 2,055 likely voters, with 688 from Michigan, 687 from Ohio,
 and 680 from Wisconsin, surveyed from September 21 to 26, 2024.
@@
 
-Siena use phone poll to recruit sample. Telephone polling is a way to
+Siena uses phone polls to recruit samples. Telephone polling is a way to
 gather public opinion by contacting individuals via landlines and mobile
@@
 York, South Carolina, Texas, and Virginia. The respondents are randomly
-selected from a national database of registered voters and are contacted
+selected from a national database of registered voters and contacted
 via both landlines and cellphones.
@@
 voters sourced from the voter file maintained by L2, a nonpartisan
-vendor, and supplemented with additional cellular phone numbers matched
+vendor, and supplemented with additional cellular phone numbers that matched
 from Marketing Systems Group. The New York Times selected the sample in
@@
 
-Stratified sampling is typically utilized to ensure all strata of the
-population are represented. When considering our population, it
-typically consists of various groupings. These can range from a country
-being divided into states, provinces, counties, or statistical districts
-to a university comprising faculties and departments or even demographic
-characteristics groups among individuals. A stratified structure allows
-us to categorize the population into mutually exclusive and collectively
-exhaustive sub-populations known as "strata"[@tellingstories].
+Stratified sampling ensures that all segments of a population are represented by dividing it into distinct, exhaustive groups, or "strata," such as regions, demographic categories, or organizational units like university faculties [@tellingstories].
 
 In this scenario, we want to collect the polls from all strata of our
-target population to balance our poll result. The sample was stratified
+target population to balance our poll results. The sample was stratified
 by political party, race, and region, and screened by M.S.G. to ensure
@@
 smaller subgroups are adequately included, allowing researchers to
-allocate resources more efficiently and gain deeper understanding into
+allocate resources more efficiently and gain a deeper understanding of
 specific groups. However, this method can lead to **higher costs** due
@@
 
-An interview was deemed complete for inclusion in the voting preference
-questions if the respondent stayed engaged in the survey after answering
-the two self-reported variables used for weighting—age and education—and
-provided responses to at least one question concerning age, education,
-or the presidential election candidate reference. If these conditions
-were not met, the interview was recorded as a non-response.
-
-To handle the non-response bias, Siena choose to use weighting
+Nonresponse bias occurs when participants choose not to answer certain questions or drop out of the survey entirely, which can distort survey results and lead to unrepresentative conclusions.
+
+Siena recorded an interview as a non-response if respondents failed to answer key weighting variables—age and education—or did not respond to at least one question related to age, education, or presidential candidate preference.
+
+To handle the non-response bias, Siena chose to use weighting
 adjustments. Weighting is like balancing a scale to make sure each group
@@
 
-Siena use several steps to address nonresponse bias and ensure the
-reliability of the results. The weighting process was conducted by The
-New York Times using the R survey package and involved multiple
-adjustments. Siena’s weighting process involved adjusting samples for
-unequal selection probabilities and turnout likelihood, based on 2020
-data. Further adjustments aligned the sample with likely electorate
-targets from the L2 voter file. The final weight combined modeled
-turnout (80%) and self-reported intentions (20%), mitigating nonresponse
-bias and ensuring the sample accurately reflected the characteristics
-and behaviors of likely voters, thereby enhancing result validity.
+Siena employs a multi-step process to address nonresponse bias and improve result reliability.
+Conducted by The New York Times using the R survey package, the process adjusts samples for unequal selection probabilities and turnout likelihood, drawing on 2020 data.
+Further refinements align the sample with likely electorate targets from the L2 voter file.
+The final weighting combines modeled turnout (80%) with self-reported intentions (20%), ensuring the sample reflects the characteristics and behaviors of likely voters and enhancing the validity of the results.
 
@@
 
-### Response bias defination
-
-In the design of the questionnaire, there will be some common bias that
+### Response bias definition
+
+In the design of the questionnaire, there will be some common biases that
 may occur when running the questionnaire.
 
-@survey define these bias as:
-
--   Moderacy response bias is the tendency to respond to each question
-    by choosing a category in the middle of the scale.
-
--   Extreme response bias is the tendency to respond with extreme values
-    on the rating scale.
-
--   Response order bias occurs when the order of response options in a
-    list or a rating scale influences the response chosen. The primacy
-    effect occurs when respondents are more likely to select one of the
-    first alternatives provided, and it is more common in written
-    surveys. This tendency can be due to satisficing, whereby a
-    respondent uses the first acceptable response alternative without
-    paying particular attention to the other options. The recency effect
-    occurs when respondents choose one of the last items presented to
-    them (more common in face-to-face or orally presented surveys).
-
--   Social desirability bias typically stems from the desire of
-    respondents to avoid embarrassment and project a favorable image to
-    others, resulting in respondents not demonstrateing their actual
-    attitudes. The prevalence of this bias will depend on the topic,
-    questions, respondent, mode of the survey, and the social context.
-    For instance, in some circles, anti-immigrant views are not
-    tolerated, and those who hold them may try to hide them. In other
-    settings, people express such views more freely.
-
--   Acquiescence is the tendency to answer items in a positive way
-    regardless of their content, for instance, systematically selecting
-    categories such as “agree,” “true,” or “yes”.
+@survey defines these biases as:
+
+- **Moderacy response bias**: The tendency to choose mid-scale responses.
+
+- **Extreme response bias**: The inclination to select extreme values on the scale.
+
+- **Response order bias**: Occurs when the position of options influences responses, with the **primacy effect** (favoring early options in written surveys) and **recency effect** (favoring later options in oral surveys) as common forms.
+
+- **Social desirability bias**: Respondents may hide true views to present a socially favorable image, influenced by topic and social context.
+
+- **Acquiescence bias**: The habit of giving positive responses, such as consistently choosing “agree” or “yes.”
 
@@
 fatigue and enhancing clarity, which is necessary for maintaining
-engagement. By incorporating both closed- and open-ended questions, it
+engagement. Incorporating both closed- and open-ended questions 
 allows for both quantifiable data and rich qualitative results. Clear
@@
 agree-disagree and yes-no formats may increase acquiescence bias, as
-respondents may lean toward favorable answers. Furthermore, some
-demographic nuances may be inadequately addressed, potentially leading
-to nonresponse bias from underrepresented groups. The risk of response
-order bias is also present, especially if randomization of options is
+respondents may lean toward favorable answers. The risk of response
+order bias is also present, especially if the randomization of options is
 not implemented, increasing the chance of recency effects in
@@
 favorable image. Lastly, with over 50 questions, the length of the
-survey may increase dropout rates, especially in time-intensive formats
+Surveys may increase dropout rates, especially in time-intensive formats
 like telephone surveys, thereby raising nonresponse bias.
@@
 nonresponse, social desirability, and order effects. Future improvements
-should focus on diversifying question types, ensuring demographic
-inclusivity, and refining question phrasing to reduce bias and enhance
+should focus on diversifying question types, and refining question phrasing to reduce bias and enhance
 validity.
@@
 
-To ensure a representative sample of likely voters, I will employ a
-Composite Measure sampling method based on past ballots cast data from
-the 2020 U.S. elections. After determining the sample size for each
-state, I will use stratified sampling based on demographics, dividing
-the population into subgroups and taking random samples from each
-subgroup. This Composite Measure sampling approach, as referenced in
-@india, enhances our chances of selecting respondents from states or
-regions that have historically exhibited higher voter engagement
-compared to the general population distribution. While some states may
-have larger populations, we aim to adjust the sampling to reflect higher
-anticipation rates.
-
-To illustrate this Composite Measure of size, consider two states with
-similar populations. For instance, although State A and State B both
-have 1 million eligible voters, State B consistently shows a higher
-ballots cast in past elections. Therefore, we will increase the
-proportion of polls conducted in State B. In this scenario, State A has
-a historical turnout rate of 50%, while State B has a turnout rate of
-70%. In a purely population-based sampling approach, both states would
-have an equal chance of being selected for polls: 50% for State A and
-50% for State B. However, by incorporating ballots cast, we modify these
-probabilities to increase the likelihood of selecting State B due to its
-higher historical turnout.
-
-In the subsequent steps, we will detail how to utilize **ballots cast**
-as a necessary factor in creating a **composite measure of size** for
-sampling U.S. election polls. Rather than relying solely on population
-size, we will adjust the sample allocation based on historical voter
-turnout, ensuring that regions with higher engagement are more
-prominently represented in our polling data.
+To achieve a representative sample of likely voters, we will use a Composite Measure sampling approach based on 2020 U.S.
+election turnout data.
+First, we will determine sample sizes for each state, then apply stratified sampling by demographics, dividing the population into subgroups and drawing random samples within each.
+This approach, as noted by @india, boosts our chances of selecting respondents from regions with historically high voter engagement, rather than relying solely on general population distribution.
+For example, given two states with 1 million eligible voters each—State A with a 50% historical turnout and State B with 70%—the composite measure adjusts sampling probabilities to favor State B, reflecting its higher turnout rate and anticipated voter engagement in the upcoming election.
+
+In the following steps, we outline how to incorporate **ballots cast** as a key factor in establishing a **composite measure of size** for sampling U.S.
+election polls.
+By weighting sample allocation according to historical participation—rather than solely on population size—we ensure that areas with higher past engagement are more accurately represented in our polling data.
+This approach enhances the relevance and reliability of insights from regions likely to influence the election.
 
@@
 
-After determining the sample size for each region, we will use
-stratified sampling across key demographic categories, such as age,
-gender, race/ethnicity, and education level. This method ensures that
-our final sample proportionally represents each subgroup within every
-region, accurately reflecting the diversity of the U.S. voting
-population. To achieve this, the sample will be stratified according to
-significant demographic and geographic variables, with strata information
-sourced from U.S. Census data available through IPUMS USA
-[@ruggles2024ipums].
+After determining regional sample sizes, we’ll apply stratified sampling across key demographics—age, gender, race/ethnicity, and education level.
+This ensures proportional representation within each region, aligning our sample with the U.S.
+voting population's diversity.
+Demographic and geographic strata will be based on U.S.
+Census data from IPUMS USA [@ruggles2024ipums].
 
@@
 
-Our target population is all U.S. citizens eligible to vote in the 2024
+Our target population is all U.S. citizens eligible to vote in 2024
 U.S. presidential election (age\>=18).
@@
 : Regional Voting Data and Sample Size Allocation calculated using
-Composite Measure Sampling Proportion based on 2020 US Election regional
+Composite Measure Sampling Proportion based on the 2020 US Election regional
 ballots cast {#tbl-samplesize}
@@
 sourced from [@wikivote], including total ballots cast, and Voting
-Eligible Population (VEP). The sample size for each region shown in
+Eligible Population (VEP). The sample size for each region is shown in
 @tbl-samplesize was determined based on the **Composite Measure Sampling
@@
 will focus our resources on survey implementation and high-quality data
-collection, developing the survey in-house and recruiting participants
+collection, developing the survey in-house, and recruiting participants
 through online survey platforms.
@@
 
-Nonresponse bias occurs when participants are unwilling or unable to
-answer certain questions or complete the survey. Handling non-response
-bias matters because it can skew survey results, leading to inaccurate
+Handling non-response bias matters because it can skew survey results, leading to inaccurate
 conclusions that do not accurately represent the entire population's
-views or characteristics. Given that our survey takes approximately 15
+views or characteristics. Given that our survey takes approximately 10
 minutes to complete, there is a risk of nonresponse bias. To mitigate
@@
 
-To ensure high data quality and accuracy, we will conduct rigorous
-respondent validation through several verification steps, ensuring only
-eligible and relevant participants are included. Respondents will
-confirm their voter registration status, with a portion cross-referenced
-against voter databases or verified via reliable panel providers like
-Qualtrics and YouGov, thus focusing the survey on registered and likely
-voters. Eligibility will also be confirmed through screening questions
-verifying age (18+) and U.S. citizenship, allowing only those who meet
-these criteria to proceed. Attention-check questions embedded throughout
-the survey will filter out inattentive participants, with non-compliant
-responses excluded from the final sample. Additionally, unique
-identifiers such as IP and email addresses will be tracked to prevent
-duplicate submissions, ensuring each response is unique. Finally,
-post-survey data cleaning will address any inconsistent or incomplete
-responses to maintain dataset reliability. These validation steps are
-essential for producing data that accurately reflects the opinions of
-eligible, registered, and attentive respondents, thereby enhancing the
-survey's overall validity.
+To ensure data quality and accuracy, we implement multiple validation steps, allowing only eligible participants who meet age (18+), U.S.
+citizenship, and voter registration criteria.
+Respondents confirm their registration, with some cross-referenced through databases or validated by panel providers like Qualtrics and YouGov.
+Attention checks filter inattentive participants, while unique identifiers (e.g., IP, email) prevent duplicates.
+Post-survey cleaning addresses any inconsistencies, ensuring that the final dataset reflects the views of registered and attentive respondents, enhancing validity.
 
@@
 
-After collecting survey responses, we will aggregate data from our two
-recruitment sources: online panel providers and social media platforms.
-To weight these panels accurately, we’ll first identify key demographic
-variables (e.g., age, gender, race/ethnicity, education level) and
-establish population benchmarks using U.S. Census data
-[@ruggles2024ipums]. For the online panel (200 respondents) and social
-media panel (400 respondents), we will calculate weights by comparing
-each panel's demographic distribution to these benchmarks, adjusting for
-under- and over-represented groups.
-
-Once individual weights are calculated for each panel, we will integrate
-them into a single weighting scheme that aligns with the target
-population's demographic makeup. These weights will then be applied
-during data analysis, allowing underrepresented groups to have an
-appropriate influence on the results. Finally, we’ll conduct
-post-stratification adjustments to ensure that the combined sample
-accurately reflects the U.S. voting population, yielding reliable
-understanding into voter preferences and behaviors.
+After collecting survey responses, we’ll combine data from online panel providers and social media.
+Using U.S.
+Census benchmarks [@ruggles2024ipums], we’ll calculate weights for key demographics (age, gender, race/ethnicity, education) to balance each panel (200 from online, 400 from social media) for under- and over-represented groups.
+These individual weights will be merged into a single scheme reflecting the target population.
+In analysis, the weights will adjust representation, and post-stratification will further align the combined sample with the U.S.
+voting population, ensuring accurate insights into voter preferences and behaviors.
 
@@
 
-The survey is designed to capture essential understanding into voting
+The survey is designed to capture an essential understanding of voting
 intentions, candidate favorability, and the issues influencing voter
@@
 acquiescence bias.
-
-### Definition of the response bias
-
-We have defined the bias we want to solve in @sec-pollster.
 

### 2024-11-04 paper/paper.qmd
update paper

@@
 In this study, we utilized several R packages to enhance our data
-manipulation, modeling, and visualization capabilities. The tidyverse
+manipulation, modeling, and visualization capabilities. The `tidyverse`
 package offered a detailed set of tools for data wrangling and
 analysis, improving workflow efficiency [@thereferencecanbewhatever].
-The here package aided in managing file paths, allowing for easy access
-to our data files [@citehere]. We relied on janitor to perform data
+The `here` package aided in managing file paths, improving the reproducible workflow of our study [@citehere].We use `testthat` to verify dataset variables, ensuring they are correctly formatted and contain expected values for analysis [@citetestthat].
+We relied on `janitor` to perform data
 cleaning, as it provides functionalities to identify and rectify quality
 issues within the dataset [@citejanitor]. For handling date-related
-operations, the lubridate package proved invaluable, simplifying the
-manipulation of time variables [@citelubridate]. Arrow supported
-efficient data input and output in a performance-oriented format,
+operations, the `lubridate` package help simplifying the
+manipulation of time variables [@citelubridate]. `arrow` supported
+efficient data input and output in a parquet format,
 essential for managing larger datasets [@citearrow].
-We use ggplot2 [@citeggplot2] to visualize the analysis of data.
+We use `ggplot2` [@citeggplot2] to visualize the analysis of data.
 In addition to the core packages, we employed several specialized libraries to facilitate specific analytical tasks.
-The modelsummary package enabled us to generate clean, interpretable model summaries, streamlining the reporting of regression and other statistical results [@citemodelsummary].
-RColorBrewer provided color palettes for visualizations, enhancing clarity and visual appeal in our plots [@citeRColorBrewer].
-The future package supported parallel processing, optimizing the runtime of intensive computations, which is especially beneficial in model training [@citefuture].
-Finally,for resampling and bootstrapping techniques, we utilized the boot package, which allowed us to assess model stability and reliability [@citeboot1;@citeboot2].
-caret facilitated model training and validation, offering a unified interface for cross-validation and performance metrics [@citecaret].
+The `modelsummary` package enabled us to generate clean, interpretable model summaries, streamlining the reporting of regression and other statistical results [@citemodelsummary].
+`RColorBrewer` provided color palettes for visualizations, enhancing clarity and visual appeal in our plots [@citeRColorBrewer].
+The `future` package supported parallel processing, optimizing the runtime of intensive computations, which is especially beneficial in model training [@citefuture].
+Finally,for validation of model using K-Fold cross validation, we utilized the `boot` package, which allowed us to assess model stability and reliability [@citeboot1;@citeboot2] and `caret` to facilitate model training and validation, offering a unified interface for cross-validation and performance metrics [@citecaret].
 Our coding practices and file organization were informed by the structure outlined
@@
 #| eval: true
-#| fig-cap: "Harris Kamala leads Donald Trump an average 2% in Predicted Support in the 2024 US Election (From August 1, 2024, to November 2, 2024)"
+#| fig-cap: "Harris Kamala leads Donald Trump an average 1% in Predicted Support in the 2024 US Election (From August 1, 2024, to November 2, 2024)"
 #| fig-subcap: ["Unweighted","Weighted"]
@@
        color = "Candidate",caption = 
-                   "Linear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state") +
+                   "Model: Candidate Support Percentage = national_poll + pollster + population + state") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
        size="Weight",
-       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state") +
+       caption = "Weights: recency_weight * sample_size_weight \nModel: Candidate Support Percentage = national_poll + pollster + population + state") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red"))  +
@@
        color = "Candidate",
-       caption = "Candidate Support Percentage = national_poll + pollster + population + state") +
+       caption = "Model: Candidate Support Percentage = national_poll + pollster + population + state") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
        size="Weight",
-       caption = "Weights: recency_weight * sample_size_weight\nCandidate Support Percentage = national_poll + pollster + population + state") +
+       caption = "Weights: recency_weight * sample_size_weight\nModel: Candidate Support Percentage = national_poll + pollster + population + state") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
     fill = "Top 5 Pollster",
-    caption = "Candidate Support Percentage = national_poll + pollster + population + state"
+    caption = "Model: Candidate Support Percentage = national_poll + pollster + population + state"
   )+ # Smoothed trend line
@@
     fill = "Top 5 Pollster",
-    caption = "Weights: recency_weight * sample_size_weight \nCandidate Support Percentage = national_poll + pollster + population + state"
+    caption = "Weights: recency_weight * sample_size_weight \nModel: Candidate Support Percentage = national_poll + pollster + population + state"
   )+ # Smoothed trend line
@@
 RMSE (Root Mean Square Error): Measures the average magnitude of
-prediction errors (lower is better).
-
+prediction errors (lower is better).\
 Harris Model: RMSE of 2.43, indicating an average prediction error of
@@
 Trump Model: RMSE of 2.57, showing a slightly average prediction error on
-average.\
+average.
 
@@
 Trump Model: MAE of 1.62, indicating slightly higher precise predictions
-compared to the Harris model.\
-
-Interpretation Summary Predictive Accuracy: The Harris model has
-slightly better predictive accuracy than the Trump model, as reflected
-by its lower RMSE and MAE values.\
-Model Fit: Harris' model explains roughly 63% of the variance in their
-respective datasets. Trump's models explain roughly 66% of the variance
+compared to the Harris model.
+
+In summary, the Harris model has slightly better predictive accuracy than the Trump model, as reflected
+by its lower RMSE and MAE values. Harris' model explains roughly 63% of the variance in their
+respective datasets, while Trump's models explain roughly 66% of the variance
 in their respective datasets. This suggests that other factors not
 included in the model may play a significant role in explaining the
-remaining variance.\
-This summary indicates the models are moderately predictive, with room
-for improvement in accuracy and fit, potentially by adding more
-predictors or adjusting model specifications.\
+remaining variance. This K-Fold Cross-Validation indicates the models are moderately predictive, with room for improvement in accuracy and fit, potentially by adding more
+predictors or adjusting model specifications.
 
@@
 #| label: fig-stanareyouokay
-#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Harris"
+#| fig-cap: "Diagnostics of Support for Harris model using residual vs fitted plot and norm Q-Q plot"
 #| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
@@
 #| label: fig-dia
-#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Trump"
+#| fig-cap: "Diagnostics of Support for Trump model using residual vs fitted plot and norm Q-Q plot"
 #| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
@@
 This survey is for academic research in Statistics. It consists of 26
-carefully designed questions and should take approximately 12-15 minutes
+carefully designed questions and should take approximately 10-15 minutes
 to complete.
@@
 
-4.  **How favorable are you towards the following candidates?**
-
-    |               | Very unfavorable | Unfavorable | Moderate | Favorable | Very favorable |
-    |------------|------------|------------|------------|------------|------------|
-    | Kamala Harris |                  |             |          |           |                |
-    | Donald Trump  |                  |             |          |           |                |
-
-5.  **How likely are you going to vote in the 2024 election?** (1 =
+4.  **How favorable are you towards the Kamala Harris?** (1 = 
+    Very Unfavorable, 5 = Very Favorable)
+
+    -   1
+    -   2
+    -   3
+    -   4
+    -   5
+
+5. **How favorable are you towards the Donald Trump?** (1 = 
+    Very Unfavorable, 5 = Very Favorable)
+
+    -   1
+    -   2
+    -   3
+    -   4
+    -   5
+
+6.  **How likely are you going to vote in the 2024 election?** (1 =
     Definitely not to vote, 10 = Definitely will vote)
@@
 
-6.  **How do you plan to cast your vote?**
+7.  **How do you plan to cast your vote?**
 
@@
 
-7.  **Did you vote in the 2020 U.S. presidential election?**
+8.  **Did you vote in the 2020 U.S. presidential election?**
 
@@
 
-8.  **If you voted in 2020, who did you vote for?**
+9.  **If you voted in 2020, who did you vote for?**
 
@@
 
-9.  **Imagine the following candidates: Candidate A favors cutting taxes
+10.  **Imagine the following candidates: Candidate A favors cutting taxes
     but has a weak stance on climate change, and Candidate B focuses on
@@
 
-10. **What do you think is the most important issue facing the United
+11. **What do you think is the most important issue facing the United
     States?** \[Select at most 3\]
@@
 
-11. **Select option 3 from the list below:**
+12. **Select option 3 from the list below:**
 
@@
 
-12. **Which social media platforms do you use to get political news?**
+13. **Which social media platforms do you use to get political news?**
     (Select all that apply)

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd

--- 2024-11-04 paper/paper.qmd
@@
 #| label: fig-recency
-#| fig-cap: Distribution of the recency of the polls after July 21 2024
+#| fig-cap: Distribution of the Poll Recency since July 21, 2024
 #| echo: false
@@
 #| label: fig-percentage
-#| fig-cap: Distribution of support percentage of Kamala Harris
+#| fig-cap: Distribution of the Support Percentage of Kamala Harris
 #| echo: false
@@
 #| label: tbl-category
-#| tbl-cap: Summary Statistics of categorical variable population and national_pull
+#| tbl-cap: Summary Statistics of the categorical variables population and national_pull
 #| echo: false
@@
 ```
-
 ### National Poll {#sec-national-poll}
@@
 #| label: fig-state
-#| fig-cap: Count of polls by the US state 
+#| fig-cap: Count of Polls by the US state 
 #| echo: false
@@
 #| label: fig-numericgrade
-#| fig-cap: Distribution of numeric grade
+#| fig-cap: Distribution of the Numeric Grade of the Polls
 #| echo: false
@@
 #| label: fig-numericgradetime
-#| fig-cap: Harris Support Over Time by Numeric Grade
+#| fig-cap: Harris Support Over Time by Numeric Grade of the polls
 #| echo: false

### 2024-11-04 paper/paper.qmd
update paper

@@
 Presidential Election by analyzing polling data with adjustments for factors like recency and sample size, simulating an approach that captures up-to-date voter sentiment.
-Using the recent 4 months of aggregated poll data, the model identifies shifts in candidate support across key battleground states, providing a nuanced view of evolving preferences as election day approaches.
+Using the recent 4 months (July 21th - November 2th) of aggregated poll data, the model identifies shifts in candidate support across key battleground states, providing a nuanced view of evolving preferences as election day approaches.
 By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering an understanding that could inform campaign strategies and public discourse.
@@
 trends; `pollster`, which represents differences in methodology and
-reliability across polling organizations; and `population`, which
-accounts for demographic and regional characteristics associated with
-each poll. Our combined weighting approach further integrates factors
-like recency and sample size to ensure that more recent, larger-sample
-polls have a greater impact on the model's predictions, providing a
+reliability across polling organizations; `population`, which
+accounts for the type of respondent group of voters associated with
+each poll; and lastly,`state`, which represents the exact U.S. state
+where the poll was conducted or focused.Our combined weighting approach further
+integrates factors like recency and sample size to ensure that more recent, 
+larger-sample polls have a greater impact on the model's predictions, providing a
 balanced and detailed assessment of candidate support.
@@
 
-## Predicted Voting Outcomes for Recent Three Months by State
+## Predicted Voting Outcomes in Key Battleground States
 

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
Update ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd

@@
 
-To enhance the predictive power of the model, historical voting data, economic
-indicators, and major news events can be used as background variables. By analyzing
-the impact of similar factors on voter sentiment in past elections, we can understand the patterns and trends that may apply to the current campaign. For
-example, high-profile events have historically influenced voter opinion, and
-understanding these influences can provide a more complete picture of the factors
-that drive support for each candidate. Given the underlying conditions that influence
-voter preferences over time, this additional context would allow the model to make
-more informed predictions.
-
-Another possible improvement is the addition of detailed demographic information, such as age,
-gender, income level, and educational background, which would allow us to identify trends among
-specific groups of voters and thus greatly enhance our analysis. Different demographics often
-have unique responses to campaign issues and activities; for example, younger voters may
-prioritize different issues compared to older voters, and income level and educational
-attainment may influence political preferences in complex ways. By incorporating this level
-of granularity, future analyses can provide a deeper understanding of voter behavior and help
-develop more targeted campaign strategies.
+To strengthen the predictive capability of the model, integrating historical voting data, economic indicators, and significant news events as contextual variables is recommended.
+Analyzing the impact of these factors on voter sentiment in prior elections can illuminate patterns and trends potentially relevant to the current campaign.
+For instance, high-profile events have historically affected voter opinions, and understanding these influences can offer a comprehensive view of the variables driving support for each candidate.
+This expanded context, capturing the evolving conditions that shape voter preferences, would enable the model to generate more nuanced predictions.
+
+Another potential enhancement involves incorporating detailed demographic information—such as age, gender, income level, and educational background—which would enable the identification of trends within specific voter groups, significantly enriching the analysis.
+Distinct demographics often respond uniquely to campaign issues; for example, younger voters may prioritize issues differently from older voters, while income levels and educational backgrounds can complexly influence political preferences.
+By integrating this granular demographic data, future analyses can yield a deeper understanding of voter behavior, supporting the development of more targeted campaign strategies.
 

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update paper with grammer error

--- 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
@@
 This approach effectively smooths out abrupt fluctuations that might otherwise result from older or smaller polls, providing a more stable and coherent view of voter sentiment.
-hough our data was filtered with recent polls after Harris's candidacy announcement, voter sentiment remains fluid, with ongoing debates and events likely to influence preferences.
+Though our data was filtered with recent polls after Harris's candidacy announcement, voter sentiment remains fluid, with ongoing debates and events likely to influence preferences.
 By emphasizing recent polls, the model is more responsive to the latest shifts in public opinion, which is especially relevant as election day approaches and voters’ preferences may crystallize.

### 2024-11-04 scripts/00-simulate_data.R
Update 00-simulate_data.R

@@ -4,7 +4,7 @@
 # Date: 3 November 2024 
 # Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
+# Pre-requisites: The `tidyverse` and `lubridate` package must be installed
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 #### Workspace setup ####

### 2024-11-04 scripts/03-clean_data.R
Update 03-clean_data.R

@@ -5,7 +5,7 @@
 # Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites:  
-# - The `tidyverse`, `janitor`,`lubridate`,`arrow` package must be installed and loaded
+# - The `tidyverse`, `janitor`,`lubridate` packages must be installed and loaded
 # - 02-download_data.R must have been run
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
@@ -13,7 +13,6 @@
 library(tidyverse)
 library(janitor)
 library(lubridate)
-library(arrow)
 #### Clean data ####
 raw_data <- read_csv("data/01-raw_data/raw_election_24.csv")
 

### 2024-11-04 scripts/03-clean_data.R
Update 03-clean_data.R

@@ -5,7 +5,7 @@
 # Contact: diana.shen@mail.utoronto.ca; jinyan.wei@mail.utoronto.ca; huayan.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites:  
-# - The `tidyverse`, `janitor`,`lubridate` packages must be installed and loaded
+# - The `tidyverse`, `janitor`,`lubridate`,`arrow` packages must be installed and loaded
 # - 02-download_data.R must have been run
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
@@ -13,6 +13,7 @@
 library(tidyverse)
 library(janitor)
 library(lubridate)
+library(arrow)
 #### Clean data ####
 raw_data <- read_csv("data/01-raw_data/raw_election_24.csv")
 

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update with wrong word usage

@@
 
+### Numeric Grade {#sec-numberic-grade}
+
+@fig-numericgrade displays the distribution of numeric grades assigned to various pollsters.
+The numeric grade is a metric that evaluates the quality or reliability of a pollster, considering factors such as methodology, historical accuracy, sample size, and pollster reputation.
+In this chart, we observe that the frequency of numeric grades peaks around 2.75 and 3.00, with a notable concentration at these values.
+This suggests that, after excluding lower-quality polls, a significant number of surveys are conducted by highly rated pollsters.
+Fewer polls have grades below 2.5, indicating a relatively lower occurrence of polls from less-reliable pollsters in this dataset.
+This distribution highlights the emphasis on high-quality pollsters, ensuring a more reliable and consistent source of polling data for subsequent analysis.
+
+```{r}
+#| label: fig-numericgrade
+#| fig-cap: Distribution of the Numeric Grade of the Polls
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(harris_data, aes(x = numeric_grade)) +
+  geom_histogram(binwidth = 0.05, fill = "gold", color = "grey30") +
+  labs(
+    x = "Numeric Grade",
+    y = "Frequency"
+  ) +
+  theme_minimal()
+```
 ## Outcome variable {#sec-outcome-variable}
@@
   labs(
-    x = "Support Percentage (%)",
+    x = "Support for Harris (%)",
     y = "Count"
@@
 
-### Numeric Grade {#sec-numberic-grade}
-
-@fig-numericgrade displays the distribution of numeric grades assigned
-to various pollsters, with the x-axis representing the numeric grade
-values and the y-axis indicates the frequency of each grade. The
-numeric grade is a metric that evaluates the quality or reliability of a
-pollster, taking into account factors such as methodology, historical
-accuracy, sample size, and pollster reputation. In this chart, we
-observe that the most common numeric grades are concentrated around 2.75
-and 3.00, with a large spike at these values, suggesting that a
-significant number of polls are conducted by highly rated pollsters.
-Fewer polls have grades below 2.5, indicating a relatively lower
-occurrence of polls from less-reliable pollsters in this dataset. This
-distribution underscores the emphasis on high-quality pollsters within
-the dataset, ensuring a more reliable and consistent source of polling
-data for subsequent analysis.
-
-```{r}
-#| label: fig-numericgrade
-#| fig-cap: Distribution of the Numeric Grade of the Polls
-#| echo: false
-#| warning: false
-#| message: false
-
-ggplot(harris_data, aes(x = numeric_grade)) +
-  geom_histogram(binwidth = 0.05, fill = "gold", color = "grey30") +
-  labs(
-    x = "Numeric Grade",
-    y = "Frequency"
-  ) +
-  theme_minimal()
-```
-
 ## Relationships between key varaibles {#sec-data-relationship}
@@
   scale_color_viridis_d() +
-  labs(y = "Harris Support Percent", x = "Date") +
+  labs(y = "Support for Harris (%)", x = "End Date of the Poll") +
   theme_classic() +
@@
 #| label: fig-numericgradetime
-#| fig-cap: Harris Support Over Time by Numeric Grade of the polls
+#| fig-cap: Harris Support Over Time by Numeric Grade of the Polls
 #| echo: false
@@
   geom_smooth(se = FALSE, span = 0.3) +
-  labs(y = "Support for Harris", x = "Date", color = "Numeric Grade") +
+  labs(y = "Support for Harris (%)", x = "End Date of the Poll", color = "Numeric Grade") +
   scale_color_viridis_d() +
@@
 represent their baseline support levels when all predictors are at
-reference values. The high ( R\^2 ) values of 0.824 for Harris’s
+reference values. The high ( $R^2$ ) values of 0.824 for Harris’s
 unweighted model and 0.892 for her weighted model, along with a similar
@@
 All models include a control for state and pollsters.
-The reference level of state is Alaska, the reference level of population is likely voter, and the reference level of pollsters is Alaska is Angus Reid.")
+The reference level of state is Alaska, the reference level of population is likely voter, and the reference level of pollsters is Angus Reid.")
 ```
@@
 All models include a control for state and pollsters.
-The reference level of state is Alaska,the reference level of population is likely voter, and the reference level of pollsters is Alaska is ABC/Washington Post.")
+The reference level of state is Alaska,the reference level of population is likely voter, and the reference level of pollsters is ABC/Washington Post.")
 ```

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update paper caption

@@
 #| label: fig-recency
-#| fig-cap: Distribution of the Poll Recency since July 21, 2024
+#| fig-cap: The distribution of the Poll Recency since July 21, 2024 highlights a strong focus on recent polling data, with the highest frequency of polls occurring within the first few days.
 #| echo: false
@@
 #| label: fig-numericgrade
-#| fig-cap: Distribution of the Numeric Grade of the Polls
+#| fig-cap: The distribution of the Numeric Grade of the Polls shows that surveys are conducted by highly rated pollsters, which ensure the reliability of the analysis.
 #| echo: false
@@
 #| label: fig-percentage
-#| fig-cap: Distribution of the Support Percentage of Kamala Harris
+#| fig-cap: The distribution of the Support Percentage of Kamala Harris clustered around 50%, with the majority of support falling between 40% and 55%.
 #| echo: false
@@
 #| label: tbl-category
-#| tbl-cap: Summary Statistics of the categorical variables population and national_pull
+#| tbl-cap: Summary statistics of the categorical variables population and national_pull reveal that the majority of the polls are state-level (68.3%) and focus primarily on likely voters (75%).
 #| echo: false
@@
 #| label: fig-state
-#| fig-cap: Count of Polls by the US state 
+#| fig-cap: Count of Polls by the US state shows that Polling Distribution Prioritizes National Sentiment and High-Impact Battleground States.
 #| echo: false
@@
 #| label: fig-pollster
-#| fig-cap: Frequency of Polls by Pollster
+#| fig-cap: Frequency of Polls Highlights Siena/NYT as Leading Pollster, Followed by YouGov and Emerson.
 #| echo: false
@@
 #| label: fig-pollstertime
-#| fig-cap: Harris Support Over Time by Pollster (Top 6 Pollsters)
+#| fig-cap: Trend Analysis of Kamala Harris Support from August to October Shows Upward Trends by Emerson and Beacon/Shaw, with Siena/NYT Showing Decline.
 #| echo: false
@@
 #| label: fig-numericgradetime
-#| fig-cap: Harris Support Over Time by Numeric Grade of the Polls
+#| fig-cap: Harris's Support Trends Stable Around 50%, with Minor Fluctuations Across Pollster Numeric Grades, Especially in Polls with Numeric Grade 2.5.
 #| echo: false
@@
 #| eval: true
-#| tbl-cap: "Summary of Multiple Linear Regression Model Predicting Harris Support Based on Polling Data"
+#| tbl-cap: "Summary of Multiple Linear Regression Model Predicting Harris Support Based on Polling Data since 21 July 2024 (Harris first declared) to 2 November 2024"
 #| label: tbl-summary1
@@
 #| eval: true
-#| tbl-cap: "Summary of Multiple Linear Regression Model Predicting Trump Support Based on Polling Data"
+#| tbl-cap: "Summary of Multiple Linear Regression Model Predicting Trump Support Based on Polling Data since 21 July 2024 (Harris first declared) to 2 November 2024"
 #| label: tbl-summary2
@@
 #| eval: true
-#| fig-cap: "Harris Kamala leads Donald Trump an average 1% in Predicted Support in the 2024 US Election (From August 1, 2024, to November 2, 2024)"
+#| fig-cap: "Harris Kamala leads Donald Trump an average 1% in Predicted Support in the 2024 US Election (From August 1, 2024, to November 2, 2024)."
 #| fig-subcap: ["Unweighted","Weighted"]
@@
 #| layout-ncol: 1
-#| fig-cap: "Harris is likely to lead Trump in Pennsylvania, Michigan, and Wisconsin by Model Prediction"
+#| fig-cap: "Harris is likely to lead Trump in Pennsylvania, Michigan, and Wisconsin by Model Prediction (From August 1, 2024, to November 2, 2024)."
 #| label: fig-support-state
@@
 #| layout-ncol: 1
-#| fig-cap: "Major Pollsters Siena/NYT and Quinnipiac favor Harris, while Emerson, AtlasIntel, and Beacon/Shaw present a more competitive picture"
+#| fig-cap: "Major Pollsters Siena/NYT and Quinnipiac favor Harris, while Emerson, AtlasIntel, and Beacon/Shaw present a more competitive picture."
 #| label: fig-support-pollster

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update paper with abstract

@@
 ---
-title: "Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach with Poll-of-Polls Data"
-subtitle: "Kamala Harris expects to win on 47.5%, leads Donald Trump by about 1% in 2024 US election"
+title: "Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach"
+subtitle: "Kamala Harris expects to win on 47.5%, leads Donald Trump by about 1% in 2024 US election in Popular Vote based on Poll-of-Polls Data and Linear Modeling."
 author: 
@@
 Presidential Election by analyzing polling data with adjustments for factors like recency and sample size, simulating an approach that captures up-to-date voter sentiment.
-Using the recent 4 months (July 21th - November 2th) of aggregated poll data, the model identifies shifts in candidate support across key battleground states, providing a nuanced view of evolving preferences as election day approaches.
+Using the recent 4 months (July 21th - November 2th) of aggregated poll data, we built a multiple linear regression model to estimate Harris’ support in popular vote and the winner of seven key battleground states.
+We estimate that  Kamala Harris will lead with an expected 47.5% support, ahead of Donald Trump by approximately 1% in popular vote and winning in three of seven key battleground states, Wisconsin, Michigan, and Pennsylvania.
 By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering an understanding that could inform campaign strategies and public discourse.
@@
   geom_point(alpha = 0.1)+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 0.5)+
+  geom_smooth(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted),se = FALSE, size = 0.5)+
   facet_wrap(~ state,ncol = 4) +
@@
   geom_point(alpha = 0.1)+ 
-  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 0.5)+ # Smoothed trend line
+  geom_smooth(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted),se = FALSE, size = 0.5)+ # Smoothed trend line
   facet_wrap(~ state,ncol = 4) +

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update paper

@@
 library(caret)   # For cross-validation
+library(knitr)
 ```
@@
   coord_cartesian(ylim = c(0, 100))
+```
+@tbl-harrissupport shows Harris' average support across states in the 2024 U.S.
+Presidential Election.
+She leads in Democratic-leaning states, with top support in Vermont (68.5%), Maryland (62.9%), and Massachusetts (61.2%).
+In key battlegrounds, Harris's support hovers around 50%, including Wisconsin (49.0%) and Pennsylvania (48.3%).
+Nationally, she averages 47.9%, with competitive support in swing states like Nevada (47.9%) and North Carolina (47.8%).
+However, in Republican-leaning states like Texas (44.3%) and Florida (44.2%), her support is lower.
+This distribution highlights Harris’s strength in Democratic regions and mixed prospects in competitive areas.
+```{r}
+#| label: tbl-harrissupport
+#| tbl-cap: Harris leads in Democratic-leaning states, showing strong support in reliably blue areas.
+In pivotal swing states, she maintains competitive support, with Wisconsin at 49% and Pennsylvania at 48.3%, reflecting her appeal in regions important for a potential electoral victory.
+However, in traditionally Republican strongholds, indicating areas where additional campaign efforts might bolster her standing.
+Nationally, Harris averages 47.9%, underscoring the competitive landscape as election day nears.
+#| echo: false
+#| warning: false
+#| message: false
+
+# Calculate average support for Kamala Harris in each state
+harris_data_state <- harris_data|>
+  group_by(state)|>
+  summarize(`Average Support (%)` = round(mean(pct, na.rm = TRUE), 1)) |>
+  arrange(desc(`Average Support (%)`))|>rename(`State` = state)
+
+# Display the result as a table
+kable(harris_data_state, caption = "Average Support for Kamala Harris by State")
+
 ```

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update paper
update typo/grammar error

@@
 Presidential Election by analyzing polling data with adjustments for factors like recency and sample size, simulating an approach that captures up-to-date voter sentiment.
-Using the recent 4 months (July 21th - November 2th) of aggregated poll data, we built a multiple linear regression model to estimate Harris’ support in popular vote and the winner of seven key battleground states.
-We estimate that  Kamala Harris will lead with an expected 47.5% support, ahead of Donald Trump by approximately 1% in popular vote and winning in three of seven key battleground states, Wisconsin, Michigan, and Pennsylvania.
+Using the recent 4 months (July 21st - November 2nd) of aggregated poll data, we built a multiple linear regression model to estimate Harris’ support in the popular vote and the winner of seven key battleground states.
+We estimate that  Kamala Harris will lead with an expected 47.5% support, ahead of Donald Trump by approximately 1% in the popular vote and winning in three of seven key battleground states, Wisconsin, Michigan, and Pennsylvania.
 By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering an understanding that could inform campaign strategies and public discourse.
@@
 The `here` package aided in managing file paths, improving the reproducible workflow of our study [@citehere].We use `testthat` to verify dataset variables, ensuring they are correctly formatted and contain expected values for analysis [@citetestthat].
+We use `knitr` to build the table using the `kable` function [@citeknitr].
 We relied on `janitor` to perform data
@@
 issues within the dataset [@citejanitor]. For handling date-related
-operations, the `lubridate` package help simplifying the
+operations, the `lubridate` package helps simplify the
 manipulation of time variables [@citelubridate]. `arrow` supported
@@
 The `future` package supported parallel processing, optimizing the runtime of intensive computations, which is especially beneficial in model training [@citefuture].
-Finally,for validation of model using K-Fold cross validation, we utilized the `boot` package, which allowed us to assess model stability and reliability [@citeboot1;@citeboot2] and `caret` to facilitate model training and validation, offering a unified interface for cross-validation and performance metrics [@citecaret].
+Finally, for validation of the model using K-Fold cross-validation, we utilized the `boot` package, which allowed us to assess model stability and reliability [@citeboot1;@citeboot2] and `caret` to facilitate model training and validation, offering a unified interface for cross-validation and performance metrics [@citecaret].
 Our coding practices and file organization were informed by the structure outlined
@@
 #| label: fig-recency
-#| fig-cap: The distribution of the Poll Recency since July 21, 2024 highlights a strong focus on recent polling data, with the highest frequency of polls occurring within the first few days.
+#| fig-cap: The distribution of the Poll Recency since July 21, 2024, highlights a strong focus on recent polling data, with the highest frequency of polls occurring within the first few days.
 #| echo: false
@@
 This suggests that, after excluding lower-quality polls, a significant number of surveys are conducted by highly rated pollsters.
-Fewer polls have grades below 2.5, indicating a relatively lower occurrence of polls from less-reliable pollsters in this dataset.
+Fewer polls have grades below 2.5, indicating a relatively lower occurrence of polls from less reliable pollsters in this dataset.
 This distribution highlights the emphasis on high-quality pollsters, ensuring a more reliable and consistent source of polling data for subsequent analysis.
@@
 #| label: fig-numericgrade
-#| fig-cap: The distribution of the Numeric Grade of the Polls shows that surveys are conducted by highly rated pollsters, which ensure the reliability of the analysis.
+#| fig-cap: The distribution of the Numeric Grade of the Polls shows that surveys are conducted by highly rated pollsters, which ensures the reliability of the analysis.
 #| echo: false
@@
 #| label: fig-percentage
-#| fig-cap: The distribution of the Support Percentage of Kamala Harris clustered around 50%, with the majority of support falling between 40% and 55%.
+#| fig-cap: The distribution of Kamala Harris's support percentage clustered around 50%, with the majority of support falling between 40% and 55%.
 #| echo: false
@@
 accounts for the type of respondent group of voters associated with
-each poll; and lastly,`state`, which represents the exact U.S. state
+each poll; and lastly, `state`, which represents the exact U.S. state
 where the poll was conducted or focused.Our combined weighting approach further
@@
 All models include a control for state and pollsters.
-The reference level of state is Alaska, the reference level of population is likely voter, and the reference level of pollsters is Angus Reid.")
+The reference level of the state is Alaska, the reference level of population is likely voter, and the reference level of pollsters is Angus Reid.")
 ```
@@
 All models include a control for state and pollsters.
-The reference level of state is Alaska,the reference level of population is likely voter, and the reference level of pollsters is ABC/Washington Post.")
+The reference level of the state is Alaska, the reference level of population is likely voter, and the reference level of pollsters is ABC/Washington Post.")
 ```
@@
   ),
-  state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 700, replace = TRUE)), 
+  state = factor(sample( c("National", "Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 700, replace = TRUE)), 
   pollster = factor(sample(levels(harris_data$pollster), size = 700, replace = TRUE), 
@@
                     levels = levels(trump_data$population)),
-   state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 700, replace = TRUE), 
+   state = factor(sample( c("National", "Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 700, replace = TRUE), 
                     levels = levels(trump_data$state)),  
@@
 #| eval: true
-#| fig-cap: "Harris Kamala leads Donald Trump an average 1% in Predicted Support in the 2024 US Election (From August 1, 2024, to November 2, 2024)."
+#| fig-cap: "Harris Kamala leads Donald Trump an average of 1% in Predicted Support in the 2024 US Election (From August 1, 2024, to November 2, 2024)."
 #| fig-subcap: ["Unweighted","Weighted"]

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update paper

@@
 Where: $W$ is the weight parameters calculated from the product of
-**sample size weight** and recency **weight**.
+**sample size weight** and **recency weight**.
 
@@
     exp(-recency \* 0.1), where "recency" represents the days since the
-    poll was conducted. This ensures that more recent data carries more
+    poll was conducted, and 0.1 is the decay rate of the poll. This ensures that more recent data carries more
     weight, while older polls have reduced influence.
@@
 information by setting entries marked as NA to National, and creating a
-national_poll indicator, assigning a value of 1 for value in state equal to National and 0 for others. Dates are standardized using the lubridate
+national_poll indicator, assigning a value of 1 for value in state equal to National and 0 for others.
+We also filter the population with only likely voters and registered voters.
+Dates are standardized using the lubridate
 package to facilitate accurate time-based analysis.

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
Final edit on result

@@
 accurately by emphasizing higher-quality and more recent polls. The
-weighting scheme integrates factors like poll recency, sample size,
-pollster quality, and frequency, as inspired by the New York Times' methodology [@nyt_polling_averages] for polling averages.
+weighting scheme integrates factors like poll recency and sample size, which are
+inspired by the New York Times' methodology [@nyt_polling_averages] for polling averages.
 
@@
 @tbl-summary1 and @tbl-summary2, the intercepts for Harris and Trump,
-estimated at 44.70% and 59.28% respectively in the unweighted models, while in weighted models, it's estimated at 45.2% and 54.8%,
+estimated at 44.70% and 51.87% respectively in the unweighted models, while in weighted models, it's estimated at 45.2% and 54.8%,
 represent their baseline support levels when all predictors are at

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update paper with figure caption

--- 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
@@
 #| tbl-cap: Harris leads in Democratic-leaning states, showing strong support in reliably blue areas.
-In pivotal swing states, she maintains competitive support, with Wisconsin at 49% and Pennsylvania at 48.3%, reflecting her appeal in regions important for a potential electoral victory.
-However, in traditionally Republican strongholds, indicating areas where additional campaign efforts might bolster her standing.
-Nationally, Harris averages 47.9%, underscoring the competitive landscape as election day nears.
+In pivotal swing states, she maintains competitive support in Wisconsin and Pennsylvania, reflecting her appeal in regions important for a potential electoral victory.
+However, in traditionally Republican strongholds, her support is lower.
+Nationally, Harris averages 47.9%.
 #| echo: false
@@
 # Display the result as a table
-kable(harris_data_state, caption = "Average Support for Kamala Harris by State")
+kable(harris_data_state)
 
@@
        color = "Candidate",caption = 
-                   "Model: Candidate Support Percentage = national_poll + pollster + population + state") +
+                   "Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
        size="Weight",
-       caption = "Weights: recency_weight * sample_size_weight \nModel: Candidate Support Percentage = national_poll + pollster + population + state") +
+       caption = "Lines are weighted by recency_weight * sample_size_weight.\nPoints are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red"))  +
@@
        color = "Candidate",
-       caption = "Model: Candidate Support Percentage = national_poll + pollster + population + state") +
+       caption = "Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
        size="Weight",
-       caption = "Weights: recency_weight * sample_size_weight\nModel: Candidate Support Percentage = national_poll + pollster + population + state") +
+       caption = "Lines are weighted by recency_weight * sample_size_weight.\nPoints are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
     fill = "Top 5 Pollster",
-    caption = "Model: Candidate Support Percentage = national_poll + pollster + population + state"
+    caption = "Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight"
   )+ # Smoothed trend line
@@
     fill = "Top 5 Pollster",
-    caption = "Weights: recency_weight * sample_size_weight \nModel: Candidate Support Percentage = national_poll + pollster + population + state"
+    caption = "Lines are weighted by recency_weight * sample_size_weight.\nPoints are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight"
   )+ # Smoothed trend line

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update paper

@@
 represent their baseline support levels when all predictors are at
-reference values. The high ( $R^2$ ) values of 0.824 for Harris’s
+reference values. The high $R^2$ values of 0.824 for Harris’s
 unweighted model and 0.892 for her weighted model, along with a similar
@@
        color = "Candidate",caption = 
-                   "Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight") +
+                   "Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatest Poll: Nov 2; Source: FiftyThirtyEight") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
        size="Weight",
-       caption = "Lines are weighted by recency_weight * sample_size_weight.\nPoints are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight") +
+       caption = "Lines are weighted by recency_weight * sample_size_weight.
+Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatest Poll: Nov 2; Source: FiftyThirtyEight") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red"))  +
@@
        color = "Candidate",
-       caption = "Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight") +
+       caption = "Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatest Poll: Nov 2; Source: FiftyThirtyEight") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
        size="Weight",
-       caption = "Lines are weighted by recency_weight * sample_size_weight.\nPoints are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight") +
+       caption = "Lines are weighted by recency_weight * sample_size_weight.
+Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatest Poll: Nov 2; Source: FiftyThirtyEight") +
   scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
@@
     fill = "Top 5 Pollster",
-    caption = "Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight"
+    caption = "Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatest Poll: Nov 2; Source: FiftyThirtyEight"
   )+ # Smoothed trend line
@@
     fill = "Top 5 Pollster",
-    caption = "Lines are weighted by recency_weight * sample_size_weight.\nPoints are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatetst Poll: Nov 2\nSource: FiftyThirtyEight"
+    caption = "Lines are weighted by recency_weight * sample_size_weight.
+Points are polls.\nModel: Candidate Support Percentage = national_poll + pollster + population + state\nLatest Poll: Nov 2; Source: FiftyThirtyEight"
   )+ # Smoothed trend line
